### 2023-09-22 src/tex/ms.tex
[showyourwork] first commit

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@afeinstein20}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
    Phasellus eu tellus sit amet tortor gravida placerat.
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
    Praesent eget sem vel leo ultrices bibendum.
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
    Curabitur auctor semper nulla donec varius orci eget risus.
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
Donec vehicula augue eu neque, morbi tristique senectus et netus et.
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
Phasellus eu tellus sit amet tortor gravida placerat.
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
Praesent eget sem vel leo ultrices bibendum.
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
Curabitur auctor semper nulla donec varius orci eget risus.
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

\end{document}

### 2023-09-22 src/tex/ms.tex
init commit v3

@@
 % Title
-\title{An open source scientific article}
+\title{Refined Flare Rates for Stars Younger than 250\,Myr}
 
 % Author list
-\author{@afeinstein20}
+\author{Adina~D.~ Feinstein}
+\altaffiliation{NHFP Sagan Fellow}
+\affiliation{Laboratory for Atmospheric and Space Physics, University of Colorado
+Boulder, UCB 600, Boulder, CO 80309}
 
@@
 \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
-    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
-    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
-    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
-    Phasellus eu tellus sit amet tortor gravida placerat.
-    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
-    Praesent eget sem vel leo ultrices bibendum.
-    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
-    Curabitur auctor semper nulla donec varius orci eget risus.
-    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-    Duis eget orci sit amet orci dignissim rutrum.
+    Photometric exoplanet detection missions have revolutionized our understanding
+    of stellar activity. Stellar flares are short-duration high-energy radiation
+    outbursts which can be readily seen across young (< 800\,Myr) stars and even
+    in high counts on mature M dwarfs. Here, we present the results of measuring
+    stellar flare rates for very young stars, with ages $4.5 - 200$\,Myr right
+    after they formed to understand the early evolution of magnetic activity. We
+    have selected a sample of 5,700 stars which belong to 26 associations,
+    nearby young moving groups, or clusters. We identified $\sim 29,000$ flares
+    using the \texttt{stella} machine-learning algorithm. We measured the flare-
+    frequency distribution slopes as a function of age and stellar effective
+    temperature.
 \end{abstract}
@@
 
-Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
-Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
-Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
-Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
-Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
-Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
-Pellentesque cursus luctus mauris \citep{Luger2021}.
+This paper is presented as follows.
+
+\section{Methodology}
+\label{sec:methods}
+
+\subsection{Sample Selection}
+
+We aim to measure the evolution in flare rates as a function of stellar age for
+stars with $1 \leq t_\textrm{age} \leq 250$\,Myr. We used the MOCA Data Base
+(Gagné et al. in prep.) to identify nearby young moving groups, associations,
+and open clusters with known ages which satisfied our criteria. We identified
+unique 26~groups from which we created our sample list. We considered all targets
+that are either bona fide members, high-likelihood candidate members, or candidate members.
+This resulted in a catalog of 30,889 stars across 26 associations. We summarize
+the sample and quote adopted ages for each association
+in Table~\ref{tab:sample}.
+
+\begin{deluxetable}{l r r r r r}[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{Adopted Ages of each Young Stellar Population and Number of
+Stars per Group \label{tab:sample}}
+\tablehead{
+\colhead{Population} & \colhead{Age [Myr]} & \colhead{N$_\textrm{stars}$} &
+\colhead{Ref.}
+}
+\startdata
+AB Doradus  &  133$_{-20}^{+15}$  &  81  & 1 \\
+Blanco 1 & 137.1$^{+7.0}_{-33}$ & 301 & 8\\
+Carina  &  45  & 91  & 2\\
+Carina-Musca & 32 & 22 & 5\\
+Chamaeleon  &  5  &  366  & 3 \\
+Columba  &  42  &  126  & 2\\
+Greater Taurus Subgroup 5 & 8.5 & 56 & 5\\
+Greater Taurus Subgroup 8 & 4.5 & 114 & 5\\
+Lower Centaurus Crux &  15  & 590  & 4\\
+MELANGE-1 & 250$_{-70}^{+50}$ & 22 & 10\\
+Octans  &  35$\pm 5$ &   98  & 6 \\
+Pisces Eridanis  &  120  &   176  & 7 \\
+Pleiades & 127.4$^{+6.3}_{-10}$ & 1304 & 8\\
+$\alpha$ Persei  &  79$_{-2.3}^{+1.5}$  &  467  & 8 \\
+IC 2602 corona &  52.5$_{-3.7}^{+2.2}$  & 10  & 8 \\
+IC 2602 system &  52.5$_{-3.7}^{+2.2}$  & 138  & 8 \\
+NGC 2451A & 48.5 & 44 & 5\\
+Oh 59 & 162.2 & 50 & 9\\
+Platais 9 & 50 & 99 & 11\\
+RSG2 & 126 & 87 & 12\\
+Theia 301  &  195  &  372  & 9\\
+Theia 95  &  30.2  &  191  & 9\\
+TW Hydrae  &  10  &  24  & 2\\
+Upper Centaurus  Lupus &  16  &  464  & 4 \\
+Upper Scorpius  &  10  &  80  & 4 \\
+Vela-CG4  &  33.7  &  352  & 5
+\enddata
+\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{Bell15};
+(3) \citet{luhman07}; (4) \citet{pecaut16}; (5) \citet{kerr21};
+(6) \citet{murphy15}; (7) \citet{curtis19}; (8) \citet{galindo22};
+(9) \citet{kounkel20}; (10) \citet{tofflemeire21}; (11) \citet{tarricq21};
+(12) \citet{roser16}; }
+\end{deluxetable}
+
+\subsection{TESS Light Curves}
+
+To ensure we were able to resolve and accurately measure the energies of flares
+on these stars \citep{howard22}, we used the 2-minute data from the TESS mission.
+We crossmatched our sample with the TESS Input Catalog (TIC) based on their RA and Dec.
+We considered a star to be in the catalog if the distance between the target and
+the nearest TIC was within $1"$. This resulted in a final sample of 5,725 unique targets
+which have been observed at 2-minute cadence between Sector 1 and Sector 67, the
+latest available sector upon this analysis. Given the proximity of many targets towards the
+northern and southern ecliptic poles (Figure~\ref{fig:sample}), many targets were observed
+over multiple sectors. We downloaded all available data, yielding a total of 17,964
+light curves.
+
+\begin{figure}[ht!]
+    \script{sample.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/sample.pdf}
+        \caption{
+            Distribution of our selected sample across the sky and colored by the
+            adopted age of the association (see Table~\ref{tab:sample}). The all-sky
+            coverage by TESS has unlocked new populations of stars to observe.
+            We take advantage of this observing strategy to measure flare rates
+            across 26 different nearby young moving groups, clusters, and associations.
+        }
+        \label{fig:sample}
+    \end{centering}
+\end{figure}
+
+\subsection{Flare Identification}
+
+We followed the machine learning flare-identification methods presented in
+\cite{feinstein20a}. This method relies on the fact that all flare events
+have similar time-dependent morphologies generally described as a sharp rise
+and an exponential decay. This method uses a convolutional neural network (CNN),
+\texttt{stella} \citep{feinstein20b}, trained on by-eye validated flare events from
+TESS Sectors 1 and 2 to identify flare events in TESS 2-minute data
+\citep{guenther19_flares, feinstein20a}. The benefits of the CNN is that it is
+insensitive to the stellar baseline, since it is trained to look only for the
+flare morphology. This means that the peaks of rotational modulation driven by
+stellar heterogeneities, which is readily seen in the light curves of young stars,
+are not accidentally identified as flares. In this way, we are able to
+build a sample of flares which is unbiased towards low-amplitude/low-energy flares,
+which are often not identified in traditional sigma-outlier identification
+methods \citep{chang15}.
+
+The \texttt{stella} CNN models take the light curve (time, flux, flux error)
+as an input and returns an array with values of [0,1], which are treated as
+the probability a data point is (1) or is not (0) part of a flare. We ran all
+light curves through 10 \texttt{stella} models and averaged the output, taking
+this as the final prediction per observation. The \texttt{stella} code uses the
+predictions per data point to group together points, identifying those as single
+flare events. It then calculates the probability of the entire flare event as
+the average of the probabilities assigned to all the data points during the flare.
+
+\begin{figure}[ht!]
+    \script{flare_distribution.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/flare_distribution.pdf}
+        \caption{
+            High level summary of the demographics of flares in our sample. Top:
+            The number of flares identified compared to the number of stars in
+            each nearby young moving group, cluster, or association. A one-to-one
+            relationship is expected. Middle: The distribution measured TESS energies
+            and equivalent durations of flares in our sample, colored by the probability
+            of the flare as identified with \texttt{steela}. Bottom: Same as the
+            middle plot, except colored by the $T_\textrm{eff}$ [K] of the star.
+            We limit our sample to stars with $T_\textrm{eff} \leq 6000$\,K.
+        }
+        \label{fig:flare_distribution}
+    \end{centering}
+\end{figure}
+
+\subsection{Modeling Flare Properties}
+
+We used the analytical flare model in
+\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}
+to fit the flares in our sample. This model builds upon the model presented
+in \cite{davenport14}, and includes a convolution of a Gaussian with a
+double exponential model. The analytical model accounts for the amplitude,
+heating timescale, rapid cooling phase timescale, and slow cooling phase
+timescale of flares. Using this model, we used a non-linear least squares
+optimization to fit for the time of the flare peak ($t_\textrm{peak}$),
+full width at half maximum (FWHM), and the amplitude ($A$), of each flare
+in the sample. We combine the model with a second-order polynomial fit to
+a 10-hour baseline before and after the flare to account for any rotational
+modulation.
+
+From these fits, we performed a series of quality checks to ensure the flares
+in our sample are real. First, we removed any flares with best-fit FWHM $ < 0$
+and $A < 0$. Second, we removed any flares with a large error on the amplitude,
+$\sigma_A > 10$ and flares where $\sigma_A > A$. Third, we removed flares where
+$A < 2 \times \textrm{RMS}$, where the RMS is calculated from the 10~hour baseline
+around the best-fit $t_\textrm{peak}$. These cuts are indicative of a poorly fit
+flare model due to the flare being overwhelmed by noise in the surrounding baseline
+light curve. We choose to include flares with a probability $P \geq 75\%$ of being
+a true flare. After these checks, we have a flare sample of 29,128~flares originating
+from 3,983 stars (Figure~\ref{fig:flare_distribution}). 83.6\% of the flares have
+probabilities of $P \geq 90\%$ of being true; 64.9\% of the flares have probabilities
+of $P \geq 99\%$ of being true.
+
+\section{Results}\label{sec:res}
+
+\begin{figure*}[ht!]
+    \script{mcmc_results.py}
+    \begin{centering}
+        \includegraphics[width=2\textwidth]{figures/mcmc_results.pdf}
+        \caption{
+            Measured flare-frequency distribution slopes, $\alpha$, as a function
+            of stellar effective temperature, $T_\textrm{eff}$ and age.
+        }
+        \label{fig:mcmc_results}
+    \end{centering}
+\end{figure*}
+
+\subsection{Flare Rates by Association}
+
+\subsection{Flare Rates by Age}
+
+\subsection{Flare Rates by Effective Temperature}
+
+\section{Conclusions}\label{sec:conclusions}
 

### 2023-09-22 src/scripts/analysis_utils.py

@@ -1,0 +1,137 @@
+import numpy as np
+from astropy import units
+from scipy.optimize import curve_fit
+from astropy import constants as const
+
+__all__ = ['get_energy_limits', 'planck', 'fit_ffd', 'linear']
+
+def planck(lam, T, rad):
+    """
+    Planck function.
+    """
+    result = 2.*np.pi*const.h*(const.c**2)/(lam**5)
+    exp = (const.h*const.c/(lam*const.k_B*T))#.to(u.m/u.m)
+    result /= (np.exp(exp) - 1.0)
+
+    result *= (lam[1]-lam[0])
+    result = result.to(units.erg/units.s/units.m**2) * (rad.to(units.m))**2
+    return result
+
+
+def get_energy_limits(tab, temp_ranges, low_ed=60, low_amp=0.005,
+                      flare_temp=9000.0):
+    """
+    Defines the lower limit for what flare energy to fit for a given stellar
+    effective temperature range.
+
+    Parameters
+    ----------
+    tab : astropy.table.Table
+       Table of flares.
+    temp_ranges : np.ndarray
+       Array of temperature ranges to evaluate over. Array should be structured as:
+       `temp_ranges = [ [lowlim1, upplim1], [lowlim2, upplim2] ]`.
+    low_ed : float, optional
+       The lower-limit flare equivalent duration to trust in units of seconds.
+       Default is 60.
+    low_amp : float, optional
+       The lower-limit flare amplitude to trust. Defualt is 0.005 (0.5% amplitude).
+    flare_temp : float, optional
+       The flare temperature to assume. Default is 9000K.
+    """
+    TEMP_LIMITS = []
+
+    lam = np.arange(600,1000) * units.nm # TESS bandpass
+
+    for z in range(len(temp_ranges)):
+
+        if z == 0:
+            minrow = tab[(tab['teff']>0) & (tab['lum']>0)]
+            minrow.sort('teff')
+            minrow = minrow[0]
+            lum = minrow['lum']
+            rad = minrow['rad']
+            real_teff = minrow['teff']
+            star = planck(lam, real_teff*units.K, rad*units.Rsun).to(units.erg/units.s)
+            flare = planck(lam, flare_temp*units.K,  rad*units.Rsun).to(units.erg/units.s)
+            scale = np.nansum(star.value) / np.nansum(flare.value)
+
[…]

### 2023-09-22 src/scripts/data_utils.py

@@ -1,0 +1,38 @@
+import os
+import numpy as np
+from astropy.table import Table
+
+from paths import (
+    data as data_dir,
+)
+
+__all__ = ['get_age_ranges']
+
+
+def get_age_ranges(age_ranges):
+    """
+    Extracts the average age per age bin and associated error.
+
+    Returns
+    -------
+    ages: np.array
+       Array of `ages[:,0] = average age`; `ages[:,1] = lower age error`;
+       `ages[:,2] = upper age error`.
+    """
+    tab = Table.read(os.path.join(data_dir,
+                                  'llamaradas-estelares_all_parameters_withcuts_final_v2.csv'),
+                     format='csv')
+
+    ages = np.zeros((len(age_ranges), 3))
+
+    for i in range(len(age_ranges)):
+        temp = tab[(tab['age']>=age_ranges[i][0]) &
+                   (tab['age']<age_ranges[i][1])]
+        avg = np.nanmean(temp['age'])
+        maxa = temp[temp['age']==np.nanmax(temp['age'])][0]['eage']
+        mina = temp[temp['age']==np.nanmin(temp['age'])][0]['eage']
+        ages[i][0] = avg
+        ages[i][1] = (avg - np.nanmin(temp['age']))
+        ages[i][2] = (np.nanmax(temp['age'])-avg)
+
+    return ages

### 2023-09-22 src/scripts/flare_distribution.py

@@ -1,0 +1,108 @@
+import os
+import sys
+import numpy as np
+from astropy import units
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+from plotting_utils import *
+
+from paths import (
+    figures as figures_dir,
+    data as data_dir,
+)
+
+set_rcparams()
+
+tab = Table.read(os.path.join(data_dir,
+                              'llamaradas-estelares_all_parameters_withcuts_final_v2.csv'),
+                 format='csv')
+
+sample = Table.read(os.path.join(data_dir,'moca_sample.csv'), format='csv')
+
+fig, (ax0, ax1, ax2) = plt.subplots(nrows=3, figsize=(6,18))
+fig.set_facecolor('w')
+
+ed = (tab['ed']*units.min).to(units.s)
+erg = tab['flare_energy']
+
+q = ((np.isnan(tab['teff']) == False) & (tab['teff'] > 0) &
+     (tab['teff'] <= 6000) & (erg.value > 0) & (ed.value > 0))
+
+#================== AX0 ========================#
+age = age_colorbar()
+
+uni, args = np.unique(sample['moca_aid'], return_index=True)
+argsort = np.argsort(sample['age'][args])
+
+counts = np.zeros((len(uni),3))
+
+for i, grp in enumerate(uni[argsort]):
+
+    count = len(sample[(sample['moca_aid']==grp)])
+
+    cflares = len(tab[(tab['moca_aid']==grp) & (tab['teff']<=6000) &
+                      (np.isnan(tab['flare_energy']) == False)])
+
+    counts[i][0] = count
+    counts[i][1] = cflares
+    counts[i][2] = sample['age'][args][argsort][i]
+
+img = ax0.scatter(counts[:,0], counts[:,1], c=np.log10(counts[:,2]),
+                  vmin=np.log10(4), vmax=np.log10(250), s=120,
+                  cmap=age, edgecolor='k', lw=0.75)
+divider = make_axes_locatable(ax0)
+cax = divider.append_axes('right', size='5%', pad=0.08)
+
+cbar = plt.colorbar(img, label='Age [Myr]', cax=cax)
+ticks = np.round(10**np.linspace(np.log10(4), np.log10(250), 6))
[…]

### 2023-09-22 src/scripts/mcmc_results.py

@@ -1,0 +1,103 @@
+import os
+import sys
+import matplotlib
+import numpy as np
+from astropy import units
+from astropy.table import Table
+import matplotlib.pyplot as plt
+
+from plotting_utils import *
+from data_utils import *
+
+from paths import (
+    figures as figures_dir,
+    data as data_dir,
+)
+
+set_rcparams()
+
+teff_cbar = teff_colorbar()
+
+temp_ranges = np.array([[2300, 3400], [3400, 3850],
+                        [3850, 4440], [4440, 5270], [5270, 5930]])
+age_ranges  = np.array([[4, 10], [10, 20], [20,40], [40, 50],
+                        [70, 80], [120, 150], [150, 300]])
+
+# Load in the files
+path = os.path.join(data_dir, 'mcmc_fits/best_fits')
+fits = np.sort([os.path.join(path, i) for i in os.listdir(path)])
+
+# Initialize the figure
+fig, ax = plt.subplots(figsize=(14,5))
+
+norm = matplotlib.colors.Normalize(vmin=temp_ranges[0][0],
+                                   vmax=temp_ranges[-1][1])
+
+ages = get_age_ranges(age_ranges)
+
+####################
+# Plot the MCMC fits
+####################
+for i, fn in enumerate(fits):
+    dat = np.load(fn)
+    label = fn.split('T')[-1].split('.')[0]
+
+    t = (temp_ranges[i][0] + temp_ranges[i][1])/2.0
+
+    rgba_color = teff_cbar.reversed()(norm(t))
+    hexnum = matplotlib.colors.rgb2hex(rgba_color)
+
+    # Ignores groupings with not enough flares for a good FFD fit
+    if fn == 'slope_fits_T3850-4440.npy':
+        q = np.array([0,1,3,4,5,6],dtype=int)
+    elif fn == 'slope_fits_T5270-5930.npy':
+        q = np.arange(1,7,1,dtype=int)
+    else:
+        q = np.arange(0,7,1,dtype=int)
+
+    # Plot!
+    plt.errorbar(ages[:,0][q],
+                 dat[0][:,0][q],
+                 xerr=[ages[:,1][q], ages[:,2][q]],
+                 yerr=[dat[0][:,1][q], dat[0][:,2][q]],
+                 marker='o', linestyle='', color=hexnum,
+                 label=label, zorder=-i)
+
+#####################################
[…]

### 2023-09-22 src/scripts/plotting_utils.py

@@ -1,0 +1,51 @@
+import os
+import sys
+import numpy as np
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from matplotlib.colors import LinearSegmentedColormap
+
+from paths import (
+    figures as figures_dir,
+    data as data_dir,
+    scripts as script_dir
+)
+
+__all__ = ['set_rcparams', 'teff_colorbar', 'prob_colorbar', 'age_colorbar']
+
+def set_rcparams():
+    tab = Table.read(os.path.join(data_dir,'rcparams.txt'), format='csv')
+    for i in range(len(tab)):
+        try:
+            plt.rcParams[tab['key'][i]] = float(tab['val'][i])
+        except ValueError:
+            plt.rcParams[tab['key'][i]] = str(tab['val'][i])
+    return
+
+def teff_colorbar():
+    """ Color map for Teff values. """
+    colors = Table.read(os.path.join(data_dir,'results_Z-1.txt'), format='csv',
+                        delimiter='&')
+
+    c = [i[1:-3] for i in
+         colors[colors['$\\log$(g)'] == 4.5]['Hex PHX \\\\ \\hline'][3:]]
+
+    stars = LinearSegmentedColormap.from_list('stars', c)
+    return stars
+
+def prob_colorbar():
+    """ Color map for probability values. """
+    blues = LinearSegmentedColormap.from_list('gradient',
+                                              ['#dbeaff',
+                                               '#a9bbf9', '#7593ff',
+                                               '#091540'])
+    return blues
+
+def age_colorbar(short=False):
+    """ Color map for age values. """
+    if short:
+        dat = np.load(os.path.join(data_dir, 'parula_data.npy')[:60])
+    else:
+        dat = np.load(os.path.join(data_dir, 'parula_data.npy'))
+    parula = LinearSegmentedColormap.from_list('parula', dat)
+    return parula

### 2023-09-22 src/scripts/sample.py

@@ -1,0 +1,51 @@
+import os
+import sys
+import numpy as np
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from matplotlib.colors import LinearSegmentedColormap
+
+from paths import (
+    figures as figures_dir,
+    data as data_dir,
+    scripts as script_dir
+)
+
+from plotting_utils import *
+
+set_rcparams()
+
+sample = Table.read(os.path.join(data_dir,'moca_sample.csv'), format='csv')
+
+RA, Dec = sample['ra'], sample['dec']
+org = 0
+projection = 'mollweide'
+
+parula = age_colorbar()
+
+x = np.remainder(RA+360-org,360) # shift RA values
+ind = x>180
+x[ind] -=360    # scale conversion to [-180, 180]
+x=-x    # reverse the scale: East to the left
+tick_labels = np.array([150, 120, 90, 60, 30, 0, 330, 300, 270, 240, 210])
+tick_labels = np.remainder(tick_labels+360+org,360)
+
+fig = plt.figure(figsize=(18, 6))
+ax = fig.add_subplot(111, projection=projection)
+img = ax.scatter(np.radians(x),np.radians(Dec), c=np.log10(sample['age']),
+                 vmin=np.log10(5), vmax=np.log10(250), s=15, cmap=parula)
+ax.set_xticklabels(tick_labels, fontsize=18)     # we add the scale on the x axis
+
+ax.set_xlabel("RA", fontsize=20)
+ax.set_ylabel("Dec", fontsize=20)
+
+ax.grid(True)
+cbar = plt.colorbar(img, location='bottom', shrink=0.45)
+cbar.ax.set_xlabel('Age [Myr]', fontsize=20)
+
+cbar.ax.set_xticks(np.linspace(np.log10(5), np.log10(250), 7))
+cbar.ax.set_xticklabels(np.linspace(5,250,7,dtype=int), fontsize=14)
+ax.set_rasterized(True)
+
+plt.savefig(os.path.join(figures_dir,'sample.pdf'), dpi=300,
+            bbox_inches='tight')

### 2023-09-26 src/tex/ms.tex
updated scripts

@@
 
-\section{Results}\label{sec:res}
+\subsection{Measuring Rotation Periods}
+
+\cite{seligman22} demonstrated that stars with low Rossby numbers $R_0 < 0.13$ have
+shallower flare frequency distribution slopes, indicative of more high energy flares
+originating from these sources. In addition to understanding flare statistics across
+young ages, we aim to expand this sample by measuring the rotation periods, $P_\textrm{rot}$,
+for the stars in our sample. To do this, we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}},
+an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination
+traditional Lomb-Scargle periodograms and wavelet transformations (Hall et al. submitted).
+\texttt{michael} measures $P_\textrm{rot}$ using the \texttt{eleanor} package, which
+extracts light curves from the TESS Full-Frame Images \citep[FFIs;][]{feinstein19}.
+We ran \texttt{michael} on all stars from which flares were identified. The estimated
+$P_\textrm{rot}$ were vetted by-eye, from the \texttt{michael} diagnostic plots. In
+total, we robustly measured \textcolor{red}{n} $P_\textrm{rot}$ across our sample of
+3,983 stars.
+
+\section{Results}\label{sec:results}
+
+We analyze our new flare sample from three perspectives. First, we perform the standard
+FFD fitting of a power-law to the distribution of flare energies. Second, we fit the FFD with the
+prescription in \cite{gershberg72}, which fits for both the FFD slope and y-intercept.
+Third, we fit a truncated power-las to the distribution of flare amplitudes, to determine
+if there is a correlation between $R_0$ and flare distributions.
+
+The number of stars, and consequently flares, per each association varied greatly,
+due to the limited number of stars observed at TESS 2-minute cadence. Therefore, instead
+of measuring FFD properties as a function of association, we opted to group stars
+by effective temperature, $T_\textrm{eff}$, and average adopted association age. We
+grouped stars in the following $T_\textrm{eff}$ space: M-stars below the fully
+convective boundary ($T_\textrm{eff} = 2300 - 3400$\,K), early type M-stars
+($T_\textrm{eff} = 3400 - 3850$\,K), late K-stars ($T_\textrm{eff} = 3850 - 4440$\,K),
+early K-stars ($T_\textrm{eff} = 4440 - 5270$\,K), and G-stars ($T_\textrm{eff} = 5270 - 5930$\,K).
+We did not include any stars hotter than $T_\textrm{eff} > 5930$\,K, as these stars
+are dominated by noise in the TESS observations. Additionally, we grouped stars
+in the following age space: $4-10$\,Myr, $10-20$\,Myr, $20-40$\,Myr, $40-50$\,Myr,
+$70-80$\,Myr, $120-150$\,Myr, and $150-300$\,Myr. We note that there is a gap in
+age from $50-70$\,Myr, which could be expanded with the identification of more
+associations in this age range. However, for the purposes of this work, we do not
+include additional sources which may fall in this age range.
+
+\subsection{Standard Power-Law Fits}\label{subsec:stats}
+
+From the $T_\textrm{eff}$ and age bins described above, we binned the flares in each
+subgroup and fit their FFD slopes, approximated as a power-law. Flares were binned
+into 25 bins in log-space from $10^{27} - 10^{35}$\,erg. We fit the FFDs from the
+energy bin with the maximum flare rate and energies higher than that. We opt to do
+this as bins of lower energies may be incomplete, and the turnover in the FFD cannot
+be accurately modeled as a power-law.
+
+We fit the FFD using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}
+and fit for the slope, $\alpha$, y-intercept, $b$, and an additional noise term, $f$, which
+accounts for an underestimation of the errors on each bin. We initialized the MCMC fit with
+300 walkers and ran our fit over 5000 steps. Upon visual inspection, we discarded the
+first 100 steps; onwards the steps were fully burned-in. The full FFDs are presented
+in Figure~\ref{fig:simple_ffd_all}, along with 100 samples from the MCMC fit. The measured
+FFD slopes, $\alpha$ are presented in Figure~\ref{fig:mcmc_results}. We approximate the
+error on the slope as the lower 16\textsuperscript{th} and upper 84\textsuperscript{th}
+percentiles from the MCMC fit.
 
@@
     \begin{centering}
-        \includegraphics[width=2\textwidth]{figures/mcmc_results.pdf}
+        \includegraphics[width=3\textwidth]{figures/mcmc_results.pdf}
         \caption{
@@
 
-\subsection{Flare Rates by Association}
+\subsection{Fitting for $\alpha$ and $\beta$}
 
-\subsection{Flare Rates by Age}
+\subsection{Truncated Power-Law Fits}
 
-\subsection{Flare Rates by Effective Temperature}
+We follow the prescription presented in \cite{seligman22}. Namely, we fit a truncated
+power-law distribution of the form
+
+\begin{equation}
+  dp/dA \propto A^{-\alpha_T} e^{-A/A_*}
+\end{equation}
+
+where $A$ is the amplitude of the flare, $A_*$ is a flare amplitude cutoff parameter
+and $\alpha_T$ is the slope, rather than
+$\alpha$. We fit the slopes using the MCMC method implemented in \texttt{emcee}
+\citep{goodman10, emcee}, using the log-likelihood function in \cite{seligman22}.
+We fit for $A_*$ and $\alpha_T$. We initialized the MCMC fit with textcolor{red}{n}
+walkers and evaluated the fit over textcolor{red}{n} steps. The first textcolor{red}{n}
+steps were discarded upon visual inspection. The results are presented in Figure~\ref{fig:trunc}.
+
+\section{Discussion}\label{sec:discuss}
+
+\subsection{Applications to ULLYSES}
+
+Measuring Far-Ultraviolet (FUV) total flux output and flare rates are
+essential for understanding the contributions of flares to exoplanet atmospheric
+mass-loss and disequilibrium chemistry. An equivalent, but significantly smaller sample
+to the stars studied here are the those observed as part of the \textit{Hubble Space Telescope}
+(HST) Ultraviolet Legacy Library of Young Stars as Essential Standards (ULLYSES)
+program. This survey observed 71 K- to M-type T Tauri stars in nine young
+galactic associations.
+
+We can extend the results presented here to estimate how many flares may be present
+in these important FUV observations.
+
+Additionally, we analyzed the TESS light curves for all of the ULLYSES targets, when
+available at 2-minute cadence. We identified a total of \textcolor{red}{n} flares.
+This is inconsistent with the overall flare statistics identified in this work, and is
+overall unexpected for young stars which are known to be more magnetically active
+\citep{ilin20, feinstein20b}. This could suggest that there is some bias in the way
+the ULLYSES sample was constructed, and that it is unexpected to find any flares in the
+FUV data. Alternatively, it could be that the ongoing accretion luminosity results
+in a brighter host star, such that the flares we normally would see are drowned
+out by the increased baseline luminosity. We do not include this flare in our
+overall statistical analysis of TESS flare rates for young stars.
 
 \section{Conclusions}\label{sec:conclusions}
+
+This work made use of the open-source package, \textcolor{red}{\textit{showyourwork!}}
+\citep{luger2021}, which promotes reproducible publications.
+
+\appendix
+\restartappendixnumbering
+
+\section{Supplemental Material}\label{appendix:supp_ffds}
+
+Miscellaneous figures and such that people might want but I don't need to show
+
+\begin{figure*}[ht!]
+    \script{simple_ffd_all.py}
+    \begin{centering}
+        \includegraphics[width=\textwidth]{figures/simple_ffd_all.pdf}
+        \caption{
+            Flare frequency distributions (FFDs) for subgroups of stars, clustered
+            by age and effective temperature, $T_\textrm{eff}$. Flares were binned
+            into 25 bins in log-space from $10^{27} - 10^{35}$\,erg. We fit the FFD
+            from the turn-over in the binned flares, likely a result of very low-energy
+            flares being missed in our flare-detection algorithm. The bins used to fit
+            the FFD are shown in black, while all bins are shown in gray. We ran an MCMC
+            fit to these distributions with a simple power law; 100 random samples from these
+            fits are over-plotted in orange. We fit distributions with $> 3$ bins.
+            The best-fit slopes from these fits are presented in Figure~\ref{fig:mcmc_results}.
+        }
+        \label{fig:simple_ffd_all}
+    \end{centering}
+\end{figure*}
 

### 2023-09-26 src/scripts/mcmc_results.py

@@ -16,7 +16,7 @@ from paths import (
 
 set_rcparams()
 
-teff_cbar = teff_colorbar()
+teff_cbar = teff_colorbar().reversed()
 
 temp_ranges = np.array([[2300, 3400], [3400, 3850],
                         [3850, 4440], [4440, 5270], [5270, 5930]])

### 2023-09-26 src/scripts/simple_ffd_all.py

@@ -1,0 +1,83 @@
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+
+from paths import (
+    data as data_dir,
+    figures as figures_dir
+)
+
+pwd1 = os.path.join(data_dir, 'mcmc_fits/samples')
+pwd2 = os.path.join(data_dir, 'mcmc_fits/fitted_data')
+
+sample_files = np.sort([os.path.join(pwd1, i) for i in os.listdir(pwd1)])
+data_files = np.sort([os.path.join(pwd2, i) for i in os.listdir(pwd2)])
+
+## Setup the figure ##
+fig, axes = plt.subplots(ncols=5, nrows=7, figsize=(20,15),
+                         sharex=True, sharey=True)
+axes = axes.reshape(-1)
+
+## Loop through the files ##
+for i, fn in enumerate(sample_files):
+
+    # Get the age range from the data file
+    name = fn.split('/')[-1]
+    fn_ages = name.split('_')[-2].split('-')
+    fn_ages = [float(fn_ages[0][1:]), float(fn_ages[1])]
+
+    # Get the teff range from the data file
+    fn_teff = name.split('_')[-1].split('-')
+    fn_teff = [float(fn_teff[0][1:]), float(fn_teff[1][:-4])]
+
+    # Load the fitted data
+    fitted_data = np.load(data_files[i], allow_pickle=True)
+    all_data = fitted_data[0]
+    fitted_data = fitted_data[1]
+
+    # Load the MCMC samples
+    flat_samples = np.load(fn)
+
+    # Plot some best-fit lines, drawn randomly from the samples
+    inds = np.random.randint(len(flat_samples), size=100)
+    if len(fitted_data[:,0]) > 3:
+        for ind in inds:
+            sample = flat_samples[ind]
+            axes[i].plot(fitted_data[:,0], np.dot(np.vander(fitted_data[:,0], 2),
+                         sample[:2]), color='#e36414', alpha=0.05)
+
+    # Plot all of the data
+    axes[i].errorbar(all_data[:,0],
+                     all_data[:,1],
+                     yerr=all_data[:,2], color='#c0d6df',
+                     marker='o', linestyle='', zorder=200)
+
+    # Plot the data that was fitted
+    axes[i].errorbar(fitted_data[:,0],
+                     fitted_data[:,1],
[…]

### 2023-09-27 src/tex/ms.tex
more additions

@@
 
+There is a $3\sigma$ discrepancy between the FFD slope measured in \cite{ilin21}
+and the work presented here at ages $\sim 120$\,Myr. This discrepancy could be the
+result of several factors. First, \cite{ilin21} used the \textit{K2} 30-minute
+light curves. This would result in a sample biased towards the highest-energy flares which
+could be sampled at this cadence. Our flare detection method is less-biased towards
+the low-energy flares due to the 2-minute cadence from TESS and our flare detection
+algorithm. Second, our sample has $\sim 2\times$ the number
+of stars and $\sim 7\times$ the number of flares than their sample. This could
+result in a more complete FFD compared to previous work.
+
 \subsection{Fitting for $\alpha$ and $\beta$}
@@
 
-This work made use of the open-source package, \textcolor{red}{\textit{showyourwork!}}
-\citep{luger2021}, which promotes reproducible publications.
+In this work, we present the first measured flare rates for stars $< 300$\,Myr using
+TESS 2-minute cadence observations. We identified originating 28,822 flares from
+3,983 stars. The results of our work are summarized as follows:
+
+\begin{enumerate}
+  \item We measured the flare-frequency distribution (FFD) slope, $\alpha$, for samples
+  of flares binned by age and $T_\textrm{eff}$. We find $\alpha$ saturates at
+  $\alpha = -0.5$ for stars younger than 300\,Myr and declines after that age.
+  This is the first evidence that, like other tracers of stellar magnetic activity,
+  flare rates saturate across spectral types.
+  \item We measured the y-intercept, $\beta$, for the same bins of flares. We find
+  that ...
+  \item We measured the rotation periods, $P_\textrm{rot}$ for \textcolor{red}{n}
+  stars in our sample using the open-source Python package \texttt{michael}.
+  \item We measured the slope of a truncated power-law, $\alpha_T$, for the same
+  bins of flares. Additionally, we measured $\alpha_T$ as a function of Rossby
+  number, $R_0$.
+\end{enumerate}
+
+\vspace{3mm}
+
+We thank Darryl Seligman and David Wilson for thoughtful insights and useful
+conversations. This work made use of the open-source package,
+\textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes
+reproducible publications. ADF acknowledges funding from ...
 

### 2023-09-27 src/scripts/simple_ffd_all.py

@@ -12,6 +12,9 @@ pwd2 = os.path.join(data_dir, 'mcmc_fits/fitted_data')
 
 sample_files = np.sort([os.path.join(pwd1, i) for i in os.listdir(pwd1)])
 data_files = np.sort([os.path.join(pwd2, i) for i in os.listdir(pwd2)])
+sample_sizes = np.load(os.path.join(data_dir,
+                                    'mcmc_fits/mcmc_sample_sizes.npy'),
+                       allow_pickle=True).item()
 
 ## Setup the figure ##
 fig, axes = plt.subplots(ncols=5, nrows=7, figsize=(20,15),
@@ -29,6 +32,10 @@ for i, fn in enumerate(sample_files):
     # Get the teff range from the data file
     fn_teff = name.split('_')[-1].split('-')
     fn_teff = [float(fn_teff[0][1:]), float(fn_teff[1][:-4])]
+
+    # Nflares & Nstars in sample
+    nflares = sample_sizes[name[13:]][0]
+    nstars = sample_sizes[name[13:]][1]
 
     # Load the fitted data
     fitted_data = np.load(data_files[i], allow_pickle=True)
@@ -58,17 +65,22 @@ for i, fn in enumerate(sample_files):
                      yerr=fitted_data[:,2], color='#0f1108',
                      marker='o', linestyle='', zorder=200)
 
+    axes[i].text(s=r'$N_{flares}$ = ' + str(nflares),
+                 x=35, y=-1.5, fontsize=12, ha='right')
+    axes[i].text(s=r'$N_{stars}$ = ' + str(nstars),
+                 x=35, y=-1.9, fontsize=12, ha='right')
+
     # Set some titles
     if i < 5:
         axes[i].set_title('{0}-{1} K'.format(int(fn_teff[0]), int(fn_teff[1])),
-                          fontsize=14)
+                          fontsize=14, fontweight='bold')
 
     # Set some ylabels
     if ((i == 4) | (i == 9) | (i == 14) | (i == 19) |
         (i == 24) | (i == 29) | (i == 34)):
         axes[i].yaxis.set_label_position('right')
         axes[i].set_ylabel('{0}-{1} Myr'.format(int(fn_ages[0]), int(fn_ages[1])),
-                           fontsize=14)
+                           fontsize=14, fontweight='bold')
 
 plt.xlim(28,35.5)
 plt.ylim(-4, -1)

### 2023-10-30 src/tex/ms.tex
young planet host flare rate comparison

@@
 % Title
-\title{Refined Flare Rates for Stars Younger than 250\,Myr}
+\title{Evidence of Magnetic Saturation from Stellar Flare Rates}
 
@@
 and an exponential decay. This method uses a convolutional neural network (CNN),
-\texttt{stella} \citep{feinstein20b}, trained on by-eye validated flare events from
+\texttt{stella} \citep{feinstein20}, trained on by-eye validated flare events from
 TESS Sectors 1 and 2 to identify flare events in TESS 2-minute data
@@
 
-\subsection{Modeling Flare Properties}
+\subsubsection{Modeling Flare Properties}
 
@@
 
-From these fits, we performed a series of quality checks to ensure the flares
-in our sample are real. First, we removed any flares with best-fit FWHM $ < 0$
-and $A < 0$. Second, we removed any flares with a large error on the amplitude,
-$\sigma_A > 10$ and flares where $\sigma_A > A$. Third, we removed flares where
-$A < 2 \times \textrm{RMS}$, where the RMS is calculated from the 10~hour baseline
-around the best-fit $t_\textrm{peak}$. These cuts are indicative of a poorly fit
-flare model due to the flare being overwhelmed by noise in the surrounding baseline
-light curve. We choose to include flares with a probability $P \geq 75\%$ of being
-a true flare. After these checks, we have a flare sample of 29,128~flares originating
-from 3,983 stars (Figure~\ref{fig:flare_distribution}). 83.6\% of the flares have
-probabilities of $P \geq 90\%$ of being true; 64.9\% of the flares have probabilities
+\subsubsection{Flare Quality Checks}
+
+The \texttt{stella} CNNs were initially trained on data from TESS Sectors 1 and 2.
+Because the noise properties from sector to sector varies, the CNNs are unable to accurately
+capture all of these changes. Additionally, the CNNs were trained on a sample of \textcolor{red}{n}
+stars, which does not necessarily encapsulate all types of variable stars or a sufficient distribution
+of variable stars (e.g., eclipsing binaries and RR Lyraes). As such, we apply the additional
+quality checks presented in \cite{Feinstein22} to ensure our flare sample has little to no contamination
+from other sources. We remove flares which satisfy the one or more of the following criteria:
+
+\begin{enumerate}
+  \item The amplitude of the flare must be $> 0.01$, or 1\%. This follows the limits set by
+        \cite{feinstein20}.
+  \item The amplitude of the flare (A) must be greater than $1.5\times$CDPP \citep[Combined Differential
+        Photometric Precision;][]{christiansen12}, similar to \cite{Feinstein22}.
+  \item For flares originating from stars with $T_\textrm{eff} > 5000$, the amplitude of the flare
+        must be greater than $12\times$CDPP. This is because the most massive stars tended to have
+        much larger scatter in the TESS noise.
+  \item The fitted equivalent duration (ED) must be positive $\textrm{ED} > 0$.
+  \item The fitted full-width half-maximum (FHWM) and A must be $> 0$.
+  \item The error on the A must be $\sigma_A < A$. This removed poorly constrained flares and often
+        flares which were buried in the TESS noise.
+\end{enumerate}
+
+We choose to include flares with a probability $P \geq 75\%$ of being
+a true flare. After these checks, we have a flare sample of 28,822~flares originating
+from 3,979 stars (Figure~\ref{fig:flare_distribution}). 83.8\% of the flares have
+probabilities of $P \geq 90\%$ of being true; 65.0\% of the flares have probabilities
 of $P \geq 99\%$ of being true.
@@
 
+\subsection{Correlation to Other Metrics of Magnetic Saturation}
+
+\subsection{Comparison to Young Planet Host Stars}
+
+The all-sky observing strategy of TESS has revealed a new population of young transiting exoplanets.
+Characterizing the local environment for these planets is crucial to understanding their subsequent evolution
+to forming the mature population of planets. It is debated whether stellar flares are beneficial or detrimental
+to exoplanets. On one hand, \textcolor{red}{creates life}. On the other hand, stellar flares and affiliated
+coronal mass ejections can permanently alter atmospheric compositions \citep{chen21} and increase the amount of
+atmospheric mass stripped during the early stages of planet evolution \citep{feinstein20}. To understand the
+evolution of these new insightful young transiting exoplanets, we compare their measured flare rates to a more
+statistical sample of stars with similar ages and $T_\textrm{eff}$.
+
+We measured the flare rates of planet hosting stars $< 300$\,Myr, comparable to the ages of our primary sample.
+We followed the methods outlined in Section~\ref{sec:methods} to detect and vet flares. For each star, we created
+an equivalent sample with respect to both age and $T_\textrm{eff}$ to compare the flare rates too. We considered
+stars with ages $\pm 30$\,Myr of the planet hosting star and $T_\textrm{eff} \pm 1000$\,K. We calculated the overall
+flare rate as Equation~\ref{eq:fr}. We report the flare rates of host star and the comparable sample in Table~\ref{tab:yprates}.
+For the comparable sample, we report the median flare rate, and the lower 16\textsuperscript{th} and upper 84\textsuperscript{th}
+percentiles.
+
+\begin{figure}[ht!]
+    \script{yp_rates.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/yp_rates.pdf}
+        \caption{
+            Comparison of flare rates from young planet host stars with respect to
+            a comparable sample with respect to age [Myr] and $T_\textrm{eff}$ [K].
+        }
+        \label{fig:yp_rates}
+    \end{centering}
+\end{figure}
+
+\begin{deluxetable}{l r r r}[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{Young Planet Host Flare Rates\label{tab:yprates}}
+\tablehead{
+\colhead{Host Name} & \colhead{Age} & \colhead{Flare Rate} & \colhead{Comp. Sample} \\
+ & \colhead{[Myr]} & \colhead{[day$^{-1}$]} & \colhead{Flare Rate [day$^{-1}$]}
+}
+\startdata
+TOI 1227 &  $11 \pm 2$ &  0.008  & $0.119_{-0.046}^{+0.148}$ \\
+HIP 67522 & $17 \pm 2$ &  0.169  & $0.046_{-0.020}^{+0.069}$ \\
+AU Mic & $22 \pm 3$ &  2.218  & $0.133_{-0.046}^{+0.171}$ \\
+V1298 Tau & $23 \pm 4$ &  0.022  & $0.074_{-0.033}^{+0.091}$ \\
+HD 109833 & $27 \pm 3$ & 0.000  & $0.046_{-0.020}^{+0.070}$ \\
+KOI-7913 & $36 \pm 10$ &  0.031  & $0.134_{-0.045}^{+0.162}$ \\
+KOI-7368 & $36 \pm 10$ &  0.029  & $0.064_{-0.030}^{+0.087}$ \\
+DS Tuc & $45 \pm 4$ &  0.420  & $0.056_{-0.024}^{+0.078}$ \\
+TOI 942 & $50_{-20}^{+30} $ &  0.040  & $0.086_{-0.038}^{+0.117}$ \\
+TOI 451 & $120 \pm 10$ &  0.128  & $0.071_{-0.029}^{+0.085}$ \\
+HIP 94235 & $133_{-20}^{+15}$ &  0.020  & $0.051_{-0.017}^{+0.079}$ \\
+TOI 1860 & $133 \pm 26$ &  0.008  & $0.067_{-0.025}^{+0.086}$ \\
+TOI 1807 & $180 ± 40$ &  0.013  & $0.060_{-0.022}^{+0.085}$ \\
+HD 18599 & $200_{-70}^{+200} $ & 0.000 & $0.025_{-0.015}^{+0.044}$ \\
+TOI 2076 & $204 \pm 50$ & 0.000 & $0.092_{-0.045}^{+0.091}$ \\
+HD 110082 & $250_{-70}^{+50} $ & 0.000 & $0.047_{-0.020}^{+0.067}$ \\
+\enddata
+\end{deluxetable}
+
 \subsection{Applications to ULLYSES}
@@
 overall unexpected for young stars which are known to be more magnetically active
-\citep{ilin20, feinstein20b}. This could suggest that there is some bias in the way
+\citep{ilin20, feinstein20}. This could suggest that there is some bias in the way
 the ULLYSES sample was constructed, and that it is unexpected to find any flares in the
@@
 \end{document}
+feinstein20

### 2023-10-30 src/scripts/flare_distribution.py

@@ -18,6 +18,7 @@ set_rcparams()
 tab = Table.read(os.path.join(data_dir,
                               'llamaradas-estelares_all_parameters_withcuts_final_v2.csv'),
                  format='csv')
+tab = tab[(tab['noise_cut1']==0) & (tab['noise_cut2']==0) & (tab['ed'] > 0) & (tab['age']>0)]
 
 sample = Table.read(os.path.join(data_dir,'moca_sample.csv'), format='csv')
 

### 2023-10-30 src/scripts/yp_rates.py

@@ -1,0 +1,135 @@
+import os
+import sys
+import matplotlib
+import numpy as np
+from astropy import units
+from astropy.table import Table
+import matplotlib.pyplot as plt
+
+from plotting_utils import *
+from data_utils import *
+
+from paths import (
+    figures as figures_dir,
+    data as data_dir,
+)
+
+set_rcparams()
+
+cmap = teff_colorbar().reversed()
+
+##################################################
+### Load tables and make appropriate data cuts ###
+##################################################
+flares = Table.read(os.path.join(data_dir,'planet_host_rates.csv'), format='csv')
+tab = Table.read(os.path.join(data_dir,'llamaradas-estelares_all_parameters_withcuts_final_v2.csv'), format='csv')
+tab = tab[(tab['noise_cut1']==0) & (tab['noise_cut2']==0) & (tab['ed'] > 0) & (tab['age']>0)]
+
+#############################
+### Calculate flare rates ###
+#############################
+yp = np.zeros(len(np.unique(flares['Target_ID'])))
+names =  np.zeros(len(np.unique(flares['Target_ID'])), dtype='U30')
+
+for i, unique in enumerate(np.unique(flares['Target_ID'])):
+    tt = flares[flares['Target_ID']==unique]['tot_time_obs'][0]
+    name = flares[flares['Target_ID']==unique]['name'][0]
+    nflare = np.nansum(flares[flares['Target_ID']==unique]['prob'])
+    yp[i] = np.round(nflare/tt,3)
+    names[i] = name
+
+##########################################
+### Append targets which have 0 flares ###
+##########################################
+yp = np.insert(yp, 4, 0)
+yp = np.append(yp, np.zeros(3))
+
+names = np.insert(names, 4, 'HD 109833')
+names = np.append(names, ['HD 18599', 'TOI 2076', 'HD 110082'])
+
+##########################################
+### Ages and Teff of planet host stars ###
+##########################################
+ages = [11, 17, 22, 23, 27, 36, 36,
+        45, 50, 120, 133, 133, 180,
+        200, 204, 250]
+teff = [3055, 5767, 3588, 5159.64,
+        5881, 4324, 5241, 5414, 4945,
[…]

### 2023-10-30 src/tex/ms.tex
caption + color bar

@@
             a comparable sample with respect to age [Myr] and $T_\textrm{eff}$ [K].
+            Circles represent the flare rate of the host star (name along the x-axis);
+            vertical bars represent the lower 16\textsuperscript{th} and upper
+            84\textsuperscript{th} percentiles for the comparable sample. The majority
+            of young planet hosting stars have flare rates towards the lower end of the
+            comparable sample's distribution. A handful of hosts have more flares, including
+            HIP 67522, AU Mic, DS Tuc A, and TOI 451. We find no correlation between
+            age or $T_\textrm{eff}$ that may result in young planet hosts having more or fewer
+            flares than a larger comparable sample. The measured flare rates are presented in
+            Table~\ref{tab:yp_rates}.
         }
@@
 \tabletypesize{\footnotesize}
-\tablecaption{Young Planet Host Flare Rates\label{tab:yprates}}
+\tablecaption{Young Planet Host Flare Rates\label{tab:yp_rates}}
 \tablehead{

### 2023-10-30 src/scripts/yp_rates.py

@@ -83,9 +83,14 @@ for i in range(len(ages)):
 #######################
 norm = matplotlib.colors.Normalize(vmin=2300,vmax=5930)
 
-fig, (ax1, ax2) = plt.subplots(nrows=2, figsize=(8,6),
+fig, axes = plt.subplots(nrows=2, figsize=(10,6),
                                gridspec_kw={'height_ratios':[1,2]})
+ax1, ax2 = axes.reshape(-1)
+
 fig.set_facecolor('w')
+
+# For the color bar only
+sc = ax1.scatter(np.arange(len(yp)), yp, c=teff, cmap=cmap, vmin=2300, vmax=5930, s=0)
 
 for i in range(len(teff)):
     rgba_color = cmap.reversed()(norm(teff[i]))
@@ -99,7 +104,7 @@ for i in range(len(teff)):
     ax2.vlines(i, std_rate[:,0][i], std_rate[:,1][i], lw=10, alpha=0.5,
                color=hexnum)
     ax.plot(i, yp[i], 'o', color=hexnum, markeredgecolor='k', lw=2,
-             ms=8)
+             ms=10)
 
 ax1.spines['bottom'].set_visible(False)
 ax2.spines['top'].set_visible(False)
@@ -119,6 +124,7 @@ ax2.plot((1 - d, 1 + d), (1 - d, 1 + d), **kwargs)  # bottom-right diagonal
 
 ax2.set_ylim(-0.01,0.4)
 plt.ylabel('Flare Rate [day$^{-1}$]', y=0.8)
+plt.xlabel('Host Star Name')
 plt.xticks(np.arange(len(yp)),
            labels=names, rotation='vertical', fontsize=14)
 
@@ -130,6 +136,9 @@ ax1.set_yticks(np.arange(2.2,2.3,0.05))
 ax1.set_ylim(2.15,2.25)
 
 plt.subplots_adjust(hspace=0.1)
+
+cbar = fig.colorbar(sc, ax=axes.ravel().tolist())
+cbar.set_label('T$_{eff}$ [K]')
 
 plt.savefig(os.path.join(figures_dir,'yp_rates.pdf'),
             dpi=300, bbox_inches='tight')

### 2023-10-31 src/tex/ms.tex
rossby # histograms

@@
 \usepackage{showyourwork}
+\usepackage{rsfso}
 
@@
 % Title
-\title{Evidence of Magnetic Saturation from Stellar Flare Rates}
+\title{Flare Rates and Rotation Periods of 5700 Stars Younger than 300 Myr}
 
@@
     frequency distribution slopes as a function of age and stellar effective
-    temperature.
+    temperature. Finally, we measure the flare rates of young planet-hosting stars and
+    compare flare rates to a larger sample of stars with similar ages and $T_\textrm{eff}$.
+    We find that the majority of planet-hosting stars have lower flare rates, with the exception of
+    HIP 67522, AU Mic, DS Tuc, and TOI 451.
 \end{abstract}
@@
 
-\subsection{Measuring Rotation Periods}
+\subsection{Measuring Rotation Periods}\label{subsec:prot}
 
@@
 $P_\textrm{rot}$ were vetted by-eye, from the \texttt{michael} diagnostic plots. In
-total, we robustly measured \textcolor{red}{n} $P_\textrm{rot}$ across our sample of
-3,983 stars.
+total, we robustly measured 1,269 $P_\textrm{rot}$ across our sample of
+3,983 stars, which is $\sim 50\%$.
 
@@
     \begin{centering}
-        \includegraphics[width=3\textwidth]{figures/mcmc_results.pdf}
+        \includegraphics[width=3\textwidth, trim={0 0 30mm 0}, clip]{figures/mcmc_results.pdf}
         \caption{
@@
 
+\section{Flare Rates Compared to P$_{rot}$}
+
+\begin{figure}[ht!]
+    \script{prot_histograms.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/prot_histograms.pdf}
+        \caption{
+            Rotation periods and flare rates for M, K, and G stars (top to bottom).
+        }
+        \label{fig:prot_histograms}
+    \end{centering}
+\end{figure}
+
 \section{Discussion}\label{sec:discuss}
-
-\subsection{Correlation to Other Metrics of Magnetic Saturation}
 
@@
 an equivalent sample with respect to both age and $T_\textrm{eff}$ to compare the flare rates too. We considered
-stars with ages $\pm 30$\,Myr of the planet hosting star and $T_\textrm{eff} \pm 1000$\,K. We calculated the overall
-flare rate as Equation~\ref{eq:fr}. We report the flare rates of host star and the comparable sample in Table~\ref{tab:yprates}.
-For the comparable sample, we report the median flare rate, and the lower 16\textsuperscript{th} and upper 84\textsuperscript{th}
-percentiles.
+stars with ages $\pm 30$\,Myr of the planet hosting star and $T_\textrm{eff} \pm 1000$\,K. We calculate the overall
+flare rate as described in \cite{Feinstein22}:
+
+\begin{equation}
+  \mathcal{R} = \frac{1}{\tau_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)
+\end{equation}
+
+where $\mathcal{R}$ is the flare rate in day$^{-1}$, $\tau_\textrm{obs}$ is the total amount of time a target was
+observed with TESS, and $p_i$ is the probability that flare $i$ is a true flare as assigned by \texttt{stella}. We present
+the flare rates of planet-hosting stars and a comparable sample of stars in Figure~\ref{fig:yp_rates} and report the measured
+rates in Table~\ref{tab:yp_rates}. For the comparable sample, we report the median flare rate, and the lower 16\textsuperscript{th}
+and upper 84\textsuperscript{th} percentiles.
 
@@
 \end{deluxetable}
+
+\subsection{Correlation to Other Metrics of Magnetic Saturation}
+
+X-ray luminosity surveys of stars have revealed a saturation limit with respect to
+the star's rotation period. Namely, there is no evolution in $L_X/L_\textrm{bol}$ for
+stars with $P_\textrm{rot} < 10$\,days \citep{Pizzolato03}.
+
+Here, we explore if flare rates evolve as a function of rotation period. We used our
+measured $P_\textrm{rot}$ as described in Section~\ref{subsec:prot}. Due to TESS's orbit,
+we limit our search of $P_\textrm{rot}$ to $< 20$\,days. This should not bias our analysis as
+young stars are known to rotate on short timescales \citep[e.g.][]{west15, popinchalk23}. We
+present our results in Figure~\ref{fig:prot}.
 

### 2023-10-31 src/scripts/prot_histograms.py

@@ -1,0 +1,132 @@
+import os
+import sys
+import matplotlib
+import numpy as np
+from astropy import units
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from matplotlib.colors import LinearSegmentedColormap
+
+from plotting_utils import *
+from data_utils import *
+
+from paths import (
+    figures as figures_dir,
+    data as data_dir,
+)
+
+set_rcparams()
+
+tab = Table.read(os.path.join(data_dir, 'combined.csv'),
+                 format='csv')
+tab = tab[tab['Good'] == 1]
+
+prot = tab['Prot']
+teff = tab['Teff']
+age  = tab['age']
+fr   = tab['flare_rate']
+
+## Calculate Rossby Number ##
+log_tau = 1.16 - 1.49*np.log10(tab['mass'])-0.54*np.log10(tab['mass'])**2
+tau = 10**log_tau
+R0_1 = prot/tau
+
+## Setup Figure ##
+fig, axes = plt.subplots(figsize=(15,8), nrows=2, ncols=3, sharex=True,
+                         sharey=True, gridspec_kw={'width_ratios':[1,1,1.2]})
+axes = axes.reshape(-1)
+fig.set_facecolor('w')
+nbins = 30
+
+## Define binning ##
+R0_bins = np.logspace(-2, 0, nbins)
+fr_bins = np.logspace(-2.5,0.1,nbins)
+
+## Colormaps ##
+c_old = ['#03045eff', '#023e8aff', '#0077b6ff', '#0096c7ff', '#00b4d8ff',
+         '#48cae4ff', '#90e0efff', '#ade8f4ff', '#caf0f8ff','#ffffff']
+cmap_old = LinearSegmentedColormap.from_list('old', c_old).reversed()
+
+c_young = ['#2f184bff', '#532b88ff', '#9b72cfff', '#c8b1e4ff', '#f4effaff',
+           '#ffffff']
+cmap_young = LinearSegmentedColormap.from_list('young', c_young).reversed()
+
+
+#######################
+### M DWARF SUBPLOT ###
+#######################
+axes[0].set_title('M stars')
+q2 = ((np.isfinite(np.log10(fr))==True) & (teff <= 3500) &
+       (age <= 50))
+im = axes[0].hist2d(R0_1[q2], fr[q2],
+                    bins=[R0_bins, fr_bins],
[…]

### 2023-11-02 src/tex/ms.tex
power law fits to Ro and flare rates

@@
 
-\section{Flare Rates Compared to P$_{rot}$}
+\section{Flare Rates Compared to $R_0$}
 
-\begin{figure}[ht!]
+The Rossby number, $R_0$, is a term which marginalizes over several properties which are known to
+affect the stellar dynamo, such as the rotation period and stellar mass. We convert our measured
+rotation periods to $R_0$, which is defined as $R_0 = P_\textrm{rot}/\tau$, where $\tau$ is the
+convective turnover time. We approximate $\tau$ following the prescription in \cite{wright11}. We
+equate the flare rates for individual stars as
+
+\begin{equation}\label{eqn:fr}
+  \mathcal{R} = \frac{1}{t_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)
+\end{equation}
+
+where $\mathcal{R}$ is the flare rate in units of day$^{-1}$, $t_\textrm{obs}$ is the total amount of time a target was
+observed with TESS, and $p_i$ is the probability that flare $i$ is a true flare as assigned by \texttt{stella}.
+We compare the calculated $R_0$ to measured flare rates for all stars we measured $P_\textrm{rot}$ for. The
+results are presented in Figure~\ref{fig:prot_histograms}.
+
+\begin{figure*}[ht!]
     \script{prot_histograms.py}
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/prot_histograms.pdf}
+        \includegraphics[width=\textwidth]{figures/prot_histograms.pdf}
         \caption{
-            Rotation periods and flare rates for M, K, and G stars (top to bottom).
+            Comparison of Rossby Number, $R_0$ and flare rate for young GKM stars.
+            We find no change in the average flare rate for GKM stars $< 250$\,Myr.
+            We see evidence that as $R_0$ increases, the average flare rate decreases.
+            This is similar to results presented in \cite{medina20}, however our sample extends this
+            trend to young GKM stars, while previous results were limited to nearby M dwarfs. The top row are
+            stars with ages $4.5 - 50$\,Myr; the bottom row are stars with ages $50 - 250$\,Myr. The
+            histograms are colored by number of stars in each bin.
         }
@@
     \end{centering}
-\end{figure}
+\end{figure*}
+
+We evaluate the relationship between age, spectral type, flare rate, and $R_0$. We divide the sample between stars
+younger and older than 50~Myr, which roughly correlates to the age at which GKM stars turn onto the main sequence.
+For stars younger than 50~Myr, we find the flare rate slightly decreases with increasing $R_0$, although there is a
+significant amount of scatter in this relationship. For stars between $50 - 250$~Myr, we see this relationship much
+clearer. For M stars, we see minimal evolution in both average flare rate and $R_0$ between the two samples. For K
+stars, we see $R_0$ evolving over the first 250~Myr, while the scatter in the flare rate decreases. For G stars, we
+see the scatter in $R_0$ decreasing, and the average flare rate across the sample decreases. We present a compiled histogram
+for all stars in our sample in the right column of Figure~\ref{fig:prot_histograms}.
+
+To better understand this trend, we fit three types of functions: (i) a constant value, (ii) a single power law, and
+(iii) a piece-wise function consisting of a constant value and a power law. For (iii), we computed these fits across a range
+of $R_0$ for where the turnover should occur. We binned the cumulative dataset consisting of all GKM stars into 50 evenly-spaced bins
+in log-space from $log_{10}(R_0) = [-2, 0]$. We computed the $\chi^2$ between
+each of these fits and the data. For stars $4.5 - 50$~Myr, we find the distribution is best-fit with a single
+power law with slope $m = -0.243 \pm 0.043$ and y-intercept $b = -1.221 \pm 0.061$. Converting the $\chi^2$ to a standard
+deviation, we find a single fit is preferred by $\sim 3\sigma$. For stars $50 - 250$~Myr, we find the distribution
+is best-fit with a piece-wise function of the form
+
+\begin{equation}
+  \mathcal{R} =
+  \Bigg \{
+  \begin{array}{ll}
+        C & R_0 \leq 0.15 \\
+        10^b * R_0^m  & R_0 > 0.15 \\
+  \end{array}
+\end{equation}
+
+where $\mathcal{R}$ is the flare rate, $C = 0.126 \pm 0.006$, $m = -0.986 \pm 0.119$, and $b = -1.687 \pm 0.078$.
+We test how our bin size affected our $R_0$ turnover. To do this, we refit our data assuming binning from $20 - 100$
+bins and find $R_0$ to be consistent with $R_0 = 0.15 \pm 0.02$. The location of the turnover is consistent to
+within $1\sigma$ with what has been seen in other observations of magnetic saturation for partially and
+fully convective stars \citep[e.g. $L_X/L_\textrm{bol}$; ][]{wright18}.
 
@@
 an equivalent sample with respect to both age and $T_\textrm{eff}$ to compare the flare rates too. We considered
-stars with ages $\pm 30$\,Myr of the planet hosting star and $T_\textrm{eff} \pm 1000$\,K. We calculate the overall
-flare rate as described in \cite{Feinstein22}:
-
-\begin{equation}
-  \mathcal{R} = \frac{1}{\tau_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)
-\end{equation}
-
-where $\mathcal{R}$ is the flare rate in day$^{-1}$, $\tau_\textrm{obs}$ is the total amount of time a target was
-observed with TESS, and $p_i$ is the probability that flare $i$ is a true flare as assigned by \texttt{stella}. We present
+stars with ages $\pm 30$\,Myr of the planet hosting star and $T_\textrm{eff} \pm 1000$\,K. We calculate the flare rate
+following Equation~\ref{eq:fr}. We present
 the flare rates of planet-hosting stars and a comparable sample of stars in Figure~\ref{fig:yp_rates} and report the measured

### 2023-11-02 src/scripts/prot_histograms.py

@@ -32,8 +32,8 @@ tau = 10**log_tau
 R0_1 = prot/tau
 
 ## Setup Figure ##
-fig, axes = plt.subplots(figsize=(15,8), nrows=2, ncols=3, sharex=True,
-                         sharey=True, gridspec_kw={'width_ratios':[1,1,1.2]})
+fig, axes = plt.subplots(figsize=(20,8), nrows=2, ncols=4, sharex=True,
+                         sharey=True, gridspec_kw={'width_ratios':[1,1,1.2,1.2]})
 axes = axes.reshape(-1)
 fig.set_facecolor('w')
 nbins = 30
@@ -51,6 +51,11 @@ c_young = ['#2f184bff', '#532b88ff', '#9b72cfff', '#c8b1e4ff', '#f4effaff',
            '#ffffff']
 cmap_young = LinearSegmentedColormap.from_list('young', c_young).reversed()
 
+c = ['#391c06ff', '#552a09ff', '#71380cff',
+     '#8e450eff', '#aa5311ff', '#c66114ff', '#e36f17ff', '#ff7d1aff',
+     '#ffba86', '#ffcca4', '#fff3f3', '#ffffff']
+cmap_c = LinearSegmentedColormap.from_list('k', c).reversed()
+
 
 #######################
 ### M DWARF SUBPLOT ###
@@ -65,7 +70,7 @@ im = axes[0].hist2d(R0_1[q2], fr[q2],
 
 q2 = ((np.isfinite(np.log10(fr))==True) & (teff <= 3500) &
       (age > 50) )
-im = axes[3].hist2d(R0_1[q2], fr[q2],
+im = axes[4].hist2d(R0_1[q2], fr[q2],
                     bins=[R0_bins, fr_bins],
                     cmap=cmap_old, vmin=0, vmax=8)
 
@@ -82,9 +87,9 @@ im = axes[1].hist2d(R0_1[q2], fr[q2],
                     cmap=cmap_young, vmax=5)
 
 
-q2 = ((np.isfinite(np.log10(fr))==True) & (teff <= 3500) & (teff < 5000) &
+q2 = ((np.isfinite(np.log10(fr))==True) & (teff > 3500) & (teff < 5000) &
       (age > 50))
-im = axes[4].hist2d(R0_1[q2], fr[q2],
+im = axes[5].hist2d(R0_1[q2], fr[q2],
                     bins=[R0_bins, fr_bins],
[…]

### 2023-11-02 src/scripts/yp_rates.py

@@ -104,7 +104,7 @@ for i in range(len(teff)):
     ax2.vlines(i, std_rate[:,0][i], std_rate[:,1][i], lw=10, alpha=0.5,
                color=hexnum)
     ax.plot(i, yp[i], 'o', color=hexnum, markeredgecolor='k', lw=2,
-             ms=10)
+             ms=12)
 
 ax1.spines['bottom'].set_visible(False)
 ax2.spines['top'].set_visible(False)
@@ -122,7 +122,7 @@ kwargs.update(transform=ax2.transAxes)  # switch to the bottom axes
 ax2.plot((-d, +d), (1 - d, 1 + d), **kwargs)  # bottom-left diagonal
 ax2.plot((1 - d, 1 + d), (1 - d, 1 + d), **kwargs)  # bottom-right diagonal
 
-ax2.set_ylim(-0.01,0.4)
+ax2.set_ylim(-0.05,0.4)
 plt.ylabel('Flare Rate [day$^{-1}$]', y=0.8)
 plt.xlabel('Host Star Name')
 plt.xticks(np.arange(len(yp)),

### 2023-11-07 src/tex/ms.tex
galex subsection

@@
     \begin{centering}
-        \includegraphics[width=3\textwidth, trim={0 0 30mm 0}, clip]{figures/mcmc_results.pdf}
+        \includegraphics[width=3.4\textwidth, trim={0 0 30mm 0}, clip]{figures/mcmc_results.pdf}
         \caption{
@@
 
+\subsection{Correlations with Far- and Near-Ultraviolet Flux}
+
+X-ray luminosity surveys of stars have revealed a saturation limit with respect to
+the star's rotation period. Namely, there is no evolution in $L_X/L_\textrm{bol}$ for
+stars with $P_\textrm{rot} < 10$\,days \citep{Pizzolato03}.
+
+The Far- and Near-Ultraviolet (FUV/NUV) is another tracer of magnetic activity. Young
+stars are known to have excess luminosity in both of these wavelengths \citep{}. We use
+archival observations from the \textit{Galaxy Evolution Explorer}
+\citep[\textit{GALEX};][]{martin05} to search for trends in FUV/NUV saturation and flare
+rate saturation. \textit{GALEX} provides broad FUV photometry from $1350-1750$
+and NUV photometry from $1750-2750$. We crossmatch our targets with the \textit{GALEX}
+catalog. We follow the sample selection methods outline in \citep{schneider18}. We search
+a $10''$ radius around the coordinates of each target in our sample. We include targets with
+no bad photometric flags (e.g. \texttt{fuv\_artifact} or \texttt{nuv\_artifact == 0}) as defined
+in the catalog. This is recommended by the \textit{GALEX} documentation, as flags could be
+assigned due to bright star window reflection, dichroic reflection, detector run proximity,
+or bright star ghost. We exclude targets with measured magnitudes brighter than 15, which
+marks the saturation limit for both the FUV and NUV photometers \citep{morrissey07}.
+
+Based on these thresholds, we find that 462 stars in our sample have NUV photometry and
+139 stars have FUV photometry. We explore if flare rate saturation and FUV/NUV saturation
+are correlated with the derived $R_0$ per star. We present our results in Figure~\ref{fig:galex}.
+We present the measured FUV/NUV flux normalized by the J-band flux of the star, since it
+is the fractional flux which acts as an activity indicator. While bolometric luminosities would
+be a better normalizing factor, we find the majority of stars in our target do not have
+this parameter measured. To assess FUV/NUV correlations in a larger statistical sense, we thus
+keep the normalization to $f_J$.
+
+\begin{figure}[ht!]
+    \script{galex.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/galex.pdf}
+        \caption{
+            Calculated NUV (left) and FUV (right) GALEX flux for stars in our
+            sample. We normalize these values by the J-band flux of the star.
+            We find no strong correlation between the NUV/FUV flux and the measured
+            flare rate or Rossby number.
+            The top row shows GKM stars $<50$~Myr; the bottom row
+            shows GKM stars $\geq 50$~Myr. M stars are shown as circles, K stars as
+            triangles, and G stars as squares. We note that $f_{NUV}$ traces the
+            photosphere of GK stars, and therefore may not be the best comparison
+            bandpass when looking for trends in magnetic activity.
+        }
+        \label{fig:galex}
+    \end{centering}
+\end{figure}
+
 \subsection{Comparison to Young Planet Host Stars}
@@
 following Equation~\ref{eq:fr}. We present
-the flare rates of planet-hosting stars and a comparable sample of stars in Figure~\ref{fig:yp_rates} and report the measured
-rates in Table~\ref{tab:yp_rates}. For the comparable sample, we report the median flare rate, and the lower 16\textsuperscript{th}
-and upper 84\textsuperscript{th} percentiles.
+the flare rates of planet-hosting stars and a comparable sample of stars in Figure~\ref{fig:yp_rates}
+and report the measured rates in Table~\ref{tab:yp_rates}. For the comparable sample, we report the
+median flare rate, and the lower 16\textsuperscript{th} and upper 84\textsuperscript{th} percentiles.
 
@@
 \end{deluxetable}
-
-\subsection{Correlation to Other Metrics of Magnetic Saturation}
-
-X-ray luminosity surveys of stars have revealed a saturation limit with respect to
-the star's rotation period. Namely, there is no evolution in $L_X/L_\textrm{bol}$ for
-stars with $P_\textrm{rot} < 10$\,days \citep{Pizzolato03}.
-
-Here, we explore if flare rates evolve as a function of rotation period. We used our
-measured $P_\textrm{rot}$ as described in Section~\ref{subsec:prot}. Due to TESS's orbit,
-we limit our search of $P_\textrm{rot}$ to $< 20$\,days. This should not bias our analysis as
-young stars are known to rotate on short timescales \citep[e.g.][]{west15, popinchalk23}. We
-present our results in Figure~\ref{fig:prot}.
 

### 2023-11-07 src/scripts/galex.py

@@ -1,0 +1,213 @@
+import os
+import sys
+import numpy as np
+from astropy import units
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+from plotting_utils import *
+
+from paths import (
+    figures as figures_dir,
+    data as data_dir,
+)
+
+set_rcparams()
+
+galex_tab = Table.read(os.path.join(data_dir, 'galex_xmatch.csv'),
+                       format='csv')
+
+""" Defining the subtables
+Cuts were defined by the HAZMAT team papers.
+"""
+nuv = galex_tab[(galex_tab['distance_arcsec'] <= 10.0) &
+                (galex_tab['nuv_artifact']==0) &
+                (galex_tab['nuv_mag'] >= 15.0)]
+
+fuv = galex_tab[(galex_tab['distance_arcsec'] <= 10.0) &
+                (galex_tab['fuv_artifact']==0) &
+                (galex_tab['fuv_mag'] >= 15.0)]
+
+""" Defining the color maps. """
+ccmap = get_galex_colormap(channel='nuv')
+pcmap = get_galex_colormap()
+
+""" Making the plot. """
+fig, ((ax4, ax3),
+      (ax2, ax1),
+      (ax6, ax5)) = plt.subplots(ncols=2, nrows=3,
+                                 figsize=(12,10),
+                                 gridspec_kw={'height_ratios':[0.07,1,1]})
+fig.set_facecolor('w')
+
+""""""""""""""""""
+""" AX1 -- NUV """
+""""""""""""""""""
+vmin, vmax = -4, -2
+cmap = ccmap
+c = np.log10(nuv['nuv_flux_density']/nuv['J_flux_density'])
+
+
+""" M stars """
+q = (nuv['teff'] < 3500) & (nuv['age'] < 50)
+ax1.scatter(nuv['R0'][q],
+            nuv['flare_rate'][q],
+            c=c[q],
+            vmin=vmin, vmax=vmax, cmap=cmap,
+            marker='o')
+
+q = (nuv['teff'] < 3500) & (nuv['age'] >= 50)
+ax5.scatter(nuv['R0'][q],
+            nuv['flare_rate'][q],
+            c=c[q],
[…]

### 2023-11-07 src/scripts/plotting_utils.py

@@ -11,7 +11,8 @@ from paths import (
     scripts as script_dir
 )
 
-__all__ = ['set_rcparams', 'teff_colorbar', 'prob_colorbar', 'age_colorbar']
+__all__ = ['set_rcparams', 'teff_colorbar', 'prob_colorbar', 'age_colorbar',
+           'get_galex_colormap']
 
 def set_rcparams():
     tab = Table.read(os.path.join(data_dir,'rcparams.txt'), format='csv')
@@ -49,3 +50,22 @@ def age_colorbar(short=False):
         dat = np.load(os.path.join(data_dir, 'parula_data.npy'))
     parula = LinearSegmentedColormap.from_list('parula', dat)
     return parula
+
+
+def get_galex_colormap(channel='fuv'):
+    """ Color maps used for GALEX data. """
+    clist = ['#000000', '#1f363dff', '#284751ff', '#305865ff',
+             '#40798cff', '#589197ff', '#70a9a1ff', '#87b5a2ff',
+             '#9ec1a3ff', '#b7d1b3ff',
+             '#cfe0c3ff', '#d7e6cd']
+    ccmap = LinearSegmentedColormap.from_list('rossby', clist)
+
+    plist = ['#f6e5cbff',
+             '#f7c4a5ff', '#9e7682ff',
+             '#605770ff', '#4d4861ff', '#0d1321']
+    pcmap = LinearSegmentedColormap.from_list('rossby', plist).reversed()
+
+    if channel=='fuv':
+        return pcmap
+    else:
+        return ccmap

### 2023-11-13 src/tex/ms.tex
angstrom
galex

@@
 \usepackage{rsfso}
+
+\newcommand{\angstrom}{\mbox{\normalfont\AA}}
 
@@
 \citep[\textit{GALEX};][]{martin05} to search for trends in FUV/NUV saturation and flare
-rate saturation. \textit{GALEX} provides broad FUV photometry from $1350-1750$
-and NUV photometry from $1750-2750$. We crossmatch our targets with the \textit{GALEX}
+rate saturation. \textit{GALEX} provides broad FUV photometry from $1350-1750 \angstrom$
+and NUV photometry from $1750-2750 \angstrom$. We crossmatch our targets with the \textit{GALEX}
 catalog. We follow the sample selection methods outline in \citep{schneider18}. We search
@@
         \caption{
-            Calculated NUV (left) and FUV (right) GALEX flux for stars in our
+            Calculated FUV (left) and NUV (right) GALEX flux for stars in our
             sample. We normalize these values by the J-band flux of the star.

### 2023-11-13 src/scripts/galex.py

@@ -159,10 +159,10 @@ cbar = plt.colorbar(im, cax=ax4, orientation='horizontal')
 ax4.set_title(r'$log_{10}(f_{FUV} / f_J)$', fontsize=16)
 ax4.tick_params(top=True, labeltop=True, bottom=False, labelbottom=False)
 
-ax5.plot(100,100,marker='o',label='M stars', lw=0, color='k')
-ax5.plot(100,100,marker='^',label='K stars', lw=0, color='k')
-ax5.plot(100,100,marker='s',label='G stars', lw=0, color='k')
-ax5.legend(bbox_to_anchor=(0.3, -0.4, 1.4, .102), loc=3,
+ax6.plot(100,100,marker='o',label='M stars', lw=0, color='k')
+ax6.plot(100,100,marker='^',label='K stars', lw=0, color='k')
+ax6.plot(100,100,marker='s',label='G stars', lw=0, color='k')
+ax6.legend(bbox_to_anchor=(0.3, -0.4, 1.4, .102), loc=3,
            ncol=3, mode="expand", borderaxespad=0.,
            markerscale=2)
 
@@ -175,18 +175,18 @@ for ax in [ax1, ax2, ax5, ax6]:
 
 ax1.set_xticklabels([])
 ax2.set_xticklabels([])
-ax2.set_yticklabels([])
-ax6.set_yticklabels([])
+ax1.set_yticklabels([])
+ax5.set_yticklabels([])
 
-ax2.set_yticklabels([])
-ax5.set_ylabel('Flare Rate [day$^{-1}$]', y=1.1)
-ax5.set_xlabel('Rossby Number', x=1.0)
 
-ax7 = ax2.twinx()
+ax6.set_ylabel('Flare Rate [day$^{-1}$]', y=1.1)
+ax6.set_xlabel('Rossby Number', x=1.0)
+
+ax7 = ax1.twinx()
 ax7.set_ylabel('4.5 - 50 Myr')
 ax7.set_yticks([])
 
-ax8 = ax6.twinx()
+ax8 = ax5.twinx()
 ax8.set_ylabel('50 - 250 Myr')
 ax8.set_yticks([])
 

### 2023-11-15 src/scripts/prot_histograms.py
option for transparent fig

@@ -158,5 +158,7 @@ axes[3].set_title('GKM stars combined')
 
 plt.subplots_adjust(wspace=0.2, hspace=0.1)
 
+#plt.savefig('/Users/belugawhale/Desktop/prot_histograms.png', dpi=300,
+#            bbox_inches='tight', transparent=True)
 plt.savefig(os.path.join(figures_dir, 'prot_histograms.pdf'), dpi=300,
             bbox_inches='tight')

### 2023-11-15 src/scripts/mcmc_results.py
changed marker

@@ -66,19 +66,20 @@ for i, fn in enumerate(fits):
 #####################################
 # Plot data from Ilin et al. (2020) #
 #####################################
+imarker = 's'
 hyades_slopes = -np.array([2.11, 1.89, 1.94, 2.17, 1.99, 1.96])+1
 plt.errorbar(695, np.nanmedian(hyades_slopes),
              xerr=75, yerr=np.nanstd(hyades_slopes),
-             color='k', marker='o')
+             color='k', marker=imarker)
 
 pleiades_slopes = -np.array([2.13, 2.06, 2.06, 1.99, 2.32, 1.92, 1.91]) + 1
 plt.errorbar(127.4, np.nanmedian(pleiades_slopes),
              xerr=8, yerr=np.nanstd(pleiades_slopes),
-             color='k', marker='o')
+             color='k', marker=imarker)
 
 praesepe_slopes = -np.array([2.09, 2.0, 1.95, 1.89, 2.39, 1.86, 1.91]) + 1
 plt.errorbar(617, np.nanmedian(praesepe_slopes), yerr=np.nanstd(praesepe_slopes),
-             color='k', marker='o', label='Ilin et al. (2020)')
+             color='k', marker=imarker, label='Ilin et al. (2020)')
 
 ##########################################
 # Plot data from Feinstein et al. (2022) #
@@ -94,10 +95,13 @@ plt.legend(bbox_to_anchor=(0., 1.02, 1., .102), loc=3,
            markerscale=2)
 
 plt.xscale('log')
+plt.ylim(-1.8, 0.0)
 plt.xlabel('Age [Myr]', fontsize=24)
 plt.ylabel('Flare Frequency\nDistribution Slope, ' + r'$\alpha$', fontsize=24)
 
 ax.set_rasterized(True)
 
+#plt.savefig('/Users/belugawhale/Desktop/mcmc_results.png', dpi=300,
+#            bbox_inches='tight', transparent=True)
 plt.savefig(os.path.join(figures_dir,'mcmc_results.pdf'),
             dpi=300, bbox_inches='tight')

### 2023-11-17 src/tex/ms.tex
add teff hist

@@
 % Title
-\title{Flare Rates and Rotation Periods of 5700 Stars Younger than 300 Myr}
+\title{Evolution of Flare Rates in GKM Stars Younger than 300 Myr}
 
@@
             and equivalent durations of flares in our sample, colored by the probability
-            of the flare as identified with \texttt{steela}. Bottom: Same as the
+            of the flare as identified with \texttt{stella}. Bottom: Same as the
             middle plot, except colored by the $T_\textrm{eff}$ [K] of the star.

### 2023-11-17 src/scripts/sample.py

@@ -16,6 +16,8 @@ from plotting_utils import *
 set_rcparams()
 
 sample = Table.read(os.path.join(data_dir,'moca_sample.csv'), format='csv')
+_, uni = np.unique(sample['ID'], return_index=True)
+sample = sample[uni]
 
 RA, Dec = sample['ra'], sample['dec']
 org = 0
@@ -30,8 +32,12 @@ x=-x    # reverse the scale: East to the left
 tick_labels = np.array([150, 120, 90, 60, 30, 0, 330, 300, 270, 240, 210])
 tick_labels = np.remainder(tick_labels+360+org,360)
 
-fig = plt.figure(figsize=(18, 6))
-ax = fig.add_subplot(111, projection=projection)
+fig, axes = plt.subplots(figsize=(8, 9), nrows=2,
+                      gridspec_kw={'height_ratios':[2,1]})
+axes[0].set_visible(False)
+axes[1].set_visible(False)
+
+ax = fig.add_subplot(211, projection=projection)
 img = ax.scatter(np.radians(x),np.radians(Dec), c=np.log10(sample['age']),
                  vmin=np.log10(5), vmax=np.log10(250), s=15, cmap=parula)
 ax.set_xticklabels(tick_labels, fontsize=18)     # we add the scale on the x axis
@@ -40,12 +46,24 @@ ax.set_xlabel("RA", fontsize=20)
 ax.set_ylabel("Dec", fontsize=20)
 
 ax.grid(True)
-cbar = plt.colorbar(img, location='bottom', shrink=0.45)
+cbar = plt.colorbar(img, location='bottom', shrink=0.65)
 cbar.ax.set_xlabel('Age [Myr]', fontsize=20)
 
-cbar.ax.set_xticks(np.linspace(np.log10(5), np.log10(250), 7))
+cbar.set_ticks(np.linspace(np.log10(5), np.log10(250), 7))
 cbar.ax.set_xticklabels(np.linspace(5,250,7,dtype=int), fontsize=14)
 ax.set_rasterized(True)
+
+## histogram of Teff ##
+ax2 = fig.add_subplot(212)
+ax2.hist(sample['Teff'], bins=np.linspace(2500,6000,100), color='k',
+         alpha=0.4)
+ax2.hist(sample['Teff'], bins=np.linspace(2500,6000,100), color='k',
+         histtype='step', lw=2)
+ax2.set_xlim(2500,6000)
[…]

### 2023-11-17 src/tex/ms.tex
bib updates

@@
 (6) \citet{murphy15}; (7) \citet{curtis19}; (8) \citet{galindo22};
-(9) \citet{kounkel20}; (10) \citet{tofflemeire21}; (11) \citet{tarricq21};
+(9) \citet{kounkel20}; (10) \citet{tofflemire21}; (11) \citet{tarricq21};
 (12) \citet{roser16}; }
@@
 
-\begin{equation}\label{eqn:fr}
+\begin{equation}\label{eq:fr}
   \mathcal{R} = \frac{1}{t_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)
@@
 overall unexpected for young stars which are known to be more magnetically active
-\citep{ilin20, feinstein20}. This could suggest that there is some bias in the way
+\citep{ilin19, feinstein20}. This could suggest that there is some bias in the way
 the ULLYSES sample was constructed, and that it is unexpected to find any flares in the

### 2023-12-07 src/tex/ms.tex
updated truncated figure yay

@@
 \begin{abstract}
-    Photometric exoplanet detection missions have revolutionized our understanding
-    of stellar activity. Stellar flares are short-duration high-energy radiation
-    outbursts which can be readily seen across young (< 800\,Myr) stars and even
-    in high counts on mature M dwarfs. Here, we present the results of measuring
-    stellar flare rates for very young stars, with ages $4.5 - 200$\,Myr right
-    after they formed to understand the early evolution of magnetic activity. We
-    have selected a sample of 5,700 stars which belong to 26 associations,
-    nearby young moving groups, or clusters. We identified $\sim 29,000$ flares
-    using the \texttt{stella} machine-learning algorithm. We measured the flare-
-    frequency distribution slopes as a function of age and stellar effective
-    temperature. Finally, we measure the flare rates of young planet-hosting stars and
-    compare flare rates to a larger sample of stars with similar ages and $T_\textrm{eff}$.
-    We find that the majority of planet-hosting stars have lower flare rates, with the exception of
-    HIP 67522, AU Mic, DS Tuc, and TOI 451.
+  Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with magnetic reconnection events.
+The magnetic activity of stars is known to decrease as a function of age and Rossby number, $R_0$, a parameterization of how strong the Coriolis force is.
+Here, we detect and characterize the flare properties of $\sim$~\textcolor{red}{n} stars younger than 300~Myr which have been observed by the Transiting Exoplanet Survey Satellite at 2-minute cadence.
+Our stars are bona fide, high-probability, or candidate members of 26 nearby young moving groups, clusters, or associations.
+We identified \textcolor{red}{n} flares originating from \textcolor{red}{n} stars.
+We robustly measured the rotation periods of $1,847$~stars.
+We measure the flare frequency distribution (FFD) slope as a function of both age and spectral type.
+We find the FFD slope, $\alpha$, saturates for all spectral types at $\alpha = -0.5$ and does not evolve over 300~Myr.
+Additionally, we find that $R_0$ and flare rate for stars $t_\textrm{age} = 100 -- 300$~Myr are saturated out to $R_0 = 0.12$, which is consistent with other indicators of magnetic activity.
+We find the FFD slope for stars with $R_0 \leq 0.12$ are shallower than stars with $R_0 > 0.12$, suggesting the Coriolis force plays a role in generating more high-energy flares.
+We cross match our targets with \textit{GALEX} and find no correlation between flare rate and Far- and Near-Ultraviolet flux.
+Finally, we compare the flare rates of planet hosting stars to comparable, larger samples of stars and find the majority of these stars are relatively flare quiet.
+This may impact the atmospheric evolution of young short-period exoplanets.
+
 \end{abstract}
@@
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
-Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
-Donec vehicula augue eu neque, morbi tristique senectus et netus et.
-Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
-Phasellus eu tellus sit amet tortor gravida placerat.
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
-Praesent eget sem vel leo ultrices bibendum.
-Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
-Curabitur auctor semper nulla donec varius orci eget risus.
-Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-Duis eget orci sit amet orci dignissim rutrum.
+Stellar flares are the radiation component of magnetic reconnection events \citep{}.
+Such events are readily seen on the Sun \citep{}, particularly now as we enter a maximum in the solar cycle \citep{}.
+Such events can be used to understand the magnetic activity of other stars \citep{}.
+Additionally, by studying stellar flares we can understand how these short-duration events may impact short-period exoplanet evolution \citep{}.
+While we cannot resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events.
+Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events, e.g.
+coronal mass ejections \citep{} or proton beams \citep{}.
+They can also inform our understanding of stellar plasma is displaced during these events \citep{}.
 
-This paper is presented as follows.
+Photometric observations of stars are more readily available thanks to exoplanet missions, and allow us to statistically characterize flare rates and energies.
+Within time-series photometry, stellar flares can be identified by a sharp rise in the stellar flux and a subsequent exponential decay, corresponding to the cooling rate \citep{}.
+\textit{Kepler} provided long-baseline high-cadence observations used to identify stellar flares.
+There has been extensive studies of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars \citep[e.g.]{Hawley14, silverberg16}.
+\cite{davenport19} found that flare activity decreased with increasing rotation period for 347 GKM stars.
+However, the flare frequency distribution (FFD) slope did not change significantly as a function of age.
+As a caveat, the ages of the stars were determined based on their rotation periods alone, relying on the assumption that gyrochronology alone accurately ages stars.
+
+After the failure of two reaction wheels, \textit{Kepler} was repurposed to the \textit{K2} mission \citep{Howell14}.
+\textit{K2} provided 70-day baseline observations for a handful of young stars in groups such as Upper Scorpius,  Pleiades, Hyades, and Praespe clusters.
+\cite{ilin19} analyzed flares K and M stars in these clusters and measured FFD slopes of ...
+
+More recently, the Transiting Exoplanet Survey Satellite \citep[TESS;][]{ricker15} has provided near all-sky photometric observations at 30-minute cadence or less.
+Such an observing strategy has allowed for more detailed studies of young stellar flares from nearby young moving groups and associations, which are disperse in the sky \citep{}.
+
+The paper is presented as follows.
+In Section~\ref{sec:methods}, we describe our sample, stellar flare identification and fitting methods, and methods for measuring stellar rotation periods.
+In Section~\ref{sec:results}, we present our flare-frequency distribution (FFD) fits as a function of stellar age, $T_\textrm{eff}$, and $R_0$.
+In Section~\ref{sec:discuss}, we search for correlations in flare rates with FUV and NUV observations from \textit{GALEX} and place the flare rates of young planet hosting stars in the context of our broader sample.
+We conclude in Section~\ref{sec:conclusions}.
+We provide additional figures and tables in Section~\ref{appendix:supp_ffds}.
 
@@
 
-\subsection{Fitting for $\alpha$ and $\beta$}
-
 \subsection{Truncated Power-Law Fits}
@@
 walkers and evaluated the fit over textcolor{red}{n} steps. The first textcolor{red}{n}
-steps were discarded upon visual inspection. The results are presented in Figure~\ref{fig:trunc}.
+steps were discarded upon visual inspection. The results are presented in Figure~\ref{fig:truncated}.
 
-\section{Flare Rates Compared to $R_0$}
+\begin{figure}[ht!]
+    \script{truncated.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/truncated.pdf}
+        \caption{
+            Flare frequency distributions, as a function of flare amplitude, for stars with $R_0 \leq 0.12$ (red) and stars with $R_0 > 0.12$ (black).
+We present the best-fit model, and the best-fit values of the model slope and normalization factor in the legends.
+Our sample of $R_0 \leq 0.12$ includes 13,132 flares from 800 stars; our sample of $R_0 > 0.12$ includes 5,603 flares from 747 stars.
+We find the stars with smaller Rossby numbers have shallower slopes, consistent with more, high-energy flares and potentially larger convective regions \citep{seligman22}.
+        }
+        \label{fig:truncated}
+    \end{centering}
+\end{figure}
+
+\subsection{Flare Rates Compared to $R_0$}
 
@@
 
-\subsection{Applications to ULLYSES}
+\subsection{Evidence of Stellar Cycles}
 
-Measuring Far-Ultraviolet (FUV) total flux output and flare rates are
-essential for understanding the contributions of flares to exoplanet atmospheric
-mass-loss and disequilibrium chemistry. An equivalent, but significantly smaller sample
-to the stars studied here are the those observed as part of the \textit{Hubble Space Telescope}
-(HST) Ultraviolet Legacy Library of Young Stars as Essential Standards (ULLYSES)
-program. This survey observed 71 K- to M-type T Tauri stars in nine young
-galactic associations.
+The Sun goes through a 12-year solar cycle, which oscillates between times of high and low activity.
+The solar cycle manifests itself in a variety of observables, including a change in the flare rate, by a factor of 10 \citep{}, and the flare energies released \citep{}.
+Constraints of stellar cycles have predominantly relied on photometry \citep[see recent review by ][]{cycleReview}.
+However, tracing stellar cycles via stellar flares may be more reliable, as flares are a direct consequence of magnetic activity.
+\cite{} explored measuring the stellar cycle length of KIC 8507979, a star in the \textit{Kepler} field which was observed for 18 90-day quarters.
+They found the flare rate decreased over each quarter, which could be fit by $L_\textrm{fl}/L_\textrm{Kp} = (-9.96 \pm 3.94) \times 10^{-2} \times t_\textrm{yr} + (2.43 \pm 0.11)$, where $t_\textrm{yr}$ is the time in years, and $L_\textrm{fl}/L_\textrm{Kp}$ is a parameterization of the \textit{Kepler} flare rate as defined by \citep{Hawley14}.
 
-We can extend the results presented here to estimate how many flares may be present
-in these important FUV observations.
+It is possible that the length of the stellar cycle is related to the $P_\textrm{rot}$/ $R_0$ of the star as ...
+\citep{}.
+If this is the case, then stars with $P_\textrm{rot}$ will have shorter stellar cycle lengths.
+The TESS Extended Mission has provided a five-year baseline, similar to \textit{Kepler}, although the sampling is sparser.
+Within our sample of fast rotators, we searched for evidence of stellar cycles.
+Our sample contains 31 stars which have been observed for $t_\textrm{obs} \geq 400$\,days and $n_\textrm{flare} > 100$.
 
-Additionally, we analyzed the TESS light curves for all of the ULLYSES targets, when
-available at 2-minute cadence. We identified a total of \textcolor{red}{n} flares.
-This is inconsistent with the overall flare statistics identified in this work, and is
-overall unexpected for young stars which are known to be more magnetically active
-\citep{ilin19, feinstein20}. This could suggest that there is some bias in the way
-the ULLYSES sample was constructed, and that it is unexpected to find any flares in the
-FUV data. Alternatively, it could be that the ongoing accretion luminosity results
-in a brighter host star, such that the flares we normally would see are drowned
-out by the increased baseline luminosity. We do not include this flare in our
-overall statistical analysis of TESS flare rates for young stars.
+We search for evidence of changes in the stellar magnetic activity by looking at (i) the maximum flare energy in a given period of time and (ii) the flare rate over that same period of time.
+We grouped our observations by year observed, even if the star was not continuously observed throughout that year.
 

### 2023-12-07 src/scripts/analysis_utils.py

@@ -1,9 +1,10 @@
 import numpy as np
 from astropy import units
+from mpmath import expint, mp, fp
 from scipy.optimize import curve_fit
 from astropy import constants as const
 
-__all__ = ['get_energy_limits', 'planck', 'fit_ffd', 'linear']
+__all__ = ['get_energy_limits', 'planck', 'fit_ffd', 'linear', 'logpdf']
 
 def planck(lam, T, rad):
     """
@@ -135,3 +136,10 @@ def fit_ffd(data, limit, yerr=None):
     data = np.array([logx, logn, np.sqrt(n[mask])])
 
     return popt, perr, data.T
+
+
+# Functional form of PDF with respect to log_10 a
+def logpdf(loga, q, astar, amp_min):
+    a = 10.**loga
+    norm = amp_min**(q-1) / fp.mpf(expint(q, amp_min/astar)) * np.log(10)
+    return norm * a**-(q-1) * np.exp(-a/astar)

### 2023-12-07 src/scripts/truncated.py

@@ -1,0 +1,96 @@
+import os
+import sys
+import numpy as np
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from matplotlib.colors import LinearSegmentedColormap
+
+from paths import (
+    figures as figures_dir,
+    data as data_dir,
+    scripts as script_dir
+)
+
+from plotting_utils import *
+from analysis_utils import logpdf
+
+set_rcparams()
+
+""" GET THE DATA """
+table = Table.read(os.path.join(data_dir,'rossby_stats.csv'), format='csv')
+lo = np.load(os.path.join(data_dir,'r0_samples_lo_v4.npy'), allow_pickle=True)
+hi = np.load(os.path.join(data_dir,'r0_samples_hi_v4.npy'), allow_pickle=True)
+amp_min = 10**-1.8
+bins = np.logspace(-2,2,100)
+
+
+logasamp = np.log10(np.logspace(np.log10(amp_min), 1.0))
+interval = 100
+
+pdf_samp_lo = np.array([logpdf(logasamp, lo[0][i,0], 10.**lo[0][i,1], amp_min)
+                        for i in range(0, lo.shape[0], interval)])
+pct_short_lo = np.percentile(pdf_samp_lo, [2.5,5,16,50,84,95,97.5], axis=0)
+
+pdf_samp_hi = np.array([logpdf(logasamp, hi[0][i,0], 10.**hi[0][i,1], amp_min)
+                        for i in range(0, hi.shape[0], interval)])
+
+pct_short_hi = np.percentile(pdf_samp_hi, [2.5,5,16,50,84,95,97.5], axis=0)
+
+fig, (ax) = plt.subplots(figsize=(8,3.5), sharex=True,
+                              sharey=True)
+
+
+colors = ['#b75d69', '#1a1423']
+alpha, lw = [0.4, 0.2], 2
+dat = [lo[1], hi[1]]
+
+""" PLOT THE DATA """
+for i in range(len(dat)):
+    ax.hist(np.log10(dat[i]), bins=30, color=colors[i], lw=0,
+                 alpha=alpha[i], density=True, range=[np.log10(amp_min), 1])
+    ax.hist(np.log10(dat[i]), bins=30, fill=None, edgecolor=colors[i],
+             lw=lw, density=True, range=[np.log10(amp_min), 1])
+
+""" PLOT THE BEST FIT MODEL """
[…]

### 2023-12-19 src/tex/ms.tex
new and improved results

@@
 
+\author[0000-0002-0726-6480]{Darryl~Z.~Seligman}
+\altaffiliation{NSF Astronomy and Astrophysics Postdoctoral Fellow}
+\affiliation{Department of Astronomy and Carl Sagan Institute, Cornell University, 122 Sciences Drive, Ithaca, NY 14853}
+
 % Abstract with filler text
 \begin{abstract}
-  Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with magnetic reconnection events.
-The magnetic activity of stars is known to decrease as a function of age and Rossby number, $R_0$, a parameterization of how strong the Coriolis force is.
-Here, we detect and characterize the flare properties of $\sim$~\textcolor{red}{n} stars younger than 300~Myr which have been observed by the Transiting Exoplanet Survey Satellite at 2-minute cadence.
-Our stars are bona fide, high-probability, or candidate members of 26 nearby young moving groups, clusters, or associations.
+Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with surface magnetic reconnection events.
+Stellar magnetic activity  generally decreases as a function of both age and of Rossby number, $R_0$, a measure of the relative dominance of the convective and rotational dynamos.
+For those reasons, it is worthwhile analyzing the flare population level characteristics for young, rapidly rotating stars.
+With this motivation, we select a sample of stars that are either (i) members, (ii) candidate members or (iii) high-probability of being  members of 26 nearby young moving groups, clusters, or associations all known to be less than 300~Myr old that have been observed by the Transiting Exoplanet Survey Satellite (TESS) at 2-minute cadence.
+With this  sample of $\sim$~\textcolor{red}{n} stars younger than 300~Myr, we present detections and characterizations of the flare properties.
 We identified \textcolor{red}{n} flares originating from \textcolor{red}{n} stars.
-We robustly measured the rotation periods of $1,847$~stars.
-We measure the flare frequency distribution (FFD) slope as a function of both age and spectral type.
+Moreover, we robustly measured the rotation periods of $1,847$~stars.
+Finally, we measure the flare frequency distribution (FFD) slope as a function of both age and spectral type.
 We find the FFD slope, $\alpha$, saturates for all spectral types at $\alpha = -0.5$ and does not evolve over 300~Myr.
-Additionally, we find that $R_0$ and flare rate for stars $t_\textrm{age} = 100 -- 300$~Myr are saturated out to $R_0 = 0.12$, which is consistent with other indicators of magnetic activity.
-We find the FFD slope for stars with $R_0 \leq 0.12$ are shallower than stars with $R_0 > 0.12$, suggesting the Coriolis force plays a role in generating more high-energy flares.
+Additionally, we find that $R_0$ and flare rate for stars $t_\textrm{age} = 100 - 300$~Myr are saturated out to $R_0 = 0.12$, which is consistent with other indicators of magnetic activity.
+We find the FFD slope for stars with $R_0 \leq 0.14$ are shallower than stars with $R_0 > 0.14$, suggesting the Coriolis force plays a role in generating more high-energy flares.
 We cross match our targets with \textit{GALEX} and find no correlation between flare rate and Far- and Near-Ultraviolet flux.
@@
 
-\section{Methodology}
-\label{sec:methods}
+\section{TESS Light Curve Characterization}\label{sec:methods}
 
-\subsection{Sample Selection}
+In this section, we provide an overview of the methodology associated with this paper.
+The various methods described here are pertinent to the remainder of the paper.
+Specifically, we describe the sample selection in subsection \ref{subsec2:sample}, TESS light curve analysis in \ref{subsec2:TESS_lightcurve}, flare identification in subsection \ref{subsec2:Flareidentification}, flare models in \ref{subsec2:model}, flare quality checks in \ref{subsec2:qualitychecks}, and measurement of stellar rotaiton periods in \ref{subsec:prot}.
 
-We aim to measure the evolution in flare rates as a function of stellar age for
-stars with $1 \leq t_\textrm{age} \leq 250$\,Myr. We used the MOCA Data Base
+\subsection{Sample Selection}\label{subsec2:sample}
+
+In this paper, we select a sample of stars that have $<300$ Myr ages based on their affiliation with nearby young moving group, clusters and associations.
+This provides an independant constraint on the age, which is more robust than only using the rotational periods.
+Moreover, we select stars that have been observed with TESS with 2-minute cadence.
+With these criteria, we obtain light curves for a sample of 3,163 young stars in total.
+
+With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}.
+In order to model the flare profile, we employ the analytical  model developed by \cite{tovar22}.
+This model is able to simultaneously (i) fit the flares and  (ii) measure the equivalent duration and energy associated with each flare.
+
+A primary goal of this paper is to  measure the evolution of the stellar flare rate and its dependance on the stellar age. Particularly, we are interested in this dependancy for
+stars with ages $1 \leq t_\textrm{age} \leq 250$\,Myr. To this end, we used the MOCA Data Base
 (Gagné et al. in prep.) to identify nearby young moving groups, associations,
-and open clusters with known ages which satisfied our criteria. We identified
-unique 26~groups from which we created our sample list. We considered all targets
-that are either bona fide members, high-likelihood candidate members, or candidate members.
-This resulted in a catalog of 30,889 stars across 26 associations. We summarize
-the sample and quote adopted ages for each association
+and open clusters with known ages which satisfied our criteria. From this database we identified
+ 26~ unique groups from which we created our  sample of stars.
+The final selected targets were required to be: (i) confirmed members, (ii) high-likelihood candidate members, or (iii) candidate members.
+These rather stringent cuts resulted in a
+ catalog of 30,889 stars across 26 associations. We summarize
+the sample and   ages for each association (and therefore star)
 in Table~\ref{tab:sample}.
@@
 \startdata
-AB Doradus  &  133$_{-20}^{+15}$  &  81  & 1 \\
-Blanco 1 & 137.1$^{+7.0}_{-33}$ & 301 & 8\\
-Carina  &  45  & 91  & 2\\
-Carina-Musca & 32 & 22 & 5\\
-Chamaeleon  &  5  &  366  & 3 \\
-Columba  &  42  &  126  & 2\\
-Greater Taurus Subgroup 5 & 8.5 & 56 & 5\\
-Greater Taurus Subgroup 8 & 4.5 & 114 & 5\\
-Lower Centaurus Crux &  15  & 590  & 4\\
-MELANGE-1 & 250$_{-70}^{+50}$ & 22 & 10\\
-Octans  &  35$\pm 5$ &   98  & 6 \\
-Pisces Eridanis  &  120  &   176  & 7 \\
-Pleiades & 127.4$^{+6.3}_{-10}$ & 1304 & 8\\
-$\alpha$ Persei  &  79$_{-2.3}^{+1.5}$  &  467  & 8 \\
-IC 2602 corona &  52.5$_{-3.7}^{+2.2}$  & 10  & 8 \\
-IC 2602 system &  52.5$_{-3.7}^{+2.2}$  & 138  & 8 \\
-NGC 2451A & 48.5 & 44 & 5\\
-Oh 59 & 162.2 & 50 & 9\\
-Platais 9 & 50 & 99 & 11\\
-RSG2 & 126 & 87 & 12\\
-Theia 301  &  195  &  372  & 9\\
-Theia 95  &  30.2  &  191  & 9\\
-TW Hydrae  &  10  &  24  & 2\\
-Upper Centaurus  Lupus &  16  &  464  & 4 \\
-Upper Scorpius  &  10  &  80  & 4 \\
-Vela-CG4  &  33.7  &  352  & 5
+AB Doradus  &  133$_{-20}^{+15}$  &  88  & 1 \\
+Blanco 1 & 137.1$^{+7.0}_{-33}$ & 428 & 2\\
+Carina  &  45  & 94  & 3\\
+Carina-Musca & 32 & 35 & 4\\
+Chamaeleon  &  5  &  424  & 5 \\
+Columba  &  42  &  126  & 3\\
+Greater Taurus Subgroup 5 & 8.5 & 56 & 4\\
+Greater Taurus Subgroup 8 & 4.5 & 122 & 4\\
+Lower Centaurus Crux & 15 & 761 & 6\\
+MELANGE-1 & 250$_{-70}^{+50}$ & 19 & 7\\
+Octans  &  35$\pm 5$ &   64  & 8 \\
+Pisces Eridanis  &  120  &   219  & 9 \\
+Pleiades & 127.4$^{+6.3}_{-10}$ & 1421 & 2\\
+$\alpha$ Persei  &  79$_{-2.3}^{+1.5}$  &  625 & 2 \\
+IC 2602 system &  52.5$_{-3.7}^{+2.2}$  & 160 & 2 \\
+NGC 2451A & 48.5 & 59 & 4\\
+Oh 59 & 162.2 & 62 & 10\\
+Platais 9 & 50 & 124 & 11\\
+RSG2 & 126 & 145 & 12\\
+Theia 301  &  195  &  437 & 10\\
+Theia 95  &  30.2  &  230 & 10\\
+TW Hydrae  &  10  &  24  & 3\\
+Upper Centaurus Lupus & 16 $\pm$ 2 & 696 & 6\\
+Upper Scorpius  &  10  &  106  &  6\\
+Vela-CG4  &  33.7  &  299  & 4\\
+\hline
+Total & & 6,824\\
 \enddata
-\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{Bell15};
-(3) \citet{luhman07}; (4) \citet{pecaut16}; (5) \citet{kerr21};
-(6) \citet{murphy15}; (7) \citet{curtis19}; (8) \citet{galindo22};
-(9) \citet{kounkel20}; (10) \citet{tofflemire21}; (11) \citet{tarricq21};
-(12) \citet{roser16}; }
+\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{galindo22}; (3) \citet{Bell15}; (4) \citet{kerr21}; (5) \citet{luhman07}; (6) \citet{pecaut16}; (7) \citet{tofflemire21}; (8) \citet{murphy15}; (9) \citet{curtis19}; (10) \citet{kounkel20}; (11) \citet{tarricq21}; (12) \citet{roser16}}
 \end{deluxetable}
 
-\subsection{TESS Light Curves}
+\subsection{TESS Light Curves}\label{subsec2:TESS_lightcurve}
 
-To ensure we were able to resolve and accurately measure the energies of flares
-on these stars \citep{howard22}, we used the 2-minute data from the TESS mission.
+As described in the previous subsection, we only select stars in our sample for which TESS light curves have been obtained with 2-minute cadance.
+The reason for doing this is so that we are able to resolve and accure accurately measure the energies of flares for each of these stars \citep{howard22}.
 We crossmatched our sample with the TESS Input Catalog (TIC) based on their RA and Dec.
-We considered a star to be in the catalog if the distance between the target and
-the nearest TIC was within $1"$. This resulted in a final sample of 5,725 unique targets
-which have been observed at 2-minute cadence between Sector 1 and Sector 67, the
-latest available sector upon this analysis. Given the proximity of many targets towards the
-northern and southern ecliptic poles (Figure~\ref{fig:sample}), many targets were observed
-over multiple sectors. We downloaded all available data, yielding a total of 17,964
-light curves.
+In order for a star to be considered as a member of the catalog, , we required that  the distance between the target and
+the nearest TIC was within $<1"$.
+
+This process provided  a final sample of 5,725 unique targets.
+These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67.
+These are the latest available sectors at the time that this analysis was performed.
+In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions of the final sample.
+It is evident that  many targets exhibit strong tendency for proximitry towards the
+northern and southern ecliptic poles (Figure~\ref{fig:sample}). Therefore, many  of these targets were observed
+over multiple sectors all of which observed the ecliptic poles. The entirety of the available data yielded  a total of 17,964
+light curves, an average of $\sim 3$ light curves per target (although with significant spread across targets).
 
 \begin{figure}[ht!]
-    \script{sample.py}
+    %\script{sample.py}
     \begin{centering}
@@
         \caption{
-            Distribution of our selected sample across the sky and colored by the
-            adopted age of the association (see Table~\ref{tab:sample}). The all-sky
-            coverage by TESS has unlocked new populations of stars to observe.
-            We take advantage of this observing strategy to measure flare rates
-            across 26 different nearby young moving groups, clusters, and associations.
+            Top: Distribution of our selected sample across the sky and colored by the adopted age of the association (see Table~\ref{tab:sample}).
+The all-sky coverage by TESS has unlocked new populations of stars to observe.
+We take advantage of this observing strategy to measure flare rates across 26 different nearby young moving groups, clusters, and associations.
+Bottom: Distribution of adopted effective temperatures, $T_\textrm{eff}$ [K] for stars in our sample.
+We include all stars with $T_\textrm{eff} \leq 6000$\,K.
         }
@@
 
-\subsection{Flare Identification}
+\subsection{Flare Identification}\label{subsec2:Flareidentification}
 
-We followed the machine learning flare-identification methods presented in
-\cite{feinstein20a}. This method relies on the fact that all flare events
-have similar time-dependent morphologies generally described as a sharp rise
-and an exponential decay. This method uses a convolutional neural network (CNN),
-\texttt{stella} \citep{feinstein20}, trained on by-eye validated flare events from
-TESS Sectors 1 and 2 to identify flare events in TESS 2-minute data
-\citep{guenther19_flares, feinstein20a}. The benefits of the CNN is that it is
-insensitive to the stellar baseline, since it is trained to look only for the
-flare morphology. This means that the peaks of rotational modulation driven by
-stellar heterogeneities, which is readily seen in the light curves of young stars,
-are not accidentally identified as flares. In this way, we are able to
-build a sample of flares which is unbiased towards low-amplitude/low-energy flares,
-which are often not identified in traditional sigma-outlier identification
+Once we had the lightcurves for each target, we performed the following procedur to identify stellar flares.
+First, we implemented the machine learning flare-identification methods presented and described in
+\cite{feinstein20}. This method relies on the fact that all flare events
+have similar time-dependent morphologies. These flare-profiles can generally be described as a sharp rise followed by
+ an exponential decay in the white light curve. The identification-technique implements  a convolutional neural network (CNN),
+\texttt{stella} \citep{feinstein20}. The neural network was trained to identify flare events in TESS 2-minute data using a catalogue of flare events from
+TESS Sectors 1 and 2 that were validated  by-eye
+\citep{guenther19_flares}.
+
+There are many benefits to using the CNN for stellar flare identification.
+Primarily, the CNN is advantageous because it is insensitive to the stellar baseline flux.
+This feature inherently stems from the fact that the network is trained to search \textit{only} based on flare morphology.
+It is therefore relatively insensitive to the absolute flux levels, so long as the inherent noise does not overwhelm the signal itself.
+One advantage of this is that rotational modulation peaks --- which are themselves  driven by
+stellar heterogeneities ---
+are not accidentally identified as flares. This is especially advantageous for our sample of young stars, which  readily exhibit rotational modulatioin and associated peaks  in their light curves.
+
+Based on these advantages, the final compiled sample of flares is \textit{unbiased} towards low-amplitude/low-energy flares.
+It is important to note that these low-energy events are typically  not identified in traditional sigma-outlier identification
 methods \citep{chang15}.
 
-The \texttt{stella} CNN models take the light curve (time, flux, flux error)
+The \texttt{stella} CNN models calculates the probability that a data point in a light curve is associated with a flaring event. Specifically, it taakes the light curve (time, flux, flux error)
 as an input and returns an array with values of [0,1], which are treated as
-the probability a data point is (1) or is not (0) part of a flare. We ran all
-light curves through 10 \texttt{stella} models and averaged the output, taking
-this as the final prediction per observation. The \texttt{stella} code uses the
-predictions per data point to group together points, identifying those as single
-flare events. It then calculates the probability of the entire flare event as
-the average of the probabilities assigned to all the data points during the flare.
+the probability a data point is (1) or is not (0) part of a flare. We ran every
+light curve through 10 independant \texttt{stella} models to ensure that our statistics were accurate.
+We then averaged the output probabilities for each 10 model runs to be the final prediction per observation.
+
+In order to identify a single flare event, the \texttt{stella} code uses the
+predictions per data point to group together points.
+We modified this stage of identification slightly from the original flare-identification method.
+Specifically, we identified all data points with a probability of being associated with a flare of $P > 0.75$.
+Any data points that were within 4 cadences of each other were considered to be a single flare event.
+We did not consider any potential flares that had three or fewer points with $P > 0.75$.
+This was motivated by the fact that  sometimes a single-point outlier is assigned a high probability of being a flare.
+Therefore, we simply neglected these events.
+We assigned the probability of the whole flare event as the probability of the peak data point.
 
 \begin{figure}[ht!]
-    \script{flare_distribution.py}
+    %\script{flare_distribution.py}
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/flare_distribution.pdf}
+        \includegraphics[width=0.9\linewidth]{figures/flare_distribution.pdf}
         \caption{
@@
 
-\subsubsection{Modeling Flare Properties}
+\subsection{Modeling Flare Properties}\label{subsec2:model}
 
-We used the analytical flare model in
-\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}
-to fit the flares in our sample. This model builds upon the model presented
-in \cite{davenport14}, and includes a convolution of a Gaussian with a
-double exponential model. The analytical model accounts for the amplitude,
-heating timescale, rapid cooling phase timescale, and slow cooling phase
-timescale of flares. Using this model, we used a non-linear least squares
+As described in the previous subsection, flares are well-described in light curves as a sudden increase in flux followed by an exponential decay.
+For this paper, we used the analytical flare model,Llamaradas Estelares which was  presented in
+\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}.
+We used these models to fit the flares and extract the flare parameters in all of the light curves of our sample.
+This model builds upon the model presented
+in \cite{davenport14}. Specifically, it includes the convolution of a Gaussian with a
+double exponential model in the flare profile.
+
+The analytical model is robust in that it is able to accounts for multiple inherent features of flares. Specifically, it can incorporate the flare (i) amplitude,
+ (ii) heating timescale, (iii) rapid cooling phase timescale, and (iv) slow cooling phase
+timescale . We implemented a nonlinear least squares
 optimization to fit for the time of the flare peak ($t_\textrm{peak}$),
-full width at half maximum (FWHM), and the amplitude ($A$), of each flare
+full width at half maximum (FWHM), and the amplitude ($A$) of each flare
 in the sample.  We combine the model with a second-order polynomial fit to
-a 10-hour baseline before and after the flare to account for any rotational
-modulation.
+a 1.2-hour baseline before and after the flare  during only the fitting stage.
+This was implemented in order to account for any rotational modulation, and therefore  was particularly relevant for the rapid rotators.
 
-\subsubsection{Flare Quality Checks}
+We calculated the equivalent duration, ED, of the flare by performing a numerical integration  of the flare flux with respect to time. We calculate the flare energy, $E_\textrm{flare}$, using,
 
-The \texttt{stella} CNNs were initially trained on data from TESS Sectors 1 and 2.
-Because the noise properties from sector to sector varies, the CNNs are unable to accurately
-capture all of these changes. Additionally, the CNNs were trained on a sample of \textcolor{red}{n}
-stars, which does not necessarily encapsulate all types of variable stars or a sufficient distribution
-of variable stars (e.g., eclipsing binaries and RR Lyraes). As such, we apply the additional
-quality checks presented in \cite{Feinstein22} to ensure our flare sample has little to no contamination
-from other sources. We remove flares which satisfy the one or more of the following criteria:
+\begin{equation}\label{eq:Eflare}
+    E_\textrm{flare} = L_\star \, A \, \textrm{ED} \, s \, .
+\end{equation}
+In equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$, where $B_\lambda(T)$ is the Planck function.
+We assume that the flare temperature is 9000~K \citep{}.
 
+\subsection{Flare Quality Checks}\label{subsec2:qualitychecks}
+
+In this subsection, we describe the methodology we employ to ensure that flares identified by the CNN are high quality.
+The \texttt{stella} CNNs were trained on data from TESS Sectors 1 and 2.
+However, the noise properties are variable aross sectors in TESS data.
+The CNNs are therefore unable to accurately
+account for and capture  this variation when operating on different sectors.
+Moreover, the original CNNs were only trained on a sample of 1,228 stars.
+This sample  does not necessarily encapsulate all or even a sufficient distribution  of variable stars types, such as eclipsing binaries, RR Lyraes, and fast rotators with rotation periods $P_\textrm{rot} < 1$~day.
+We  therefore apply  additional
+quality checks to ensure our flare sample has little to no contamination
+from other sources.
+
+Specifically, we remove flares from our sample which did not satisfy  one or more of the following criteria.
 \begin{enumerate}
-  \item The amplitude of the flare must be $> 0.01$, or 1\%. This follows the limits set by
-        \cite{feinstein20}.
-  \item The amplitude of the flare (A) must be greater than $1.5\times$CDPP \citep[Combined Differential
-        Photometric Precision;][]{christiansen12}, similar to \cite{Feinstein22}.
-  \item For flares originating from stars with $T_\textrm{eff} > 5000$, the amplitude of the flare
-        must be greater than $12\times$CDPP. This is because the most massive stars tended to have
-        much larger scatter in the TESS noise.
-  \item The fitted equivalent duration (ED) must be positive $\textrm{ED} > 0$.
-  \item The fitted full-width half-maximum (FHWM) and A must be $> 0$.
-  \item The error on the A must be $\sigma_A < A$. This removed poorly constrained flares and often
-        flares which were buried in the TESS noise.
+    \item  The amplitude of the flare must be $> 0.01$, or 1\%. This follows the limits set by \cite{feinstein20}.
+    \item The flare amplitude  must be at least twice the standard deviation of the light curve 30 minutes before and 45 minutes after the flare.
+This ensures that the feature is not a sharp noise artifact.
+    \item  The fitted flare model parameters must be physically motivated: FWHM $> 0$; $A > 0$; ED $> 0$.
+    \item The flare parameters   must be $\sigma_A < 0.5$ and $\sigma_{t_\textrm{peak}} < 0.01$.
 \end{enumerate}
+We find that when the errors on the first criteria are larger than the cut-offs, the flares are often simply  mischaracterized noise.
 
-We choose to include flares with a probability $P \geq 75\%$ of being
-a true flare. After these checks, we have a flare sample of 28,822~flares originating
-from 3,979 stars (Figure~\ref{fig:flare_distribution}). 83.8\% of the flares have
-probabilities of $P \geq 90\%$ of being true; 65.0\% of the flares have probabilities
-of $P \geq 99\%$ of being true.
+As a final check, we performed an exhaustive by-eye verification of flares from light curves for stars with flare rates, $\mathcal{R} > 1$~day$^{-1}$.
+These stars  generally tend to have $T_\textrm{eff} > 5000$~K and TESS magnitudes $< 8$.
+Therefore, their light curves are dominated by sharp noisewhich \texttt{stella} often mischaracterizes as flares.
+
+As a final cut, the sample only includes events that have  a probability $P \geq 90\%$ of being
+a true flare.
+After performing these additional checks, we obtain a final flare sample of \textcolor{red}{n}~flares originating from \textcolor{red}{n} stars (Figure~\ref{fig:flare_distribution}).
+\textcolor{red}{n}\% of the flares have probabilities of $P \geq 90\%$ of being true; \textcolor{red}{n}\% of the flares have probabilities of $P \geq 99\%$ of being true.
 
 \subsection{Measuring Rotation Periods}\label{subsec:prot}
+In this paper we have two  primary goals. The first is to improve our understanding of flare statistics across
+ ages for young stars. \citet{seligman22} demonstrated that stars with low Rossby numbers $R_0 < 0.13$ exhibit
+shallower flare frequency distribution slopes. These shallower slopes are caused by  an excess of  high energy flares compared to lower energy flares
+originating from these sources.  In addition to improving flare statistics, we  aim to expand the sample for which flare frequency slope and  rossby number (from $P_\textrm{rot}$) have been measured.
 
-\cite{seligman22} demonstrated that stars with low Rossby numbers $R_0 < 0.13$ have
-shallower flare frequency distribution slopes, indicative of more high energy flares
-originating from these sources. In addition to understanding flare statistics across
-young ages, we aim to expand this sample by measuring the rotation periods, $P_\textrm{rot}$,
-for the stars in our sample. To do this, we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}},
-an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination
+In order to perform this, we describe how we measure stellar rotation periods from the TESS light curves. To this end we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}}
+which is an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination
 traditional Lomb-Scargle periodograms and wavelet transformations (Hall et al. submitted).
@@
 extracts light curves from the TESS Full-Frame Images \citep[FFIs;][]{feinstein19}.
-We ran \texttt{michael} on all stars from which flares were identified. The estimated
-$P_\textrm{rot}$ were vetted by-eye, from the \texttt{michael} diagnostic plots. In
-total, we robustly measured 1,269 $P_\textrm{rot}$ across our sample of
-3,983 stars, which is $\sim 50\%$.
+
+We ran \texttt{michael} on all stars in our samples from which flares were identified. The estimated
+rotational periods were subsequently vetted by-eye  with the \texttt{michael} diagnostic plots.
+This vetting was implemented to ensure that the measured $P_\textrm{rot}$ was not a harmonic of the true $P_\textrm{rot}$.
+In
+total, we robustly measured rotation periods for 1,847 stars.
 

### 2023-12-19 src/scripts/data_utils.py

@@ -20,7 +20,7 @@ def get_age_ranges(age_ranges):
        `ages[:,2] = upper age error`.
     """
     tab = Table.read(os.path.join(data_dir,
-                                  'llamaradas-estelares_all_parameters_withhotcuts_final_v4.csv'),
+                                  'final_flare_catalog_v6.csv'),
                      format='csv')
 
     ages = np.zeros((len(age_ranges), 3))

### 2023-12-19 src/scripts/flare_distribution.py

@@ -16,13 +16,14 @@ from paths import (
 set_rcparams()
 
 tab = Table.read(os.path.join(data_dir,
-                              'llamaradas-estelares_all_parameters_withhotcuts_final_v4.csv'),
+                              'final_flare_catalog_v6.csv'),
                  format='csv')
 tab = tab[(tab['ed'] > 0) & (tab['age']>0)]
 
 sample = Table.read(os.path.join(data_dir,'moca_sample.csv'), format='csv')
 
-fig, (ax0, ax1, ax2) = plt.subplots(nrows=3, figsize=(6,18))
+#fig, (ax0, ax1, ax2) = plt.subplots(nrows=3, figsize=(6,18))
+fig, (ax0, ax2) = plt.subplots(nrows=2, figsize=(6,12))
 fig.set_facecolor('w')
 
 ed = (tab['ed']*units.min).to(units.s)
@@ -67,6 +68,7 @@ ax0.set_yscale('log')
 ax0.set_xscale('log')
 
 #================== AX1 ========================#
+"""
 prob = prob_colorbar()
 
 img = ax1.scatter(np.log10(erg.value[q]), np.log10(ed.value[q]),
@@ -79,7 +81,7 @@ plt.colorbar(img, label='Probability [%]', cax=cax)
 
 ax1.set_xlabel(r'log$_{10}$(Flare Energy [erg])')
 ax1.set_ylabel(r'log$_{10}$(ED [sec])')
-
+"""
 #================== AX2 ========================#
 teff = teff_colorbar()
 
@@ -94,12 +96,12 @@ plt.colorbar(img, label='log$_{10}$(T$_{eff}$ [K])', cax=cax)
 ax2.set_xlabel(r'log$_{10}$(Flare Energy [erg])')
 ax2.set_ylabel(r'log$_{10}$(ED [sec])')
 
-for ax in [ax1, ax2]:
-    ax.set_xlim(26,35)
+for ax in [ax2]:#, ax1]:
+    ax.set_xlim(27,35)
     ax.set_ylim(-1.65,4.2)
 
 ax0.set_rasterized(True)
-ax1.set_rasterized(True)
+#ax1.set_rasterized(True)
 ax2.set_rasterized(True)
 
 plt.subplots_adjust(hspace=0.3)

### 2023-12-19 src/scripts/prot_histograms.py

@@ -17,7 +17,7 @@ from paths import (
 
 set_rcparams()
 
-tab = Table.read(os.path.join(data_dir, 'combined_v4.csv'),
+tab = Table.read(os.path.join(data_dir, 'combined_prot_flarerate_v6.csv'),
                  format='csv')
 tab = tab[tab['Good'] == 1]
 

### 2023-12-19 src/scripts/truncated.py

@@ -17,11 +17,12 @@ from analysis_utils import logpdf
 set_rcparams()
 
 """ GET THE DATA """
-table = Table.read(os.path.join(data_dir,'rossby_stats.csv'), format='csv')
-lo = np.load(os.path.join(data_dir,'r0_samples_lo_v4.npy'), allow_pickle=True)
-hi = np.load(os.path.join(data_dir,'r0_samples_hi_v4.npy'), allow_pickle=True)
+table = Table.read(os.path.join(data_dir,'rossby_stats_v6.csv'), format='csv')
+lo = np.load(os.path.join(data_dir,'r0_samples_lo_v6.npy'), allow_pickle=True)
+hi = np.load(os.path.join(data_dir,'r0_samples_hi_v6.npy'), allow_pickle=True)
 amp_min = 10**-1.8
 bins = np.logspace(-2,2,100)
+R0 = 0.13617449664429532
 
 
 logasamp = np.log10(np.logspace(np.log10(amp_min), 1.0))
@@ -55,12 +56,12 @@ for i in range(len(dat)):
 axes, pct = [ax, ax], [pct_short_lo, pct_short_hi]
 for i in range(len(axes)):
     if i == 1:
-        labelS = '$R_0 > 0.12$' + '\n'
+        labelS = '$R_0 >$' + str(np.round(R0,3)) + '\n'
         label = r'$\alpha = ' + '{0:.3f}'.format(table['alpha'][i]) + '_{' + \
                 '-{0:.3f}'.format(table['alpha_lo'][i]) + '}^{' + \
                 '+{0:.3f}'.format(table['alpha_hi'][i]) + '}$'
     else:
-        labelS = '$R_0 \leq 0.12$' + '\n'
+        labelS = '$R_0 \leq$' + str(np.round(R0,3)) + '\n'
         label = r'$\alpha = ' + '{0:.3f} \pm {1:.3f}$'.format(table['alpha'][i],
                                                             table['alpha_lo'][i])
     labelA = r'$A_* = ' + '{0:.3f}'.format(table['A'][i]) + '_{' + \
@@ -92,5 +93,5 @@ leg = plt.legend(ncol=2, fontsize=16, markerscale=4,
 for legobj in leg.legendHandles:
     legobj.set_linewidth(5.0)
 
-plt.savefig(os.path.join(figures_dir, 'truncated.pdf'), 
+plt.savefig(os.path.join(figures_dir, 'truncated.pdf'),
             bbox_inches='tight', dpi=300)

### 2023-12-19 src/scripts/yp_rates.py

@@ -22,7 +22,7 @@ cmap = teff_colorbar().reversed()
 ### Load tables and make appropriate data cuts ###
 ##################################################
 flares = Table.read(os.path.join(data_dir,'planet_host_rates.csv'), format='csv')
-tab = Table.read(os.path.join(data_dir,'llamaradas-estelares_all_parameters_withhotcuts_final_v4.csv'),
+tab = Table.read(os.path.join(data_dir,'final_flare_catalog_v6.csv'),
                  format='csv')
 tab = tab[(tab['ed'] > 0) & (tab['age']>0)]
 

### 2024-01-09 src/tex/ms.tex
post holiday changes

@@
 
+%%%%%%% COMMANDS FOR THIS PAPER
 \newcommand{\angstrom}{\mbox{\normalfont\AA}}
+\newcommand{\nflares}{26,355}
+\newcommand{\nflarestars}{3,160}
+\newcommand{\nstars}{6,824}
+\newcommand{\nprot}{1,847}
 
@@
 % Title
-\title{Evolution of Flare Rates in GKM Stars Younger than 300 Myr}
+\title{Evolution of Flare Activity in GKM Stars Younger than 300 Myr over Five Years of TESS Observations}
 
-% Author list
-\author{Adina~D.~ Feinstein}
+\shorttitle{Evolution of young stellar flare rates}
+\shortauthors{Feinstein et al.}
+
+\author[0000-0002-9464-8101]{Adina~D.~Feinstein}
 \altaffiliation{NHFP Sagan Fellow}
-\affiliation{Laboratory for Atmospheric and Space Physics, University of Colorado
-Boulder, UCB 600, Boulder, CO 80309}
+\affiliation{Laboratory for Atmospheric and Space Physics, University of Colorado Boulder, UCB 600, Boulder, CO 80309}
 
@@
 
+\author[0000-0002-1002-3674]{Kevin~France}
+\affiliation{Laboratory for Atmospheric and Space Physics, University of Colorado Boulder, UCB 600, Boulder, CO 80309}
+\affiliation{Department of Astrophysical and Planetary Sciences, University of Colorado, UCB 389, Boulder, CO 80309, USA}
+\affiliation{Center for Astrophysics and Space Astronomy, University of Colorado, 389 UCB, Boulder, CO 80309, USA}
+
+\author[0000-0002-2592-9612]{Jonathan Gagné}
+\affiliation{Planétarium Rio Tinto Alcan, Escape pour la Vie, 4801 av. Pierre-de Coubertin, Montréal, Québec, Canada}
+\affiliation{Institute for Research on Exoplanets, Université de Montréal, Départment de Physique, C.P. 6128 Succ. Centre-ville, Monetréal, QC H3C 3J7, Canada}
+
+\author[0000-0001-7458-1176]{Adam~Kowalski}
+\affiliation{Department of Astrophysical and Planetary Sciences, University of Colorado, UCB 389, Boulder, CO 80309, USA}
+\affiliation{National Solar Observatory, University of Colorado Boulder, 3665 Discovery Drive, Boulder CO 80303, USA}
+
 % Abstract with filler text
@@
 Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with surface magnetic reconnection events.
-Stellar magnetic activity  generally decreases as a function of both age and of Rossby number, $R_0$, a measure of the relative dominance of the convective and rotational dynamos.
-For those reasons, it is worthwhile analyzing the flare population level characteristics for young, rapidly rotating stars.
-With this motivation, we select a sample of stars that are either (i) members, (ii) candidate members or (iii) high-probability of being  members of 26 nearby young moving groups, clusters, or associations all known to be less than 300~Myr old that have been observed by the Transiting Exoplanet Survey Satellite (TESS) at 2-minute cadence.
-With this  sample of $\sim$~\textcolor{red}{n} stars younger than 300~Myr, we present detections and characterizations of the flare properties.
-We identified \textcolor{red}{n} flares originating from \textcolor{red}{n} stars.
-Moreover, we robustly measured the rotation periods of $1,847$~stars.
-Finally, we measure the flare frequency distribution (FFD) slope as a function of both age and spectral type.
-We find the FFD slope, $\alpha$, saturates for all spectral types at $\alpha = -0.5$ and does not evolve over 300~Myr.
-Additionally, we find that $R_0$ and flare rate for stars $t_\textrm{age} = 100 - 300$~Myr are saturated out to $R_0 = 0.12$, which is consistent with other indicators of magnetic activity.
-We find the FFD slope for stars with $R_0 \leq 0.14$ are shallower than stars with $R_0 > 0.14$, suggesting the Coriolis force plays a role in generating more high-energy flares.
+Stellar magnetic activity generally decreases as a function of both age and Rossby number, $R_0$, a measure of the relative dominance of the convective and rotational dynamos.
+However, without young stars have been overlooked in flare studies due to lack of long baseline observations and challenges with flare-detection methods.
+With this motivation, we select a sample of stars that are either (i) members, (ii) candidate members or (iii) have a high-probability of being  members of 26 nearby young moving groups, clusters, or associations all known to be less than 300~Myr old that have been observed by the Transiting Exoplanet Survey Satellite (TESS) at 2-minute cadence.
+With this sample of \nstars\ stars younger than 300~Myr, we identified \nflares\ flares originating from \nflarestars\ stars.
+Moreover, we robustly measured the rotation periods of \nprot~stars.
+We measure the flare frequency distribution (FFD) slope as a function of both age and spectral type and find the FFD slope, $\alpha$, saturates for all spectral types at $\alpha = -0.5$ and is constant over the 300~Myr window studied here.
+Additionally, we find that $R_0$ and flare rate for stars $t_\textrm{age} = 100 - 300$~Myr are saturated out to $R_0 = 0.14$, which is consistent with other indicators of magnetic activity.
 We cross match our targets with \textit{GALEX} and find no correlation between flare rate and Far- and Near-Ultraviolet flux.
-Finally, we compare the flare rates of planet hosting stars to comparable, larger samples of stars and find the majority of these stars are relatively flare quiet.
+We compare the flare rates of planet hosting stars to comparable, larger samples of stars and find the majority of planet-hosting stars are relatively flare quiet.
 This may impact the atmospheric evolution of young short-period exoplanets.
+Finally, we detect evidence of stellar flare variations across five years of TESS data in eleven young stars, likely as a result of longer timescale stellar cycles.
 
@@
 Such events can be used to understand the magnetic activity of other stars \citep{}.
-Additionally, by studying stellar flares we can understand how these short-duration events may impact short-period exoplanet evolution \citep{}.
-While we cannot resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events.
+Additionally, by studying stellar flares we can understand how these short-duration events may impact exoplanet evolution \citep{}.
+While we cannot angularly resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events.
 Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events, e.g.
@@
 
-Photometric observations of stars are more readily available thanks to exoplanet missions, and allow us to statistically characterize flare rates and energies.
+Photometric observations of stars are more readily available thanks to exoplanet transit discovery missions, and allow us to statistically characterize flare rates and energies.
+NASA's \textit{Kepler}, \textit{K2}, and the Transiting Exoplanet Survey Satellite (TESS) missions have provided a wealth of stellar variability data in addition to their primary objective of detecting transiting exoplanets.
 Within time-series photometry, stellar flares can be identified by a sharp rise in the stellar flux and a subsequent exponential decay, corresponding to the cooling rate \citep{}.
-\textit{Kepler} provided long-baseline high-cadence observations used to identify stellar flares.
-There has been extensive studies of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars \citep[e.g.]{Hawley14, silverberg16}.
+\textit{Kepler} \citep{Borucki10} provided long-baseline high-cadence observations used to identify stellar flares.
+There has been extensive studies of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.][]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars \citep[e.g.][]{Hawley14, silverberg16}.
 \cite{davenport19} found that flare activity decreased with increasing rotation period for 347 GKM stars.
 However, the flare frequency distribution (FFD) slope did not change significantly as a function of age.
-As a caveat, the ages of the stars were determined based on their rotation periods alone, relying on the assumption that gyrochronology alone accurately ages stars.
+As a caveat, the ages of the stars were determined based on their rotation periods, relying on the assumption that gyrochronology alone accurately ages stars.
 
-After the failure of two reaction wheels, \textit{Kepler} was repurposed to the \textit{K2} mission \citep{Howell14}.
 \textit{K2} provided 70-day baseline observations for a handful of young stars in groups such as Upper Scorpius,  Pleiades, Hyades, and Praespe clusters.
-\cite{ilin19} analyzed flares K and M stars in these clusters and measured FFD slopes of ...
+\cite{ilin19, ilin21} analyzed flares K and M stars in these clusters and found that the overall flare activity decreased as a function of age.
+This relationship was steeper for more massive stars in the sample.
+\cite{paudel18} surveyed 10 M6 - L0 dwarfs observed with \textit{K2} and found the L0 dwarf had a much shallower FFD than the M dwarfs.
+On average, they found that very young targets, defined by the tangential velocity of the star, overall had more flares.
 
-More recently, the Transiting Exoplanet Survey Satellite \citep[TESS;][]{ricker15} has provided near all-sky photometric observations at 30-minute cadence or less.
-Such an observing strategy has allowed for more detailed studies of young stellar flares from nearby young moving groups and associations, which are disperse in the sky \citep{}.
+More recently, TESS \citep{ricker15} has provided near all-sky photometric observations at 30-minute cadence or less.
+Such an observing strategy has allowed for more detailed studies of young stellar flares from nearby young moving groups and associations, which are disperse in the sky \citep{gagne18}.
+These new data have allowed for detailed studies of individual stars, for example characterizing eight superflares ($E_f > 10^{34}$~erg) on the young star AB Doradus over $\sim 60$ days of continuous observations \citep{schmitt19}.
+
+The 11-year solar activity cycle represents a change in the magnetic activity of the Sun, and manifests itself in a variety of observables e.g., an increase in the total number of sunspots \citep{clette14, kilcik14}, an increase in the number of flares and coronal mass ejections \citep{crossby93, webb94, lin23}, and an increase in the total solar irradiance \citep{lean1987}.
+The majority of insights we have gained in long-term activity cycles on other stars is through photometric monitoring and spectroscopic monitoring \citep{saar99}.
+\cite{lehtinen16} collected 16 to 27 years of B- and V-band photometry for 21 young active solar-type stars.
+They found evidence of long-term stellar activity cycles in 18 targets following as $P_\textrm{rot}/P_\textrm{cycle} \propto R_0^{-1}$, where $P_\textrm{rot}$ is the rotation period, $P_\textrm{cycle}$ is the period of the stellar activity cycle, and $R_0$ is the Rossby number.
+Additionally, 50 years of spectroscopic observations of HD~166620 from the Mount Wilson Observatory and Keck revealed both a $\sim 16$~year periodicity in emission from the core of the \ion{Ca}{2} H and K lines \citep{olah16} and evidence that this star entered a grand minima \citep{baum22}.
+A more complete review on the state of stellar activity cycles can be found by \cite{jeffers23} and \cite{isik23}.
+
+In addition to photometric and spectroscopic observations, solar flares trace the length of the solar activity cycle.
+The high-cadence observations from \textit{Kepler} (4-year baseline) and TESS (currently 5-year baseline) are providing data sufficient for searching for stellar activity cycle from the variations in stellar flare rates.
+\cite{davenport20} demonstrated that the flare rate and FFDs of GJ~1234 has not changed appreciably over 10~years of observations with both \textit{Kepler} and TESS.
+On the other hand, \cite{scoggins19} found that  KIC 8507979, an M3V star, showed a clear decline in flare rate and change in FFD over 4-years of \textit{Kepler} observations.
+While it is not expected to find flare rate and distribution variations in all stars given detection limitations, KIC 8507979 demonstrates the ability to study long-term flare variability as a potential tracer for stellar activity cycles.
 
@@
 In this section, we provide an overview of the methodology associated with this paper.
-The various methods described here are pertinent to the remainder of the paper.
-Specifically, we describe the sample selection in subsection \ref{subsec2:sample}, TESS light curve analysis in \ref{subsec2:TESS_lightcurve}, flare identification in subsection \ref{subsec2:Flareidentification}, flare models in \ref{subsec2:model}, flare quality checks in \ref{subsec2:qualitychecks}, and measurement of stellar rotaiton periods in \ref{subsec:prot}.
+Specifically, we describe the sample selection in subsection \ref{subsec2:sample}, TESS light curve analysis in \ref{subsec2:TESS_lightcurve}, flare identification in subsection \ref{subsec2:Flareidentification}, how we fit for flare parameters in \ref{subsec2:model}, flare quality checks in \ref{subsec2:qualitychecks}, and measuring stellar rotation periods in \ref{subsec:prot}.
 
@@
 
-In this paper, we select a sample of stars that have $<300$ Myr ages based on their affiliation with nearby young moving group, clusters and associations.
-This provides an independant constraint on the age, which is more robust than only using the rotational periods.
-Moreover, we select stars that have been observed with TESS with 2-minute cadence.
-With these criteria, we obtain light curves for a sample of 3,163 young stars in total.
+A primary goal of this paper is to measure the dependence of the stellar flare rates on stellar age.
+Particularly, we are interested in this dependency for stars with ages $1 \leq t_\textrm{age} \leq 300$\,Myr.
+To this end, we used the MOCA Data Base (Gagné et al.
+in prep.) to identify nearby young moving groups, associations, and open clusters with known ages which satisfied our criteria.
+From this database we identified 26~ unique groups from which we created our sample of stars.
+The final selected targets were required to be: (i) confirmed members, (ii) high-likelihood candidate members, or (iii) candidate members.
+Membership to these groups has been primarily determined using kinematic information from \textit{Gaia} \citep{gaia16, gaia18}.
+These rather stringent cuts resulted in a catalog of 30,889 stars across 26 associations.
+We summarize the sample and ages for each association (and therefore star) in Table~\ref{tab:sample}.
 
-With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}.
+%With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}.
 In order to model the flare profile, we employ the analytical model developed by \cite{tovar22}.
 This model is able to simultaneously (i) fit the flares and  (ii) measure the equivalent duration and energy associated with each flare.
-
-A primary goal of this paper is to  measure the evolution of the stellar flare rate and its dependance on the stellar age. Particularly, we are interested in this dependancy for
-stars with ages $1 \leq t_\textrm{age} \leq 250$\,Myr. To this end, we used the MOCA Data Base
-(Gagné et al. in prep.) to identify nearby young moving groups, associations,
-and open clusters with known ages which satisfied our criteria. From this database we identified
- 26~ unique groups from which we created our  sample of stars.
-The final selected targets were required to be: (i) confirmed members, (ii) high-likelihood candidate members, or (iii) candidate members.
-These rather stringent cuts resulted in a
- catalog of 30,889 stars across 26 associations. We summarize
-the sample and   ages for each association (and therefore star)
-in Table~\ref{tab:sample}.
 
@@
 Blanco 1 & 137.1$^{+7.0}_{-33}$ & 428 & 2\\
-Carina  &  45  & 94  & 3\\
+Carina  &  45$\pm 9$  & 94  & 3\\
 Carina-Musca & 32 & 35 & 4\\
@@
 \hline
-Total & & 6,824\\
+Total & & \nstars\\
 \enddata
@@
 
-As described in the previous subsection, we only select stars in our sample for which TESS light curves have been obtained with 2-minute cadance.
-The reason for doing this is so that we are able to resolve and accure accurately measure the energies of flares for each of these stars \citep{howard22}.
-We crossmatched our sample with the TESS Input Catalog (TIC) based on their RA and Dec.
-In order for a star to be considered as a member of the catalog, , we required that  the distance between the target and
-the nearest TIC was within $<1"$.
+As described in the previous subsection, we select stars in our sample for which TESS light curves have been obtained with 2-minute cadence.
+The reason for doing this is so that we are able to resolve and accurately measure the properties of flares for each of these stars \citep{howard22}.
+We cross-matched our sample obtained with the MOCA Database with the TESS Input Catalog (TIC) based on their Gaia DR2 RA and Dec.
+We required that the distance between the target and the nearest TIC target was within $<1"$.
 
-This process provided  a final sample of 5,725 unique targets.
-These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67.
-These are the latest available sectors at the time that this analysis was performed.
-In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions of the final sample.
-It is evident that  many targets exhibit strong tendency for proximitry towards the
+This process provided a final sample of \nstars\ unique targets.
+These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67; Sector 67 was the latest available sectors at the time that this analysis was performed.
+In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions and effective temperatures, $T_\textrm{eff}$, of the final sample.
+We use $T_\textrm{eff}$ as our stellar characterization metric over the standard $M_\star$ because $\sim 600$ stars in our sample are lacking mass information in the TIC.
+It is evident that  many targets exhibit strong tendency for proximity towards the
 northern and southern ecliptic poles (Figure~\ref{fig:sample}). Therefore, many of these targets were observed
-over multiple sectors all of which observed the ecliptic poles. The entirety of the available data yielded  a total of 17,964
-light curves, an average of $\sim 3$ light curves per target (although with significant spread across targets).
+over multiple sectors.
+The entirety of the available data yielded 17,964 light curves processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16}.
+Our sample has an average of $\sim 3$ light curves per target (although with significant spread across targets).
+For our analysis, we used the SPOC-processed SAP\_FLUX.
 
 \begin{figure}[ht!]
-    %\script{sample.py}
+    \script{sample.py}
     \begin{centering}
@@
 
-Once we had the lightcurves for each target, we performed the following procedur to identify stellar flares.
-First, we implemented the machine learning flare-identification methods presented and described in
-\cite{feinstein20}. This method relies on the fact that all flare events
-have similar time-dependent morphologies. These flare-profiles can generally be described as a sharp rise followed by
- an exponential decay in the white light curve. The identification-technique implements  a convolutional neural network (CNN),
-\texttt{stella} \citep{feinstein20}. The neural network was trained to identify flare events in TESS 2-minute data using a catalogue of flare events from
-TESS Sectors 1 and 2 that were validated  by-eye
+Once we had the light curves for each target, we performed the following procedure to identify stellar flares.
+First, we implemented the machine learning flare-identification methods presented and described in \cite{feinstein20}.
+This method relies on the fact that all flare events have similar time-dependent morphologies.
+These flare-profiles can generally be described as a sharp rise followed by an exponential decay in the white light curve.
+This identification-technique implements the convolutional neural network (CNN),
+\texttt{stella} \citep{feinstein20}.
+The neural network was trained to identify flare events in TESS 2-minute data using a catalogue of flare events from TESS Sectors 1 and 2 that were validated  by-eye
 \citep{guenther19_flares}.
@@
 It is therefore relatively insensitive to the absolute flux levels, so long as the inherent noise does not overwhelm the signal itself.
-One advantage of this is that rotational modulation peaks --- which are themselves  driven by
-stellar heterogeneities ---
-are not accidentally identified as flares. This is especially advantageous for our sample of young stars, which  readily exhibit rotational modulatioin and associated peaks  in their light curves.
+This means that rotational modulation peaks --- which are themselves driven by
+stellar heterogeneities --- are not accidentally identified as flares.
+This is especially advantageous for our sample of young stars, which  readily exhibit rotational modulation in their light curves.
 
@@
 methods \citep{chang15}.
+The \texttt{stella} CNN models calculates the probability that a data point in a light curve is associated with a flaring event.
+Specifically, it takes the light curve (time, flux, flux error) as an input and returns an array with values of [0,1], which are treated as the probability a data point is (1) or is not (0) part of a flare.
+We ran every light curve through 10 independent \texttt{stella} models and averaged the outputs to ensure that our statistics were accurate.
+We note that in this processing, the CNN ignores 200-minutes before and after any gaps in the data.
+Therefore, any flares which occur during these times are not identified.
 
-The \texttt{stella} CNN models calculates the probability that a data point in a light curve is associated with a flaring event. Specifically, it taakes the light curve (time, flux, flux error)
-as an input and returns an array with values of [0,1], which are treated as
-the probability a data point is (1) or is not (0) part of a flare. We ran every
-light curve through 10 independant \texttt{stella} models to ensure that our statistics were accurate.
-We then averaged the output probabilities for each 10 model runs to be the final prediction per observation.
-
-In order to identify a single flare event, the \texttt{stella} code uses the
-predictions per data point to group together points.
+In order to identify a single flare event, the \texttt{stella} code uses the predictions per data point to group together points.
 We modified this stage of identification slightly from the original flare-identification method.
@@
 This was motivated by the fact that  sometimes a single-point outlier is assigned a high probability of being a flare.
-Therefore, we simply neglected these events.
+Therefore, we neglected these events.
 We assigned the probability of the whole flare event as the probability of the peak data point.
@@
 \begin{figure}[ht!]
-    %\script{flare_distribution.py}
+    \script{flare_distribution.py}
     \begin{centering}
@@
         \caption{
-            High level summary of the demographics of flares in our sample. Top:
-            The number of flares identified compared to the number of stars in
-            each nearby young moving group, cluster, or association. A one-to-one
-            relationship is expected. Middle: The distribution measured TESS energies
-            and equivalent durations of flares in our sample, colored by the probability
-            of the flare as identified with \texttt{stella}. Bottom: Same as the
-            middle plot, except colored by the $T_\textrm{eff}$ [K] of the star.
+            High level summary of the demographics of flares in our sample.
+Top: The number of flares identified compared to the number of stars in each nearby young moving group, cluster, or association.
+A one-to-one relationship is expected.
+Middle: The distribution measured TESS energies
+            and equivalent durations of flares in our sample, colored by the probability of the flare as identified with \texttt{stella}.
+Bottom: Same as the middle plot, except colored by the $T_\textrm{eff}$ [K] of the star.
 We limit our sample to stars with $T_\textrm{eff} \leq 6000$\,K.
@@
 As described in the previous subsection, flares are well-described in light curves as a sudden increase in flux followed by an exponential decay.
-For this paper, we used the analytical flare model,Llamaradas Estelares which was  presented in
-\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}.
-We used these models to fit the flares and extract the flare parameters in all of the light curves of our sample.
-This model builds upon the model presented
-in \cite{davenport14}. Specifically, it includes the convolution of a Gaussian with a
-double exponential model in the flare profile.
+For this paper, we used the analytical flare model, Llamaradas Estelares which was presented in
+\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}, to fit the flares and extract the flare parameters in all of the light curves of our sample.
+This model builds upon the model presented in \cite{davenport14}.
+Specifically, it includes the convolution of a Gaussian with a double exponential model in the flare profile.
 
-The analytical model is robust in that it is able to accounts for multiple inherent features of flares. Specifically, it can incorporate the flare (i) amplitude,
- (ii) heating timescale, (iii) rapid cooling phase timescale, and (iv) slow cooling phase
-timescale . We implemented a nonlinear least squares
-optimization to fit for the time of the flare peak ($t_\textrm{peak}$),
-full width at half maximum (FWHM), and the amplitude ($A$) of each flare
-in the sample.  We combine the model with a second-order polynomial fit to
-a 1.2-hour baseline before and after the flare  during only the fitting stage.
-This was implemented in order to account for any rotational modulation, and therefore  was particularly relevant for the rapid rotators.
+The analytical model is robust in that it is able to accounts for multiple inherent features of flares.
+Specifically, it can incorporate the flare (i) amplitude, (ii) heating timescale, (iii) rapid cooling phase timescale, and (iv) slow cooling phase timescale.
+We implemented a nonlinear least squares optimization to fit for the time of the flare peak ($t_\textrm{peak}$), full width at half maximum (FWHM), and the amplitude ($A$) of each flare in the sample.
+We combine the model with a second-order polynomial fit to a 1.2-hour baseline before and after the flare  during only the fitting stage.
+This was implemented in order to account for any slope due to rotational modulation, and therefore was particularly relevant for the rapid rotators ($P_\textrm{rot} < 2$~days).
 
-We calculated the equivalent duration, ED, of the flare by performing a numerical integration  of the flare flux with respect to time. We calculate the flare energy, $E_\textrm{flare}$, using,
+We calculated the equivalent duration, ED, of the flare by integrating the quiescent-normalized flare flux with respect to time. We calculate the flare energy, $E_\textrm{flare}$, using,
 
@@
 \end{equation}
-In equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$, where $B_\lambda(T)$ is the Planck function.
-We assume that the flare temperature is 9000~K \citep{}.
+In Equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$, where $B_\lambda(T)$ is the Planck function.
+We assume that the flare temperature is 9000~K \citep{kretzschmar11}.
+Although 900
 
@@
 The \texttt{stella} CNNs were trained on data from TESS Sectors 1 and 2.
-However, the noise properties are variable aross sectors in TESS data.
+However, the noise properties are variable across sectors in TESS data.
 The CNNs are therefore unable to accurately
@@
 We therefore apply additional
-quality checks to ensure our flare sample has little to no contamination
-from other sources.
+quality checks to ensure our flare sample has little to no contamination from other sources.
 
@@
 \end{enumerate}
-We find that when the errors on the first criteria are larger than the cut-offs, the flares are often simply  mischaracterized noise.
+We find that when the errors on the first and fourth criteria are larger than the cut-offs, the flares are often simply mischaracterized noise.
 
@@
 These stars generally tend to have $T_\textrm{eff} > 5000$~K and TESS magnitudes $< 8$.
-Therefore, their light curves are dominated by sharp noisewhich \texttt{stella} often mischaracterizes as flares.
-
-As a final cut, the sample only includes events that have  a probability $P \geq 90\%$ of being
-a true flare.
-After performing these additional checks, we obtain a final flare sample of \textcolor{red}{n}~flares originating from \textcolor{red}{n} stars (Figure~\ref{fig:flare_distribution}).
-\textcolor{red}{n}\% of the flares have probabilities of $P \geq 90\%$ of being true; \textcolor{red}{n}\% of the flares have probabilities of $P \geq 99\%$ of being true.
+Therefore, their light curves are dominated by sharp noise which \texttt{stella} often mischaracterizes as flares.
+As a final cut, the sample only includes events that have  a probability $P \geq 98\%$ of being
+a true flare. After performing these additional checks, we obtain a final flare sample of \nflares\ flares originating from \nflarestars\ stars (Figure~\ref{fig:flare_distribution}).
 
 \subsection{Measuring Rotation Periods}\label{subsec:prot}
-In this paper we have two  primary goals. The first is to improve our understanding of flare statistics across
- ages for young stars. \citet{seligman22} demonstrated that stars with low Rossby numbers $R_0 < 0.13$ exhibit
-shallower flare frequency distribution slopes. These shallower slopes are caused by  an excess of  high energy flares compared to lower energy flares
-originating from these sources.  In addition to improving flare statistics, we  aim to expand the sample for which flare frequency slope and  rossby number (from $P_\textrm{rot}$) have been measured.
 
-In order to perform this, we describe how we measure stellar rotation periods from the TESS light curves. To this end we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}}
-which is an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination
-traditional Lomb-Scargle periodograms and wavelet transformations (Hall et al. submitted).
-\texttt{michael} measures $P_\textrm{rot}$ using the \texttt{eleanor} package, which
-extracts light curves from the TESS Full-Frame Images \citep[FFIs;][]{feinstein19}.
+In addition to understanding flare statistics across young stars, we measure the rotation periods, $P_\textrm{rot}$ of stars in our sample and search for correlations between $P_\textrm{rot}$ and Rossby number, $R_0$.
+\citet{seligman22} demonstrated that stars with low Rossby numbers $R_0 < 0.13$ exhibit shallower flare frequency distribution slopes.
+These shallower slopes are caused by  an excess of  high energy flares compared to lower energy flares originating from these sources.
 
-We ran \texttt{michael} on all stars in our samples from which flares were identified. The estimated
-rotational periods were subsequently vetted by-eye  with the \texttt{michael} diagnostic plots.
-This vetting was implemented to ensure that the measured $P_\textrm{rot}$ was not a harmonic of the true $P_\textrm{rot}$.
+In order to perform this, we describe how we measure stellar rotation periods from the TESS light curves.
+To this end we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}}, an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination traditional Lomb-Scargle periodograms and wavelet transformations (Hall et al.
+submitted).
+\texttt{michael} measures $P_\textrm{rot}$ using the \texttt{eleanor} package, which extracts light curves from the TESS Full-Frame Images \citep[FFIs;][]{feinstein19}.
+
+We ran \texttt{michael} on all stars in our samples from which flares were identified.
+The estimated rotational periods were subsequently vetted by-eye  with the \texttt{michael} diagnostic plots.
+This vetting was implemented to ensure that the measured $P_\textrm{rot}$ was not a harmonic of the true $P_\textrm{rot}$ or that the period is from an occulting companion.
 In
-total, we robustly measured rotation periods for 1,847 stars.
+total, we robustly measured rotation periods for \nprot\ stars. Additionally, we identified 17 eclipsing binaries or potentially new planet candidates.
 
-\section{Results}\label{sec:results}
+\section{Flare Rates of Young Stars}\label{sec:results}
 
-We analyze our new flare sample from three perspectives. First, we perform the standard
-FFD fitting of a power-law to the distribution of flare energies. Second, we fit the FFD with the
-prescription in \cite{gershberg72}, which fits for both the FFD slope and y-intercept.
-Third, we fit a truncated power-las to the distribution of flare amplitudes, to determine
-if there is a correlation between $R_0$ and flare distributions.
+In this section, we use the previous methodology to estimate the flare rates of the young stars in our sample.
+We implement three main steps in this analysis.
+First, we perform the standard FFD fitting of a power-law to the distribution of flare energies described in subsection \ref{subsec:energy_ffd}.
+Next, to determine if there is a correlation between $R_0$ and flare distributions we fit a truncated power-law to the distribution of flare amplitudes in subsection \ref{subsec3_truncated}.
+Finally we fit the relationship between $R_0$ and flare rates in subsection \ref{subsec:rossby}.
 
-The number of stars, and consequently flares, per each association varied greatly,
-due to the limited number of stars observed at TESS 2-minute cadence. Therefore, instead
-of measuring FFD properties as a function of association, we opted to group stars
-by effective temperature, $T_\textrm{eff}$, and average adopted association age. We
-grouped stars in the following $T_\textrm{eff}$ space: M-stars below the fully
-convective boundary ($T_\textrm{eff} = 2300 - 3400$\,K), early type M-stars
-($T_\textrm{eff} = 3400 - 3850$\,K), late K-stars ($T_\textrm{eff} = 3850 - 4440$\,K),
-early K-stars ($T_\textrm{eff} = 4440 - 5270$\,K), and G-stars ($T_\textrm{eff} = 5270 - 5930$\,K).
-We did not include any stars hotter than $T_\textrm{eff} > 5930$\,K, as these stars
-are dominated by noise in the TESS observations. Additionally, we grouped stars
-in the following age space: $4-10$\,Myr, $10-20$\,Myr, $20-40$\,Myr, $40-50$\,Myr,
-$70-80$\,Myr, $120-150$\,Myr, and $150-300$\,Myr. We note that there is a gap in
-age from $50-70$\,Myr, which could be expanded with the identification of more
-associations in this age range. However, for the purposes of this work, we do not
-include additional sources which may fall in this age range.
+The number of stars, and consequently the number of flares in  each association varied greatly (Figure~\ref{fig:flare_distribution}).
+This was primarily caused by the limited number of stars that had been observed at 2-minute cadence in TESS.
+We therefore did not measure FFD properties as a function of association.
+Instead, we group stars by $T_\textrm{eff}$ and average adopted association age.
 
-\subsection{Standard Power-Law Fits}\label{subsec:stats}
+We define the following spectral type bins by $T_\textrm{eff}$:
+ \begin{itemize}
+     \item M-stars below the fully convective boundary ($T_\textrm{eff} = 2300 - 3400$\,K)
+     \item  early type M-stars ($T_\textrm{eff} = 3400 - 3850$\,K)
+     \item  late K-stars ($T_\textrm{eff} = 3850 - 4440$\,K)
+     \item early K-stars ($T_\textrm{eff} = 4440 - 5270$\,K)
+     \item G-stars ($T_\textrm{eff} = 5270 - 5930$\,K)
+ \end{itemize}
+We did not include any stars hotter than $T_\textrm{eff} > 5930$\,K.
+These hot stars generally exhibit light curves  dominated by noise in the TESS observations.
+Additionally, we grouped stars in the following age space: $4-10$\,Myr (including Upper Scorpius and TW Hydrae), $10-20$\,Myr, $20-40$\,Myr, $40-50$\,Myr, $70-80$\,Myr, $120-150$\,Myr, and $150-300$\,Myr.
+We note that there is a gap in age from $50-70$\,Myr, which could be expanded with the identification of more associations in this age range.
 
-From the $T_\textrm{eff}$ and age bins described above, we binned the flares in each
-subgroup and fit their FFD slopes, approximated as a power-law. Flares were binned
-into 25 bins in log-space from $10^{27} - 10^{35}$\,erg. We fit the FFDs from the
-energy bin with the maximum flare rate and energies higher than that. We opt to do
-this as bins of lower energies may be incomplete, and the turnover in the FFD cannot
-be accurately modeled as a power-law.
+\subsection{Standard Power-Law Fits}\label{subsec:energy_ffd}
 
-We fit the FFD using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}
-and fit for the slope, $\alpha$, y-intercept, $b$, and an additional noise term, $f$, which
-accounts for an underestimation of the errors on each bin. We initialized the MCMC fit with
-300 walkers and ran our fit over 5000 steps. Upon visual inspection, we discarded the
-first 100 steps; onwards the steps were fully burned-in. The full FFDs are presented
-in Figure~\ref{fig:simple_ffd_all}, along with 100 samples from the MCMC fit. The measured
-FFD slopes, $\alpha$ are presented in Figure~\ref{fig:mcmc_results}. We approximate the
-error on the slope as the lower 16\textsuperscript{th} and upper 84\textsuperscript{th}
-percentiles from the MCMC fit.
-
-\begin{figure*}[ht!]
+\begin{figure*}[bht!]
     \script{mcmc_results.py}
     \begin{centering}
-        \includegraphics[width=3.4\textwidth, trim={0 0 30mm 0}, clip]{figures/mcmc_results.pdf}
+        \includegraphics[width=\textwidth, trim={0 0 60cm 0}, clip]{figures/mcmc_results.pdf}
         \caption{
-            Measured flare-frequency distribution slopes, $\alpha$, as a function
-            of stellar effective temperature, $T_\textrm{eff}$ and age.
+            Measured flare-frequency distribution slopes, $\alpha$, as a function of stellar effective temperature, $T_\textrm{eff}$ and age.
+We measured these FFDs with respect to flare energy.
+We find the FFD slopes as a function of energy are consistent with $\alpha = -0.6 ~\textrm{to} -0.2$ for stars $< 300$~Myr in TESS observations.
+A shallower FFD slope is indicative of more high-energy flares.
+We present all measured FFDs in Figure~\ref{appendix:supp_ffds}, and all measured slopes and errors in Table~\ref{tab:best_fits}.
+We find the shallowest slopes for stars $T_\textrm{eff} = 3400 - 4440$\,K, with a range from $\alpha = -0.44~ \textrm{to} -0.22$.
+We do not include the results for stars $T_\textrm{eff} = 3850 - 4440$\,K and $t_\textrm{age} = 20 - 40$\,Myr as this bin contained only six stars with detected flares.
+We present the average results of measured FFD slopes for the Hyades, Pleiades, and Praesepe clusters from \cite{ilin21} as black squares.
+We present the results of measured FFD slopes for all TESS primary mission targets in white circles \citep{Feinstein22}.
+We present these data as ``field-age".
+We discuss what drives the difference between our sample and \cite{ilin21} in Section~\ref{subsec:energy_ffd}.
         }
@@
 
-There is a $3\sigma$ discrepancy between the FFD slope measured in \cite{ilin21}
-and the work presented here at ages $\sim 120$\,Myr. This discrepancy could be the
-result of several factors. First, \cite{ilin21} used the \textit{K2} 30-minute
-light curves. This would result in a sample biased towards the highest-energy flares which
-could be sampled at this cadence. Our flare detection method is less-biased towards
-the low-energy flares due to the 2-minute cadence from TESS and our flare detection
-algorithm. Second, our sample has $\sim 2\times$ the number
-of stars and $\sim 7\times$ the number of flares than their sample. This could
-result in a more complete FFD compared to previous work.
+We fit the stars FFD slopes, approximated as a power-law, using the $T_\textrm{eff}$ and age bins described above.
+Flares were binned into 25 bins in log-space from $10^{27} - 10^{35}$\,erg.
+We perform the FFD  fits using the energy bin with the maximum flare rate as the base level, and then with all flare energies higher than that.
+We perform this cut  because lower energy bins may be incomplete, exhibiting a turnover in the FFD at lower energies.
+Moreover, the energy turnover in the FFD cannot be accurately modeled as a power-law.
 
-\subsection{Truncated Power-Law Fits}
+We fit the FFD using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}.
+Specifically, we fit for the slope, $\alpha$, y-intercept, $b$, and an additional noise term, $f$.
+This noise term  accounts for an underestimation of the errors in each bin.
+We initialized the MCMC fit with 300 walkers and ran our fit over 5000 steps.
+We discarded the first 100 steps upon visual inspection, after which the steps were fully burned-in.
 
-We follow the prescription presented in \cite{seligman22}. Namely, we fit a truncated
-power-law distribution of the form
+The full FFDs are presented in Figure~\ref{fig:simple_ffd_all}, along with 100 samples from the MCMC fit. The measured
+FFD slopes, $\alpha$, are presented in Figure~\ref{fig:mcmc_results}. We approximate the error on the slope as the lower 16\textsuperscript{th} and upper 84\textsuperscript{th}
+percentiles from the MCMC fit.
 
-\begin{equation}
-  dp/dA \propto A^{-\alpha_T} e^{-A/A_*}
-\end{equation}
+There is a $1-3\sigma$ discrepancy between the FFD slope measured in \cite{ilin21} and the work presented here at ages $\sim 120$\,Myr ($\alpha$ ranges from $-1.32 \pm 0.19 ~\textrm{to} -0.91 \pm 0.18$, depending on the $T_\textrm{eff}$ bin).
+\cite{ilin21} used the \textit{K2} 30-minute light curves for their analysis, compared with our TESS 2-minute light curves.
+Additionally, our sample has $\sim 2 \times$ the number of stars and $\sim 7 \times$ the number of flares than \cite{ilin21}.
+First, we test if these differences are driven by differences in sample binning.
+We reevaluate the FFDs assuming the $T_\textrm{eff}$ bins presented in Table 3 of \cite{ilin21}.
+We find $\alpha$ remains consistent with our presented values to within $\sim 1\sigma$ of the nearest temperature bin.
+Second, we reevaluate the FFDs assuming the total number of flares fit in \cite{ilin21}.
+Our sample has $\sim 2\times$ the number of stars and $\sim 7\times$ the number of flares than their sample.
+We draw $n_\textrm{fit, Ilin et al.
+(2021)}$ \citep[last column in Table 3 of ][]{ilin21} flares from our sample 100 times without replacement, refit the FFD, and take the average FFD slope from that sub-sample of flares to our results.
+We find $\alpha$ remains consistent with our presented values to $\sim 2\sigma$.
+We note that in most cases $n_\textrm{fit, Ilin et al.
+(2021)} < n_\textrm{fit, this work}$.
+Therefore, the increased disagreement in $\alpha$ could be due to smaller sample sizes.
 
-where $A$ is the amplitude of the flare, $A_*$ is a flare amplitude cutoff parameter
-and $\alpha_T$ is the slope, rather than
-$\alpha$. We fit the slopes using the MCMC method implemented in \texttt{emcee}
-\citep{goodman10, emcee}, using the log-likelihood function in \cite{seligman22}.
-We fit for $A_*$ and $\alpha_T$. We initialized the MCMC fit with textcolor{red}{n}
-walkers and evaluated the fit over textcolor{red}{n} steps. The first textcolor{red}{n}
-steps were discarded upon visual inspection. The results are presented in Figure~\ref{fig:truncated}.
+Additionally, we test if the difference in $\alpha$ is driven by the cadence differences between \textit{K2} (30-minute) and TESS (2-minute).
+We bin all of the flares in our sample down the 30-minute cadence, re-fit for flare $A$ and ED, and recalculate the flare energy.
+We re-fit the FFD for this altered sample and measure an FFD slopes consistent to $\sim 1 \sigma$ with our presented in this work.
+Therefore, the discrepancy seen here is not driven by observational differences between \textit{K2} and TESS.
 
-\begin{figure}[ht!]
-    \script{truncated.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/truncated.pdf}
-        \caption{
-            Flare frequency distributions, as a function of flare amplitude, for stars with $R_0 \leq 0.12$ (red) and stars with $R_0 > 0.12$ (black).
-We present the best-fit model, and the best-fit values of the model slope and normalization factor in the legends.
-Our sample of $R_0 \leq 0.12$ includes 13,132 flares from 800 stars; our sample of $R_0 > 0.12$ includes 5,603 flares from 747 stars.
-We find the stars with smaller Rossby numbers have shallower slopes, consistent with more, high-energy flares and potentially larger convective regions \citep{seligman22}.
-        }
-        \label{fig:truncated}
-    \end{centering}
-\end{figure}
+Finally, we test if the differences are driven by the energy ranges fit over.
+The CNN-based flare detection algorithm has previously been demonstrated to be less-biased against lower energy flares.
+Like this work, \cite{ilin21} fits the FFD across flare energies which are not affected by a reduced efficiency in the low-energy flare detection.
+In energy space, these fits begin between $E_f = 10^{32-33}$~erg, compared to our fits which begin between $E_f = 10^{31-32}$~erg (Figure~\ref{appendix:supp_ffds}).
+When we limit our sample to $E_f \geq 10^{32.5}$~erg, we find the FFD slopes become \textit{steeper} and more consistent with $alpha$ presented in \cite{ilin21}.
+Therefore, the difference in $\alpha$ between this work and \cite{ilin21} for stars with $t_\textrm{age} = 120 - 150$~Myr is driven by the lower energy flares, with which we are more complete to with TESS than \textit{K2}.
 
-\subsection{Flare Rates Compared to $R_0$}
+The measured FFD slopes are shallower than those measured using smaller samples of young stars.
+\cite{jackman21} fit the three FFDs for M3-M5, M0-M2, and K5-K8 stars younger than 40~Myr that had been observed with Next Generation Transit Survey.
+They measured slopes of $0.94 \pm 0.04$, $0.69 \pm 0.05$, $0.82 \pm 0.14$ per bin, which each contained $\leq 120$~flares.
+It is also worth noting that the slopes measured here are based on up to an order of magnitude more flares per fit.
 
-The Rossby number, $R_0$, is a term which marginalizes over several properties which are known to
-affect the stellar dynamo, such as the rotation period and stellar mass. We convert our measured
-rotation periods to $R_0$, which is defined as $R_0 = P_\textrm{rot}/\tau$, where $\tau$ is the
-convective turnover time. We approximate $\tau$ following the prescription in \cite{wright11}. We
-equate the flare rates for individual stars as
+\subsection{Flare Rate Dependence on Rossby Number}\label{subsec:rossby}
 
-\begin{equation}\label{eq:fr}
-  \mathcal{R} = \frac{1}{t_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)
-\end{equation}
-
-where $\mathcal{R}$ is the flare rate in units of day$^{-1}$, $t_\textrm{obs}$ is the total amount of time a target was
-observed with TESS, and $p_i$ is the probability that flare $i$ is a true flare as assigned by \texttt{stella}.
-We compare the calculated $R_0$ to measured flare rates for all stars we measured $P_\textrm{rot}$ for. The
-results are presented in Figure~\ref{fig:prot_histograms}.
-
-\begin{figure*}[ht!]
+\begin{figure*}[htb!]
     \script{prot_histograms.py}
@@
 
-We evaluate the relationship between age, spectral type, flare rate, and $R_0$. We divide the sample between stars
-younger and older than 50~Myr, which roughly correlates to the age at which GKM stars turn onto the main sequence.
-For stars younger than 50~Myr, we find the flare rate slightly decreases with increasing $R_0$, although there is a
-significant amount of scatter in this relationship. For stars between $50 - 250$~Myr, we see this relationship much
-clearer. For M stars, we see minimal evolution in both average flare rate and $R_0$ between the two samples. For K
-stars, we see $R_0$ evolving over the first 250~Myr, while the scatter in the flare rate decreases. For G stars, we
-see the scatter in $R_0$ decreasing, and the average flare rate across the sample decreases. We present a compiled histogram
-for all stars in our sample in the right column of Figure~\ref{fig:prot_histograms}.
+The Rossby number, $R_0$, is a parameter which marginalizes over several properties which are known to affect the stellar dynamo, such as the rotation period and stellar mass.
+Specifically, in the context of stellar dynamo the Rossby number indicates the dominance of the convective verses rotational dynamo.
+It is defined as $R_0 = P_\textrm{rot}/\tau$, where $\tau$ is the convective turnover time.
+We convert our measured rotation periods to $R_0$,  approximating $\tau$ following the prescription in \cite{wright11}.
+We
+equate the flare rates, $\mathcal{R}$, for individual stars as
 
-To better understand this trend, we fit three types of functions: (i) a constant value, (ii) a single power law, and
-(iii) a piece-wise function consisting of a constant value and a power law. For (iii), we computed these fits across a range
-of $R_0$ for where the turnover should occur. We binned the cumulative dataset consisting of all GKM stars into 50 evenly-spaced bins
-in log-space from $log_{10}(R_0) = [-2, 0]$. We computed the $\chi^2$ between
-each of these fits and the data. For stars $4.5 - 50$~Myr, we find the distribution is best-fit with a single
-power law with slope $m = -0.243 \pm 0.043$ and y-intercept $b = -1.221 \pm 0.061$. Converting the $\chi^2$ to a standard
-deviation, we find a single fit is preferred by $\sim 3\sigma$. For stars $50 - 250$~Myr, we find the distribution
-is best-fit with a piece-wise function of the form
+\begin{equation}\label{eq:fr}
+  \mathcal{R} = \frac{1}{t_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)\,.
+\end{equation}
+In Equation (\ref{eq:fr}), $\mathcal{R}$ is the flare rate in units of day$^{-1}$, $t_\textrm{obs}$ is the total amount of time a target was observed with TESS, and $p_i$ is the probability that flare $i$ is a true flare as assigned by \texttt{stella}.
+We compare the calculated $R_0$ to measured flare rates for all stars we measured $P_\textrm{rot}$ for. The results are presented in Figure~\ref{fig:prot_histograms}.
 
-\begin{equation}
+From these results, we are able to evaluate the dependence of the flare rate on age, spectral type,  and $R_0$.
+We split the sample between stars younger and older than 50~Myr.
+This age roughly correlates to the age at which GKM stars turn onto the main sequence.
+The flare rate of stars younger than 50~Myr slightly decreases with increasing $R_0$.
+However, there is a significant amount of scatter in this relationship.
+
+As can be seen by comparing the upper and  lower panels in Figure ~\ref{fig:prot_histograms}, the flare rate dependence on Rossby number is most evident in older, more massive stars  between $50 - 300$~Myr.
+For M stars, we see minimal evolution in both the average flare rate and $R_0$ between the two samples.
+For K stars,  $R_0$ evolves more dramatically during the first 250~Myr while the scatter in the flare rate decreases.
+For G stars, the scatter in $R_0$ decreases  and the average flare rate across the sample decreases.
+We present a compiled histogram for all stars in our sample in the right column of Figure~\ref{fig:prot_histograms}.
+
+To better understand this trend, we fit three functions to the flare rate Rossby number parameter space: (i) a constant value, (ii) a single power law, and (iii) a piece-wise function consisting of a constant value and a power law.
+We computed the $\chi^2$ between each of these fits and the data.
+For (iii), we fit for where the $R_0$ turnover should occur by computing the $\chi^2$ across a range of $R_0 = [0.09, 0.18]$.
+We weighted the data points based on the density of points in a given bin (Figure~\ref{fig:prot_histograms}).
+For stars $4.5 - 50$~Myr, we find the distribution is best-fit with a single power law with slope $m = -0.102 \pm 0.018$ and y-intercept $b = -0.660 \pm 0.017$.
+For stars $50 - 250$~Myr, we find the distribution is best-fit with a piece-wise function of the form
+
+\begin{equation}\label{eq:piecewiseft}
   \mathcal{R} =
@@
   \begin{array}{ll}
-        C & R_0 \leq 0.15 \\
-        10^b * R_0^m  & R_0 > 0.15 \\
+        C & R_0 \leq 0.136 \\
+        10^b * R_0^m  & R_0 > 0.136 \\
   \end{array}
 \end{equation}
+In Equation (\ref{eq:piecewiseft}), $\mathcal{R}$ is the flare rate, $C = 0.269 \pm 0.007$, $m = -0.612 \pm 0.039$, and $b = -1.113 \pm 0.035$.
+The location of the turnover is consistent  with what has been measured in other observations of magnetic saturation for partially and fully convective stars \citep[e.g.
+$L_X/L_\textrm{bol}$; ][]{wright18}.
 
-where $\mathcal{R}$ is the flare rate, $C = 0.126 \pm 0.006$, $m = -0.986 \pm 0.119$, and $b = -1.687 \pm 0.078$.
-We test how our bin size affected our $R_0$ turnover. To do this, we refit our data assuming binning from $20 - 100$
-bins and find $R_0$ to be consistent with $R_0 = 0.15 \pm 0.02$. The location of the turnover is consistent to
-within $1\sigma$ with what has been seen in other observations of magnetic saturation for partially and
-fully convective stars \citep[e.g. $L_X/L_\textrm{bol}$; ][]{wright18}.
+A similar relationship was discussed in \cite{Davenport16}.
+With a sample of 851,168 flares detected in both \textit{Kepler} 1- and 30-minute cadence data, \cite{Davenport16} found that the relationship between Rossby number and relative flare luminosity could be fit by a broken power law, with a break at $R_0 = 0.03$ and a slope of $\sim -1$ dominating higher $R_0$.
+While the metrics used between \cite{Davenport16} and this paper are different, both suggest a saturation in flares for stars with low $R_0$.
+Additionally, \cite{medina20} found a broken power-law relationship between $R_0$ and the flare rate for flares with $E_f > 3.16 \times 10^{31}$\,erg, the sample's completeness threshold.
+\cite{medina20} analyzed light curves of 419 low-mass ($M_\star = 0.1 - 0.3 M_\odot$) main-sequence stars in the Solar neighborhood as observed by TESS.
+This study found that the flare rate saturates at $log(\mathcal{R}) = -1.30 \pm -0.08$ for $R_0 < 0.1$ and rapidly declines for $R_0 > 0.1$.
+While neither of these previous studies allow for a direct comparison to our results, given the differences in sample selection, all point towards evidence of flare rate saturation for stars with low $R_0$ and a steep drop-off in flare rate for stars with higher $R_0$.
+
+\subsection{Truncated Power-Law Fits}\label{subsec3_truncated}
+
+We search for evidence of variations of the FFDs as a function of Rossby number, $R_0$.
+This is motivated by the data  presented in \cite{seligman22}.
+In that work, they  modeled flares driven by magnetic reconnection events driven by rotational forces as well as convective dynamo.
+\cite{seligman22} found that stars with $R_0 < 0.13$ exhibited shallower FFD slopes than stars with $R_0 \geq 0.13$ to several sigma significance.
+The differences in the FFDs were indicative of relatively more high-energy flares to low-energy flares.
+This was interpreted as evidence of a more dominant rotational dynamo compared to the convective dynamo, which preferentially produced longer magnetic braids in the stellar coronae.
+
+In this subsection, we test this theory with a much larger sample of stars (\nprot\ instead of $807$ stars).
+We fit the distributions separated by the fitted $R_0$ presented in Section~\ref{subsec:rossby}.
+In order to perform the fits, we follow the prescription described in greater detail in \cite{seligman22}.
+Here, we provide a brief summary of the prescription.
+Specifically, we fit a truncated power-law distribution of the form,
+
+\begin{equation}\label{eq:dpda}
+  dp/dA \propto A^{-\alpha_T} e^{-A/A_*}\,.
+\end{equation}
+In Equation (\ref{eq:dpda}),  $A$ is the amplitude of the flare, $A_*$ is a flare amplitude cutoff parameter and $\alpha_T$ is the slope, rather than $\alpha$.
+We fit the slopes using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}.
+We used the log-likelihood function in \cite{seligman22} and  fit for $A_*$ and $\alpha_T$.
+We initialized the MCMC fit with 200 walkers and evaluated the fit over 5000 steps.
+The first 1000 steps were discarded upon visual inspection.
+The results are presented in Figure~\ref{fig:truncated}.
+
+\begin{figure}[ht!]
+    \script{truncated.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/truncated.pdf}
+        \caption{
+            Flare frequency distributions, as a function of flare amplitude, for stars with $R_0 \leq 0.12$ (red) and stars with $R_0 > 0.12$ (black).
+We present the best-fit model, and the best-fit values of the model slope and normalization factor in the legends.
+Our sample of $R_0 \leq 0.12$ includes 13,132 flares from 800 stars; our sample of $R_0 > 0.12$ includes 5,603 flares from 747 stars.
+We find the stars with smaller Rossby numbers have shallower slopes, consistent with more, high-energy flares and potentially larger convective regions \citep{seligman22}.
+        }
+        \label{fig:truncated}
+    \end{centering}
+\end{figure}
+
+We find that stars with $R_0 \leq 0.136$ have a best-fit slope of $\alpha_T = 1.076 \pm 0.020$, while stars with larger $R_0$ have a best-fit slope of $\alpha_T = 1.604 \pm 0.040$.
+\textcolor{red}{fill out more.}
 

### 2024-01-09 src/scripts/flare_distribution.py

@@ -97,7 +97,7 @@ ax2.set_xlabel(r'log$_{10}$(Flare Energy [erg])')
 ax2.set_ylabel(r'log$_{10}$(ED [sec])')
 
 for ax in [ax2]:#, ax1]:
-    ax.set_xlim(27,35)
+    ax.set_xlim(27 ,35)
     ax.set_ylim(-1.65,4.2)
 
 ax0.set_rasterized(True)

### 2024-01-09 src/scripts/mcmc_results.py

@@ -27,7 +27,7 @@ path = os.path.join(data_dir, 'mcmc_fits/best_fits')
 fits = np.sort([os.path.join(path, i) for i in os.listdir(path)])
 
 # Initialize the figure
-fig, ax = plt.subplots(figsize=(14,5))
+fig, ax = plt.subplots(figsize=(10,3))
 
 norm = matplotlib.colors.Normalize(vmin=temp_ranges[0][0],
                                    vmax=temp_ranges[-1][1])
@@ -60,7 +60,7 @@ for i, fn in enumerate(fits):
                  xerr=[ages[:,1][q], ages[:,2][q]],
                  yerr=[dat[0][:,1][q], dat[0][:,2][q]],
                  marker='o', linestyle='', color=hexnum,
-                 label=label, zorder=-i)
+                 label=label+'K', zorder=-i)
 
 #####################################
 # Plot data from Ilin et al. (2020) #
@@ -72,7 +72,8 @@ plt.errorbar(695, np.nanmedian(hyades_slopes),
              color='k', marker=imarker)
 
 pleiades_slopes = -np.array([2.13, 2.06, 2.06, 1.99, 2.32, 1.92, 1.91]) + 1
-plt.errorbar(127.4, np.nanmedian(pleiades_slopes),
+plt.errorbar(127.4,
+             np.nanmedian(pleiades_slopes),
              xerr=8, yerr=np.nanstd(pleiades_slopes),
              color='k', marker=imarker)
 
@@ -90,13 +91,13 @@ plt.errorbar(np.full(5, 2000),
              color='w', marker='o', linestyle='', label='Feinstein et al. (2022)')
 
 plt.legend(bbox_to_anchor=(0., 1.02, 1., .102), loc=3,
-           ncol=3, mode="expand", borderaxespad=0.,
-           markerscale=2)
+           ncol=4, mode="expand", borderaxespad=0.,
+           markerscale=2, fontsize=12)
 
 plt.xscale('log')
 plt.ylim(-1.8, 0.0)
-plt.xlabel('Age [Myr]', fontsize=24)
-plt.ylabel('Flare Frequency\nDistribution Slope, ' + r'$\alpha$', fontsize=24)
+plt.xlabel('Age [Myr]', fontsize=20)
+plt.ylabel('Flare Frequency\nDistribution Slope, ' + r'$\alpha$', fontsize=20)
 
 ax.set_rasterized(True)
 

### 2024-01-09 src/scripts/simple_ffd_all.py

@@ -13,7 +13,7 @@ pwd2 = os.path.join(data_dir, 'mcmc_fits/fitted_data')
 sample_files = np.sort([os.path.join(pwd1, i) for i in os.listdir(pwd1)])
 data_files = np.sort([os.path.join(pwd2, i) for i in os.listdir(pwd2)])
 sample_sizes = np.load(os.path.join(data_dir,
-                                    'mcmc_fits/mcmc_sample_sizes_v4.npy'),
+                                    'mcmc_fits/mcmc_sample_sizes_v6.npy'),
                        allow_pickle=True).item()
 
 ## Setup the figure ##

### 2024-01-09 src/tex/ms.tex
updated references

@@
 
+\correspondingauthor{Adina~D.~Feinstein;\\ \twitter{afeinstein20}; \github{afeinstein20}} \email{adina.feinstein@lasp.colorado.edu}
+
 % Abstract with filler text
@@
 
-Stellar flares are the radiation component of magnetic reconnection events \citep{}.
-Such events are readily seen on the Sun \citep{}, particularly now as we enter a maximum in the solar cycle \citep{}.
-Such events can be used to understand the magnetic activity of other stars \citep{}.
-Additionally, by studying stellar flares we can understand how these short-duration events may impact exoplanet evolution \citep{}.
+Stellar flares are the radiation component of magnetic reconnection events \citep{benz10}.
+Such events are readily seen on the Sun \citep{carrington1859, lu91, fletcher11}, particularly now as we enter a maximum in the solar cycle \citep{webb94}.
+Such events can be used to understand the magnetic activity of other stars \citep{feigelson99, berdyugina05, kowalski10, feinstein22_criticality}.
+Additionally, by studying stellar flares we can understand how these short-duration events may impact exoplanet evolution \citep{france16, guenther19_flares, chen21}.
 While we cannot angularly resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events.
 Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events, e.g.
-coronal mass ejections \citep{} or proton beams \citep{}.
-They can also inform our understanding of stellar plasma is displaced during these events \citep{}.
+coronal mass ejections \citep{argiroffi19, vida19} or proton beams \citep{orrall76, woodgate92}.
 

### 2024-01-15 src/tex/ms.tex
newfits

@@
 \affiliation{National Solar Observatory, University of Colorado Boulder, 3665 Discovery Drive, Boulder CO 80303, USA}
-
-\correspondingauthor{Adina~D.~Feinstein;\\ \twitter{afeinstein20}; \github{afeinstein20}} \email{adina.feinstein@lasp.colorado.edu}
 
@@
 
-Miscellaneous figures and such that people might want but I don't need to show
+Here, we present all of our best-fit slopes and intercepts for various flare-frequency distributions (FFDs) fit throughout this work.
+We include our fits outlined in Sections~\ref{subsec:energy_ffd}.
+We present the FFDs as a function of energy in Figure~\ref{fig:simple_ffd_all}.
+We show 100 random draws from our MCMC fitting to these distributions as orange lines.
+We fit each distribution with $E > 10^{29}$\,erg, which roughly represents the turnover in each distribution.
+We do not fit the slope for $T_\textrm{eff} = [3850 - 4440]$~K at 20 -- 40~Myr due to our limited sample size (6 stars in total).
 
@@
 
+\begin{deluxetable*}{l | r | r r r r r r }[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{Best-fit slope and normalization parameters for stars of different temperatures and ages\label{tab:best_fits}}
+\tablehead{
+\colhead{$T_\textrm{eff}$ [K]} & \colhead{Age [Myr]} & \colhead{$\alpha_\textrm{E}$} & \colhead{$\sigma_{\alpha_\textrm{E}}$} & \colhead{$\beta_\textrm{E}$} & \colhead{$\sigma_{\beta_\textrm{E}}$} &  \colhead{$n_\textrm{E, fit}$} & \colhead{$N_\textrm{E}$} %& \colhead{$\alpha_\textrm{T}$} & \colhead{$\sigma_{\alpha_\textrm{T}}$} & \colhead{$A_*$} & \colhead{$\sigma_{A_*}$} &  \colhead{$n_\textrm{T, tot}$} & \colhead{$n_\textrm{T, fit}$} & \colhead{$N_\textrm{T}$}
+}
+\startdata
+2300 -- 3400 & 4 -- 10  &  -0.516  &  0.074  &  14.514  &  2.409  &  731  &  96 \\
+& 10 -- 20  &  -0.336  &  0.031  &  8.296  &  0.973  &  1183  &  166 \\
+& 20 -- 40  &  -0.499  &  0.058  &  13.564  &  1.858  &  526  &  75 \\
+& 40 -- 50  &  -0.397  &  0.045  &  10.248  &  1.400  &  3358  &  111 \\
+& 70 -- 80  &  -0.383  &  0.083  &  10.244  &  2.685  &  341  &  102 \\
+& 120 -- 150  &  -0.657  &  0.097  &  18.757  &  3.161  &  3797  &  615 \\
+& 150 -- 300  &  -0.341  &  0.063  &  8.799  &  2.029  &  295  &  60 \\
+\hline
+3400 -- 3850  & 4 -- 10  &  -0.206  &  0.025  &  4.536  &  0.821  &  397  &  44 \\
+& 10 -- 20  &  -0.345  &  0.038  &  8.768  &  1.199  &  474  &  43 \\
+& 20 -- 40  &  -0.405  &  0.054  &  10.890  &  1.741  &  194  &  17 \\
+& 40 -- 50  &  -0.408  &  0.037  &  10.770  &  1.182  &  1420  &  43 \\
+& 70 -- 80  &  -0.432  &  0.075  &  11.893  &  2.471  &  291  &  77 \\
+& 120 -- 150  &  -0.525  &  0.062  &  14.557  &  1.998  &  1185  &  167 \\
+& 150 -- 300  &  -0.339  &  0.058  &  8.683  &  1.904  &  262  &  56 \\
+\hline
+3850 -- 4440  & 4 -- 10  &  -0.221  &  0.040  &  4.884  &  1.314  &  207  &  34 \\
+& 10 -- 20  &  -0.350  &  0.016  &  8.998  &  0.545  &  480  &  65 \\
+& 20 -- 40  &  -0.202  &  0.077  &  4.425  &  2.492  &  51  &  6 \\
+& 40 -- 50  &  -0.379  &  0.062  &  9.873  &  1.982  &  175  &  11 \\
+& 70 -- 80  &  -0.455  &  0.102  &  12.498  &  3.347  &  63  &  25 \\
+& 120 -- 150  &  -0.419  &  0.046  &  11.010  &  1.494  &  684  &  116 \\
+& 150 -- 300  &  -0.323  &  0.029  &  8.026  &  0.929  &  247  &  39 \\
+\hline
+4440 -- 5270  & 4 -- 10  &  -0.348  &  0.031  &  8.850  &  1.014  &  112  &  25 \\
+& 10 -- 20  &  -0.408  &  0.043  &  10.914  &  1.417  &  558  &  111 \\
+& 20 -- 40  &  -0.440  &  0.033  &  11.635  &  1.075  &  250  &  29 \\
+& 40 -- 50  &  -0.331  &  0.089  &  8.325  &  2.893  &  202  &  30 \\
+& 70 -- 80  &  -0.390  &  0.085  &  10.152  &  2.749  &  122  &  37 \\
+& 120 -- 150  &  -0.375  &  0.029  &  9.593  &  0.930  &  572  &  111 \\
+& 150 -- 300  &  -0.560  &  0.126  &  15.056  &  3.951  &  115  &  35 \\
+\hline
+5270 -- 5930  &  4 -- 10  &  -0.271  &  0.049  &  6.280  &  1.586  &  166  &  44 \\
+& 10 -- 20  &  -0.419  &  0.055  &  11.266  &  1.820  &  195  &  67 \\
+& 20 -- 40  &  -0.465  &  0.035  &  12.377  &  1.149  &  636  &  58 \\
+& 40 -- 50  &  -0.479  &  0.054  &  13.071  &  1.780  &  347  &  36 \\
+& 70 -- 80  &  -0.337  &  0.083  &  8.416  &  2.656  &  57  &  27 \\
+& 120 -- 150  &  -0.450  &  0.045  &  11.977  &  1.460  &  236  &  62 \\
+& 150 -- 300  &  -0.305  &  0.081  &  6.826  &  2.598  &  64  &  22 \\
+\enddata
+\tablecomments{$n_\textrm{E, fit}$ is the number of flares fit per bin; $N_E$ is the number of stars in each bin.}
+\end{deluxetable*}
+
 \bibliography{bib}

### 2024-01-15 src/scripts/analysis_utils.py

@@ -130,7 +130,7 @@ def fit_ffd(data, limit, yerr=None):
                            p0=[-0.8, 22],
                            bounds=([-2.0, -50.0],
                                    [0.0, 50.0]),
-                           maxfev=10000)
+                           maxfev=1000000)
     perr = np.sqrt(np.diag(pcov))
 
     data = np.array([logx, logn, np.sqrt(n[mask])])

### 2024-01-22 src/tex/ms.tex
ready for submission!

@@
 % Define document class
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn, linenumbers]{aastex631}
 \usepackage{showyourwork}
 \usepackage{rsfso}
+\usepackage{rotating}
 
@@
 \begin{abstract}
-Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with surface magnetic reconnection events.
-Stellar magnetic activity generally decreases as a function of both age and Rossby number, $R_0$, a measure of the relative dominance of the convective and rotational dynamos.
-However, without young stars have been overlooked in flare studies due to lack of long baseline observations and challenges with flare-detection methods.
-With this motivation, we select a sample of stars that are either (i) members, (ii) candidate members or (iii) have a high-probability of being  members of 26 nearby young moving groups, clusters, or associations all known to be less than 300~Myr old that have been observed by the Transiting Exoplanet Survey Satellite (TESS) at 2-minute cadence.
-With this sample of \nstars\ stars younger than 300~Myr, we identified \nflares\ flares originating from \nflarestars\ stars.
-Moreover, we robustly measured the rotation periods of \nprot~stars.
-We measure the flare frequency distribution (FFD) slope as a function of both age and spectral type and find the FFD slope, $\alpha$, saturates for all spectral types at $\alpha = -0.5$ and is constant over the 300~Myr window studied here.
-Additionally, we find that $R_0$ and flare rate for stars $t_\textrm{age} = 100 - 300$~Myr are saturated out to $R_0 = 0.14$, which is consistent with other indicators of magnetic activity.
-We cross match our targets with \textit{GALEX} and find no correlation between flare rate and Far- and Near-Ultraviolet flux.
-We compare the flare rates of planet hosting stars to comparable, larger samples of stars and find the majority of planet-hosting stars are relatively flare quiet.
-This may impact the atmospheric evolution of young short-period exoplanets.
-Finally, we detect evidence of stellar flare variations across five years of TESS data in eleven young stars, likely as a result of longer timescale stellar cycles.
+
+Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with surface magnetic reconnection events. Stellar magnetic activity generally decreases as a
+function of both age and Rossby number, $R_0$, a measure of the relative importance of the convective and rotational dynamos.  Young stars ($<300$ Myr) have typically been
+overlooked in population-level flare studies because of the lack of long baseline observations and challenges with flare-detection methods. Here, we select a sample of stars
+that are members of 26 nearby  moving groups, clusters, or associations with ages $<$300~Myr  that have been observed by the Transiting Exoplanet Survey Satellite (TESS) at
+2-minute cadence.  With this sample of \nstars\ stars, we identified \nflares\ flares originating from \nflarestars\ stars. Moreover, we robustly measured the rotation periods
+of \nprot~stars within this population. We measure the flare frequency distribution (FFD) slope as a function of both age and spectral type and find the FFD slope, $\alpha$,
+saturates for all spectral types at $\alpha \sim -0.5$ and is constant over the 300~Myr. Additionally, we find that flare rates for stars $t_\textrm{age} = 50 - 250$~Myr are
+saturated below $R_0 < 0.14$, which is consistent with other indicators of magnetic activity. Taking advantage of the long temporal baseline of TESS, we search for evidence
+of annual flare rate variability. We present eleven young stars which tentatively show evidence of flare rate variations across five years of TESS data, potentially correlated
+with long term stellar activity cycles. Additionally, we cross match our entire sample  with \textit{GALEX} and find no correlation between flare rate and Far- and Near-Ultraviolet
+flux. Finally, we find the flare rates of planet hosting stars are relatively lower than a  comparable, larger samples of stars. This trend may have ramifications for the atmospheric
+evolution of young, short-period exoplanets.
 
@@
 % Main body with filler text
-\section{Introduction}
-\label{sec:intro}
+\section{Introduction} \label{sec:intro}
 
-Stellar flares are the radiation component of magnetic reconnection events \citep{benz10}.
-Such events are readily seen on the Sun \citep{carrington1859, lu91, fletcher11}, particularly now as we enter a maximum in the solar cycle \citep{webb94}.
-Such events can be used to understand the magnetic activity of other stars \citep{feigelson99, berdyugina05, kowalski10, feinstein22_criticality}.
-Additionally, by studying stellar flares we can understand how these short-duration events may impact exoplanet evolution \citep{france16, guenther19_flares, chen21}.
-While we cannot angularly resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events.
-Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events, e.g.
-coronal mass ejections \citep{argiroffi19, vida19} or proton beams \citep{orrall76, woodgate92}.
+Stellar flares are the radiation component of magnetic reconnection events \citep{benz10}. Such events are readily seen on the Sun \citep{carrington1859, lu91, fletcher11},
+particularly during the maximum in the solar cycle \citep{webb94}. Solar flares can be used as proxies for magnetic activity occurring on other stars
+\citep{feigelson99, berdyugina05, kowalski10, feinstein22_criticality}. Additionally, these short-duration flaring events can have significant ramifications on the evolution
+of short-period extrasolar planets \citep{france16, guenther19_flares, chen21}. While stellar flares are typically not spatially resolvable, they do lend themselves to
+characterization via spectroscopic and photometric signatures. Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes
+affiliated with such events such as coronal mass ejections \citep{argiroffi19, vida19}, proton beams \citep{orrall76, woodgate92}, and accelerated electrons \citep{osten05, smith05}.
 
-Photometric observations of stars are more readily available thanks to exoplanet transit discovery missions, and allow us to statistically characterize flare rates and energies.
-NASA's \textit{Kepler}, \textit{K2}, and the Transiting Exoplanet Survey Satellite (TESS) missions have provided a wealth of stellar variability data in addition to their primary objective of detecting transiting exoplanets.
-Within time-series photometry, stellar flares can be identified by a sharp rise in the stellar flux and a subsequent exponential decay, corresponding to the cooling rate \citep{}.
-\textit{Kepler} \citep{Borucki10} provided long-baseline high-cadence observations used to identify stellar flares.
-There has been extensive studies of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.][]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars \citep[e.g.][]{Hawley14, silverberg16}.
-\cite{davenport19} found that flare activity decreased with increasing rotation period for 347 GKM stars.
-However, the flare frequency distribution (FFD) slope did not change significantly as a function of age.
-As a caveat, the ages of the stars were determined based on their rotation periods, relying on the assumption that gyrochronology alone accurately ages stars.
+Photometric observations of stars are more readily available now with exoplanet transit discovery missions, and allow us to statistically characterize flare rates
+and energies at optical/near-infrared wavelengths. Observations of M dwarfs with the Sloan Digital Sky Survey revealed a correlation between the flaring fraction of
+stars with height above the galactic plane, a proxy for age \citep{kowalski09, hilton10}. More recently, NASA's \textit{Kepler}, \textit{K2}, and the Transiting
+Exoplanet Survey Satellite (TESS) missions have provided a wealth of stellar variability data in addition to their primary objective of detecting transiting exoplanets.
+Flares can be identified within time-series photometry by a sharp rise and subsequent exponential decay in flux,  with the latter corresponding to the cooling rate
+\citep{kowalski13}. \textit{Kepler} \citep{Borucki10} provided long-baseline high-cadence observations used to identify stellar flares. There has been extensive studies
+of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.][]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars
+\citep[e.g.][]{Hawley14, silverberg16}. \cite{davenport19} found that flare activity decreased with increasing rotation period for 347 GKM stars. However, the flare
+frequency distribution (FFD) slope did not vary significantly as a function of age. As a caveat, the ages of the stars in this study were determined based on their
+rotation periods, relying on the assumption that gyrochronology alone accurately ages stars.
 
-\textit{K2} provided 70-day baseline observations for a handful of young stars in groups such as Upper Scorpius,  Pleiades, Hyades, and Praespe clusters.
-\cite{ilin19, ilin21} analyzed flares K and M stars in these clusters and found that the overall flare activity decreased as a function of age.
-This relationship was steeper for more massive stars in the sample.
-\cite{paudel18} surveyed 10 M6 - L0 dwarfs observed with \textit{K2} and found the L0 dwarf had a much shallower FFD than the M dwarfs.
-On average, they found that very young targets, defined by the tangential velocity of the star, overall had more flares.
+\textit{K2} provided 70-day baseline observations for a handful of young stars in groups such as Upper Scorpius,  Pleiades, Hyades, and Praespe clusters. \cite{ilin19, ilin21}
+analyzed flares from K and M stars in these clusters and found that the overall flare activity decreased as a function of age. Moreover, this relationship was steeper for
+more massive stars in the sample. \cite{paudel18} surveyed 10 M6 - L0 dwarfs observed with \textit{K2} and found the L0 dwarfs had significantly shallower FFDs than the M
+dwarfs. They found that, on average, young targets (defined by the tangential velocity of the star) exhibited more flares overall. More recently, TESS \citep{ricker15} has
+provided near all-sky photometric observations at 30-minute cadence or less. This observing strategy has allowed for more detailed studies of young stellar flares from nearby,
+disperse young moving groups and associations. These  data permit detailed studies of individual stars, for example characterizing eight superflares ($E_f > 10^{34}$~erg) on
+the young star AB Doradus over $\sim 60$ days of continuous observations \citep{schmitt19}, as well as statistical studies of flares across a range of spectral types and ages
+\citep{doyle20, feinstein22_criticality, pietras22, yang23}.
 
-More recently, TESS \citep{ricker15} has provided near all-sky photometric observations at 30-minute cadence or less.
-Such an observing strategy has allowed for more detailed studies of young stellar flares from nearby young moving groups and associations, which are disperse in the sky \citep{gagne18}.
-These new data have allowed for detailed studies of individual stars, for example characterizing eight superflares ($E_f > 10^{34}$~erg) on the young star AB Doradus over $\sim 60$ days of continuous observations \citep{schmitt19}.
+The 11-year solar activity cycle represents a change in the magnetic activity of the Sun, and manifests itself in a variety of observables including increases in the total
+number of sunspots \citep{clette14, kilcik14}, flares and coronal mass ejections \citep{crossby93, webb94, lin23}, and an increase in the total solar irradiance \citep{lean1987}.
+Insights into the long-term activity cycles on other stars have been limited to photometric and spectroscopic monitoring \citep{saar99}. \cite{lehtinen16} collected 16 to 27 years
+of B- and V-band photometry for 21 young active solar-type stars. They found evidence of long-term stellar activity cycles in 18 targets for which$P_\textrm{rot}/P_\textrm{cycle}
+\propto R_0^{-1}$, where $P_\textrm{rot}$ is the rotation period, $P_\textrm{cycle}$ is the period of the stellar activity cycle, and $R_0$ is the Rossby number. Additionally,
+50 years of spectroscopic observations of HD~166620 from the Mount Wilson Observatory and Keck revealed both a $\sim 16$~year periodicity in emission from the core of the
+\ion{Ca}{2} H and K lines \citep{olah16} and evidence that this star entered a grand minima \citep{baum22}. A more complete review on the state of stellar activity cycles can be
+found in \cite{jeffers23} and \cite{isik23}.
 
-The 11-year solar activity cycle represents a change in the magnetic activity of the Sun, and manifests itself in a variety of observables e.g., an increase in the total number of sunspots \citep{clette14, kilcik14}, an increase in the number of flares and coronal mass ejections \citep{crossby93, webb94, lin23}, and an increase in the total solar irradiance \citep{lean1987}.
-The majority of insights we have gained in long-term activity cycles on other stars is through photometric monitoring and spectroscopic monitoring \citep{saar99}.
-\cite{lehtinen16} collected 16 to 27 years of B- and V-band photometry for 21 young active solar-type stars.
-They found evidence of long-term stellar activity cycles in 18 targets following as $P_\textrm{rot}/P_\textrm{cycle} \propto R_0^{-1}$, where $P_\textrm{rot}$ is the rotation period, $P_\textrm{cycle}$ is the period of the stellar activity cycle, and $R_0$ is the Rossby number.
-Additionally, 50 years of spectroscopic observations of HD~166620 from the Mount Wilson Observatory and Keck revealed both a $\sim 16$~year periodicity in emission from the core of the \ion{Ca}{2} H and K lines \citep{olah16} and evidence that this star entered a grand minima \citep{baum22}.
-A more complete review on the state of stellar activity cycles can be found by \cite{jeffers23} and \cite{isik23}.
+In addition to photometric and spectroscopic observations, solar flares trace the length of the solar activity cycle. The high-cadence observations from \textit{Kepler} (4-year baseline)
+and TESS (currently 5-year baseline) provide  sufficient data for searches of stellar activity cycles from the variations in stellar flare rates. \cite{davenport20} demonstrated that
+the flare rate and FFDs of GJ~1234 has not changed appreciably over 10~years of observations with both \textit{Kepler} and TESS. On the other hand, \cite{scoggins19} found that the M3V
+star star KIC 8507979 showed a clear decline in flare rate and change in FFD over 4-years of \textit{Kepler} observations. While it is not expected to find flare rate and distribution
+variations in all stars given detection limitations, KIC 8507979 demonstrates the ability to study long-term flare variability as a potential tracer for stellar activity cycles.
 
-In addition to photometric and spectroscopic observations, solar flares trace the length of the solar activity cycle.
-The high-cadence observations from \textit{Kepler} (4-year baseline) and TESS (currently 5-year baseline) are providing data sufficient for searching for stellar activity cycle from the variations in stellar flare rates.
-\cite{davenport20} demonstrated that the flare rate and FFDs of GJ~1234 has not changed appreciably over 10~years of observations with both \textit{Kepler} and TESS.
-On the other hand, \cite{scoggins19} found that  KIC 8507979, an M3V star, showed a clear decline in flare rate and change in FFD over 4-years of \textit{Kepler} observations.
-While it is not expected to find flare rate and distribution variations in all stars given detection limitations, KIC 8507979 demonstrates the ability to study long-term flare variability as a potential tracer for stellar activity cycles.
-
-The paper is presented as follows.
-In Section~\ref{sec:methods}, we describe our sample, stellar flare identification and fitting methods, and methods for measuring stellar rotation periods.
-In Section~\ref{sec:results}, we present our flare-frequency distribution (FFD) fits as a function of stellar age, $T_\textrm{eff}$, and $R_0$.
-In Section~\ref{sec:discuss}, we search for correlations in flare rates with FUV and NUV observations from \textit{GALEX} and place the flare rates of young planet hosting stars in the context of our broader sample.
-We conclude in Section~\ref{sec:conclusions}.
+The paper is presented as follows. In Section~\ref{sec:methods}, we describe our sample, and stellar flare and rotation period identification methods. In Section~\ref{sec:results},
+we present our flare-frequency distribution (FFD) fits as a function of stellar age, $T_\textrm{eff}$, and $R_0$. In Section~\ref{sec:cycles}, we present evidence of flare rate changes
+over the 5-year TESS baseline in eleven young stars, likely correlated with long term stellar activity cycles. In Section~\ref{sec:discuss}, we search for correlations in flare rates
+with FUV and NUV observations from \textit{GALEX} and place the flare rates of young planet hosting stars in the context of our broader sample.  We conclude in Section~\ref{sec:conclusions}.
 We provide additional figures and tables in Section~\ref{appendix:supp_ffds}.
@@
 
-In this section, we provide an overview of the methodology associated with this paper.
-Specifically, we describe the sample selection in subsection \ref{subsec2:sample}, TESS light curve analysis in \ref{subsec2:TESS_lightcurve}, flare identification in subsection \ref{subsec2:Flareidentification}, how we fit for flare parameters in \ref{subsec2:model}, flare quality checks in \ref{subsec2:qualitychecks}, and measuring stellar rotation periods in \ref{subsec:prot}.
+Here, we provide an overview of the methodology used in this paper. Specifically, we describe the sample selection in Section~\ref{subsec2:sample}, TESS light curve analysis in
+Section~\ref{subsec2:TESS_lightcurve}, flare identification in Section~\ref{subsec2:Flareidentification}, flare fitting parameters in Section~\ref{subsec2:model}, flare quality
+checks in Section~\ref{subsec2:qualitychecks}, and  stellar rotation period measurements in Section~\ref{subsec:prot}.
 
@@
 
-A primary goal of this paper is to measure the dependence of the stellar flare rates on stellar age.
-Particularly, we are interested in this dependency for stars with ages $1 \leq t_\textrm{age} \leq 300$\,Myr.
-To this end, we used the MOCA Data Base (Gagné et al.
-in prep.) to identify nearby young moving groups, associations, and open clusters with known ages which satisfied our criteria.
-From this database we identified 26~ unique groups from which we created our sample of stars.
-The final selected targets were required to be: (i) confirmed members, (ii) high-likelihood candidate members, or (iii) candidate members.
-Membership to these groups has been primarily determined using kinematic information from \textit{Gaia} \citep{gaia16, gaia18}.
-These rather stringent cuts resulted in a catalog of 30,889 stars across 26 associations.
-We summarize the sample and ages for each association (and therefore star) in Table~\ref{tab:sample}.
+A primary goal of this paper is to measure the relationship between the flare rates and ages of stars. We are particularly interested in this dependency for young stars with ages
+$4 \leq t_\textrm{age} \leq 300$\,Myr. To this end, we used the MOCA Data Base (Gagné et al. in prep.)\footnote{\url{https://mocadb.ca/}} to identify 26~ nearby, aged, young moving
+groups, associations, and open clusters from which we created our sample of stars. The final targets were required to be: (i) confirmed members, (ii) high-likelihood candidate members,
+or (iii) candidate members.  Membership to these groups has been primarily determined using kinematic information from \textit{Gaia} \citep{gaia16, gaia18}. The membership status is
+determined by the probability that BANYAN-$\Sigma$ assigns based on how well the kinematics of the target matches with the kinematics of the group \citep{gagne18}. These rather
+stringent cuts resulted in a catalog of 30,889 stars across 26 associations. We summarize the sample and ages for each association (and therefore star) in Table~\ref{tab:sample}.
 
-%With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}.
-In order to model the flare profile, we employ the analytical model developed by \cite{tovar22}.
-This model is able to simultaneously (i) fit the flares and  (ii) measure the equivalent duration and energy associated with each flare.
+%With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}. In order to model the
+flare profile, we employ the analytical model developed by \cite{tovar22}. This model is able to simultaneously (i) fit the flares and  (ii) measure the equivalent duration and energy
+associated with each flare.
 
@@
 \tablecaption{Adopted Ages of each Young Stellar Population and Number of
-Stars per Group \label{tab:sample}}
+Stars per Group, $N_\textrm{stars}$ \label{tab:sample}}
 \tablehead{
@@
 \enddata
-\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{galindo22}; (3) \citet{Bell15}; (4) \citet{kerr21}; (5) \citet{luhman07}; (6) \citet{pecaut16}; (7) \citet{tofflemire21}; (8) \citet{murphy15}; (9) \citet{curtis19}; (10) \citet{kounkel20}; (11) \citet{tarricq21}; (12) \citet{roser16}}
+\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{galindo22}; (3) \citet{Bell15}; (4) \citet{kerr21}; (5) \citet{luhman07}; (6) \citet{pecaut16}; (7)
+\citet{tofflemire21}; (8) \citet{murphy15}; (9) \citet{curtis19}; (10) \citet{kounkel20}; (11) \citet{tarricq21}; (12) \citet{roser16}}
 \end{deluxetable}
@@
 
-As described in the previous subsection, we select stars in our sample for which TESS light curves have been obtained with 2-minute cadence.
-The reason for doing this is so that we are able to resolve and accurately measure the properties of flares for each of these stars \citep{howard22}.
-We cross-matched our sample obtained with the MOCA Database with the TESS Input Catalog (TIC) based on their Gaia DR2 RA and Dec.
-We required that the distance between the target and the nearest TIC target was within $<1"$.
+We cross-matched our MOCA Database sample with the TESS Input Catalog (TIC) based on their Gaia DR2 RA and Dec; we required that the distance between the target and the nearest
+TIC target was within $<1"$. We down-selected our sample to stars that have been observed with TESS at 2-minute cadence. This ensures that we are able to temporally resolve and
+accurately measure the properties of flares for each of these stars \citep{howard22}.
 
-This process provided a final sample of \nstars\ unique targets.
-These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67; Sector 67 was the latest available sectors at the time that this analysis was performed.
-In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions and effective temperatures, $T_\textrm{eff}$, of the final sample.
-We use $T_\textrm{eff}$ as our stellar characterization metric over the standard $M_\star$ because $\sim 600$ stars in our sample are lacking mass information in the TIC.
-It is evident that  many targets exhibit strong tendency for proximity towards the
-northern and southern ecliptic poles (Figure~\ref{fig:sample}). Therefore, many of these targets were observed
-over multiple sectors.
-The entirety of the available data yielded 17,964 light curves processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16}.
-Our sample has an average of $\sim 3$ light curves per target (although with significant spread across targets).
-For our analysis, we used the SPOC-processed SAP\_FLUX.
+This process provided a final sample of \nstars\ unique targets. These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67; Sector 67 was
+the latest available sector at the time that this analysis was performed. In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions, ages and effective
+temperatures, $T_\textrm{eff}$, of the final sample. Because many of the groups are located at or near the ecliptic poles, many of our targets were observed over multiple TESS
+sectors. We use $T_\textrm{eff}$ as our stellar characterization metric over the standard $M_\star$ because $\sim 600$ stars in our sample lack mass information in the TIC.
+The entirety of the available data yielded 17,964 light curves processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16}. Our sample has an average
+of $\sim 3$ light curves per target (although with significant spread across targets). For our analysis, we used the SPOC-processed SAP\_FLUX.
 
@@
         \caption{
-            Top: Distribution of our selected sample across the sky and colored by the adopted age of the association (see Table~\ref{tab:sample}).
-The all-sky coverage by TESS has unlocked new populations of stars to observe.
-We take advantage of this observing strategy to measure flare rates across 26 different nearby young moving groups, clusters, and associations.
-Bottom: Distribution of adopted effective temperatures, $T_\textrm{eff}$ [K] for stars in our sample.
-We include all stars with $T_\textrm{eff} \leq 6000$\,K.
+            Top: Distribution of the selected sample across the sky and colored by the adopted age of the association (see Table~\ref{tab:sample}). The all-sky coverage by TESS
+            has unlocked new populations of stars to observe. We take advantage of this observing strategy to measure flare rates across 26 different nearby young moving groups,
+            clusters, and associations. Bottom: Distribution of adopted effective temperatures, $T_\textrm{eff}$ [K] for stars in our sample. We include all stars with $T_\textrm{eff} \leq 6000$\,K.
         }
@@
 
-Once we had the light curves for each target, we performed the following procedure to identify stellar flares.
-First, we implemented the machine learning flare-identification methods presented and described in \cite{feinstein20}.
-This method relies on the fact that all flare events have similar time-dependent morphologies.
-These flare-profiles can generally be described as a sharp rise followed by an exponential decay in the white light curve.
-This identification-technique implements the convolutional neural network (CNN),
-\texttt{stella} \citep{feinstein20}.
-The neural network was trained to identify flare events in TESS 2-minute data using a catalogue of flare events from TESS Sectors 1 and 2 that were validated  by-eye
-\citep{guenther19_flares}.
+Once we downloaded the light curves for each target, we performed the following procedure to identify stellar flares. First, we implemented the machine learning flare-identification
+methods presented and described in \cite{feinstein20}. This method relies on the similar time-dependent morphologies of all flare events. These flare-profiles can generally be
+described as a sharp rise followed by an exponential decay in the white light curve. This identification-technique implements the convolutional neural network (CNN) \texttt{stella}
+\citep{feinstein20}. The CNN  was trained on  a   by-eye validated catalogue of flares from TESS Sectors 1 and 2 with 2-minute data \citep{guenther19_flares}.
 
-There are many benefits to using the CNN for stellar flare identification.
-Primarily, the CNN is advantageous because it is insensitive to the stellar baseline flux.
-This feature inherently stems from the fact that the network is trained to search \textit{only} based on flare morphology.
-It is therefore relatively insensitive to the absolute flux levels, so long as the inherent noise does not overwhelm the signal itself.
-This means that rotational modulation peaks --- which are themselves driven by
-stellar heterogeneities --- are not accidentally identified as flares.
-This is especially advantageous for our sample of young stars, which  readily exhibit rotational modulation in their light curves.
+There are several benefits to using the CNN for stellar flare identification. Primarily, the CNN is insensitive to the stellar baseline flux because it is trained to search
+\textit{only} based on flare morphology. It is therefore relatively insensitive to the absolute flux levels, so long as the inherent noise does not overwhelm the signal itself.
+An additional benefit is that rotational modulation peaks --- which are themselves driven by stellar heterogeneities --- are not accidentally identified as flares. This holds true
+for stars with rotation periods, $P_\textrm{rot} > 1$~day. This is especially advantageous for our sample of young stars, which readily exhibit rotational modulation in their light curves.
 
-Based on these advantages, the final compiled sample of flares is \textit{unbiased} towards low-amplitude/low-energy flares.
-It is important to note that these low-energy events are typically not identified in traditional sigma-outlier identification
-methods \citep{chang15}.
-The \texttt{stella} CNN models calculates the probability that a data point in a light curve is associated with a flaring event.
-Specifically, it takes the light curve (time, flux, flux error) as an input and returns an array with values of [0,1], which are treated as the probability a data point is (1) or is not (0) part of a flare.
-We ran every light curve through 10 independent \texttt{stella} models and averaged the outputs to ensure that our statistics were accurate.
-We note that in this processing, the CNN ignores 200-minutes before and after any gaps in the data.
-Therefore, any flares which occur during these times are not identified.
+Based on these advantages, the final compiled sample of flares is unbiased towards low-amplitude/low-energy flares. It is important to note that these low-energy events are typically
+not identified in traditional sigma-outlier identification
+methods \citep{chang15}. The \texttt{stella} CNN models calculate the probability that a data point in a light curve is associated with a flaring event. Specifically, it takes the light
+curve (time, flux, flux error) as an input and returns an array with values of [0,1], which are treated as the probability a data point is (1) or is not (0) part of a flare. We ran every
+light curve through 10 independent \texttt{stella} models and averaged the outputs to ensure that our statistics were accurate. We note that in this processing, the CNN ignores 200-minutes
+before and after any gaps in the data. Therefore, any flares which occur during these times are not identified.
 
-In order to identify a single flare event, the \texttt{stella} code uses the predictions per data point to group together points.
-We modified this stage of identification slightly from the original flare-identification method.
-Specifically, we identified all data points with a probability of being associated with a flare of $P > 0.75$.
-Any data points that were within 4 cadences of each other were considered to be a single flare event.
-We did not consider any potential flares that had three or fewer points with $P > 0.75$.
-This was motivated by the fact that  sometimes a single-point outlier is assigned a high probability of being a flare.
-Therefore, we neglected these events.
-We assigned the probability of the whole flare event as the probability of the peak data point.
+The \texttt{stella} code groups individual points with the predictions per data point when identifying a single flare event. We modified this stage of identification slightly from the
+original flare-identification method. Specifically, we identified all data points with a probability of being associated with a flare of $P > 0.75$. Any data points that were within 4
+cadences of each other were considered to be a single flare event. We did not consider any potential flares that had three or fewer points with $P > 0.75$. This method rejects single-point
+outliers which can be assigned  high probabilities of being  flares. We assigned the probability of the whole flare event as the probability of the peak data point.
 
@@
         \caption{
-            High level summary of the demographics of flares in our sample.
-Top: The number of flares identified compared to the number of stars in each nearby young moving group, cluster, or association.
-A one-to-one relationship is expected.
-Middle: The distribution measured TESS energies
+            High level summary of the demographics of flares in our sample. Top: The number of flares identified compared to the number of stars in each nearby young moving group, cluster,
+            or association. A linear relationship is expected. Bottom: The distribution of measured TESS energies
             and equivalent durations of flares in our sample, colored by the probability of the flare as identified with \texttt{stella}.
-Bottom: Same as the middle plot, except colored by the $T_\textrm{eff}$ [K] of the star.
-We limit our sample to stars with $T_\textrm{eff} \leq 6000$\,K.
         }
@@
 
-As described in the previous subsection, flares are well-described in light curves as a sudden increase in flux followed by an exponential decay.
-For this paper, we used the analytical flare model, Llamaradas Estelares which was presented in
-\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}, to fit the flares and extract the flare parameters in all of the light curves of our sample.
-This model builds upon the model presented in \cite{davenport14}.
-Specifically, it includes the convolution of a Gaussian with a double exponential model in the flare profile.
+Flares are well-described in light curves as a sudden increase in flux followed by an exponential decay. We used the analytic flare model, Llamaradas Estelares which was presented in
+\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}, to fit and extract parameters of flares in all of the light curves of our sample. This model builds
+upon the model presented in \cite{davenport14}. Specifically, it includes the convolution of a Gaussian with a double exponential model in the flare profile.
 
-The analytical model is robust in that it is able to accounts for multiple inherent features of flares.
-Specifically, it can incorporate the flare (i) amplitude, (ii) heating timescale, (iii) rapid cooling phase timescale, and (iv) slow cooling phase timescale.
-We implemented a nonlinear least squares optimization to fit for the time of the flare peak ($t_\textrm{peak}$), full width at half maximum (FWHM), and the amplitude ($A$) of each flare in the sample.
-We combine the model with a second-order polynomial fit to a 1.2-hour baseline before and after the flare  during only the fitting stage.
+The analytic model robustly  accounts for physically-motivated flare features. Specifically, it can incorporate the flare (i) amplitude, (ii) heating timescale, (iii) rapid cooling phase
+timescale, and (iv) slow cooling phase timescale. We implemented a nonlinear least squares optimization to fit the flare peak time ($t_\textrm{peak}$), full width at half maximum (FWHM),
+and the amplitude ($A$) of each flare in the sample.  We combine the model with a second-order polynomial fit to a 1.2-hour baseline before and after the flare  during only the fitting stage.
 This was implemented in order to account for any slope due to rotational modulation, and therefore was particularly relevant for the rapid rotators ($P_\textrm{rot} < 2$~days).
@@
 \end{equation}
-In Equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$, where $B_\lambda(T)$ is the Planck function.
-We assume that the flare temperature is 9000~K \citep{kretzschmar11}.
-Although 900
+In Equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$, where $B_\lambda(T)$ is
+the Planck function. We assume that the flare temperature is 9000~K \citep{hawley92, hawley95}, although recent NUV flare observations suggest this may be an underestimation
+\citep{kowalski19, brasseur23, berger23}.
 
@@
 
-In this subsection, we describe the methodology we employ to ensure that flares identified by the CNN are high quality.
-The \texttt{stella} CNNs were trained on data from TESS Sectors 1 and 2.
-However, the noise properties are variable across sectors in TESS data.
-The CNNs are therefore unable to accurately
-account for and capture  this variation when operating on different sectors.
-Moreover, the original CNNs were only trained on a sample of 1,228 stars.
-This sample  does not necessarily encapsulate all or even a sufficient distribution  of variable stars types, such as eclipsing binaries, RR Lyraes, and fast rotators with rotation periods $P_\textrm{rot} < 1$~day.
-We therefore apply additional
+The \texttt{stella} CNNs were trained on data from TESS Sectors 1 and 2. However, the noise properties are variable across sectors in TESS data. The CNNs are therefore unable to
+accurately account for and capture  this variation when operating on different sectors. Moreover, the original CNNs were only trained on a sample of 1,228 stars. This training sample
+does not necessarily encapsulate a sufficient distribution  of variable stars types, such as eclipsing binaries, RR Lyraes, and fast rotators with $P_\textrm{rot} < 1$~day, which
+results in the CNNs not being able to properly distinguish these temporal features from flares. We therefore apply additional
 quality checks to ensure our flare sample has little to no contamination from other sources.
 
-Specifically, we remove flares from our sample which did not satisfy  one or more of the following criteria.
+Specifically, we remove flares from our sample which did not satisfy  one or more of the following criteria:
 \begin{enumerate}
-    \item  The amplitude of the flare must be $> 0.01$, or 1\%. This follows the limits set by \cite{feinstein20}.
-    \item The flare amplitude  must be at least twice the standard deviation of the light curve 30 minutes before and 45 minutes after the flare.
-This ensures that the feature is not a sharp noise artifact.
+    \item  The amplitude of the flare must be $> 0.01$, the same limits set by \cite{feinstein20}.
+    \item The flare amplitude  must be at least twice the standard deviation of the light curve 30 minutes before and 45 minutes after the flare. This ensures that the feature is not
+    a sharp noise artifact.
     \item  The fitted flare model parameters must be physically motivated: FWHM $> 0$; $A > 0$; ED $> 0$.
@@
 \end{enumerate}
-We find that when the errors on the first and fourth criteria are larger than the cut-offs, the flares are often simply mischaracterized noise.
 
-As a final check, we performed an exhaustive by-eye verification of flares from light curves for stars with flare rates, $\mathcal{R} > 1$~day$^{-1}$.
-These stars generally tend to have $T_\textrm{eff} > 5000$~K and TESS magnitudes $< 8$.
-Therefore, their light curves are dominated by sharp noise which \texttt{stella} often mischaracterizes as flares.
-As a final cut, the sample only includes events that have  a probability $P \geq 98\%$ of being
-a true flare. After performing these additional checks, we obtain a final flare sample of \nflares\ flares originating from \nflarestars\ stars (Figure~\ref{fig:flare_distribution}).
+We find that flares are often simply mischaracterized noise when the errors on the first and fourth criteria are larger than the cut-offs. These quality checks highlight the need
+to continuously update machine learning models, especially when looking at data with varying instrumental systematics.
+
+As a final check, we performed an exhaustive by-eye verification of flares from light curves for stars with flare rates, $\mathcal{R} > 1$~day$^{-1}$. These stars generally tend
+to have $T_\textrm{eff} > 5000$~K and TESS magnitudes $< 8$. Therefore, their light curves are dominated by sharp noise which \texttt{stella} often mischaracterizes as flares. As a
+final cut, the sample only includes events that have  a probability $P \geq 98\%$ of being a true flare. After performing these additional checks, we obtain a robust final flare sample
+of \nflares\ flares originating from \nflarestars\ stars (Figure~\ref{fig:flare_distribution}).
 
@@
 
-In addition to understanding flare statistics across young stars, we measure the rotation periods, $P_\textrm{rot}$ of stars in our sample and search for correlations between $P_\textrm{rot}$ and Rossby number, $R_0$.
-\citet{seligman22} demonstrated that stars with low Rossby numbers $R_0 < 0.13$ exhibit shallower flare frequency distribution slopes.
-These shallower slopes are caused by  an excess of  high energy flares compared to lower energy flares originating from these sources.
+In addition to understanding flare statistics across young stars, we measure the rotation periods, $P_\textrm{rot}$ of stars in our sample. We then search for correlations between
+$P_\textrm{rot}$ and Rossby number, $R_0$. \citet{seligman22} demonstrated that stars with low Rossby numbers $R_0 < 0.13$ exhibit shallower flare frequency distribution slopes. These
+shallower slopes are caused by  an excess of  high energy flares compared to lower energy flares.
 
-In order to perform this, we describe how we measure stellar rotation periods from the TESS light curves.
-To this end we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}}, an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination traditional Lomb-Scargle periodograms and wavelet transformations (Hall et al.
-submitted).
+In order to perform this, we describe how we measure stellar rotation periods from the TESS light curves. To this end we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}},
+an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination traditional Lomb-Scargle periodograms and wavelet transformations (Hall et al. submitted).
 \texttt{michael} measures $P_\textrm{rot}$ using the \texttt{eleanor} package, which extracts light curves from the TESS Full-Frame Images \citep[FFIs;][]{feinstein19}.
 
-We ran \texttt{michael} on all stars in our samples from which flares were identified.
-The estimated rotational periods were subsequently vetted by-eye  with the \texttt{michael} diagnostic plots.
-This vetting was implemented to ensure that the measured $P_\textrm{rot}$ was not a harmonic of the true $P_\textrm{rot}$ or that the period is from an occulting companion.
-In
-total, we robustly measured rotation periods for \nprot\ stars. Additionally, we identified 17 eclipsing binaries or potentially new planet candidates.
+We ran \texttt{michael} on all stars in our samples from which flares were identified. The estimated rotational periods were subsequently vetted by-eye  with the \texttt{michael}
+diagnostic plots. This vetting was implemented to ensure that the measured $P_\textrm{rot}$ was not a harmonic of the true $P_\textrm{rot}$ or  from an occulting companion. This led
+to robust measurements of rotation periods for \nprot\ stars in total. Additionally, we identified 17 eclipsing binaries or potentially new planet candidates.
 
@@
 
-In this section, we use the previous methodology to estimate the flare rates of the young stars in our sample.
-We implement three main steps in this analysis.
-First, we perform the standard FFD fitting of a power-law to the distribution of flare energies described in subsection \ref{subsec:energy_ffd}.
-Next, to determine if there is a correlation between $R_0$ and flare distributions we fit a truncated power-law to the distribution of flare amplitudes in subsection \ref{subsec3_truncated}.
-Finally we fit the relationship between $R_0$ and flare rates in subsection \ref{subsec:rossby}.
+In this section, we use the previously described methodology to estimate the flare rates of the young stars in our sample. We implement three main steps in this analysis. First, we
+perform the standard FFD fitting of a power-law to the distribution of flare energies described in Section~\ref{subsec:energy_ffd}. Next we fit the relationship between $R_0$ and
+flare rates in Section~\ref{subsec:rossby}. Finally we fit a truncated power-law to the distribution of flare amplitudes in  Section~\ref{subsec3_truncated}  to identify correlations
+between $R_0$ and flare distributions.
 
-The number of stars, and consequently the number of flares in  each association varied greatly (Figure~\ref{fig:flare_distribution}).
-This was primarily caused by the limited number of stars that had been observed at 2-minute cadence in TESS.
-We therefore did not measure FFD properties as a function of association.
-Instead, we group stars by $T_\textrm{eff}$ and average adopted association age.
+The number of stars and flares in  each association varied greatly (Figure~\ref{fig:flare_distribution}). This was primarily caused by the limited number of stars that had been
+observed at 2-minute cadence in TESS.  We therefore did not measure FFD properties as a function of association. Instead, we group stars by $T_\textrm{eff}$ and average adopted
+association age.
 
@@
  \begin{itemize}
-     \item M-stars below the fully convective boundary ($T_\textrm{eff} = 2300 - 3400$\,K)
-     \item  early type M-stars ($T_\textrm{eff} = 3400 - 3850$\,K)
-     \item  late K-stars ($T_\textrm{eff} = 3850 - 4440$\,K)
-     \item early K-stars ($T_\textrm{eff} = 4440 - 5270$\,K)
-     \item G-stars ($T_\textrm{eff} = 5270 - 5930$\,K)
+     \item M-stars below the fully convective boundary ($T_\textrm{eff} = 2300 - 3400$\,K),
+     \item  early type M-stars ($T_\textrm{eff} = 3400 - 3850$\,K),
+     \item  late K-stars ($T_\textrm{eff} = 3850 - 4440$\,K),
+     \item early K-stars ($T_\textrm{eff} = 4440 - 5270$\,K),
+     \item G-stars ($T_\textrm{eff} = 5270 - 5930$\,K).
  \end{itemize}
-We did not include any stars hotter than $T_\textrm{eff} > 5930$\,K.
-These hot stars generally exhibit light curves  dominated by noise in the TESS observations.
-Additionally, we grouped stars in the following age space: $4-10$\,Myr (including Upper Scorpius and TW Hydrae), $10-20$\,Myr, $20-40$\,Myr, $40-50$\,Myr, $70-80$\,Myr, $120-150$\,Myr, and $150-300$\,Myr.
+We did not include any stars hotter than $T_\textrm{eff} > 5930$\,K.  These hot stars generally exhibit light curves  dominated by noise in the TESS observations. Additionally, we
+grouped stars in the following age space: $4-10$\,Myr (including Upper Scorpius and TW Hydrae), $10-20$\,Myr, $20-40$\,Myr, $40-50$\,Myr, $70-80$\,Myr, $120-150$\,Myr, and $150-300$\,Myr.
 We note that there is a gap in age from $50-70$\,Myr, which could be expanded with the identification of more associations in this age range.
@@
     \begin{centering}
-        \includegraphics[width=\textwidth, trim={0 0 60cm 0}, clip]{figures/mcmc_results.pdf}
+        \includegraphics[width=\textwidth, trim={0cm 0 60cm 0}, clip]{figures/mcmc_results.pdf}
         \caption{
-            Measured flare-frequency distribution slopes, $\alpha$, as a function of stellar effective temperature, $T_\textrm{eff}$ and age.
-We measured these FFDs with respect to flare energy.
-We find the FFD slopes as a function of energy are consistent with $\alpha = -0.6 ~\textrm{to} -0.2$ for stars $< 300$~Myr in TESS observations.
-A shallower FFD slope is indicative of more high-energy flares.
-We present all measured FFDs in Figure~\ref{appendix:supp_ffds}, and all measured slopes and errors in Table~\ref{tab:best_fits}.
-We find the shallowest slopes for stars $T_\textrm{eff} = 3400 - 4440$\,K, with a range from $\alpha = -0.44~ \textrm{to} -0.22$.
-We do not include the results for stars $T_\textrm{eff} = 3850 - 4440$\,K and $t_\textrm{age} = 20 - 40$\,Myr as this bin contained only six stars with detected flares.
-We present the average results of measured FFD slopes for the Hyades, Pleiades, and Praesepe clusters from \cite{ilin21} as black squares.
-We present the results of measured FFD slopes for all TESS primary mission targets in white circles \citep{Feinstein22}.
-We present these data as ``field-age".
-We discuss what drives the difference between our sample and \cite{ilin21} in Section~\ref{subsec:energy_ffd}.
+            Measured flare-frequency distribution slopes, $\alpha$, as a function of stellar effective temperature, $T_\textrm{eff}$ and age. We measured these FFDs with respect to flare
+            energy. We find the FFD slopes as a function of energy are consistent with $\alpha = -0.6 ~\textrm{to} -0.2$ for stars $< 300$~Myr in TESS observations. A shallower FFD slope
+            is indicative of more high-energy flares. We present all measured FFDs in Figure~\ref{appendix:supp_ffds}, and all measured slopes and errors in Table~\ref{tab:best_fits}.
+            We find the shallowest slopes for stars $T_\textrm{eff} = 3400 - 4440$\,K, with a range from $\alpha = -0.44~ \textrm{to} -0.22$. We do not include the results for stars
+            $T_\textrm{eff} = 3850 - 4440$\,K and $t_\textrm{age} = 20 - 40$\,Myr as this bin contained only six stars with detected flares. We present the average results of measured
+            FFD slopes for the Hyades, Pleiades, and Praesepe clusters from \cite{ilin21} as black squares. We present the results of measured FFD slopes for all TESS primary mission
+            targets in white circles \citep{Feinstein22} as ``field-age". We discuss what drives the difference between our sample and \cite{ilin21} in Section~\ref{subsec:energy_ffd}.
         }
@@
 
-We fit the stars FFD slopes, approximated as a power-law, using the $T_\textrm{eff}$ and age bins described above.
-Flares were binned into 25 bins in log-space from $10^{27} - 10^{35}$\,erg.
-We perform the FFD  fits using the energy bin with the maximum flare rate as the base level, and then with all flare energies higher than that.
-We perform this cut  because lower energy bins may be incomplete, exhibiting a turnover in the FFD at lower energies.
-Moreover, the energy turnover in the FFD cannot be accurately modeled as a power-law.
+We fit the stars FFD slopes, approximated as a power-law, using the $T_\textrm{eff}$ and age bins described above. Flares were binned into 25 bins in log-space from $10^{27} - 10^{35}$\,erg.
+The FFD has a notable turnover energy, $E_\textrm{turnover}$, when our detection method is incomplete due the low-amplitude of those flares. The FFD slope is often fit to flares with
+energies $E \geq E_\textrm{turnover}$. We perform our fits following the same methodology. This turnover in the FFD cannot be accurately modeled with a power-law. We present our FFDs as a
+function of $T_\textrm{eff}$ and age in Figure~\ref{fig:simple_ffd_all}; points which were fit to measure the FFD slope are presented in black, while the full FFD is presented in gray.
 
-We fit the FFD using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}.
-Specifically, we fit for the slope, $\alpha$, y-intercept, $b$, and an additional noise term, $f$.
-This noise term  accounts for an underestimation of the errors in each bin.
-We initialized the MCMC fit with 300 walkers and ran our fit over 5000 steps.
-We discarded the first 100 steps upon visual inspection, after which the steps were fully burned-in.
+We fit the FFD using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}. Specifically, we fit for the slope, $\alpha$, y-intercept, $b$, and an additional noise term,
+$f$. This noise term  accounts for an underestimation of the errors in each bin. We initialized the MCMC fit with 300 walkers and ran our fit over 5000 steps.  We discarded the first 100
+steps upon visual inspection, after which the steps were fully burned-in. The measured FFD slopes, $\alpha$, are presented in Figure~\ref{fig:mcmc_results}. We approximate the error on the
+slope as the lower 16\textsuperscript{th} and upper 84\textsuperscript{th} percentiles from the MCMC fit.
 
-The full FFDs are presented in Figure~\ref{fig:simple_ffd_all}, along with 100 samples from the MCMC fit. The measured
-FFD slopes, $\alpha$, are presented in Figure~\ref{fig:mcmc_results}. We approximate the error on the slope as the lower 16\textsuperscript{th} and upper 84\textsuperscript{th}
-percentiles from the MCMC fit.
+Overall, we measure a shallower FFD for stars of all masses at $t_\textrm{age} < 300$~Myr. A shallower FFD indicates there are more high-energy flares. The measured FFD slopes are shallower
+than those measured using smaller samples of young stars. \cite{jackman21} fit the three FFDs for M3-M5, M0-M2, and K5-K8 stars younger than 40~Myr that had been observed with Next Generation
+Transit Survey. They measured slopes of $0.94 \pm 0.04$, $0.69 \pm 0.05$, $0.82 \pm 0.14$ per bin, which each contained $\leq 120$~flares.  It is also worth noting that the slopes measured
+here are based on up to an order of magnitude more flares per fit. Our sample also has a longer temporal baseline, allowing for the occurrence of more high-energy flares. Accumulating more
+high-energy flares in the FFD, if such events occur, will result in a shallower FFD slopes. TESS flare statistics for main sequence stars have indicated steeper FFDs \citep{feinstein22_criticality}.
+Therefore, the FFDs presented here are not strictly impacted by longer observations, but are the result of more high-energy flares on young stars.
 
-There is a $1-3\sigma$ discrepancy between the FFD slope measured in \cite{ilin21} and the work presented here at ages $\sim 120$\,Myr ($\alpha$ ranges from $-1.32 \pm 0.19 ~\textrm{to} -0.91 \pm 0.18$, depending on the $T_\textrm{eff}$ bin).
-\cite{ilin21} used the \textit{K2} 30-minute light curves for their analysis, compared with our TESS 2-minute light curves.
-Additionally, our sample has $\sim 2 \times$ the number of stars and $\sim 7 \times$ the number of flares than \cite{ilin21}.
-First, we test if these differences are driven by differences in sample binning.
-We reevaluate the FFDs assuming the $T_\textrm{eff}$ bins presented in Table 3 of \cite{ilin21}.
-We find $\alpha$ remains consistent with our presented values to within $\sim 1\sigma$ of the nearest temperature bin.
-Second, we reevaluate the FFDs assuming the total number of flares fit in \cite{ilin21}.
-Our sample has $\sim 2\times$ the number of stars and $\sim 7\times$ the number of flares than their sample.
-We draw $n_\textrm{fit, Ilin et al.
-(2021)}$ \citep[last column in Table 3 of ][]{ilin21} flares from our sample 100 times without replacement, refit the FFD, and take the average FFD slope from that sub-sample of flares to our results.
-We find $\alpha$ remains consistent with our presented values to $\sim 2\sigma$.
-We note that in most cases $n_\textrm{fit, Ilin et al.
-(2021)} < n_\textrm{fit, this work}$.
-Therefore, the increased disagreement in $\alpha$ could be due to smaller sample sizes.
+There is a $1-3\sigma$ discrepancy between the FFD slope measured in \cite{ilin21} and the work presented here at ages $\sim 120$\,Myr ($\alpha$ ranges from
+$-1.32 \pm 0.19 ~\textrm{to} -0.91 \pm 0.18$, depending on the $T_\textrm{eff}$ bin). \cite{ilin21} used the \textit{K2} 30-minute light curves for their analysis, compared with our TESS
+2-minute light curves. Additionally, our sample has $\sim 2 \times$ the number of stars and $\sim 7 \times$ the number of flares as in \cite{ilin21}. First, we test if these discrepancies
+are driven by differences in sample binning. We reevaluate the FFDs assuming the $T_\textrm{eff}$ bins presented in Table 3 of \cite{ilin21}. We find $\alpha$ remains consistent with our
+presented values to within $\sim 1\sigma$ of the nearest temperature bin. Second, we reevaluate the FFDs assuming the total number of flares fit in \cite{ilin21}. We
+draw $n_\textrm{fit, Ilin et al. (2021)}$ \citep[last column in Table 3 of ][]{ilin21} flares from our sample 100 times without replacement, refit the FFD, and take the average FFD slope
+from that sub-sample of flares to our results.  We find $\alpha$ remains consistent with our presented values to $\sim 2\sigma$. We note that in most cases
+$n_\textrm{fit, Ilin et al. (2021)} < n_\textrm{fit, this work}$. Therefore, the increased disagreement in $\alpha$ could be due to smaller sample sizes.
 
-Additionally, we test if the difference in $\alpha$ is driven by the cadence differences between \textit{K2} (30-minute) and TESS (2-minute).
-We bin all of the flares in our sample down the 30-minute cadence, re-fit for flare $A$ and ED, and recalculate the flare energy.
-We re-fit the FFD for this altered sample and measure an FFD slopes consistent to $\sim 1 \sigma$ with our presented in this work.
-Therefore, the discrepancy seen here is not driven by observational differences between \textit{K2} and TESS.
+Additionally, we test if the difference in $\alpha$ is driven by the cadence differences between \textit{K2} (30-minute) and TESS (2-minute). We bin all of the flares in our sample down
+to a 30-minute cadence, re-fit for flare $A$ and ED, and recalculate the flare energy. We re-fit the FFD for this altered sample and measure  FFD slopes consistent to $\sim 1 \sigma$ with
+those presented in this work. Therefore, the discrepancy seen here is not driven by observational differences between \textit{K2} and TESS.
 
-Finally, we test if the differences are driven by the energy ranges fit over.
-The CNN-based flare detection algorithm has previously been demonstrated to be less-biased against lower energy flares.
-Like this work, \cite{ilin21} fits the FFD across flare energies which are not affected by a reduced efficiency in the low-energy flare detection.
-In energy space, these fits begin between $E_f = 10^{32-33}$~erg, compared to our fits which begin between $E_f = 10^{31-32}$~erg (Figure~\ref{appendix:supp_ffds}).
-When we limit our sample to $E_f \geq 10^{32.5}$~erg, we find the FFD slopes become \textit{steeper} and more consistent with $alpha$ presented in \cite{ilin21}.
-Therefore, the difference in $\alpha$ between this work and \cite{ilin21} for stars with $t_\textrm{age} = 120 - 150$~Myr is driven by the lower energy flares, with which we are more complete to with TESS than \textit{K2}.
-
-The measured FFD slopes are shallower than those measured using smaller samples of young stars.
-\cite{jackman21} fit the three FFDs for M3-M5, M0-M2, and K5-K8 stars younger than 40~Myr that had been observed with Next Generation Transit Survey.
-They measured slopes of $0.94 \pm 0.04$, $0.69 \pm 0.05$, $0.82 \pm 0.14$ per bin, which each contained $\leq 120$~flares.
-It is also worth noting that the slopes measured here are based on up to an order of magnitude more flares per fit.
+Finally, we test if the differences are driven by the range of energies that are fit. The CNN-based flare detection algorithm has previously been demonstrated to be less-biased against lower
+energy flares. Like this work, \cite{ilin21} fit the FFD across flare energies which are not affected by a reduced efficiency in the low-energy flare detection, $E \geq E_\textrm{turnover}$.
+In energy space, these fits begin between $E_f = 10^{32-33}$~erg, compared to our fits which begin between $E_f = 10^{31-32}$~erg (Figure~\ref{appendix:supp_ffds}). When we limit our sample
+to $E_f \geq 10^{32.5}$~erg, we find the FFD slopes become \textit{steeper} and more consistent with the values of $\alpha$ presented in \cite{ilin21}. Therefore, the difference in $\alpha$
+between this work and \cite{ilin21} for stars with $t_\textrm{age} = 120 - 150$~Myr is driven by the lower energy flares, with which we are more complete to with TESS than \textit{K2}.
 
@@
         \caption{
-            Comparison of Rossby Number, $R_0$ and flare rate for young GKM stars.
-            We find no change in the average flare rate for GKM stars $< 250$\,Myr.
-            We see evidence that as $R_0$ increases, the average flare rate decreases.
-            This is similar to results presented in \cite{medina20}, however our sample extends this
-            trend to young GKM stars, while previous results were limited to nearby M dwarfs. The top row are
-            stars with ages $4.5 - 50$\,Myr; the bottom row are stars with ages $50 - 250$\,Myr. The
+            Comparison of Rossby Number, $R_0$ and flare rate for young GKM stars. For the younger sample (top row; $t_\textrm{age} = 4.5 - 50$~Myr), we find no correlations between flare
+            rate and $R_0$. For the slightly older sample (bottom row; $t_\textrm{age} = 50 - 250$~Myr), we find no change in the average flare rate for M stars. For K and G stars, we start
+            to see some evolution in this relationship. For K and G stars, we that as $R_0$ increases, the average flare rate decreases. This could indicate that as stars spin-down, their
+            flare activity also begins to decline. We find that for the full GKM sample of stars (bottom row, rightmost column), the relationship between $R_0$ and flare rate is best-fit by
+            a broken power law, with a turnover at $R_0 = 0.136$. For the younger full sample (top row, rightmost column), we find this relationship is best-fit by a single power law. The
             histograms are colored by number of stars in each bin.
@@
 
-The Rossby number, $R_0$, is a parameter which marginalizes over several properties which are known to affect the stellar dynamo, such as the rotation period and stellar mass.
-Specifically, in the context of stellar dynamo the Rossby number indicates the dominance of the convective verses rotational dynamo.
-It is defined as $R_0 = P_\textrm{rot}/\tau$, where $\tau$ is the convective turnover time.
-We convert our measured rotation periods to $R_0$,  approximating $\tau$ following the prescription in \cite{wright11}.
-We
+The Rossby number, $R_0$, is a parameter which incorporates  several properties which are known to affect the stellar dynamo, such as the rotation period and stellar mass. In the context of
+stellar dynamo the Rossby number indicates the dominance of the convective verses rotational dynamo. It is defined as $R_0 = P_\textrm{rot}/\tau$, where $\tau$ is the convective turnover
+time. We convert our measured rotation periods to $R_0$,  approximating $\tau$ following the prescription in \cite{wright11}. We
 equate the flare rates, $\mathcal{R}$, for individual stars as
@@
 \end{equation}
-In Equation (\ref{eq:fr}), $\mathcal{R}$ is the flare rate in units of day$^{-1}$, $t_\textrm{obs}$ is the total amount of time a target was observed with TESS, and $p_i$ is the probability that flare $i$ is a true flare as assigned by \texttt{stella}.
-We compare the calculated $R_0$ to measured flare rates for all stars we measured $P_\textrm{rot}$ for. The results are presented in Figure~\ref{fig:prot_histograms}.
+In Equation (\ref{eq:fr}), $\mathcal{R}$ is the flare rate in units of day$^{-1}$, $t_\textrm{obs}$ is the total amount of time a target was observed with TESS, and $p_i$ is the probability
+that flare $i$ is a true flare as assigned by \texttt{stella}. We compare the calculated $R_0$ to measured flare rates for all stars with measured $P_\textrm{rot}$. The results are presented
+in Figure~\ref{fig:prot_histograms}.
 
-From these results, we are able to evaluate the dependence of the flare rate on age, spectral type,  and $R_0$.
-We split the sample between stars younger and older than 50~Myr.
-This age roughly correlates to the age at which GKM stars turn onto the main sequence.
-The flare rate of stars younger than 50~Myr slightly decreases with increasing $R_0$.
-However, there is a significant amount of scatter in this relationship.
+From these results, we are able to evaluate the dependence of the flare rate on age, spectral type,  and $R_0$. We split the sample between stars younger and older than 50~Myr. This age roughly
+correlates to the age at which GKM stars turn onto the main sequence. The flare rate of stars younger than 50~Myr slightly decreases with increasing $R_0$. However, there is a significant amount
+of scatter in this relationship.
 
-As can be seen by comparing the upper and  lower panels in Figure ~\ref{fig:prot_histograms}, the flare rate dependence on Rossby number is most evident in older, more massive stars  between $50 - 300$~Myr.
-For M stars, we see minimal evolution in both the average flare rate and $R_0$ between the two samples.
-For K stars,  $R_0$ evolves more dramatically during the first 250~Myr while the scatter in the flare rate decreases.
-For G stars, the scatter in $R_0$ decreases  and the average flare rate across the sample decreases.
-We present a compiled histogram for all stars in our sample in the right column of Figure~\ref{fig:prot_histograms}.
+As can be seen by comparing the upper and  lower panels in Figure ~\ref{fig:prot_histograms}, the flare rate dependence on Rossby number is most evident in older, more massive stars  between
+$50 - 250$~Myr. There is minimal evolution in both the average flare rate and $R_0$ between the two samples for M stars. For K stars,  $R_0$ evolves more dramatically during the first 250~Myr
+while the scatter in the flare rate decreases. For G stars, the scatter in $R_0$ decreases and the average flare rate across the sample decreases. We present a compiled histogram for all stars
+in our sample in the right column of Figure~\ref{fig:prot_histograms}.
 
-To better understand this trend, we fit three functions to the flare rate Rossby number parameter space: (i) a constant value, (ii) a single power law, and (iii) a piece-wise function consisting of a constant value and a power law.
-We computed the $\chi^2$ between each of these fits and the data.
-For (iii), we fit for where the $R_0$ turnover should occur by computing the $\chi^2$ across a range of $R_0 = [0.09, 0.18]$.
-We weighted the data points based on the density of points in a given bin (Figure~\ref{fig:prot_histograms}).
-For stars $4.5 - 50$~Myr, we find the distribution is best-fit with a single power law with slope $m = -0.102 \pm 0.018$ and y-intercept $b = -0.660 \pm 0.017$.
-For stars $50 - 250$~Myr, we find the distribution is best-fit with a piece-wise function of the form
+To better understand this trend for the GKM sample, we fit three functions to the flare rate Rossby number parameter space: (i) a constant value, (ii) a single power law, and (iii) a piece-wise
+function consisting of a constant value and a power law.  We computed the $\chi^2$ between each of these fits and the data. For (iii), we fit for where the $R_0$ turnover should occur by
+computing the $\chi^2$ across a range of $R_0 = [0.09, 0.18]$. We weighted the data points based on the density of points in a given bin (Figure~\ref{fig:prot_histograms}). For  $4.5 - 50$~Myr
+old stars, the distribution is best-fit with a single power law with slope $m = -0.102 \pm 0.018$ and y-intercept $b = -0.660 \pm 0.017$. For stars $50 - 250$~Myr, the distribution is best-fit
+with a piece-wise function of the form:
 
@@
 \end{equation}
-In Equation (\ref{eq:piecewiseft}), $\mathcal{R}$ is the flare rate, $C = 0.269 \pm 0.007$, $m = -0.612 \pm 0.039$, and $b = -1.113 \pm 0.035$.
-The location of the turnover is consistent  with what has been measured in other observations of magnetic saturation for partially and fully convective stars \citep[e.g.
-$L_X/L_\textrm{bol}$; ][]{wright18}.
+In Equation (\ref{eq:piecewiseft}), $\mathcal{R}$ is the flare rate, $C = 0.269 \pm 0.007$, $m = -0.612 \pm 0.039$, and $b = -1.113 \pm 0.035$. The location of the turnover is consistent
+with what has been measured in other observations of magnetic saturation for partially and fully convective stars \citep[e.g. $L_X/L_\textrm{bol}$; ][]{wright18}.
 
-A similar relationship was discussed in \cite{Davenport16}.
-With a sample of 851,168 flares detected in both \textit{Kepler} 1- and 30-minute cadence data, \cite{Davenport16} found that the relationship between Rossby number and relative flare luminosity could be fit by a broken power law, with a break at $R_0 = 0.03$ and a slope of $\sim -1$ dominating higher $R_0$.
-While the metrics used between \cite{Davenport16} and this paper are different, both suggest a saturation in flares for stars with low $R_0$.
-Additionally, \cite{medina20} found a broken power-law relationship between $R_0$ and the flare rate for flares with $E_f > 3.16 \times 10^{31}$\,erg, the sample's completeness threshold.
-\cite{medina20} analyzed light curves of 419 low-mass ($M_\star = 0.1 - 0.3 M_\odot$) main-sequence stars in the Solar neighborhood as observed by TESS.
-This study found that the flare rate saturates at $log(\mathcal{R}) = -1.30 \pm -0.08$ for $R_0 < 0.1$ and rapidly declines for $R_0 > 0.1$.
-While neither of these previous studies allow for a direct comparison to our results, given the differences in sample selection, all point towards evidence of flare rate saturation for stars with low $R_0$ and a steep drop-off in flare rate for stars with higher $R_0$.
+With a sample of 851,168 flares detected in both \textit{Kepler} 1- and 30-minute cadence data, \cite{Davenport16} searched for a relationship between Rossby number and relative flare
+luminosity. This work determined that the relationship could be fit by a broken power law, with a break at $R_0 = 0.03$ and a slope of $m \sim -1$ dominating higher $R_0$. However, a single
+power law is slightly preferred over the broken power law. While the metrics used between \cite{Davenport16} and this paper are different, both suggest a saturation in flares for stars with
+low $R_0$. Additionally, \cite{medina20} found a broken power-law relationship between $R_0$ and the flare rate for flares with $E_f > 3.16 \times 10^{31}$\,erg, corresponding to the
+completeness threshold of their sample. \cite{medina20} analyzed light curves of 419 low-mass ($M_\star = 0.1 - 0.3 M_\odot$) main-sequence stars in the Solar neighborhood  observed by TESS.
+They found that the flare rate saturates at $log(\mathcal{R}) = -1.30 \pm -0.08$ for $R_0 < 0.1$ and rapidly declines for $R_0 > 0.1$. \cite{yang23} analysed 7,082 stars with measured
+$P_\textrm{rot}$ observed during TESS sectors 1–30, and found a broken-power law described the relationship between $\Delta$Flare$/L_\star$ for M dwarfs, with a break between $R_0 = 0.1 - 0.13$,
+which is consistent with this work. While there are differences in sample selection between our work and previous studies, all are consistent with flare rate saturation for stars with low $R_0$
+and a steep drop-off in flare rate for stars with higher $R_0 > 0.1$.
 
@@
 
-We search for evidence of variations of the FFDs as a function of Rossby number, $R_0$.
-This is motivated by the data  presented in \cite{seligman22}.
-In that work, they  modeled flares driven by magnetic reconnection events driven by rotational forces as well as convective dynamo.
-\cite{seligman22} found that stars with $R_0 < 0.13$ exhibited shallower FFD slopes than stars with $R_0 \geq 0.13$ to several sigma significance.
-The differences in the FFDs were indicative of relatively more high-energy flares to low-energy flares.
-This was interpreted as evidence of a more dominant rotational dynamo compared to the convective dynamo, which preferentially produced longer magnetic braids in the stellar coronae.
+We search for evidence of variations of the FFDs as a function of flare amplitude versus Rossby number, $R_0$. This is motivated by the data  presented in \cite{seligman22}. In that work, they
+modeled flares driven by magnetic reconnection events driven by rotational forces as well as convective dynamo.  \cite{seligman22} found that stars with $R_0 < 0.13$ exhibited shallower FFD
+slopes than stars with $R_0 \geq 0.13$ to several sigma significance. The differences in the FFDs were indicative of relatively more high-energy flares to low-energy flares. This was interpreted
+as evidence of a more dominant rotational dynamo compared to the convective dynamo, which preferentially produced longer magnetic braids in the stellar coronae.
 
-In this subsection, we test this theory with a much larger sample of stars (\nprot\ instead of $807$ stars).
-We fit the distributions separated by the fitted $R_0$ presented in Section~\ref{subsec:rossby}.
-In order to perform the fits, we follow the prescription described in greater detail in \cite{seligman22}.
-Here, we provide a brief summary of the prescription.
+In this subsection, we test this theory with a much larger sample of stars (\nprot\ instead of $807$ stars). We fit the distributions separated by the fitted $R_0$ presented in
+Section~\ref{subsec:rossby}. In order to perform the fits, we follow the prescription described in greater detail in \cite{seligman22}. Here, we provide a brief summary of the prescription.
 Specifically, we fit a truncated power-law distribution of the form,
@@
 \end{equation}
-In Equation (\ref{eq:dpda}),  $A$ is the amplitude of the flare, $A_*$ is a flare amplitude cutoff parameter and $\alpha_T$ is the slope, rather than $\alpha$.
-We fit the slopes using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}.
-We used the log-likelihood function in \cite{seligman22} and  fit for $A_*$ and $\alpha_T$.
-We initialized the MCMC fit with 200 walkers and evaluated the fit over 5000 steps.
-The first 1000 steps were discarded upon visual inspection.
-The results are presented in Figure~\ref{fig:truncated}.
+In Equation (\ref{eq:dpda}),  $A$ is the amplitude of the flare, $A_*$ is a flare amplitude cutoff parameter and $\alpha_T$ is the slope, rather than $\alpha$. We fit the slopes using the
+MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}. We used the log-likelihood function in \cite{seligman22} and  fit for $A_*$ and $\alpha_T$. We initialized the MCMC fit
+with 200 walkers and evaluated the fit over 5000 steps. The first 1000 steps were discarded upon visual inspection. The results are presented in Figure~\ref{fig:truncated}.
 
@@
         \caption{
-            Flare frequency distributions, as a function of flare amplitude, for stars with $R_0 \leq 0.12$ (red) and stars with $R_0 > 0.12$ (black).
-We present the best-fit model, and the best-fit values of the model slope and normalization factor in the legends.
-Our sample of $R_0 \leq 0.12$ includes 13,132 flares from 800 stars; our sample of $R_0 > 0.12$ includes 5,603 flares from 747 stars.
-We find the stars with smaller Rossby numbers have shallower slopes, consistent with more, high-energy flares and potentially larger convective regions \citep{seligman22}.
+            Flare frequency distributions, as a function of flare amplitude, for stars with $R_0 \leq 0.12$ (red) and stars with $R_0 > 0.12$ (black). We present the best-fit model, and the
+            best-fit values of the model slope and normalization factor in the legends. Our sample of $R_0 \leq 0.12$ includes 13,132 flares from 800 stars; our sample of $R_0 > 0.12$
+            includes 5,603 flares from 747 stars. We find the stars with smaller Rossby numbers have shallower slopes, consistent with more, high-energy flares and a more dominant rotational
+            dynamo \citep{seligman22}.
         }
@@
 
-We find that stars with $R_0 \leq 0.136$ have a best-fit slope of $\alpha_T = 1.076 \pm 0.020$, while stars with larger $R_0$ have a best-fit slope of $\alpha_T = 1.604 \pm 0.040$.
-\textcolor{red}{fill out more.}
+We find that stars with $R_0 \leq 0.136$ have a best-fit slope of $\alpha_T = 1.076 \pm 0.020$, while stars with larger $R_0$ have a best-fit slope of $\alpha_T = 1.604 \pm 0.040$. This
+result agrees with the results presented in \cite{seligman22}. This is not the first instance we have seen a correlation in FFDs as a function of $R_0$. \cite{candelaresi14} noted that
+faster rotating stars have higher superflare rates derived from \textit{Kepler} data. The spectroscopic survey presented in \cite{notsu19} found that the maximum flare energy decreased
+as $P_\textrm{rot}$, and consequently $R_0$, increased. \cite{mondrik19} identified flares across 2,226 stars observed with MEarth and found an increase in flare rate between stars with
+low $R_0 < 0.04$ and stars with intermediate $R_0 = (0.04, 0.44)$, and a subsequent decrease in flare rate for stars with high $R_0 > 0.44$. While our bins of stars by $R_0$ are not as
+fine as those presented in \cite{mondrik19}, the correlation in $\Delta R_0$ remains consistent.
+
+\section{Evidence for Stellar Cycles from Variable Flare Activity}\label{sec:cycles}
+
+The Sun undergoes an 11-year solar cycle during  which it oscillates between high and low magnetic activity. This magnetic cycle manifests  in a variety of observables. One of the primary
+indicators of the solar cycle is a stark change in the flare rate; this rate can vary by more than an order of magnitude between Solar maxima and minima \citep{webb94}. However, it is worth
+noting that other, shorter periodicities have been observed in Solar flares \citep{}. Moreover, energetics of the flares that are produced on the solar surface vary dramatically over the
+course of the solar cycle \citep{Bai1987,Bai2003}. Direct and indirect evidence  of the solar cycle have also been observed in radio flux, total solar irradiance, the magnitude and geometry
+of the magnetic field, coronal mass ejections affiliated with flares, geomagnetic activity, cosmic ray fluxes and radioisotopes in ice cores and tree rings.
+For a recent review, see \citet{Hathaway2015}.
+
+While other stars should also experience activity cycles like the Sun, they are more difficult to measure. Constraints on stellar cycles have predominantly relied on long baseline variations
+in stellar photometry \citep[see recent reviews by ][]{jeffers23, isik23}, typically observed at cadences which cannot resolve stellar flares. However,  tracing stellar cycles via stellar
+flares may be more reliable, as flares are a direct consequence of magnetic activity. \cite{} explored measuring the stellar cycle length of KIC 8507979, a star in the \textit{Kepler} field
+which was observed for 18 90-day quarters. \cite{scoggins19} found the flare rate decreased over each quarter, which could be fit by
+$L_\textrm{fl}/L_\textrm{Kp} = (-9.96 \pm 3.94) \times 10^{-2} \times t_\textrm{yr} + (2.43 \pm 0.11)$, where $t_\textrm{yr}$ is the time in years, and $L_\textrm{fl}/L_\textrm{Kp}$ is a
+parameterization of the \textit{Kepler} flare rate \citep{lurie15}.
+
+%It is possible that the length of the stellar cycle is related to the rotational period $P_\textrm{rot}$ or the Rossby number $R_0$ of the star as ... \citep{}. If this is the case,
+then stars with $P_\textrm{rot}$ will have shorter stellar cycle lengths.
+
+\subsection{Flare Observables from the Sun}
+
+Here, we explore observables from solar flares between 2002 and 2018 in the Reuven Ramaty High Energy Solar Spectroscopic Imager \citep[RHESSI;][]{lin02} flare
+catalog.\footnote{\url{https://hesperia.gsfc.nasa.gov/rhessi3/data-access/rhessi-data/flare-list/index.html}} The RHESSI mission observes the Sun in the hard X-ray
+(HXR; $> 25$~keV) and has detected over $100,000$ solar flares in 16 years of operations. These observations covered the second half of solar Cycle 23 and the beginning of
+solar Cycle 24. We use the publicly available RHESSI flare catalog to determine  metrics that would be most useful when searching for evidence of stellar cycles. One potential
+issue with this analysis is that the HXR observations from RHESSI and white-light observations from TESS may not be directly correlated. However, there is a close spatial and
+temporal correspondence between HXR and white-light flares on the Sun \citep{fletcher07, krucker11, kleint16}. Therefore, the HXR solar flares with energies between $25 - 50$~keV
+are likely representative of solar white-light flares, and are a comparable sample to our TESS sample. First, the total number of flares detected in the $25 - 50$~keV bandpass
+varied by 650~flares from solar maximum in 2002 to solar minimum in 2008. This variation correlates to a change in flare rate from $1.81$ to $0.02$ flares day$^{-1}$ on average.
+Second, the flare frequency distribution changes between solar minimum and maximum because the frequency of the highest-energy flares decreases.  Finally, the total flare luminosity
+relative to the total luminosity correlates with the stellar cycle. This is defined by \cite{lurie15} as
+
+\begin{equation}
+    \frac{L_\textrm{flare}}{L_\star} \equiv \frac{\xi_\textrm{flare}}{t_\textrm{exp}}
+\end{equation}
+
+where $L_\textrm{flare}$ is the total luminosity emitted by flares, $L_\star$ is the luminosity of the star, $\xi_\textrm{flare}$ is sum of the equivalent duration of all flares
+observed, and $t_\textrm{exp}$ is the exposure time of the observations. These results for the Sun are presented in the left-most column of Figure~\ref{fig:stellar_cycles}.
+
+\begin{sidewaysfigure*}[ht!]
+    \vspace{-10cm}
+    \script{stellar_cycles.py}
+    \begin{centering}
+        \includegraphics[width=\textwidth]{figures/stellar_cycles.pdf}
+        \caption{
+            Comparison of three flare-driven metrics in searching for evidence of stellar cycles. Each column contains information for the Sun (left), followed by TIC 142015852,
+            269797536, 270676943, and 278825715. The top row shows trends in the fractional luminosity emitted in flares, $L_{fl}/L_\textrm{TESS} \equiv \xi_\textrm{flare}/t_\textrm{exp}$
+            \citep{lurie15}. The second and third rows show the calculated flare rate and cumulative flare frequency distribution (FFD) respectively. For the Sun, we used the RHESSI X-ray
+            flare catalog and binned the flares per year from February 2002 - February 2014. The Sun shows clear trends in $\xi_\textrm{flare}/t_\textrm{exp}$ and flare rate over the 12-year
+            solar cycle. The cumulative FFD shows that (i) the overall number of flares decreases, which can be seen in the flare rate as well and (ii)  the high-energy flare end of the
+            distribution decreases. A quadratic polynomial is plotted to help guide the eye. It is important to note that these fits do not provide constraints on the length of potential
+            stellar cycles in these stars due to the limited baseline obtained with TESS thus far.
+We present the measured flare rates and fractional luminosity emitted for each star in Table~\ref{tab:cycles}
+        }
+        \label{fig:stellar_cycles}
+    \end{centering}
+\end{sidewaysfigure*}
+
+\subsection{Quantifying Flare Activity over 5 Years of TESS Observations}
+
+The TESS Extended Missions have provided a five-year baseline that we can use to search for evidence of stellar cycles. This is a comparable baseline to \textit{Kepler}, although with sparser
+sampling. We search for evidence of stellar cycles  within our sample of fast rotators. Our sample contains 108 stars which have been observed for $t_\textrm{obs} \geq 200$\,days across five
+years. We search for evidence of changes in the stellar magnetic activity by looking for correlations in (i) variations in the total luminosity emitted in flares  (ii) the total flare rate per
+year and (iii) annual changes in the FFD.  We group our observations by the year in which the observations were taken, even for the cases where the star was not continuously observed throughout
+that year (e.g. Sectors 1-26 are Year 1, Sectors 27-55 are Year 2, and Sectors 56-67 are Year 3.
+
+We searched our 108 candidates by eye for correlations in the aforementioned criteria. The correlations are categorized into the following four options: (i) \textbf{Positive}:  $E_\textrm{f, max}$
+and the total number of flares has increased over five years; (ii) \textbf{Negative}:  $E_\textrm{f, max}$ and the total number of flares has decreased over five years; (iii) \textbf{Trough}:
+$E_\textrm{f, max}$ and the total number of flares was greater in the first and third years observed with a minima in the second year; (iv) \textbf{Peak}:  $E_\textrm{f, max}$ and the total number
+of flares was fewer in the first and third years observed with a maxima in the second year.
+
+From these three observables, we identified eleven stars which all display evidence of scenario Peak, with the exception of one star displaying evidence of scenario Negative, which are presented in
+Figure~\ref{fig:stellar_cycles}. These stars are TIC
+142015852, 235056185, 260351540, 270676943, 272349442, 308186412, 339668420, 350559457, 391745863, 393490554, and 452357628.  Our sample includes seven early type M-stars, two late K-stars, one
+early K-star, and one G-star. TIC 272349442 is a candidate member of TW Hydrae ($t_\textrm{age} = 10 \pm 3$\,Myr), TIC 142015852, 270676943, 308186412, 339668420, 350559457, and 452357628 are
+candidate members of Carina ($t_\textrm{age} = 45 \pm 9$\,Myr), TIC 235056185 and  260351540 are candidate members of IC 2602 ($t_\textrm{age} = 52.5 \pm 2.95$\,Myr), and TIC 391745863 and 393490554
+are candidate members of the AB Doradus Moving Group ($t_\textrm{age} = 133 \pm 12.5$\,Myr).
+
+We report the measured $\xi_\textrm{flare}/t_\textrm{exp}$ and flare rates across all three years in presented in Figure~\ref{fig:stellar_cycles} in Table~\ref{tab:cycles}. Across our sample, we
+find the largest change in flare parameters in TIC 235056185, which has a $\Delta log_{10}(\xi_\textrm{flare} / t_\textrm{exp}) = 1.14$ and $\Delta \mathcal{R} = 0.5$. Additionally, we see some
+targets (e.g. TIC 350559457) become very flare quiet, going from $\mathcal{R} = 0.2$~day$^{-1}$ to $\mathcal{R} = 0.05$~day$^{-1}$, which is obvious when visually inspecting the light curve. For
+stars showing the Peak scenario, we find that the year before and after the peak do not necessarily return to the same value of $\xi_\textrm{flare} / t_\textrm{exp}$ and $\mathcal{R}$, although it
+does for some stars.
+
+\subsection{Flare Recovery per TESS Year}\label{subsec:inj-rec}
+
+The majority of stars identified with evidence of stellar cycles exhibit the Peak scenario. To determine if this is astrophysical or driven by some unknown instrumental systematic,
+we perform an injection-recovery test on this sub-sample of stars. Injection-recovery tests are used to address biases in our detection method.  Injection-recovery tests are typically
+not recommended for machine-learning detection techniques \citep{feinstein20}. However, we perform them because these are some of the first results of searching for evidence of stellar
+cycles via flare activity.
+
+We inject a total of 50 flares into each sector of data for our eleven stars. We draw the amplitude of our flares from a Gaussian distribution centered at a 3\% increase in flux, with a
+standard deviation of 1\%. We do not inject flares with amplitudes below 0.5\%. We used the Llamaradas Estelares flare model. We fit a line between flare amplitude and FWHM from our new
+catalog to extract an appropriate FHWM for any given amplitude. We added additional noise to the FHWM, as the relationship between amplitude and FWHM exhibits scatter similar to
+distribution of flare energy and ED shown in Figure~\ref{fig:flare_distribution}. Once the flares were injected, we followed the steps outlined in
+Sections~\ref{subsec2:Flareidentification} - \ref{subsec2:qualitychecks} to identify these injected flares.
+
+We considered a flare recovered if the $t_\textrm{peak}$ is within 15~minutes of the injected $t_\textrm{peak}$. We are able to recover 93\% of flares with $A \geq 3$\% and 80\% of flares
+with $A < 3$\%. This is consistent with previous results using this flare identification method \citep{feinstein20}. We note that there is a steep drop-off in flare recovery rate at
+$T_\textrm{mag} > 13$,  with average recovery rates dropping from  90\% to 70\%.  The variation in recovery rates between years observed by TESS ranges from $1 - 8$\% across all eleven
+targets. There is no correlation between recovery rate,  $\xi_\textrm{flare}/t_\textrm{exp}$ and flare rate, with the exception of TIC 142015852 and 339668420. We find an 8\% increase
+between Years 1 and 2, and a 3\% decrease between Years 2 and 3 in the recovery rate for TIC 142015852. Additionally, we find an 1\% increase between Years 1 and 2, and a 2\% decrease
+between Years 2 and 3 in the recovery rate for TIC 339668420. An 8\% change in the recovered flare rate correlates to $\Delta (\xi_\textrm{flare} / t_\textrm{exp}) = 0.09$, assuming
+ED~$= 1$\,minute, and a $\Delta \mathcal{R} = 0.03$. These estimates are smaller than the annual variations seen in flare statistics for these two stars, leading us to conclude that these
+variations are astrophysical.
+
+\subsection{Observing Peaks in Stellar Flare Activity}
+
+In the Section~\ref{subsec:inj-rec} we demonstrated that 10 out of 108 stars with $> 200$~days of observations exhibited Peak behavior in their variability patterns and found no bias in flare
+detection as a function of year. This is approximately what we would expect to find for an unbiased sample. Our analysis requires a large number of bright flares to be observable to
+characterize the stellar cycle. Therefore, our sample of objects should be biased towards stars that are undergoing a local maximum, rather than a local miinimum, in their activity cycle.
+
+It is not clear what the length of the activity cycles are for stars other than the Sun. For this order of magnitude estimate we therefore assume that the activity cycles of all stars in our
+sample are similar to that of the Sun. This approximation is valid   if the length of stellar cycles on average is not more than an order of magnitude different than that of the sun. By
+observing $N\sim$108 stars for a $\tau\sim$5 year baseline, assuming that each has a $P\sim10$ year activity cycle, we would expect that during that time period $\tau /P N\sim50$ stars should
+experience a peak in their stellar cycle during the observations. Moreover, our analysis will only be sensitive to activity cycles if there is not only a peak, but also lower activity in the
+year before and after the peak. Therefore, the number of stars that we would expect to identify that have a peak in year 2 should be $\tau /P N /3\sim16$. Therefore we would expect to identify
+$\sim16$ stars exhibiting a peak in their activity cycle during these observations, which is  similar to what we have found. However, it is likely that there is a variety of lengths of stellar
+cycles in our population and the exact correspondence between the number found and the number estimated is simply a manifestation of the crude order of magnitude approximation that we employed
+rather than an exact correspondence. Nevertheless, this represents  tentative detections of peaks in stellar activity cycles and that on average the length of these cycles is not an order of
+magnitude different than that of the Sun.
+
+\subsection{Validating Stellar Activity Cycles}
+
+The stars presented in this work present examples that stellar activity cycles could be identified by characterizing stellar flares and measuring flare rates. In addition to flare rates, it would
+be beneficial to conduct detailed spectroscopic follow-up of these candidates. For example, detailed monitoring of \ion{Ca}{2} H \& K lines for these targets could reveal if their activity cycles
+are similar to that seen from the flare rates. Unfortunately, our candidates are located too far south to have been included in the Mount Wilson HK project, which aimed to understand stellar
+chromospheric activity on a variety of timescales \citep{Wilson68}. Monitoring of the overall XUV luminosities of these targets could provide additional insights into the variability of the targets.
+Additionally, more continuous time-series photometry of these targets would provide more stringent constraints on the flare variability for these targets. While long time-series photometry,
+such as that achieved with TESS and \textit{Kepler} are ideal, more sparse but consistent photometric monitoring for stellar flares may provide useful additional supplemental data to TESS observations.
+This is especially true for the times when TESS is observing in the opposite ecliptic hemisphere.
+
+The TESS Full-Frame Images (FFIs) allow for the creation of light curves for objects in $\sim 95\%$ of the sky \citep[e.g.][]{feinstein19}. During its primary mission (July 2018 - July 2020),
+the TESS FFIs were taken every 30-minutes. During its first extended mission (July 2020 - September 2022), the FFI cadence was decreased to 10-minutes. Now, during its second extended mission
+(September 2022 - September 2025), the FFI cadence was again decreased to 3-minutes. At 3-minutes, we can more accurately identify and  resolve the structure of stellar flares \citep{howard22}.
+A detailed search of flare variability for stars in the TESS FFIs may provide a more statistical view of how flare rates change on long timescales, and if they can yield insights into stellar
+activity cycles.
 
@@
 
-X-ray luminosity surveys of stars have revealed a saturation limit with respect to
-the star's rotation period. Namely, there is no evolution in $L_X/L_\textrm{bol}$ for
-stars with $P_\textrm{rot} < 10$\,days \citep{Pizzolato03}.
+The stellar X-ray coronal emission is known to be a tracer of overall magnetic activity. Therefore,  it should theoretically depend on the dynamo of the star, and on observable parameters that
+are related to the dynamo such as the rotational period. Empirical evidence indicates that there are distinct saturated and non-saturated regimes for coronal X-ray emission from main sequence
+stars. Specifically, stellar X-ray luminosity surveys have revealed that the saturation limit depends on the stellar rotation period. Namely, there is no evolution in $L_X/L_\textrm{bol}$ for
+stars with $P_\textrm{rot} < 10$\,days \citep{Pizzolato03}. The rotation period is a good predictor of the X-ray luminosity for stars with longer $P_\textrm{rot}$.
 
-The Far- and Near-Ultraviolet (FUV/NUV) is another tracer of magnetic activity. Young
-stars are known to have excess luminosity in both of these wavelengths \citep{}. We use
-archival observations from the \textit{Galaxy Evolution Explorer}
-\citep[\textit{GALEX};][]{martin05} to search for trends in FUV/NUV saturation and flare
-rate saturation. \textit{GALEX} provides broad FUV photometry from $1350-1750 \angstrom$
-and NUV photometry from $1750-2750 \angstrom$. We crossmatch our targets with the \textit{GALEX}
-catalog. We follow the sample selection methods outline in \citep{schneider18}. We search
-a $10''$ radius around the coordinates of each target in our sample. We include targets with
-no bad photometric flags (e.g. \texttt{fuv\_artifact} or \texttt{nuv\_artifact == 0}) as defined
-in the catalog. This is recommended by the \textit{GALEX} documentation, as flags could be
-assigned due to bright star window reflection, dichroic reflection, detector run proximity,
-or bright star ghost. We exclude targets with measured magnitudes brighter than 15, which
-marks the saturation limit for both the FUV and NUV photometers \citep{morrissey07}.
+The Far- and Near-Ultraviolet (FUV/NUV) emission is another tracer of magnetic activity. Younger, more active stars display excess luminosity in both of these wavelengths \citep{Shkolnik2013}.
+We use archival observations from the \textit{Galaxy Evolution Explorer} \citep[\textit{GALEX};][]{martin05} to search for trends in FUV/NUV saturation and flare rate saturation, similar to the
+established X-ray trends. \textit{GALEX} provides broad FUV photometry from $1350-1750 \angstrom$ and NUV photometry from $1750-2750 \angstrom$. We crossmatch our target stars with the
+\textit{GALEX} catalog following the sample selection methods outline in \citep{schneider18}. Specifically, we search using a $10''$ radius around the coordinates of each target in our sample.
+We include targets with no bad photometric flags (e.g. \texttt{fuv\_artifact} or \texttt{nuv\_artifact == 0}) as defined
+in the catalog. It is recommended by the \textit{GALEX} documentation to exclude any objects with these flags associated. Additionally, we exclude targets with measured magnitudes brighter than
+15, which marks the saturation limit for both the FUV and NUV photometers \citep{morrissey07}.Based on these thresholds, we find that 462 stars in our sample have NUV photometry and 139 stars have
+FUV photometry.
 
-Based on these thresholds, we find that 462 stars in our sample have NUV photometry and
-139 stars have FUV photometry. We explore if flare rate saturation and FUV/NUV saturation
-are correlated with the derived $R_0$ per star. We present our results in Figure~\ref{fig:galex}.
-We present the measured FUV/NUV flux normalized by the J-band flux of the star, since it
-is the fractional flux which acts as an activity indicator. While bolometric luminosities would
-be a better normalizing factor, we find the majority of stars in our target do not have
-this parameter measured. To assess FUV/NUV correlations in a larger statistical sense, we thus
-keep the normalization to $f_J$.
+We investigate whether the saturation of flare rate and FUV/NUV emission are correlated with the derived $R_0$ in each star. We present our results comparing the FUV and NUV flux and the measured
+flare rate and Rossby number in Figure~\ref{fig:galex}. We present the measured FUV/NUV flux normalized by the J-band flux, which acts as an activity indicator. In theory, the bolometric luminosities
+should be a better normalization factor than the J-band flux. However, the majority of stars in our sample do not have bolometric luminosity  measurements. Therefore, we keep the normalization to
+$f_J$ while assessing FUV/NUV correlations for the larger statistical sample.
+
+While there is tentative evidence of trends between the flare rate and the Rossby number (see Section~\ref{subsec:rossby}), there is inconclusive evidence that the normalized FUV and NUV flux
+follow this trend. We note that  the number of stars in our sample which have \textit{GALEX} FUV measurements is small ($N_\textrm{stars} = 139$) and therefore might not be representative of the
+broader population. It is worth noting that the NUV flux traces the photosphere for many of these stars, as opposed to the X-rays which trace coronal emission. Additionally, the FUV still has
+contributions from the photosphere for G stars. Therefore, it is possible that the lack of a correlation between the regimes identified for X-ray emission is due to the fact that the UV is tracing
+different stellar atmospheric regions that are not associated with the magnetic activity. %This is indicative that the X-ray stellar activity-rotation relationship and saturation regimes may
+not hold for FUV and NUV flux.
 
@@
             Calculated FUV (left) and NUV (right) GALEX flux for stars in our
-            sample. We normalize these values by the J-band flux of the star.
-            We find no strong correlation between the NUV/FUV flux and the measured
+            sample normalized  by the stellar J-band flux.
+            There is no obvious correlation between the fractional NUV/FUV flux and the measured
             flare rate or Rossby number.
@@
             triangles, and G stars as squares. We note that $f_{NUV}$ traces the
-            photosphere of GK stars, and therefore may not be the best comparison
+            photosphere of G, K, and massive M stars, and therefore may not be the best comparison
             bandpass when looking for trends in magnetic activity.
@@
 
-\subsection{Comparison to Young Planet Host Stars}
+The FUV and NUV flux from \textit{GALEX} is a superposition of many different emission lines. These lines  trace various regions of the stellar atmosphere ranging from the corona to the
+photosphere depending on their formation temperatures. It is possible that the blending of lines produces the lack of correlation between FUV/NUV flux, $R_0$, and flare rate. Spectroscopic
+observations of targets with $R_0$ which span the transition out of the saturated regime may reveal a stronger relationship between these parameters. \cite{pineda21} reported evidence of broken
+power-law relationship between $R_0$ and FUV emission lines for $\sim 20$ stars observed with the Space Telescope Imaging Spectrograph on the \textit{Hubble} Space Telescope. Depending on the
+emission line analysed, \cite{pineda21} found a saturated regime for $R_0 < 0.18 - 0.24$, with a steep drop-off for higher $R_0$. Additionally, \cite{loyd21} evaluated the relationship between
+FUV emission lines and $R_0$ for 12  Tucana-Horologium ($t_\textrm{age} = 40$~Myr), 9 Hyades  ($t_\textrm{age} = 650$~Myr), and 7 field-aged ($t_\textrm{age} = 2-10$~Gyr) M stars. They found a
+saturated $log_{10}(R_0) = -0.876_{-0.061}^{+0.037}$, which is consistent with the X-ray flux and $R_0$ relationship.
 
-The all-sky observing strategy of TESS has revealed a new population of young transiting exoplanets.
-Characterizing the local environment for these planets is crucial to understanding their subsequent evolution
-to forming the mature population of planets. It is debated whether stellar flares are beneficial or detrimental
-to exoplanets. On one hand, \textcolor{red}{creates life}. On the other hand, stellar flares and affiliated
-coronal mass ejections can permanently alter atmospheric compositions \citep{chen21} and increase the amount of
-atmospheric mass stripped during the early stages of planet evolution \citep{feinstein20}. To understand the
-evolution of these new insightful young transiting exoplanets, we compare their measured flare rates to a more
-statistical sample of stars with similar ages and $T_\textrm{eff}$.
+The ROentgen Survey with an Imaging Telescope Array (eROSITA) instrument \citep{predehl07, predehl21} on the Russian Spectrum-RG mission is an all-sky X-ray survey from $\sim 0.2-8$~keV. The
+synergies between eROSITA and TESS are already being explored. \cite{magaudda22}, used the measured $L_X$ from eROSITA and $P_\textrm{rot}/R_0$ from TESS for 704 M dwarfs to reconfirm the known
+X-ray activity relationship.
+It is possible that these combined data may show a  clearer relationship between $R_0$ and flare rate in the X-ray than shown here  in the FUV/NUV (Figure~\ref{fig:galex}).
 
-We measured the flare rates of planet hosting stars $< 300$\,Myr, comparable to the ages of our primary sample.
-We followed the methods outlined in Section~\ref{sec:methods} to detect and vet flares. For each star, we created
-an equivalent sample with respect to both age and $T_\textrm{eff}$ to compare the flare rates too. We considered
-stars with ages $\pm 30$\,Myr of the planet hosting star and $T_\textrm{eff} \pm 1000$\,K. We calculate the flare rate
-following Equation~\ref{eq:fr}. We present
-the flare rates of planet-hosting stars and a comparable sample of stars in Figure~\ref{fig:yp_rates}
-and report the measured rates in Table~\ref{tab:yp_rates}. For the comparable sample, we report the
-median flare rate, and the lower 16\textsuperscript{th} and upper 84\textsuperscript{th} percentiles.
+\subsection{Flare Rates of Young Planet Host Stars Verses Comparison Sample}
+
+The all-sky observing strategy of TESS has revealed a new population of young transiting exoplanets.  Characterization of the  environment of these planets is crucial to understanding their
+subsequent evolution. Specifically, the stellar environment can impact how these young planets evolve into their mature counterparts.
+
+It is unclear whether stellar flares are beneficial or detrimental to the habitability of exoplanets. It is possible that stellar flares can trigger the development of prebiotic chemistry
+\citep{Rugheimer2015,airapetian16,Ranjan2017,Rimmer2018}. On the other hand, stellar flares and affiliated coronal mass ejections can permanently alter atmospheric compositions \citep{chen21}.
+This alteration may increase the amount of atmospheric mass stripped during the early stages of planet evolution \citep{feinstein20}. Therefore,  understanding the environment of young
+transiting exoplanets can  provide insight into their evolution.
+
+To this end we compare  measured flare rates of young, planet hosting stars to a statistical sample of stars with similar ages and $T_\textrm{eff}$ that do not have confirmed short-period planets.
+Specifically, we measured the flare rates of planet hosting stars with ages $< 300$\,Myr, comparable to the ages of our primary sample. We followed the methods outlined in Section~\ref{sec:methods}
+to detect and vet flares for the planet-hosting stars.
+
+For our comparison sample, we considered stars with ages $\pm 30$\,Myr of the planet hosting star and $T_\textrm{eff} \pm 1000$\,K. For each of the stars in the control samples, we calculate the
+flare rate following Equation~\ref{eq:fr}. We present the flare rates of planet-hosting stars and a comparable sample of stars in Figure~\ref{fig:yp_rates} and report the measured rates in
+Table~\ref{tab:yp_rates}. For the control samples, we report the median flare rate, and the lower 16\textsuperscript{th} and upper 84\textsuperscript{th} percentiles.
+
+Flare rates are slightly diminished for the majority of planet hosting stars compared to the control sample. This could be interpreted as evidence that the presence of planets inhibits magnetic
+reconnection events and activity, or that the presence of flares biases transit-detection algorithms. However, for all cases where the flare rates are diminished in the presence of a short-period
+planet, the difference between the flare rates are within 1$-\sigma$ and not statistically significant.
+
+There are a handful of cases where stars hosting short-period planet exhibit drastically higher flare rates. The most dramatic case is for the 23 Myr AU Mic \citep{jeffries05,malo14,Mamajek14},
+where the flare rate is more than an order of magnitude higher than in the control sample.  AU Mic and its transiting planets are generally considered as a benchmark laboratory for understanding
+the impact of stellar activity on young exoplanet atmospheres. The system hosts an  extended debris disk \citep{kalas04, liu04, metchev05} along with \textit{two} short-period transiting planets
+\citep{plavchan20, martioli21, gilbert22}. It is worth noting that this flare rate is consistent with that measured by \citet{gilbert22, feinstein22_aumic}, and is not attributed to star-planet
+interactions \citep{ilin22}. In addition to this, HIP 67522, DS Tuc A, and TOI 451 all exhibit higher flare rates than the comparison sample.
+
+It is unclear what differentiates the planet hosting systems with higher flare rates from the control sample. \cite{france18} and \cite{behr23} found that planet hosting stars are less active
+than an equivalent control sample of field age stars in the UV. In Figure~\ref{fig:yp_rates} the color of the points corresponds to the effective temperature of the star. It appears that the
+flare rates of the planet hosting stars compared to the control sample is randomly distributed with respect to the effective temperature of the star. It is possible that there is a small age
+effect: the systems with higher flare rates are some of the youngest planet hosting stars: HIP 67522 is $17 \pm 2$ Myr, AU Mic is $22 \pm 3$ Myr, DS Tuc is $45 \pm 4$  Myr and TOI 451 is $120 \pm 10$ Myr.
+There is a slight preference for the younger systems to exhibit elevated flare rates, but this is marginal evidence at best. Future observations of these systems with elevated flare rates may
+reveal what causes this feature.
 
@@
         \caption{
-            Comparison of flare rates from young planet host stars with respect to
-            a comparable sample with respect to age [Myr] and $T_\textrm{eff}$ [K].
-            Circles represent the flare rate of the host star (name along the x-axis);
-            vertical bars represent the lower 16\textsuperscript{th} and upper
-            84\textsuperscript{th} percentiles for the comparable sample. The majority
-            of young planet hosting stars have flare rates towards the lower end of the
-            comparable sample's distribution. A handful of hosts have more flares, including
-            HIP 67522, AU Mic, DS Tuc A, and TOI 451. We find no correlation between
-            age or $T_\textrm{eff}$ that may result in young planet hosts having more or fewer
-            flares than a larger comparable sample. The measured flare rates are presented in
+            Comparison of flare rates from young planet host stars with respect to a comparable sample with respect to age [Myr] and $T_\textrm{eff}$ [K].
+Circles represent the flare rate of the host star (name along the x-axis); vertical bars represent the lower 16\textsuperscript{th} and upper 84\textsuperscript{th} percentiles for the comparable sample.
+The majority of young planet host stars have comparable flare rates to the lower end of the comparison sample.
+A handful of hosts have more flares, including HIP 67522, AU Mic, DS Tuc A, and TOI 451.
+We find no correlation with spectral type or age which may indicate why these host stars are relatively flare quiet.
+The measured flare rates are presented in
             Table~\ref{tab:yp_rates}.
@@
 
-\begin{deluxetable}{l r r r}[!ht]
+\begin{deluxetable}{l r r r r}[!ht]
 \tabletypesize{\footnotesize}
@@
 \tablehead{
-\colhead{Host Name} & \colhead{Age} & \colhead{Flare Rate} & \colhead{Comp. Sample} \\
+\colhead{Host Name} & \colhead{Age} & \colhead{Flare Rate} & \colhead{Comp. Sample} & \colhead{$N$} \\
  & \colhead{[Myr]} & \colhead{[day$^{-1}$]} & \colhead{Flare Rate [day$^{-1}$]}
@@
 \startdata
-TOI 1227 &  $11 \pm 2$ &  0.008  & $0.119_{-0.046}^{+0.148}$ \\
-HIP 67522 & $17 \pm 2$ &  0.169  & $0.046_{-0.020}^{+0.069}$ \\
-AU Mic & $22 \pm 3$ &  2.218  & $0.133_{-0.046}^{+0.171}$ \\
-V1298 Tau & $23 \pm 4$ &  0.022  & $0.074_{-0.033}^{+0.091}$ \\
-HD 109833 & $27 \pm 3$ & 0.000  & $0.046_{-0.020}^{+0.070}$ \\
-KOI-7913 & $36 \pm 10$ &  0.031  & $0.134_{-0.045}^{+0.162}$ \\
-KOI-7368 & $36 \pm 10$ &  0.029  & $0.064_{-0.030}^{+0.087}$ \\
-DS Tuc & $45 \pm 4$ &  0.420  & $0.056_{-0.024}^{+0.078}$ \\
-TOI 942 & $50_{-20}^{+30} $ &  0.040  & $0.086_{-0.038}^{+0.117}$ \\
-TOI 451 & $120 \pm 10$ &  0.128  & $0.071_{-0.029}^{+0.085}$ \\
-HIP 94235 & $133_{-20}^{+15}$ &  0.020  & $0.051_{-0.017}^{+0.079}$ \\
-TOI 1860 & $133 \pm 26$ &  0.008  & $0.067_{-0.025}^{+0.086}$ \\
-TOI 1807 & $180 ± 40$ &  0.013  & $0.060_{-0.022}^{+0.085}$ \\
-HD 18599 & $200_{-70}^{+200} $ & 0.000 & $0.025_{-0.015}^{+0.044}$ \\
-TOI 2076 & $204 \pm 50$ & 0.000 & $0.092_{-0.045}^{+0.091}$ \\
-HD 110082 & $250_{-70}^{+50} $ & 0.000 & $0.047_{-0.020}^{+0.067}$ \\
+TOI 1227 &  $11 \pm 2$ &  0.008  & $0.065_{-0.042}^{+0.074}$ & 168 \\
+\textbf{HIP 67522} & $17 \pm 2$ &  0.169  & $0.081_{-0.043}^{+0.099}$ & 368 \\
+\textbf{AU Mic} & $22 \pm 3$ &  2.218  & $0.104_{-0.066}^{+0.188}$ & 590 \\
+V1298 Tau & $23 \pm 4$ &  0.022  & $0.116_{-0.07}^{+0.107}$ & 300 \\
+HD 109833 & $27 \pm 3$ & 0.000  & $0.077_{-0.039}^{+0.097}$ & 415 \\
+KOI-7913 & $36 \pm 10$ &  0.031  & $0.152_{-0.094}^{+0.165}$ & 312 \\
+KOI-7368 & $36 \pm 10$ &  0.029 & $0.116_{-0.071}^{+0.107}$ & 285 \\
+\textbf{DS Tuc} & $45 \pm 4$ &  0.420  & $0.104_{-0.061}^{+0.104}$ & 281 \\
+TOI 942 & $50_{-20}^{+30} $ &  0.040  & $0.092_{-0.049}^{+0.146}$ & 120 \\
+\textbf{TOI 451} & $120 \pm 10$ &  0.128  & $0.059_{-0.03}^{+0.136}$ & 204 \\
+HIP 94235 & $133_{-20}^{+15}$ & 0.020 & $0.048_{-0.028}^{+0.094}$ & 165 \\
+TOI 1860 & $133 \pm 26$ &  0.008  & $0.049_{-0.026}^{+0.108}$ & 207 \\
+TOI 1807 & $180 ± 40$ &  0.013  & $0.06_{-0.038}^{+0.11}$ & 53 \\
+HD 18599 & $200_{-70}^{+200} $ & 0.000 & $0.033_{-0.02}^{+0.066}$ & 22 \\
+TOI 2076 & $204 \pm 50$ & 0.000 & $0.083_{-0.041}^{+0.122}$ & 55 \\
+HD 110082 & $250_{-70}^{+50} $ & 0.000 & $0.088_{-0.045}^{+0.045}$ & 2 \\
 \enddata
+\tablecomments{$N$ is the total number of stars used to calculate the comparable sample flare rate. We highlight host stars with  flare rates higher than those in the comparison sample.}
 \end{deluxetable}
-
-\subsection{Evidence of Stellar Cycles}
-
-The Sun goes through a 12-year solar cycle, which oscillates between times of high and low activity.
-The solar cycle manifests itself in a variety of observables, including a change in the flare rate, by a factor of 10 \citep{}, and the flare energies released \citep{}.
-Constraints of stellar cycles have predominantly relied on photometry \citep[see recent review by ][]{cycleReview}.
-However, tracing stellar cycles via stellar flares may be more reliable, as flares are a direct consequence of magnetic activity.
-\cite{} explored measuring the stellar cycle length of KIC 8507979, a star in the \textit{Kepler} field which was observed for 18 90-day quarters.
-They found the flare rate decreased over each quarter, which could be fit by $L_\textrm{fl}/L_\textrm{Kp} = (-9.96 \pm 3.94) \times 10^{-2} \times t_\textrm{yr} + (2.43 \pm 0.11)$, where $t_\textrm{yr}$ is the time in years, and $L_\textrm{fl}/L_\textrm{Kp}$ is a parameterization of the \textit{Kepler} flare rate as defined by \citep{Hawley14}.
-
-It is possible that the length of the stellar cycle is related to the $P_\textrm{rot}$/ $R_0$ of the star as ...
-\citep{}.
-If this is the case, then stars with $P_\textrm{rot}$ will have shorter stellar cycle lengths.
-The TESS Extended Mission has provided a five-year baseline, similar to \textit{Kepler}, although the sampling is sparser.
-Within our sample of fast rotators, we searched for evidence of stellar cycles.
-Our sample contains 31 stars which have been observed for $t_\textrm{obs} \geq 400$\,days and $n_\textrm{flare} > 100$.
-
-We search for evidence of changes in the stellar magnetic activity by looking at (i) the maximum flare energy in a given period of time and (ii) the flare rate over that same period of time.
-We grouped our observations by year observed, even if the star was not continuously observed throughout that year.
 
@@
 
-In this work, we present the first measured flare rates for stars $< 300$\,Myr using
-TESS 2-minute cadence observations. We identified originating 28,822 flares from
-3,983 stars. The results of our work are summarized as follows:
+In this work, we present the first measured flare rates for stars $< 300$\,Myr using TESS 2-minute cadence observations.
+We identified \nflares\ flares from \nflarestars\ stars (Figures~\ref{fig:sample} and \ref{fig:flare_distribution}).
+The results of our work are summarized as follows:
 
 \begin{enumerate}
-  \item We measured the flare-frequency distribution (FFD) slope, $\alpha$, for samples
-  of flares binned by age and $T_\textrm{eff}$. We find $\alpha$ saturates at
-  $\alpha = -0.5$ for stars younger than 300\,Myr and declines after that age.
-  This is the first evidence that, like other tracers of stellar magnetic activity,
-  flare rates saturate across spectral types.
-  \item We measured the y-intercept, $\beta$, for the same bins of flares. We find
-  that ...
-  \item We measured the rotation periods, $P_\textrm{rot}$ for \textcolor{red}{n}
-  stars in our sample using the open-source Python package \texttt{michael}.
-  \item We measured the slope of a truncated power-law, $\alpha_T$, for the same
-  bins of flares. Additionally, we measured $\alpha_T$ as a function of Rossby
-  number, $R_0$.
+  \item We measured the flare-frequency distribution (FFD) slope, $\alpha$, for samples of flares binned by age and $T_\textrm{eff}$.
+We find $\alpha$ saturates at $\alpha = -0.6 ~ \textrm{to} -0.2$ for stars younger than 300\,Myr and declines after that age (Figure~\ref{fig:mcmc_results}).
+This is the first evidence that flare rates saturate across spectral types, as do  other tracers of stellar magnetic activity,.
+
+  \item We measured rotation periods for \nprot\ stars and find that the relationship between flare rate and Rossby number, $R_0$, is best described as a piece-wise function with a turnover at $R_0 = 0.136$ for stars $t_\textrm{age} > 50$\,Myr (Figure~\ref{fig:prot_histograms}).
+Additionally, we find that stars with $R_0 \leq 0.136$ have a shallower FFD than stars with $R_0 > 0.136$, which is evidence of a more dominant rotational dynamo compared to the convective dynamo (Figure~\ref{fig:truncated}); this is consistent with results presented in \cite{seligman22}.
+
+  \item We searched for evidence of far- and near-Ultraviolet (FUV/NUV) flux saturation as a function of $R_0$, similar to what is seen in the X-ray, by cross matching our sample with the \textit{GALEX} catalogs.
+We find no correlation between the FUV and NUV flux with flare rate (Figure~\ref{fig:galex}).
+The NUV (and for the G-type stars, the FUV) flux traces the photosphere for many of the stars in our sample, unlike the X-ray which traces the corona.
+Spectrally-resolved NUV and FUV observations where the chromospheric emission lines can be  isolated may be a more promising means of investigating this connection.
+Future synergies between eROSITA and TESS may reveal such relationships as well.
+
+  \item We compared the flare rates of planet-hosting young stars with a comparable sample with $t_\text{age} = t_\textrm{age, host} \pm 30$\,Myr and $T_\textrm{eff} = T_\textrm{eff, host} \pm 1000$\,K.
+We find that the majority of planet-hosting stars are flare inactive relative to a larger population of similar stars (although not to a statistically significant level), with the exception of HIP~67522, AU~Mic, DS~Tuc, and TOI~451 (Figure~\ref{fig:yp_rates}).
+
+  \item We searched for evidence of long-term stellar cycles by evaluating changes in flare rates and FFDs  over five years of TESS observations.
+We identified ten candidates which show potential evidence of a local maxima in their stellar cycle, and one candidate which shows a decline in flare activity (Figure~\ref{fig:stellar_cycles}).
+We determine that these maxima are not due to flare-detection biases via injection recovery tests.
+While we are unable to obtain stellar cycle timescales from three data points, these results highlight the insights flares can bring to understanding stellar dynamos for targets with more TESS observations (e.g.
+stars in the continuous viewing zones) and the use of future TESS extended missions.
+
 \end{enumerate}
@@
 
-We thank Darryl Seligman and David Wilson for thoughtful insights and useful
-conversations. This work made use of the open-source package,
-\textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes
-reproducible publications. ADF acknowledges funding from ...
+\section{acknowledgements}
+
+We thank David Wilson for thoughtful insights and useful conversations.
+This work made use of the open-source package, \textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes reproducible publications.
+ADF acknowledges funding from NASA through the NASA Hubble Fellowship grant HST-HF2-51530.001-A awarded by STScI.
+DZS is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-2202135.
+This research award is partially funded by a generous gift of Charles Simonyi to the NSF Division of Astronomical Sciences.
+The award is made in recognition of significant contributions to Rubin Observatory’s Legacy Survey of Space and Time.
 
@@
 
-Here, we present all of our best-fit slopes and intercepts for various flare-frequency distributions (FFDs) fit throughout this work.
-We include our fits outlined in Sections~\ref{subsec:energy_ffd}.
+In this appendix we present all of our best-fit slopes and intercepts for various flare-frequency distributions (FFDs) fit throughout this work.
+The fits outlined in Sections~\ref{subsec:energy_ffd} are included.
 We present the FFDs as a function of energy in Figure~\ref{fig:simple_ffd_all}.
-We show 100 random draws from our MCMC fitting to these distributions as orange lines.
+100 random draws from our MCMC fitting to these distributions are shown as orange lines.
 We fit each distribution with $E > 10^{29}$\,erg, which roughly represents the turnover in each distribution.
@@
 
+\vspace{3mm}
+
 \begin{figure*}[ht!]
-    \script{simple_ffd_all.py}
+    %\script{simple_ffd_all.py}
     \begin{centering}
@@
             Flare frequency distributions (FFDs) for subgroups of stars, clustered
-            by age and effective temperature, $T_\textrm{eff}$. Flares were binned
+            by age and effective temperature, $T_\textrm{eff}$. Flares were sorted
             into 25 bins in log-space from $10^{27} - 10^{35}$\,erg. We fit the FFD
-            from the turn-over in the binned flares, likely a result of very low-energy
-            flares being missed in our flare-detection algorithm. The bins used to fit
+            from the turn-over in the binned flares, likely a result of  low-energy
+            flares  missed by the flare-detection algorithm. The bins used to fit
             the FFD are shown in black, while all bins are shown in gray. We ran an MCMC
@@
 \tablehead{
-\colhead{$T_\textrm{eff}$ [K]} & \colhead{Age [Myr]} & \colhead{$\alpha_\textrm{E}$} & \colhead{$\sigma_{\alpha_\textrm{E}}$} & \colhead{$\beta_\textrm{E}$} & \colhead{$\sigma_{\beta_\textrm{E}}$} &  \colhead{$n_\textrm{E, fit}$} & \colhead{$N_\textrm{E}$} %& \colhead{$\alpha_\textrm{T}$} & \colhead{$\sigma_{\alpha_\textrm{T}}$} & \colhead{$A_*$} & \colhead{$\sigma_{A_*}$} &  \colhead{$n_\textrm{T, tot}$} & \colhead{$n_\textrm{T, fit}$} & \colhead{$N_\textrm{T}$}
+\colhead{$T_\textrm{eff}$ [K]} & \colhead{Age [Myr]} & \colhead{$\alpha_\textrm{E}$} & \colhead{$\sigma_{\alpha_\textrm{E}}$} & \colhead{$\beta_\textrm{E}$} & \colhead{$\sigma_{\beta_\textrm{E}}$} &  \colhead{$n_\textrm{E, fit}$} & \colhead{$N_\textrm{E}$}
 }
@@
 
+\begin{deluxetable*}{l | r r r | r r r}[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{Evidence of stellar cycles from variable flare properties \label{tab:cycles}}
+\tablehead{
+\colhead{TIC} & \colhead{} & \colhead{log$_{10}(\xi_\textrm{flare}/t_\textrm{exp})$} & \colhead{}  & \colhead{} & \colhead{$\mathcal{R}$ [d$^{-1}$]} \\
+\hline
+\colhead{} & \colhead{Year 1} & \colhead{Year 2} & \colhead{Year 3}  & \colhead{Year 1} & \colhead{Year 2} & \colhead{Year 3}
+}
+\startdata
+142015852 & 0.61 & 1.26 & 0.69 & 0.31 & 0.58 & 0.38 \\
+270676943 & 1.26 & 1.28 & 0.55 & 0.72 & 0.71 & 0.43 \\
+272349442 & 0.80 & 1.10 & 0.93 & 1.98 & 2.03 & 1.86 \\
+308186412 & 1.54 & 2.00 & 1.43 & 0.95 & 0.99 & 0.93 \\
+391745863 & 1.49 & 1.56 & 1.33 & 0.38 & 0.44 & 0.37 \\
+393490554 & 1.79 & 1.88 & 1.77 & 0.97 & 1.42 & 1.17 \\
+452357628 & 1.03 & 1.58 & 1.21 & 0.80 & 0.87 & 0.80 \\
+235056185 & 0.73 & 0.89 & -0.41 & 0.74 & 0.61 & 0.24 \\
+260351540 & 1.09 & 0.78 & 0.46 & 0.24 & 0.15 & 0.09 \\
+339668420 & 0.30 & 0.83 & 0.37 & 0.28 & 0.53 & 0.16 \\
+350559457 & 1.15 & 1.38 & -0.19 & 0.20 & 0.21 & 0.05\\
+\enddata
+\end{deluxetable*}
+
+\software{%
+    numpy \citep{numpy},
+    matplotlib \citep{matplotlib},
+    scipy \citep{jones01},
+    lightkurve \footnote{\url{https://doi.org/10.5281/zenodo.2557026}}, banyan-$\Sigma$ \citep{gagne18},
+    astropy \citep{astropy:2013, astropy18}, \texttt{stella} \citep{stella_joss, feinstein20}, tensorflow \citep{Abadi2016}, astroquery \citep{astroquery19}
+    }
+
+\facility{TESS}
+
 \bibliography{bib}
@@
 \end{document}
-feinstein20

### 2024-01-23 src/tex/ms.tex
updated abstract

@@
 
-Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with surface magnetic reconnection events. Stellar magnetic activity generally decreases as a
-function of both age and Rossby number, $R_0$, a measure of the relative importance of the convective and rotational dynamos.  Young stars ($<300$ Myr) have typically been
-overlooked in population-level flare studies because of the lack of long baseline observations and challenges with flare-detection methods. Here, we select a sample of stars
-that are members of 26 nearby  moving groups, clusters, or associations with ages $<$300~Myr  that have been observed by the Transiting Exoplanet Survey Satellite (TESS) at
-2-minute cadence.  With this sample of \nstars\ stars, we identified \nflares\ flares originating from \nflarestars\ stars. Moreover, we robustly measured the rotation periods
-of \nprot~stars within this population. We measure the flare frequency distribution (FFD) slope as a function of both age and spectral type and find the FFD slope, $\alpha$,
-saturates for all spectral types at $\alpha \sim -0.5$ and is constant over the 300~Myr. Additionally, we find that flare rates for stars $t_\textrm{age} = 50 - 250$~Myr are
-saturated below $R_0 < 0.14$, which is consistent with other indicators of magnetic activity. Taking advantage of the long temporal baseline of TESS, we search for evidence
-of annual flare rate variability. We present eleven young stars which tentatively show evidence of flare rate variations across five years of TESS data, potentially correlated
-with long term stellar activity cycles. Additionally, we cross match our entire sample  with \textit{GALEX} and find no correlation between flare rate and Far- and Near-Ultraviolet
-flux. Finally, we find the flare rates of planet hosting stars are relatively lower than a  comparable, larger samples of stars. This trend may have ramifications for the atmospheric
-evolution of young, short-period exoplanets.
+Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with surface magnetic reconnection events.
+Stellar magnetic activity generally decreases as a
+function of both age and Rossby number, $R_0$, a measure of the relative importance of the convective and
+rotational dynamos.  Young stars ($<300$ Myr) have typically been
+overlooked in population-level flare studies due to challenges with
+flare-detection methods. Here, we select a sample of stars
+that are members of 26 nearby  moving groups, clusters, or associations with ages $<$300~Myr  that have been observed
+by the Transiting Exoplanet Survey Satellite (TESS) at
+2-minute cadence.  We identified \nflares\ flares originating from \nflarestars\
+stars and robustly measure the rotation periods of \nprot~stars. We measure and find the flare frequency
+distribution (FFD) slope, $\alpha$,
+saturates for all spectral types at $\alpha \sim -0.5$ and is constant over 300~Myr. Additionally, we find that
+flare rates for stars $t_\textrm{age} = 50 - 250$~Myr are
+saturated below $R_0 < 0.14$, which is consistent with other indicators of magnetic activity. We find evidence
+of annual flare rate variability in eleven stars, potentially correlated with long term stellar activity cycles.
+Additionally, we cross match our entire sample  with \textit{GALEX} and find no
+correlation between flare rate and Far- and Near-Ultraviolet flux.
+Finally, we find the flare rates of planet hosting stars are relatively lower than comparable, larger samples
+of stars, which may have ramifications for the atmospheric
+evolution of short-period exoplanets.
 
@@
 accurately account for and capture  this variation when operating on different sectors. Moreover, the original CNNs were only trained on a sample of 1,228 stars. This training sample
-does not necessarily encapsulate a sufficient distribution  of variable stars types, such as eclipsing binaries, RR Lyraes, and fast rotators with $P_\textrm{rot} < 1$~day, which
+does not necessarily encapsulate a sufficient distribution  of variable stars types, such as eclipsing binaries, RR Lyraes, and fast
+rotators with $P_\textrm{rot} < 1$~day \citep{lawson19}, which
 results in the CNNs not being able to properly distinguish these temporal features from flares. We therefore apply additional

### 2024-04-30 src/tex/ms.tex
referee report edits

@@
 
-Stellar flares are the radiation component of magnetic reconnection events \citep{benz10}. Such events are readily seen on the Sun \citep{carrington1859, lu91, fletcher11},
-particularly during the maximum in the solar cycle \citep{webb94}. Solar flares can be used as proxies for magnetic activity occurring on other stars
-\citep{feigelson99, berdyugina05, kowalski10, feinstein22_criticality}. Additionally, these short-duration flaring events can have significant ramifications on the evolution
-of short-period extrasolar planets \citep{france16, guenther19_flares, chen21}. While stellar flares are typically not spatially resolvable, they do lend themselves to
-characterization via spectroscopic and photometric signatures. Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes
-affiliated with such events such as coronal mass ejections \citep{argiroffi19, vida19}, proton beams \citep{orrall76, woodgate92}, and accelerated electrons \citep{osten05, smith05}.
-
-Photometric observations of stars are more readily available now with exoplanet transit discovery missions, and allow us to statistically characterize flare rates
-and energies at optical/near-infrared wavelengths. Observations of M dwarfs with the Sloan Digital Sky Survey revealed a correlation between the flaring fraction of
-stars with height above the galactic plane, a proxy for age \citep{kowalski09, hilton10}. More recently, NASA's \textit{Kepler}, \textit{K2}, and the Transiting
-Exoplanet Survey Satellite (TESS) missions have provided a wealth of stellar variability data in addition to their primary objective of detecting transiting exoplanets.
-Flares can be identified within time-series photometry by a sharp rise and subsequent exponential decay in flux,  with the latter corresponding to the cooling rate
-\citep{kowalski13}. \textit{Kepler} \citep{Borucki10} provided long-baseline high-cadence observations used to identify stellar flares. There has been extensive studies
-of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.][]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars
-\citep[e.g.][]{Hawley14, silverberg16}. \cite{davenport19} found that flare activity decreased with increasing rotation period for 347 GKM stars. However, the flare
-frequency distribution (FFD) slope did not vary significantly as a function of age. As a caveat, the ages of the stars in this study were determined based on their
-rotation periods, relying on the assumption that gyrochronology alone accurately ages stars.
-
-\textit{K2} provided 70-day baseline observations for a handful of young stars in groups such as Upper Scorpius,  Pleiades, Hyades, and Praespe clusters. \cite{ilin19, ilin21}
-analyzed flares from K and M stars in these clusters and found that the overall flare activity decreased as a function of age. Moreover, this relationship was steeper for
-more massive stars in the sample. \cite{paudel18} surveyed 10 M6 - L0 dwarfs observed with \textit{K2} and found the L0 dwarfs had significantly shallower FFDs than the M
-dwarfs. They found that, on average, young targets (defined by the tangential velocity of the star) exhibited more flares overall. More recently, TESS \citep{ricker15} has
-provided near all-sky photometric observations at 30-minute cadence or less. This observing strategy has allowed for more detailed studies of young stellar flares from nearby,
-disperse young moving groups and associations. These  data permit detailed studies of individual stars, for example characterizing eight superflares ($E_f > 10^{34}$~erg) on
-the young star AB Doradus over $\sim 60$ days of continuous observations \citep{schmitt19}, as well as statistical studies of flares across a range of spectral types and ages
-\citep{doyle20, feinstein22_criticality, pietras22, yang23}.
-
-The 11-year solar activity cycle represents a change in the magnetic activity of the Sun, and manifests itself in a variety of observables including increases in the total
-number of sunspots \citep{clette14, kilcik14}, flares and coronal mass ejections \citep{crossby93, webb94, lin23}, and an increase in the total solar irradiance \citep{lean1987}.
-Insights into the long-term activity cycles on other stars have been limited to photometric and spectroscopic monitoring \citep{saar99}. \cite{lehtinen16} collected 16 to 27 years
-of B- and V-band photometry for 21 young active solar-type stars. They found evidence of long-term stellar activity cycles in 18 targets for which$P_\textrm{rot}/P_\textrm{cycle}
-\propto R_0^{-1}$, where $P_\textrm{rot}$ is the rotation period, $P_\textrm{cycle}$ is the period of the stellar activity cycle, and $R_0$ is the Rossby number. Additionally,
-50 years of spectroscopic observations of HD~166620 from the Mount Wilson Observatory and Keck revealed both a $\sim 16$~year periodicity in emission from the core of the
-\ion{Ca}{2} H and K lines \citep{olah16} and evidence that this star entered a grand minima \citep{baum22}. A more complete review on the state of stellar activity cycles can be
-found in \cite{jeffers23} and \cite{isik23}.
-
-In addition to photometric and spectroscopic observations, solar flares trace the length of the solar activity cycle. The high-cadence observations from \textit{Kepler} (4-year baseline)
-and TESS (currently 5-year baseline) provide  sufficient data for searches of stellar activity cycles from the variations in stellar flare rates. \cite{davenport20} demonstrated that
-the flare rate and FFDs of GJ~1234 has not changed appreciably over 10~years of observations with both \textit{Kepler} and TESS. On the other hand, \cite{scoggins19} found that the M3V
-star star KIC 8507979 showed a clear decline in flare rate and change in FFD over 4-years of \textit{Kepler} observations. While it is not expected to find flare rate and distribution
-variations in all stars given detection limitations, KIC 8507979 demonstrates the ability to study long-term flare variability as a potential tracer for stellar activity cycles.
-
-The paper is presented as follows. In Section~\ref{sec:methods}, we describe our sample, and stellar flare and rotation period identification methods. In Section~\ref{sec:results},
-we present our flare-frequency distribution (FFD) fits as a function of stellar age, $T_\textrm{eff}$, and $R_0$. In Section~\ref{sec:cycles}, we present evidence of flare rate changes
-over the 5-year TESS baseline in eleven young stars, likely correlated with long term stellar activity cycles. In Section~\ref{sec:discuss}, we search for correlations in flare rates
-with FUV and NUV observations from \textit{GALEX} and place the flare rates of young planet hosting stars in the context of our broader sample.  We conclude in Section~\ref{sec:conclusions}.
+Stellar flares are the radiation component of magnetic reconnection events \citep{benz10}.
+Such events are readily seen on the Sun \citep{carrington1859, lu91, fletcher11}, particularly during the maximum in the solar cycle \citep{webb94}.
+Solar flares can be used as proxies for magnetic activity occurring on other stars \citep{feigelson99, berdyugina05, kowalski10, feinstein22_criticality}.
+Additionally, these short-duration flaring events can have significant ramifications on the evolution of short-period extrasolar planets \citep{france16, guenther19_flares, chen21}.
+While stellar flares are typically not spatially resolvable, they do lend themselves to characterization via spectroscopic and photometric signatures.
+Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events such as coronal mass ejections \citep{argiroffi19, vida19}, proton beams \citep{orrall76, woodgate92}, and accelerated electrons \citep{osten05, smith05}.
+
+Photometric observations of stars are more readily available now with exoplanet transit discovery missions, and allow us to statistically characterize flare rates and energies at optical/near-infrared wavelengths.
+Observations of M dwarfs with the Sloan Digital Sky Survey revealed a correlation between the flaring fraction of stars with height above the galactic plane, a proxy for age \citep{kowalski09, hilton10}.
+More recently, NASA's \textit{Kepler}, \textit{K2}, and the Transiting Exoplanet Survey Satellite (TESS) missions have provided a wealth of stellar variability data in addition to their primary objective of detecting transiting exoplanets.
+Flares can be identified within time-series photometry by a sharp rise and subsequent exponential decay in flux,  with the latter corresponding to the cooling rate \citep{kowalski13}.
+\textit{Kepler} \citep{Borucki10} provided long-baseline high-cadence observations used to identify stellar flares.
+There has been extensive studies of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.][]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars \citep[e.g.][]{Hawley14, silverberg16}.
+\cite{davenport19} found that flare activity decreased with increasing rotation period for 347 GKM stars.
+However, the flare frequency distribution (FFD) slope did not vary significantly as a function of age.
+As a caveat, the ages of the stars in this study were determined based on their rotation periods, relying on the assumption that gyrochronology alone accurately ages stars.
+
+\textit{K2} provided 70-day baseline observations for a handful of young stars in groups such as Upper Scorpius,  Pleiades, Hyades, and Praespe clusters.
+\cite{ilin19, ilin21} analyzed flares from K and M stars in these clusters and found that the overall flare activity decreased as a function of age.
+Moreover, this relationship was steeper for more massive stars in the sample.
+\cite{paudel18} surveyed 10 M6 - L0 dwarfs observed with \textit{K2} and found the L0 dwarfs had significantly shallower FFDs than the M dwarfs.
+They found that, on average, young targets (defined by the tangential velocity of the star) exhibited more flares overall.
+More recently, TESS \citep{ricker15} has provided near all-sky photometric observations at 30-minute cadence or less.
+This observing strategy has allowed for more detailed studies of young stellar flares from nearby, disperse young moving groups and associations.
+These  data permit detailed studies of individual stars, for example characterizing eight superflares ($E_f > 10^{34}$~erg) on the young star AB Doradus over $\sim 60$ days of continuous observations \citep{schmitt19}, as well as statistical studies of flares across a range of spectral types and ages \citep{doyle20, feinstein22_criticality, pietras22, yang23}.
+
+The 11-year solar activity cycle represents a change in the magnetic activity of the Sun, and manifests itself in a variety of observables including increases in the total number of sunspots \citep{clette14, kilcik14}, flares and coronal mass ejections \citep{crossby93, webb94, lin23}, and an increase in the total solar irradiance \citep{lean1987}.
+Insights into the long-term activity cycles on other stars have been limited to photometric and spectroscopic monitoring \citep{saar99}.
+\cite{lehtinen16} collected 16 to 27 years of B- and V-band photometry for 21 young active solar-type stars.
+They found evidence of long-term stellar activity cycles in 18 targets for which$P_\textrm{rot}/P_\textrm{cycle} \propto R_0^{-1}$, where $P_\textrm{rot}$ is the rotation period, $P_\textrm{cycle}$ is the period of the stellar activity cycle, and $R_0$ is the Rossby number.
+Additionally, 50 years of spectroscopic observations of HD~166620 from the Mount Wilson Observatory and Keck revealed both a $\sim 16$~year periodicity in emission from the core of the \ion{Ca}{2} H and K lines \citep{olah16} and evidence that this star entered a grand minima \citep{baum22}.
+A more complete review on the state of stellar activity cycles can be found in \cite{jeffers23} and \cite{isik23}.
+
+In addition to photometric and spectroscopic observations, solar flares trace the length of the solar activity cycle.
+The high-cadence observations from \textit{Kepler} (4-year baseline) and TESS (currently 5-year baseline) provide  sufficient data for searches of stellar activity cycles from the variations in stellar flare rates.
+\cite{davenport20} demonstrated that the flare rate and FFDs of GJ~1234 has not changed appreciably over 10~years of observations with both \textit{Kepler} and TESS.
+On the other hand, \cite{scoggins19} found that the M3V star star KIC 8507979 showed a clear decline in flare rate and change in FFD over 4-years of \textit{Kepler} observations.
+While it is not expected to find flare rate and distribution variations in all stars given detection limitations, KIC 8507979 demonstrates the ability to study long-term flare variability as a potential tracer for stellar activity cycles.
+
+The paper is presented as follows. In Section~\ref{sec:methods}, we describe our sample,
+and stellar flare and rotation period identification methods. In Section~\ref{sec:results},
+we present our flare-frequency distribution (FFD) fits as a function of stellar age, $T_\textrm{eff}$,
+and $R_0$. In Section~\ref{sec:cycles}, we present evidence of flare rate changes over
+the 5-year TESS baseline in eleven young stars, likely correlated with long term stellar
+activity cycles. In Section~\ref{sec:discuss}, we search for correlations in flare rates
+with FUV and NUV observations from \textit{GALEX} and place the flare rates of young planet
+hosting stars in the context of our broader sample.  We conclude in Section~\ref{sec:conclusions}.
 We provide additional figures and tables in Section~\ref{appendix:supp_ffds}.
 
+\textcolor{red}{This paper was written using the \textit{showyourwork!} open-source
+software package. The objective of \textit{showyourwork!} is to improve reproducibility
+and transparency of scientific research by compiling the manuscript and figures
+simultaneously. All of the data in this work is hosted on GitHub\footnote{The GitHub is
+hyperlinked in the \textit{showyourwork!} stamp at the top of the first page of this manuscript,
+ and can also be found here: \url{https://github.com/afeinstein20/young-stellar-flares}.} and
+ Zenodo.\footnote{} At the end of every caption figure in this manuscript, there is a GitHub icon
+ (\faGithub), which links to the Python script used to create that figure.}
+
 \section{TESS Light Curve Characterization}\label{sec:methods}
 
-Here, we provide an overview of the methodology used in this paper. Specifically, we describe the sample selection in Section~\ref{subsec2:sample}, TESS light curve analysis in
-Section~\ref{subsec2:TESS_lightcurve}, flare identification in Section~\ref{subsec2:Flareidentification}, flare fitting parameters in Section~\ref{subsec2:model}, flare quality
-checks in Section~\ref{subsec2:qualitychecks}, and  stellar rotation period measurements in Section~\ref{subsec:prot}.
+Here, we provide an overview of the methodology used in this paper. Specifically, we describe
+the sample selection in Section~\ref{subsec2:sample}, TESS light curve analysis in
+Section~\ref{subsec2:TESS_lightcurve}, flare identification in Section~\ref{subsec2:Flareidentification},
+flare fitting parameters in Section~\ref{subsec2:model}, flare quality checks in
+Section~\ref{subsec2:qualitychecks}, and  stellar rotation period measurements in Section~\ref{subsec:prot}.
 
@@
 
-A primary goal of this paper is to measure the relationship between the flare rates and ages of stars. We are particularly interested in this dependency for young stars with ages
-$4 \leq t_\textrm{age} \leq 300$\,Myr. To this end, we used the MOCA Data Base (Gagné et al. in prep.)\footnote{\url{https://mocadb.ca/}} to identify 26~ nearby, aged, young moving
-groups, associations, and open clusters from which we created our sample of stars. The final targets were required to be: (i) confirmed members, (ii) high-likelihood candidate members,
-or (iii) candidate members.  Membership to these groups has been primarily determined using kinematic information from \textit{Gaia} \citep{gaia16, gaia18}. The membership status is
-determined by the probability that BANYAN-$\Sigma$ assigns based on how well the kinematics of the target matches with the kinematics of the group \citep{gagne18}. These rather
-stringent cuts resulted in a catalog of 30,889 stars across 26 associations. We summarize the sample and ages for each association (and therefore star) in Table~\ref{tab:sample}.
-
-%With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}. In order to model the
-flare profile, we employ the analytical model developed by \cite{tovar22}. This model is able to simultaneously (i) fit the flares and  (ii) measure the equivalent duration and energy
-associated with each flare.
+A primary goal of this paper is to measure the relationship between the flare rates and
+ages of stars. We are particularly interested in this dependency for young stars with ages
+$4 \leq t_\textrm{age} \leq 300$\,Myr. To this end, we used the MOCA Data Base (Gagné et al.
+in prep.)\footnote{\url{https://mocadb.ca/}} to identify 26~ nearby, aged, young moving groups,
+associations, and open clusters from which we created our sample of stars. The final targets
+were required to be: (i) confirmed members, (ii) high-likelihood candidate members, or (iii)
+candidate members.  Membership to these groups has been primarily determined using kinematic
+information from \textit{Gaia} \citep{gaia16, gaia18}. The membership status is determined by
+the probability that BANYAN-$\Sigma$ assigns based on how well the kinematics of the target
+matches with the kinematics of the group \citep{gagne18}. These rather stringent cuts resulted
+in a catalog of 30,889 stars across 26 associations. We summarize the sample and ages for each
+association (and therefore star) in Table~\ref{tab:sample}.
 
@@
 
-We cross-matched our MOCA Database sample with the TESS Input Catalog (TIC) based on their Gaia DR2 RA and Dec; we required that the distance between the target and the nearest
-TIC target was within $<1"$. We down-selected our sample to stars that have been observed with TESS at 2-minute cadence. This ensures that we are able to temporally resolve and
-accurately measure the properties of flares for each of these stars \citep{howard22}.
-
-This process provided a final sample of \nstars\ unique targets. These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67; Sector 67 was
-the latest available sector at the time that this analysis was performed. In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions, ages and effective
-temperatures, $T_\textrm{eff}$, of the final sample. Because many of the groups are located at or near the ecliptic poles, many of our targets were observed over multiple TESS
-sectors. We use $T_\textrm{eff}$ as our stellar characterization metric over the standard $M_\star$ because $\sim 600$ stars in our sample lack mass information in the TIC.
-The entirety of the available data yielded 17,964 light curves processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16}. Our sample has an average
-of $\sim 3$ light curves per target (although with significant spread across targets). For our analysis, we used the SPOC-processed SAP\_FLUX.
+We cross-matched our MOCA Database sample with the TESS Input Catalog (TIC) based
+on their Gaia DR2 RA and Dec; we required that the distance between the target and
+the nearest TIC target was within $<1"$. We down-selected our sample to stars that
+have been observed with TESS at 2-minute cadence. This ensures that we are able to
+temporally resolve and accurately measure the properties of flares for each of these
+stars \citep{howard22}.
+
+This process provided a final sample of \nstars\ unique targets. These targets
+have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67;
+Sector 67 was the latest available sector at the time that this analysis was performed.
+In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions, ages
+and effective temperatures, $T_\textrm{eff}$, of the final sample. Because many of
+the groups are located at or near the ecliptic poles, many of our targets were observed
+over multiple TESS sectors. We use $T_\textrm{eff}$ as our stellar characterization
+metric over the standard $M_\star$ because $\sim 600$ stars in our sample lack mass
+information in the TIC. The entirety of the available data yielded 17,964 light curves
+processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16},
+\textcolor{red}{which can be accessed on MAST under DOI  \href{http://dx.doi.org/10.17909/t9-nmc8-f686}{10.17909/t9-nmc8-f686}.}
+Our sample has an average of $\sim 3$ light curves per target (although with significant
+spread across targets). \textcolor{red}{We downloaded all light curves using \texttt{lightkurve}\footnote{\url{https://doi.org/10.5281/zenodo.4654522}}.}
+For our analysis, we used the SPOC-processed SAP\_FLUX.
 
@@
 
-Once we downloaded the light curves for each target, we performed the following procedure to identify stellar flares. First, we implemented the machine learning flare-identification
-methods presented and described in \cite{feinstein20}. This method relies on the similar time-dependent morphologies of all flare events. These flare-profiles can generally be
-described as a sharp rise followed by an exponential decay in the white light curve. This identification-technique implements the convolutional neural network (CNN) \texttt{stella}
-\citep{feinstein20}. The CNN  was trained on  a   by-eye validated catalogue of flares from TESS Sectors 1 and 2 with 2-minute data \citep{guenther19_flares}.
-
-There are several benefits to using the CNN for stellar flare identification. Primarily, the CNN is insensitive to the stellar baseline flux because it is trained to search
-\textit{only} based on flare morphology. It is therefore relatively insensitive to the absolute flux levels, so long as the inherent noise does not overwhelm the signal itself.
-An additional benefit is that rotational modulation peaks --- which are themselves driven by stellar heterogeneities --- are not accidentally identified as flares. This holds true
-for stars with rotation periods, $P_\textrm{rot} > 1$~day. This is especially advantageous for our sample of young stars, which readily exhibit rotational modulation in their light curves.
-
-Based on these advantages, the final compiled sample of flares is unbiased towards low-amplitude/low-energy flares. It is important to note that these low-energy events are typically
-not identified in traditional sigma-outlier identification
-methods \citep{chang15}. The \texttt{stella} CNN models calculate the probability that a data point in a light curve is associated with a flaring event. Specifically, it takes the light
-curve (time, flux, flux error) as an input and returns an array with values of [0,1], which are treated as the probability a data point is (1) or is not (0) part of a flare. We ran every
-light curve through 10 independent \texttt{stella} models and averaged the outputs to ensure that our statistics were accurate. We note that in this processing, the CNN ignores 200-minutes
-before and after any gaps in the data. Therefore, any flares which occur during these times are not identified.
-
-The \texttt{stella} code groups individual points with the predictions per data point when identifying a single flare event. We modified this stage of identification slightly from the
-original flare-identification method. Specifically, we identified all data points with a probability of being associated with a flare of $P > 0.75$. Any data points that were within 4
-cadences of each other were considered to be a single flare event. We did not consider any potential flares that had three or fewer points with $P > 0.75$. This method rejects single-point
-outliers which can be assigned  high probabilities of being  flares. We assigned the probability of the whole flare event as the probability of the peak data point.
+Once we downloaded the light curves for each target, we performed the following
+procedure to identify stellar flares. We implemented the machine learning
+flare-identification methods presented and described in \cite{feinstein20}.
+This method relies on the similar time-dependent morphologies of all flare events.
+These flare-profiles can generally be described as a sharp rise followed by an
+exponential decay in the white light curve. This identification-technique implements
+the convolutional neural network (CNN) \texttt{stella} \citep{feinstein20},
+\textcolor{red}{although other architectures have been explored for flare identification
+\citep[e.g.][]{vida18}.}  The CNN  was trained on a by-eye validated catalogue of flares
+from TESS Sectors 1 and 2 with 2-minute data \citep{guenther19_flares}.
+
+There are several benefits to using the CNN for stellar flare identification. Primarily,
+the CNN is insensitive to the stellar baseline flux because it is trained to search
+\textit{only} based on flare morphology. It is therefore relatively insensitive to
+the absolute flux levels, so long as the inherent noise does not overwhelm the signal
+itself. An additional benefit is that rotational modulation peaks --- which are
+themselves driven by stellar heterogeneities --- are not accidentally identified as
+flares. This holds true for stars with rotation periods, $P_\textrm{rot} > 1$~day.
+This is especially advantageous for our sample of young stars, which readily exhibit
+rotational modulation in their light curves.
+
+Based on these advantages, the final compiled sample of flares is unbiased towards
+low-amplitude/low-energy flares. It is important to note that these low-energy events
+are typically not identified in traditional sigma-outlier identification
+methods \textcolor{red}{\citep[e.g.][]{chang15, vasilyev22}}. \textcolor{red}{While
+significant developments have been achieved to better model and detrend stellar
+variability \citep[e.g.][]{bicz22}, these methods can be computationally intensive}
+The \texttt{stella} CNN models calculate the probability that a data point in a light
+curve is associated with a flaring event. Specifically, it takes the light curve (time,
+flux, flux error) as an input and returns an array with values of [0,1], which are
+treated as the probability a data point is (1) or is not (0) part of a flare. We ran
+every light curve through 10 independent \texttt{stella} models and averaged the
+outputs to ensure that our statistics were accurate. We note that in this processing,
+the CNN ignores 200-minutes before and after any gaps in the data. Therefore, any
+flares which occur during these times are not identified. \textcolor{red}{From by-eye
+vetting of $\sim 300$ light curves, we found 2~flares within the first 200~minutes of
+the orbital gaps. Therefore, we estimate $\leq 120$~flares are missed in our catalog.}
+
+The \texttt{stella} code groups individual points with the predictions per data point
+when identifying a single flare event. We modified this stage of identification slightly
+from the original flare-identification method. Specifically, we identified all data
+points with a probability of being associated with a flare of $P > 0.75$. Any data
+points that were within 4 cadences of each other were considered to be a single flare
+event. We did not consider any potential flares that had three or fewer points with
+$P > 0.75$. This method rejects single-point outliers which can be assigned  high
+probabilities of being  flares. We assigned the probability of the whole flare event
+as the probability of the peak data point.
 
@@
 
-Flares are well-described in light curves as a sudden increase in flux followed by an exponential decay. We used the analytic flare model, Llamaradas Estelares which was presented in
-\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}, to fit and extract parameters of flares in all of the light curves of our sample. This model builds
-upon the model presented in \cite{davenport14}. Specifically, it includes the convolution of a Gaussian with a double exponential model in the flare profile.
-
-The analytic model robustly  accounts for physically-motivated flare features. Specifically, it can incorporate the flare (i) amplitude, (ii) heating timescale, (iii) rapid cooling phase
-timescale, and (iv) slow cooling phase timescale. We implemented a nonlinear least squares optimization to fit the flare peak time ($t_\textrm{peak}$), full width at half maximum (FWHM),
-and the amplitude ($A$) of each flare in the sample.  We combine the model with a second-order polynomial fit to a 1.2-hour baseline before and after the flare  during only the fitting stage.
-This was implemented in order to account for any slope due to rotational modulation, and therefore was particularly relevant for the rapid rotators ($P_\textrm{rot} < 2$~days).
-
-We calculated the equivalent duration, ED, of the flare by integrating the quiescent-normalized flare flux with respect to time. We calculate the flare energy, $E_\textrm{flare}$, using,
+Flares are well-described in light curves as a sudden increase in flux followed
+by an exponential decay. We used the analytic flare model, Llamaradas Estelares
+which was presented in \cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}},
+to fit and extract parameters of flares in all of the light curves of our sample.
+This model builds upon the model presented in \cite{davenport14}. Specifically,
+it includes the convolution of a Gaussian with a double exponential model in the
+flare profile.
+
+The analytic model robustly  accounts for physically-motivated flare features.
+Specifically, it can incorporate the flare (i) amplitude, (ii) heating timescale,
+(iii) rapid cooling phase timescale, and (iv) slow cooling phase timescale. We
+implemented a nonlinear least squares optimization to fit the flare peak time
+($t_\textrm{peak}$), full width at half maximum (FWHM), and the amplitude ($A$)
+of each flare in the sample. \textcolor{red}{We note that there are several other
+physically-motivated flare models which could be used, such as those presented in
+\cite{gryciuk17, pietras22, yang23_lp}; these models include using two profiles to
+fit the impulsive and late phases of the flare.} We combine the model with a
+second-order polynomial fit to a 1.2-hour baseline before and after the flare
+during only the fitting stage. This was implemented in order to account for any
+slope due to rotational modulation, and therefore was particularly relevant for the
+rapid rotators ($P_\textrm{rot} < 2$~days).
+
+We calculated the equivalent duration, ED, of the flare by integrating the
+quiescent-normalized flare flux with respect to time. We calculate the flare
+energy, $E_\textrm{flare}$, using,
 
@@
 \end{equation}
-In Equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$, where $B_\lambda(T)$ is
-the Planck function. We assume that the flare temperature is 9000~K \citep{hawley92, hawley95}, although recent NUV flare observations suggest this may be an underestimation
-\citep{kowalski19, brasseur23, berger23}.
+In Equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a
+scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$,
+where $B_\lambda(T)$ is the Planck function. We assume that the flare temperature is
+9000~K \citep{hawley92, hawley95}, although recent NUV flare observations suggest
+this may be an underestimation \citep{kowalski19, brasseur23, berger23}.
+
+\subsubsection{\textcolor{red}{Comparison of Flare Models}}
+
+\textcolor{red}{\cite{tovar22} demonstrated that the flare model works well for
+flares with amplitudes $\geq 2$ (i.e. double the baseline flux). However, other
+works such as \cite{pietras22} have demonstrated that a double-flare profile better
+fits high energy flares. To quantify how well the Llamaradas Estelares model works,
+we refit and calculate the $\chi^2$ for a subset of high amplitude flares ($A \geq 0.4$)
+using Equation 3 in \cite{pietras22}, a double-peak flare model, which is:}
+
+\begin{equation}\label{eqn:flare}
+\begin{split}
+    f(\tau) = \int_0^\tau\bigg( A_1\, \exp\bigg[\frac{-(t-B_1)^2}{C_1^2}\bigg] \,\exp\bigg[\frac{(t-\tau)}{D_1}\bigg]\\+A_2 \,\exp\bigg[\frac{-(t-B_2)^2}{C_2^2}\bigg] \,\exp\bigg[\frac{(t-\tau)}{D_2}\bigg]\bigg) \textrm{d}t
+\end{split}
+\end{equation}
+
+\textcolor{red}{where $A$ is is related to amplitude of the flare, $B$ relates
+to the total energy released during the flare, $C$ relates to the timescale of
+the flare, $D$ is related to the decay timescale, $\tau$ is the time of a given
+cadence, and $t$ is the time to integrate over. The subscripts 1 and 2 indicate
+which flare variables are associated with the first and second flare profile. We
+refit 900~high-amplitude flares following Equation~\ref{eqn:flare}. We plot the
+results of this refitting in Figure~\ref{fig:model_fit}.}
+
+\begin{figure}[ht!]
+    \script{model_fit.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/model_fit.pdf}
+        \caption{
+            \textcolor{red}{Comparison fits between the Llamaradas Estelares
+            single-peak model from \cite{tovar22} and the double-peak flare model
+            from \cite{pietras22} for flares with $A \geq 0.4$. Top (A): Comparison
+            in the $\chi^2$ between the best-fit model for 900 flares. A one-to-one
+            line is plotted in peach to guide the eye. Across this sample of
+            high-amplitude flares, there is good agreement between the fits for
+            these two distinct models. Bottom: Comparison in best-fit models for
+            a subset of flares. The best-fit Llamaradas Estelares model is plotted
+            in blue; the best-fit double-peak model is plotted in orange. We
+            highlight examples where the double-peak flare model has the better
+            fit (B, C), the Llamaradas Estelares flare model has the better fit
+            (D, E), and where the models perform equally as well (F, G). We note
+            there is no correlation between flare amplitude and preferred model.}
+        }
+        \label{fig:model_fit}
+    \end{centering}
+\end{figure}
+
+\textcolor{red}{Broadly, we find the flare model from \cite{tovar22} and \cite{pietras22}
+to fit the majority of the high-amplitude flares equally as well (Figure~\ref{fig:model_fit}\,A).
+We highlight several examples where one model fits better than the other in Figure~\ref{fig:model_fit}\,B-E,
+and cases where both profiles fit the data equally as well Figure~\ref{fig:model_fit}\,F-G.
+Flares which prefer the Llamaradas Estelares model tend to have a more accurately fit flare
+amplitude. Flares which prefer the double-peak model tend to have an extended decay timescale,
+which is better fit by the addition of a secondary flare. Flares which are fit equally well by
+both models tend to have a better fit to the amplitude in the Llamaradas Estelares model, but a
+better fit to the decay timescale in the double-peak flare model.}
 
@@
 
-The \texttt{stella} CNNs were trained on data from TESS Sectors 1 and 2. However, the noise properties are variable across sectors in TESS data. The CNNs are therefore unable to
-accurately account for and capture  this variation when operating on different sectors. Moreover, the original CNNs were only trained on a sample of 1,228 stars. This training sample
-does not necessarily encapsulate a sufficient distribution  of variable stars types, such as eclipsing binaries, RR Lyraes, and fast
-rotators with $P_\textrm{rot} < 1$~day \citep{lawson19}, which
-results in the CNNs not being able to properly distinguish these temporal features from flares. We therefore apply additional
-quality checks to ensure our flare sample has little to no contamination from other sources.
+The \texttt{stella} CNNs were trained on data from TESS Sectors 1 and 2. However, the
+noise properties are variable across sectors in TESS data. The CNNs are therefore unable
+to accurately account for and capture  this variation when operating on different sectors.
+Moreover, the original CNNs were only trained on a sample of 1,228 stars. This training
+sample does not necessarily encapsulate a sufficient distribution  of variable stars types,
+such as eclipsing binaries, RR Lyraes, and fast rotators with $P_\textrm{rot} < 1$~day
+\citep{lawson19}, which results in the CNNs not being able to properly distinguish these
+temporal features from flares. We therefore apply additional quality checks to ensure our
+flare sample has little to no contamination from other sources.
 
@@
     \item  The amplitude of the flare must be $> 0.01$, the same limits set by \cite{feinstein20}.
-    \item The flare amplitude  must be at least twice the standard deviation of the light curve 30 minutes before and 45 minutes after the flare. This ensures that the feature is not
-    a sharp noise artifact.
+    \item The flare amplitude  must be at least twice the standard deviation of the light curve
+    30 minutes before and 45 minutes after the flare. This ensures that the feature is not a sharp noise artifact.
     \item  The fitted flare model parameters must be physically motivated: FWHM $> 0$; $A > 0$; ED $> 0$.
@@
 
-We find that flares are often simply mischaracterized noise when the errors on the first and fourth criteria are larger than the cut-offs. These quality checks highlight the need
-to continuously update machine learning models, especially when looking at data with varying instrumental systematics.
-
-As a final check, we performed an exhaustive by-eye verification of flares from light curves for stars with flare rates, $\mathcal{R} > 1$~day$^{-1}$. These stars generally tend
-to have $T_\textrm{eff} > 5000$~K and TESS magnitudes $< 8$. Therefore, their light curves are dominated by sharp noise which \texttt{stella} often mischaracterizes as flares. As a
-final cut, the sample only includes events that have  a probability $P \geq 98\%$ of being a true flare. After performing these additional checks, we obtain a robust final flare sample
-of \nflares\ flares originating from \nflarestars\ stars (Figure~\ref{fig:flare_distribution}).
+We find that flares are often simply mischaracterized noise when the errors on the first
+and fourth criteria are larger than the cut-offs. These quality checks highlight the
+need to continuously update machine learning models, especially when looking at data
+with varying instrumental systematics.
+
+As a final check, we performed an exhaustive by-eye verification of flares from light
+curves for stars with flare rates, $\mathcal{R} > 1$~day$^{-1}$. These stars generally
+tend to have $T_\textrm{eff} > 5000$~K and TESS magnitudes $< 8$. Therefore, their
+light curves are dominated by sharp noise which \texttt{stella} often mischaracterizes
+as flares. As a final cut, the sample only includes events that have  a probability
+$P \geq 98\%$ of being a true flare. After performing these additional checks, we
+obtain a robust final flare sample of \nflares\ flares originating from \nflarestars\
+stars (Figure~\ref{fig:flare_distribution}).
 
@@
 
-In addition to understanding flare statistics across young stars, we measure the rotation periods, $P_\textrm{rot}$ of stars in our sample. We then search for correlations between
-$P_\textrm{rot}$ and Rossby number, $R_0$. \citet{seligman22} demonstrated that stars with low Rossby numbers $R_0 < 0.13$ exhibit shallower flare frequency distribution slopes. These
-shallower slopes are caused by  an excess of  high energy flares compared to lower energy flares.
-
-In order to perform this, we describe how we measure stellar rotation periods from the TESS light curves. To this end we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}},
-an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination traditional Lomb-Scargle periodograms and wavelet transformations (Hall et al. submitted).
-\texttt{michael} measures $P_\textrm{rot}$ using the \texttt{eleanor} package, which extracts light curves from the TESS Full-Frame Images \citep[FFIs;][]{feinstein19}.
-
-We ran \texttt{michael} on all stars in our samples from which flares were identified. The estimated rotational periods were subsequently vetted by-eye  with the \texttt{michael}
-diagnostic plots. This vetting was implemented to ensure that the measured $P_\textrm{rot}$ was not a harmonic of the true $P_\textrm{rot}$ or  from an occulting companion. This led
-to robust measurements of rotation periods for \nprot\ stars in total. Additionally, we identified 17 eclipsing binaries or potentially new planet candidates.
+In addition to understanding flare statistics across young stars, we measure the
+rotation periods, $P_\textrm{rot}$ of stars in our sample. We then search for correlations
+between $P_\textrm{rot}$ and Rossby number, $R_0$. \citet{seligman22} demonstrated that
+stars with low Rossby numbers $R_0 < 0.13$ exhibit shallower flare frequency distribution
+slopes. These shallower slopes are caused by  an excess of  high energy flares compared
+to lower energy flares.
+
+In order to perform this, we describe how we measure stellar rotation periods from
+the TESS light curves. To this end we used \texttt{michael}\footnote{\url{https://github.com/ojhall94/michael}},
+an open-source Python package that robustly measures $P_\textrm{rot}$ using a combination
+traditional Lomb-Scargle periodograms and wavelet transformations (Hall et al. submitted).
+\texttt{michael} measures $P_\textrm{rot}$ using the \texttt{eleanor} package, which
+extracts light curves from the TESS Full-Frame Images \citep[FFIs;][]{feinstein19}.
+
+We ran \texttt{michael} on all stars in our samples from which flares were identified.
+The estimated rotational periods were subsequently vetted by-eye  with the \texttt{michael}
+diagnostic plots. This vetting was implemented to ensure that the measured $P_\textrm{rot}$
+was not a harmonic of the true $P_\textrm{rot}$ or  from an occulting companion. This led
+to robust measurements of rotation periods for \nprot\ stars in total. Additionally, we
+identified 17 eclipsing binaries or potentially new planet candidates.
 
@@
 
-In this section, we use the previously described methodology to estimate the flare rates of the young stars in our sample. We implement three main steps in this analysis. First, we
-perform the standard FFD fitting of a power-law to the distribution of flare energies described in Section~\ref{subsec:energy_ffd}. Next we fit the relationship between $R_0$ and
-flare rates in Section~\ref{subsec:rossby}. Finally we fit a truncated power-law to the distribution of flare amplitudes in  Section~\ref{subsec3_truncated}  to identify correlations
-between $R_0$ and flare distributions.
-
-The number of stars and flares in  each association varied greatly (Figure~\ref{fig:flare_distribution}). This was primarily caused by the limited number of stars that had been
-observed at 2-minute cadence in TESS.  We therefore did not measure FFD properties as a function of association. Instead, we group stars by $T_\textrm{eff}$ and average adopted
-association age.
+In this section, we use the previously described methodology to estimate the flare
+rates of the young stars in our sample. We implement three main steps in this analysis.
+First, we perform the standard FFD fitting of a power-law to the distribution of
+flare energies described in Section~\ref{subsec:energy_ffd}. Next we fit the relationship
+between $R_0$ and flare rates in Section~\ref{subsec:rossby}. Finally we fit a
+truncated power-law to the distribution of flare amplitudes in  Section~\ref{subsec3_truncated}
+to identify correlations between $R_0$ and flare distributions.
+
+The number of stars and flares in  each association varied greatly
+(Figure~\ref{fig:flare_distribution}). This was primarily caused by the limited
+number of stars that had been observed at 2-minute cadence in TESS.  We therefore
+did not measure FFD properties as a function of association. Instead, we group
+stars by $T_\textrm{eff}$ and average adopted association age.
 
@@
  \end{itemize}
-We did not include any stars hotter than $T_\textrm{eff} > 5930$\,K.  These hot stars generally exhibit light curves  dominated by noise in the TESS observations. Additionally, we
-grouped stars in the following age space: $4-10$\,Myr (including Upper Scorpius and TW Hydrae), $10-20$\,Myr, $20-40$\,Myr, $40-50$\,Myr, $70-80$\,Myr, $120-150$\,Myr, and $150-300$\,Myr.
-We note that there is a gap in age from $50-70$\,Myr, which could be expanded with the identification of more associations in this age range.
+We did not include any stars hotter than $T_\textrm{eff} > 5930$\,K. These hot
+stars generally exhibit light curves  dominated by noise in the TESS observations.
+Additionally, we grouped stars in the following age space: $4-10$\,Myr (including
+Upper Scorpius and TW Hydrae), $10-20$\,Myr, $20-40$\,Myr, $40-50$\,Myr, $70-80$\,Myr,
+$120-150$\,Myr, and $150-300$\,Myr. We note that there is a gap in age from $50-70$\,Myr,
+which could be expanded with the identification of more associations in this age range.
 
@@
         \caption{
-            Measured flare-frequency distribution slopes, $\alpha$, as a function of stellar effective temperature, $T_\textrm{eff}$ and age. We measured these FFDs with respect to flare
-            energy. We find the FFD slopes as a function of energy are consistent with $\alpha = -0.6 ~\textrm{to} -0.2$ for stars $< 300$~Myr in TESS observations. A shallower FFD slope
-            is indicative of more high-energy flares. We present all measured FFDs in Figure~\ref{appendix:supp_ffds}, and all measured slopes and errors in Table~\ref{tab:best_fits}.
-            We find the shallowest slopes for stars $T_\textrm{eff} = 3400 - 4440$\,K, with a range from $\alpha = -0.44~ \textrm{to} -0.22$. We do not include the results for stars
-            $T_\textrm{eff} = 3850 - 4440$\,K and $t_\textrm{age} = 20 - 40$\,Myr as this bin contained only six stars with detected flares. We present the average results of measured
-            FFD slopes for the Hyades, Pleiades, and Praesepe clusters from \cite{ilin21} as black squares. We present the results of measured FFD slopes for all TESS primary mission
-            targets in white circles \citep{Feinstein22} as ``field-age". We discuss what drives the difference between our sample and \cite{ilin21} in Section~\ref{subsec:energy_ffd}.
+            Measured flare-frequency distribution slopes, $\alpha$, as a function
+            of stellar effective temperature, $T_\textrm{eff}$ and age. We measured
+            these FFDs with respect to flare energy. We find the FFD slopes as a
+            function of energy are consistent with $\alpha = -0.6 ~\textrm{to} -0.2$
+            for stars $< 300$~Myr in TESS observations. A shallower FFD slope is
+            indicative of more high-energy flares. We present all measured FFDs in
+            Figure~\ref{appendix:supp_ffds}, and all measured slopes and errors in
+            Table~\ref{tab:best_fits}. We find the shallowest slopes for stars
+            $T_\textrm{eff} = 3400 - 4440$\,K, with a range from $\alpha = -0.44~ \textrm{to} -0.22$.
+            We do not include the results for stars $T_\textrm{eff} = 3850 - 4440$\,K
+            and $t_\textrm{age} = 20 - 40$\,Myr as this bin contained only six stars with
+            detected flares. We present the average results of measured FFD slopes for
+            the Hyades, Pleiades, and Praesepe clusters from \cite{ilin21} as black
+            squares. We present the results of measured FFD slopes for all TESS primary
+            mission targets in white circles \citep{Feinstein22} as ``field-age". We
+            discuss what drives the difference between our sample and \cite{ilin21} in
+            Section~\ref{subsec:energy_ffd}.
          }
@@
 
-We fit the stars FFD slopes, approximated as a power-law, using the $T_\textrm{eff}$ and age bins described above. Flares were binned into 25 bins in log-space from $10^{27} - 10^{35}$\,erg.
-The FFD has a notable turnover energy, $E_\textrm{turnover}$, when our detection method is incomplete due the low-amplitude of those flares. The FFD slope is often fit to flares with
-energies $E \geq E_\textrm{turnover}$. We perform our fits following the same methodology. This turnover in the FFD cannot be accurately modeled with a power-law. We present our FFDs as a
-function of $T_\textrm{eff}$ and age in Figure~\ref{fig:simple_ffd_all}; points which were fit to measure the FFD slope are presented in black, while the full FFD is presented in gray.
-
-We fit the FFD using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}. Specifically, we fit for the slope, $\alpha$, y-intercept, $b$, and an additional noise term,
-$f$. This noise term  accounts for an underestimation of the errors in each bin. We initialized the MCMC fit with 300 walkers and ran our fit over 5000 steps.  We discarded the first 100
-steps upon visual inspection, after which the steps were fully burned-in. The measured FFD slopes, $\alpha$, are presented in Figure~\ref{fig:mcmc_results}. We approximate the error on the
-slope as the lower 16\textsuperscript{th} and upper 84\textsuperscript{th} percentiles from the MCMC fit.
-
-Overall, we measure a shallower FFD for stars of all masses at $t_\textrm{age} < 300$~Myr. A shallower FFD indicates there are more high-energy flares. The measured FFD slopes are shallower
-than those measured using smaller samples of young stars. \cite{jackman21} fit the three FFDs for M3-M5, M0-M2, and K5-K8 stars younger than 40~Myr that had been observed with Next Generation
-Transit Survey. They measured slopes of $0.94 \pm 0.04$, $0.69 \pm 0.05$, $0.82 \pm 0.14$ per bin, which each contained $\leq 120$~flares.  It is also worth noting that the slopes measured
-here are based on up to an order of magnitude more flares per fit. Our sample also has a longer temporal baseline, allowing for the occurrence of more high-energy flares. Accumulating more
-high-energy flares in the FFD, if such events occur, will result in a shallower FFD slopes. TESS flare statistics for main sequence stars have indicated steeper FFDs \citep{feinstein22_criticality}.
-Therefore, the FFDs presented here are not strictly impacted by longer observations, but are the result of more high-energy flares on young stars.
-
-There is a $1-3\sigma$ discrepancy between the FFD slope measured in \cite{ilin21} and the work presented here at ages $\sim 120$\,Myr ($\alpha$ ranges from
-$-1.32 \pm 0.19 ~\textrm{to} -0.91 \pm 0.18$, depending on the $T_\textrm{eff}$ bin). \cite{ilin21} used the \textit{K2} 30-minute light curves for their analysis, compared with our TESS
-2-minute light curves. Additionally, our sample has $\sim 2 \times$ the number of stars and $\sim 7 \times$ the number of flares as in \cite{ilin21}. First, we test if these discrepancies
-are driven by differences in sample binning. We reevaluate the FFDs assuming the $T_\textrm{eff}$ bins presented in Table 3 of \cite{ilin21}. We find $\alpha$ remains consistent with our
-presented values to within $\sim 1\sigma$ of the nearest temperature bin. Second, we reevaluate the FFDs assuming the total number of flares fit in \cite{ilin21}. We
-draw $n_\textrm{fit, Ilin et al. (2021)}$ \citep[last column in Table 3 of ][]{ilin21} flares from our sample 100 times without replacement, refit the FFD, and take the average FFD slope
-from that sub-sample of flares to our results.  We find $\alpha$ remains consistent with our presented values to $\sim 2\sigma$. We note that in most cases
-$n_\textrm{fit, Ilin et al. (2021)} < n_\textrm{fit, this work}$. Therefore, the increased disagreement in $\alpha$ could be due to smaller sample sizes.
-
-Additionally, we test if the difference in $\alpha$ is driven by the cadence differences between \textit{K2} (30-minute) and TESS (2-minute). We bin all of the flares in our sample down
-to a 30-minute cadence, re-fit for flare $A$ and ED, and recalculate the flare energy. We re-fit the FFD for this altered sample and measure  FFD slopes consistent to $\sim 1 \sigma$ with
-those presented in this work. Therefore, the discrepancy seen here is not driven by observational differences between \textit{K2} and TESS.
-
-Finally, we test if the differences are driven by the range of energies that are fit. The CNN-based flare detection algorithm has previously been demonstrated to be less-biased against lower
-energy flares. Like this work, \cite{ilin21} fit the FFD across flare energies which are not affected by a reduced efficiency in the low-energy flare detection, $E \geq E_\textrm{turnover}$.
-In energy space, these fits begin between $E_f = 10^{32-33}$~erg, compared to our fits which begin between $E_f = 10^{31-32}$~erg (Figure~\ref{appendix:supp_ffds}). When we limit our sample
-to $E_f \geq 10^{32.5}$~erg, we find the FFD slopes become \textit{steeper} and more consistent with the values of $\alpha$ presented in \cite{ilin21}. Therefore, the difference in $\alpha$
-between this work and \cite{ilin21} for stars with $t_\textrm{age} = 120 - 150$~Myr is driven by the lower energy flares, with which we are more complete to with TESS than \textit{K2}.
+We fit the stars FFD slopes, approximated as a power-law, using the $T_\textrm{eff}$
+and age bins described above. Flares were binned into 25 bins in log-space from
+$10^{27} - 10^{35}$\,erg. The FFD has a notable turnover energy, $E_\textrm{turnover}$,
+when our detection method is incomplete due the low-amplitude of those flares.
+The FFD slope is often fit to flares with energies $E \geq E_\textrm{turnover}$.
+We perform our fits following the same methodology. This turnover in the FFD
+cannot be accurately modeled with a power-law. We present our FFDs as a function
+of $T_\textrm{eff}$ and age in Figure~\ref{fig:simple_ffd_all}; points which were
+fit to measure the FFD slope are presented in black, while the full FFD is presented
+in gray.
+
+We fit the FFD using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}.
+Specifically, we fit for the slope, $\alpha$, y-intercept, $b$, and an additional
+noise term, $f$. This noise term  accounts for an underestimation of the errors in
+each bin. We initialized the MCMC fit with 300 walkers and ran our fit over 5000
+steps.  We discarded the first 100 steps upon visual inspection, after which the
+steps were fully burned-in. The measured FFD slopes, $\alpha$, are presented in
+Figure~\ref{fig:mcmc_results}. We approximate the error on the slope as the lower
+16\textsuperscript{th} and upper 84\textsuperscript{th} percentiles from the MCMC fit.
+
+Overall, we measure a shallower FFD for stars of all masses at $t_\textrm{age} < 300$~Myr.
+A shallower FFD indicates there are more high-energy flares. The measured FFD slopes
+are shallower than those measured using smaller samples of young stars. \cite{jackman21}
+fit the three FFDs for M3-M5, M0-M2, and K5-K8 stars younger than 40~Myr that had been
+observed with Next Generation Transit Survey. They measured slopes of $0.94 \pm 0.04$,
+$0.69 \pm 0.05$, $0.82 \pm 0.14$ per bin, which each contained $\leq 120$~flares.
+It is also worth noting that the slopes measured here are based on up to an order of
+magnitude more flares per fit. Our sample also has a longer temporal baseline,
+allowing for the occurrence of more high-energy flares. Accumulating more high-energy
+flares in the FFD, if such events occur, will result in a shallower FFD slopes. TESS
+flare statistics for main sequence stars have indicated steeper FFDs \citep{feinstein22_criticality}.
+Therefore, the FFDs presented here are not strictly impacted by longer observations,
+but are the result of more high-energy flares on young stars.
+
+There is a $1-3\sigma$ discrepancy between the FFD slope measured in \cite{ilin21}
+and the work presented here at ages $\sim 120$\,Myr ($\alpha$ ranges from
+$-1.32 \pm 0.19 ~\textrm{to} -0.91 \pm 0.18$, depending on the $T_\textrm{eff}$ bin).
+\cite{ilin21} used the \textit{K2} 30-minute light curves for their analysis, compared
+with our TESS 2-minute light curves. Additionally, our sample has $\sim 2 \times$
+the number of stars and $\sim 7 \times$ the number of flares as in \cite{ilin21}.
+First, we test if these discrepancies are driven by differences in sample binning.
+We reevaluate the FFDs assuming the $T_\textrm{eff}$ bins presented in Table 3 of
+\cite{ilin21}. We find $\alpha$ remains consistent with our presented values to
+within $\sim 1\sigma$ of the nearest temperature bin. Second, we reevaluate the
+FFDs assuming the total number of flares fit in \cite{ilin21}. We draw
+$n_\textrm{fit, Ilin et al. (2021)}$ \citep[last column in Table 3 of ][]{ilin21}
+flares from our sample 100 times without replacement, refit the FFD, and take
+the average FFD slope from that sub-sample of flares to our results.  We find
+$\alpha$ remains consistent with our presented values to $\sim 2\sigma$. We note
+that in most cases $n_\textrm{fit, Ilin et al. (2021)} < n_\textrm{fit, this work}$.
+Therefore, the increased disagreement in $\alpha$ could be due to smaller sample sizes.
+
+Additionally, we test if the difference in $\alpha$ is driven by the cadence
+differences between \textit{K2} (30-minute) and TESS (2-minute). We bin all of
+the flares in our sample down to a 30-minute cadence, re-fit for flare $A$ and ED,
+and recalculate the flare energy. We re-fit the FFD for this altered sample and
+measure  FFD slopes consistent to $\sim 1 \sigma$ with those presented in this work.
+Therefore, the discrepancy seen here is not driven by observational differences
+between \textit{K2} and TESS.
+
+Finally, we test if the differences are driven by the range of energies that are fit.
+The CNN-based flare detection algorithm has previously been demonstrated to be
+less-biased against lower energy flares. Like this work, \cite{ilin21} fit the FFD
+across flare energies which are not affected by a reduced efficiency in the low-energy
+flare detection, $E \geq E_\textrm{turnover}$. In energy space, these fits begin
+between $E_f = 10^{32-33}$~erg, compared to our fits which begin between
+$E_f = 10^{31-32}$~erg (Figure~\ref{appendix:supp_ffds}). When we limit our sample
+to $E_f \geq 10^{32.5}$~erg, we find the FFD slopes become \textit{steeper} and
+more consistent with the values of $\alpha$ presented in \cite{ilin21}. Therefore,
+the difference in $\alpha$ between this work and \cite{ilin21} for stars with
+$t_\textrm{age} = 120 - 150$~Myr is driven by the lower energy flares, with which
+we are more complete to with TESS than \textit{K2}.
 
@@
         \caption{
-            Comparison of Rossby Number, $R_0$ and flare rate for young GKM stars. For the younger sample (top row; $t_\textrm{age} = 4.5 - 50$~Myr), we find no correlations between flare
-            rate and $R_0$. For the slightly older sample (bottom row; $t_\textrm{age} = 50 - 250$~Myr), we find no change in the average flare rate for M stars. For K and G stars, we start
-            to see some evolution in this relationship. For K and G stars, we that as $R_0$ increases, the average flare rate decreases. This could indicate that as stars spin-down, their
-            flare activity also begins to decline. We find that for the full GKM sample of stars (bottom row, rightmost column), the relationship between $R_0$ and flare rate is best-fit by
-            a broken power law, with a turnover at $R_0 = 0.136$. For the younger full sample (top row, rightmost column), we find this relationship is best-fit by a single power law. The
+            Comparison of Rossby Number, $R_0$ and flare rate for young GKM stars.
+            For the younger sample (top row; $t_\textrm{age} = 4.5 - 50$~Myr), we
+            find no correlations between flare rate and $R_0$. For the slightly
+            older sample (bottom row; $t_\textrm{age} = 50 - 250$~Myr), we find
+            no change in the average flare rate for M stars. For K and G stars,
+            we start to see some evolution in this relationship. For K and G
+            stars, we that as $R_0$ increases, the average flare rate decreases.
+            This could indicate that as stars spin-down, their flare activity
+            also begins to decline. We find that for the full GKM sample of
+            stars (bottom row, rightmost column), the relationship between $R_0$
+            and flare rate is best-fit by a broken power law, with a turnover
+            at $R_0 = 0.136$. For the younger full sample (top row, rightmost column),
+            we find this relationship is best-fit by a single power law. The
             histograms are colored by number of stars in each bin.
@@
 
-The Rossby number, $R_0$, is a parameter which incorporates  several properties which are known to affect the stellar dynamo, such as the rotation period and stellar mass. In the context of
-stellar dynamo the Rossby number indicates the dominance of the convective verses rotational dynamo. It is defined as $R_0 = P_\textrm{rot}/\tau$, where $\tau$ is the convective turnover
-time. We convert our measured rotation periods to $R_0$,  approximating $\tau$ following the prescription in \cite{wright11}. We
+The Rossby number, $R_0$, is a parameter which incorporates  several properties which
+are known to affect the stellar dynamo, such as the rotation period and stellar mass.
+In the context of stellar dynamo the Rossby number indicates the dominance of the
+convective verses rotational dynamo. It is defined as $R_0 = P_\textrm{rot}/\tau$,
+where $\tau$ is the convective turnover time. We convert our measured rotation periods
+to $R_0$,  approximating $\tau$ following the prescription in \cite{wright11}. We
 equate the flare rates, $\mathcal{R}$, for individual stars as
@@
 \end{equation}
-In Equation (\ref{eq:fr}), $\mathcal{R}$ is the flare rate in units of day$^{-1}$, $t_\textrm{obs}$ is the total amount of time a target was observed with TESS, and $p_i$ is the probability
-that flare $i$ is a true flare as assigned by \texttt{stella}. We compare the calculated $R_0$ to measured flare rates for all stars with measured $P_\textrm{rot}$. The results are presented
-in Figure~\ref{fig:prot_histograms}.
-
-From these results, we are able to evaluate the dependence of the flare rate on age, spectral type,  and $R_0$. We split the sample between stars younger and older than 50~Myr. This age roughly
-correlates to the age at which GKM stars turn onto the main sequence. The flare rate of stars younger than 50~Myr slightly decreases with increasing $R_0$. However, there is a significant amount
-of scatter in this relationship.
-
-As can be seen by comparing the upper and  lower panels in Figure ~\ref{fig:prot_histograms}, the flare rate dependence on Rossby number is most evident in older, more massive stars  between
-$50 - 250$~Myr. There is minimal evolution in both the average flare rate and $R_0$ between the two samples for M stars. For K stars,  $R_0$ evolves more dramatically during the first 250~Myr
-while the scatter in the flare rate decreases. For G stars, the scatter in $R_0$ decreases and the average flare rate across the sample decreases. We present a compiled histogram for all stars
-in our sample in the right column of Figure~\ref{fig:prot_histograms}.
-
-To better understand this trend for the GKM sample, we fit three functions to the flare rate Rossby number parameter space: (i) a constant value, (ii) a single power law, and (iii) a piece-wise
-function consisting of a constant value and a power law.  We computed the $\chi^2$ between each of these fits and the data. For (iii), we fit for where the $R_0$ turnover should occur by
-computing the $\chi^2$ across a range of $R_0 = [0.09, 0.18]$. We weighted the data points based on the density of points in a given bin (Figure~\ref{fig:prot_histograms}). For  $4.5 - 50$~Myr
-old stars, the distribution is best-fit with a single power law with slope $m = -0.102 \pm 0.018$ and y-intercept $b = -0.660 \pm 0.017$. For stars $50 - 250$~Myr, the distribution is best-fit
-with a piece-wise function of the form:
+
+In Equation (\ref{eq:fr}), $\mathcal{R}$ is the flare rate in units of day$^{-1}$,
+$t_\textrm{obs}$ is the total amount of time a target was observed with TESS, and
+$p_i$ is the probability that flare $i$ is a true flare as assigned by \texttt{stella}.
+We compare the calculated $R_0$ to measured flare rates for all stars with measured
+$P_\textrm{rot}$. The results are presented in Figure~\ref{fig:prot_histograms}.
+
+From these results, we are able to evaluate the dependence of the flare rate on age,
+spectral type,  and $R_0$. We split the sample between stars younger and older than
+50~Myr. This age roughly correlates to the age at which GKM stars turn onto the main
+sequence. The flare rate of stars younger than 50~Myr slightly decreases with
+increasing $R_0$. However, there is a significant amount of scatter in this relationship.
+
+As can be seen by comparing the upper and  lower panels in Figure ~\ref{fig:prot_histograms},
+the flare rate dependence on Rossby number is most evident in older, more massive stars
+between $50 - 250$~Myr. There is minimal evolution in both the average flare rate
+and $R_0$ between the two samples for M stars. For K stars,  $R_0$ evolves more
+dramatically during the first 250~Myr while the scatter in the flare rate decreases.
+For G stars, the scatter in $R_0$ decreases and the average flare rate across the
+sample decreases. We present a compiled histogram for all stars in our sample in the
+right column of Figure~\ref{fig:prot_histograms}.
+
+To better understand this trend for the GKM sample, we fit three functions to the
+flare rate Rossby number parameter space: (i) a constant value, (ii) a single power
+law, and (iii) a piece-wise function consisting of a constant value and a power law.
+We computed the $\chi^2$ between each of these fits and the data. For (iii), we fit
+for where the $R_0$ turnover should occur by computing the $\chi^2$ across a range
+of $R_0 = [0.09, 0.18]$. We weighted the data points based on the density of points
+in a given bin (Figure~\ref{fig:prot_histograms}). For  $4.5 - 50$~Myr old stars,
+the distribution is best-fit with a single power law with slope $m = -0.102 \pm 0.018$
+and y-intercept $b = -0.660 \pm 0.017$. For stars $50 - 250$~Myr, the distribution
+is best-fit with a piece-wise function of the form:
 
@@
 \end{equation}
-In Equation (\ref{eq:piecewiseft}), $\mathcal{R}$ is the flare rate, $C = 0.269 \pm 0.007$, $m = -0.612 \pm 0.039$, and $b = -1.113 \pm 0.035$. The location of the turnover is consistent
-with what has been measured in other observations of magnetic saturation for partially and fully convective stars \citep[e.g. $L_X/L_\textrm{bol}$; ][]{wright18}.
-
-With a sample of 851,168 flares detected in both \textit{Kepler} 1- and 30-minute cadence data, \cite{Davenport16} searched for a relationship between Rossby number and relative flare
-luminosity. This work determined that the relationship could be fit by a broken power law, with a break at $R_0 = 0.03$ and a slope of $m \sim -1$ dominating higher $R_0$. However, a single
-power law is slightly preferred over the broken power law. While the metrics used between \cite{Davenport16} and this paper are different, both suggest a saturation in flares for stars with
-low $R_0$. Additionally, \cite{medina20} found a broken power-law relationship between $R_0$ and the flare rate for flares with $E_f > 3.16 \times 10^{31}$\,erg, corresponding to the
-completeness threshold of their sample. \cite{medina20} analyzed light curves of 419 low-mass ($M_\star = 0.1 - 0.3 M_\odot$) main-sequence stars in the Solar neighborhood  observed by TESS.
-They found that the flare rate saturates at $log(\mathcal{R}) = -1.30 \pm -0.08$ for $R_0 < 0.1$ and rapidly declines for $R_0 > 0.1$. \cite{yang23} analysed 7,082 stars with measured
-$P_\textrm{rot}$ observed during TESS sectors 1–30, and found a broken-power law described the relationship between $\Delta$Flare$/L_\star$ for M dwarfs, with a break between $R_0 = 0.1 - 0.13$,
-which is consistent with this work. While there are differences in sample selection between our work and previous studies, all are consistent with flare rate saturation for stars with low $R_0$
-and a steep drop-off in flare rate for stars with higher $R_0 > 0.1$.
+In Equation (\ref{eq:piecewiseft}), $\mathcal{R}$ is the flare rate, $C = 0.269 \pm 0.007$,
+$m = -0.612 \pm 0.039$, and $b = -1.113 \pm 0.035$. The location of the turnover is
+consistent with what has been measured in other observations of magnetic saturation
+for partially and fully convective stars \citep[e.g. $L_X/L_\textrm{bol}$; ][]{wright18}.
+
+With a sample of 851,168 flares detected in both \textit{Kepler} 1- and 30-minute
+cadence data, \cite{Davenport16} searched for a relationship between Rossby number
+and relative flare luminosity. This work determined that the relationship could be
+fit by a broken power law, with a break at $R_0 = 0.03$ and a slope of $m \sim -1$
+dominating higher $R_0$. However, a single power law is slightly preferred over the
+broken power law. While the metrics used between \cite{Davenport16} and this paper
+are different, both suggest a saturation in flares for stars with low $R_0$. Additionally,
+\cite{medina20} found a broken power-law relationship between $R_0$ and the flare
+rate for flares with $E_f > 3.16 \times 10^{31}$\,erg, corresponding to the completeness
+threshold of their sample. \cite{medina20} analyzed light curves of 419 low-mass
+($M_\star = 0.1 - 0.3 M_\odot$) main-sequence stars in the Solar neighborhood
+observed by TESS.  They found that the flare rate saturates at
+$log(\mathcal{R}) = -1.30 \pm -0.08$ for $R_0 < 0.1$ and rapidly declines for $R_0 > 0.1$.
+\cite{yang23} analysed 7,082 stars with measured $P_\textrm{rot}$ observed during
+TESS sectors 1–30, and found a broken-power law described the relationship between
+$\Delta$Flare$/L_\star$ for M dwarfs, with a break between $R_0 = 0.1 - 0.13$, which
+is consistent with this work. While there are differences in sample selection between
+our work and previous studies, all are consistent with flare rate saturation for
+stars with low $R_0$ and a steep drop-off in flare rate for stars with higher $R_0 > 0.1$.
 
@@
 
-We search for evidence of variations of the FFDs as a function of flare amplitude versus Rossby number, $R_0$. This is motivated by the data  presented in \cite{seligman22}. In that work, they
-modeled flares driven by magnetic reconnection events driven by rotational forces as well as convective dynamo.  \cite{seligman22} found that stars with $R_0 < 0.13$ exhibited shallower FFD
-slopes than stars with $R_0 \geq 0.13$ to several sigma significance. The differences in the FFDs were indicative of relatively more high-energy flares to low-energy flares. This was interpreted
-as evidence of a more dominant rotational dynamo compared to the convective dynamo, which preferentially produced longer magnetic braids in the stellar coronae.
-
-In this subsection, we test this theory with a much larger sample of stars (\nprot\ instead of $807$ stars). We fit the distributions separated by the fitted $R_0$ presented in
-Section~\ref{subsec:rossby}. In order to perform the fits, we follow the prescription described in greater detail in \cite{seligman22}. Here, we provide a brief summary of the prescription.
-Specifically, we fit a truncated power-law distribution of the form,
+We search for evidence of variations of the FFDs as a function of flare amplitude
+versus Rossby number, $R_0$. This is motivated by the data  presented in \cite{seligman22}.
+In that work, they  modeled flares driven by magnetic reconnection events driven by
+rotational forces as well as convective dynamo.  \cite{seligman22} found that stars
+with $R_0 < 0.13$ exhibited shallower FFD slopes than stars with $R_0 \geq 0.13$ to
+several sigma significance. The differences in the FFDs were indicative of relatively
+more high-energy flares to low-energy flares. This was interpreted as evidence of a
+more dominant rotational dynamo compared to the convective dynamo, which preferentially
+produced longer magnetic braids in the stellar coronae.
+
+In this subsection, we test this theory with a much larger sample of stars (\nprot\
+instead of $807$ stars). We fit the distributions separated by the fitted $R_0$
+presented in Section~\ref{subsec:rossby}. In order to perform the fits, we follow
+the prescription described in greater detail in \cite{seligman22}. Here, we provide
+a brief summary of the prescription. Specifically, we fit a truncated power-law
+distribution of the form,
 
@@
 \end{equation}
-In Equation (\ref{eq:dpda}),  $A$ is the amplitude of the flare, $A_*$ is a flare amplitude cutoff parameter and $\alpha_T$ is the slope, rather than $\alpha$. We fit the slopes using the
-MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}. We used the log-likelihood function in \cite{seligman22} and  fit for $A_*$ and $\alpha_T$. We initialized the MCMC fit
-with 200 walkers and evaluated the fit over 5000 steps. The first 1000 steps were discarded upon visual inspection. The results are presented in Figure~\ref{fig:truncated}.
+
+In Equation (\ref{eq:dpda}),  $A$ is the amplitude of the flare, $A_*$ is a flare
+amplitude cutoff parameter and $\alpha_T$ is the slope, rather than $\alpha$. We fit
+the slopes using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}.
+We used the log-likelihood function in \cite{seligman22} and  fit for $A_*$ and $\alpha_T$.
+We initialized the MCMC fit with 200 walkers and evaluated the fit over 5000 steps.
+The first 1000 steps were discarded upon visual inspection. The results are presented
+in Figure~\ref{fig:truncated}.
 
@@
         \caption{
-            Flare frequency distributions, as a function of flare amplitude, for stars with $R_0 \leq 0.12$ (red) and stars with $R_0 > 0.12$ (black). We present the best-fit model, and the
-            best-fit values of the model slope and normalization factor in the legends. Our sample of $R_0 \leq 0.12$ includes 13,132 flares from 800 stars; our sample of $R_0 > 0.12$
-            includes 5,603 flares from 747 stars. We find the stars with smaller Rossby numbers have shallower slopes, consistent with more, high-energy flares and a more dominant rotational
-            dynamo \citep{seligman22}.
+            Flare frequency distributions, as a function of flare amplitude,
+            for stars with $R_0 \leq 0.12$ (red) and stars with $R_0 > 0.12$
+            (black). We present the best-fit model, and the best-fit values of
+            the model slope and normalization factor in the legends. Our sample
+            of $R_0 \leq 0.12$ includes 13,132 flares from 800 stars; our sample
+            of $R_0 > 0.12$ includes 5,603 flares from 747 stars. We find the stars
+            with smaller Rossby numbers have shallower slopes, consistent with more,
+            high-energy flares and a more dominant rotational dynamo \citep{seligman22}.
         }
@@
 
-We find that stars with $R_0 \leq 0.136$ have a best-fit slope of $\alpha_T = 1.076 \pm 0.020$, while stars with larger $R_0$ have a best-fit slope of $\alpha_T = 1.604 \pm 0.040$. This
-result agrees with the results presented in \cite{seligman22}. This is not the first instance we have seen a correlation in FFDs as a function of $R_0$. \cite{candelaresi14} noted that
-faster rotating stars have higher superflare rates derived from \textit{Kepler} data. The spectroscopic survey presented in \cite{notsu19} found that the maximum flare energy decreased
-as $P_\textrm{rot}$, and consequently $R_0$, increased. \cite{mondrik19} identified flares across 2,226 stars observed with MEarth and found an increase in flare rate between stars with
-low $R_0 < 0.04$ and stars with intermediate $R_0 = (0.04, 0.44)$, and a subsequent decrease in flare rate for stars with high $R_0 > 0.44$. While our bins of stars by $R_0$ are not as
-fine as those presented in \cite{mondrik19}, the correlation in $\Delta R_0$ remains consistent.
+We find that stars with $R_0 \leq 0.136$ have a best-fit slope of
+$\alpha_T = 1.076 \pm 0.020$, while stars with larger $R_0$ have a best-fit slope
+of $\alpha_T = 1.604 \pm 0.040$. This result agrees with the results presented in
+\cite{seligman22}. This is not the first instance we have seen a correlation in FFDs
+as a function of $R_0$. \cite{candelaresi14} noted that faster rotating stars have
+higher superflare rates derived from \textit{Kepler} data. The spectroscopic survey
+presented in \cite{notsu19} found that the maximum flare energy decreased as
+$P_\textrm{rot}$, and consequently $R_0$, increased. \cite{mondrik19} identified
+flares across 2,226 stars observed with MEarth and found an increase in flare rate
+between stars with low $R_0 < 0.04$ and stars with intermediate $R_0 = (0.04, 0.44)$,
+and a subsequent decrease in flare rate for stars with high $R_0 > 0.44$. While our
+bins of stars by $R_0$ are not as fine as those presented in \cite{mondrik19}, the
+correlation in $\Delta R_0$ remains consistent.
 
@@
 
-The Sun undergoes an 11-year solar cycle during  which it oscillates between high and low magnetic activity. This magnetic cycle manifests  in a variety of observables. One of the primary
-indicators of the solar cycle is a stark change in the flare rate; this rate can vary by more than an order of magnitude between Solar maxima and minima \citep{webb94}. However, it is worth
-noting that other, shorter periodicities have been observed in Solar flares \citep{}. Moreover, energetics of the flares that are produced on the solar surface vary dramatically over the
-course of the solar cycle \citep{Bai1987,Bai2003}. Direct and indirect evidence  of the solar cycle have also been observed in radio flux, total solar irradiance, the magnitude and geometry
-of the magnetic field, coronal mass ejections affiliated with flares, geomagnetic activity, cosmic ray fluxes and radioisotopes in ice cores and tree rings.
-For a recent review, see \citet{Hathaway2015}.
-
-While other stars should also experience activity cycles like the Sun, they are more difficult to measure. Constraints on stellar cycles have predominantly relied on long baseline variations
-in stellar photometry \citep[see recent reviews by ][]{jeffers23, isik23}, typically observed at cadences which cannot resolve stellar flares. However,  tracing stellar cycles via stellar
-flares may be more reliable, as flares are a direct consequence of magnetic activity. \cite{} explored measuring the stellar cycle length of KIC 8507979, a star in the \textit{Kepler} field
-which was observed for 18 90-day quarters. \cite{scoggins19} found the flare rate decreased over each quarter, which could be fit by
-$L_\textrm{fl}/L_\textrm{Kp} = (-9.96 \pm 3.94) \times 10^{-2} \times t_\textrm{yr} + (2.43 \pm 0.11)$, where $t_\textrm{yr}$ is the time in years, and $L_\textrm{fl}/L_\textrm{Kp}$ is a
-parameterization of the \textit{Kepler} flare rate \citep{lurie15}.
-
-%It is possible that the length of the stellar cycle is related to the rotational period $P_\textrm{rot}$ or the Rossby number $R_0$ of the star as ... \citep{}. If this is the case,
-then stars with $P_\textrm{rot}$ will have shorter stellar cycle lengths.
+The Sun undergoes an 11-year solar cycle during  which it oscillates between high and
+low magnetic activity. This magnetic cycle manifests  in a variety of observables. One
+of the primary indicators of the solar cycle is a stark change in the flare rate; this
+rate can vary by more than an order of magnitude between Solar maxima and minima
+\citep{webb94}. Moreover, energetics of the flares that are produced on the solar
+surface vary dramatically over the course of the solar cycle \citep{Bai1987,Bai2003}.
+Direct and indirect evidence  of the solar cycle have also been observed in radio flux,
+total solar irradiance, the magnitude and geometry of the magnetic field, coronal
+mass ejections affiliated with flares, geomagnetic activity, cosmic ray fluxes and
+radioisotopes in ice cores and tree rings. For a recent review, see \citet{Hathaway2015}.
+
+While other stars should also experience activity cycles like the Sun, they are
+more difficult to measure. \textcolor{red}{Constraints on stellar cycles have
+predominantly relied on long baseline variations in stellar photometry, typically
+observed at cadences which cannot resolve stellar flares \citep[see recent reviews
+by ][]{jeffers23, isik23}}. However,  tracing stellar cycles via stellar flares may
+be more reliable, as flares are a direct consequence of magnetic activity. \cite{scoggins19}
+explored measuring the stellar cycle length of KIC 8507979, a star in the \textit{Kepler}
+field which was observed for 18 90-day quarters. \cite{scoggins19} found the flare rate
+decreased over each quarter, which could be fit by
+$L_\textrm{fl}/L_\textrm{Kp} = (-9.96 \pm 3.94) \times 10^{-2} \times t_\textrm{yr} + (2.43 \pm 0.11)$,
+where $t_\textrm{yr}$ is the time in years, and $L_\textrm{fl}/L_\textrm{Kp}$ is
+a parameterization of the \textit{Kepler} flare rate \citep{lurie15}.
 
@@
 
-Here, we explore observables from solar flares between 2002 and 2018 in the Reuven Ramaty High Energy Solar Spectroscopic Imager \citep[RHESSI;][]{lin02} flare
-catalog.\footnote{\url{https://hesperia.gsfc.nasa.gov/rhessi3/data-access/rhessi-data/flare-list/index.html}} The RHESSI mission observes the Sun in the hard X-ray
-(HXR; $> 25$~keV) and has detected over $100,000$ solar flares in 16 years of operations. These observations covered the second half of solar Cycle 23 and the beginning of
-solar Cycle 24. We use the publicly available RHESSI flare catalog to determine  metrics that would be most useful when searching for evidence of stellar cycles. One potential
-issue with this analysis is that the HXR observations from RHESSI and white-light observations from TESS may not be directly correlated. However, there is a close spatial and
-temporal correspondence between HXR and white-light flares on the Sun \citep{fletcher07, krucker11, kleint16}. Therefore, the HXR solar flares with energies between $25 - 50$~keV
-are likely representative of solar white-light flares, and are a comparable sample to our TESS sample. First, the total number of flares detected in the $25 - 50$~keV bandpass
-varied by 650~flares from solar maximum in 2002 to solar minimum in 2008. This variation correlates to a change in flare rate from $1.81$ to $0.02$ flares day$^{-1}$ on average.
-Second, the flare frequency distribution changes between solar minimum and maximum because the frequency of the highest-energy flares decreases.  Finally, the total flare luminosity
-relative to the total luminosity correlates with the stellar cycle. This is defined by \cite{lurie15} as
+Here, we explore observables from solar flares between 2002 and 2018 in the Reuven
+Ramaty High Energy Solar Spectroscopic Imager \citep[RHESSI;][]{lin02} flare
+catalog.\footnote{\url{https://hesperia.gsfc.nasa.gov/rhessi3/data-access/rhessi-data/flare-list/index.html}}
+\textcolor{red}{The RHESSI mission observes the Sun across a wide range of X-ray energies,
+from 3 keV-17 MeV, with high temporal and energy resolutions as well as with high signal
+sensitivity. Such a wide energy range enables the ability to explore both thermal and
+non-thermal emission observed during flare events. Over 16 years of operations, over
+$100,000$ solar flares have been observed and characterized in RHESSI data.} These
+observations covered the second half of solar Cycle 23 and the beginning of Solar
+Cycle 24. We use the publicly available RHESSI flare catalog to determine  metrics
+that would be most useful when searching for evidence of stellar cycles. One potential
+issue with this analysis is that the HXR observations from RHESSI and white-light
+observations from TESS may not be directly correlated. However, there is a close spatial
+and temporal correspondence between HXR and white-light flares on the Sun
+\citep{fletcher07, krucker11, kleint16}. \textcolor{red}{In particular, \cite{namekata17}
+demonstrated the difference spatially resolved flares as observed with RHESSI HXR and the
+Solar Dynamics Observatory (SDO)/Helioseismic and Magnetic Imager (HMI) white-light. In
+some examples, the HMI white-light emission is seen to last longer than the HXR,
+indicating the white-light emission is related to non-thermal electrons.}
+
+\textcolor{red}{However, other examples of simultaneous HXR and white-light flare
+observations in \citep{namekata17} show similar flare durations. Therefore, we take
+the HXR solar flares with energies between $25 - 50$~keV as likely representative
+of solar white-light flares, and are a comparable sample to our TESS sample.} First,
+the total number of flares detected in the $25 - 50$~keV bandpass varied by 650~flares
+from solar maximum in 2002 to solar minimum in 2008. This variation correlates to
+a change in flare rate from $1.81$ to $0.02$ flares day$^{-1}$ on average. Second,
+the flare frequency distribution changes between solar minimum and maximum because
+the frequency of the highest-energy flares decreases.  Finally, the total flare
+luminosity relative to the total luminosity correlates with the stellar cycle.
+This is defined by \cite{lurie15} as
 
@@
 
-where $L_\textrm{flare}$ is the total luminosity emitted by flares, $L_\star$ is the luminosity of the star, $\xi_\textrm{flare}$ is sum of the equivalent duration of all flares
-observed, and $t_\textrm{exp}$ is the exposure time of the observations. These results for the Sun are presented in the left-most column of Figure~\ref{fig:stellar_cycles}.
+where $L_\textrm{flare}$ is the total luminosity emitted by flares, $L_\star$ is
+the luminosity of the star, $\xi_\textrm{flare}$ is sum of the equivalent duration
+of all flares observed, and $t_\textrm{exp}$ is the exposure time of the observations.
+These results for the Sun are presented in the left-most column of Figure~\ref{fig:stellar_cycles}.
 
@@
 
-The TESS Extended Missions have provided a five-year baseline that we can use to search for evidence of stellar cycles. This is a comparable baseline to \textit{Kepler}, although with sparser
-sampling. We search for evidence of stellar cycles  within our sample of fast rotators. Our sample contains 108 stars which have been observed for $t_\textrm{obs} \geq 200$\,days across five
-years. We search for evidence of changes in the stellar magnetic activity by looking for correlations in (i) variations in the total luminosity emitted in flares  (ii) the total flare rate per
-year and (iii) annual changes in the FFD.  We group our observations by the year in which the observations were taken, even for the cases where the star was not continuously observed throughout
-that year (e.g. Sectors 1-26 are Year 1, Sectors 27-55 are Year 2, and Sectors 56-67 are Year 3.
-
-We searched our 108 candidates by eye for correlations in the aforementioned criteria. The correlations are categorized into the following four options: (i) \textbf{Positive}:  $E_\textrm{f, max}$
-and the total number of flares has increased over five years; (ii) \textbf{Negative}:  $E_\textrm{f, max}$ and the total number of flares has decreased over five years; (iii) \textbf{Trough}:
-$E_\textrm{f, max}$ and the total number of flares was greater in the first and third years observed with a minima in the second year; (iv) \textbf{Peak}:  $E_\textrm{f, max}$ and the total number
-of flares was fewer in the first and third years observed with a maxima in the second year.
-
-From these three observables, we identified eleven stars which all display evidence of scenario Peak, with the exception of one star displaying evidence of scenario Negative, which are presented in
-Figure~\ref{fig:stellar_cycles}. These stars are TIC
-142015852, 235056185, 260351540, 270676943, 272349442, 308186412, 339668420, 350559457, 391745863, 393490554, and 452357628.  Our sample includes seven early type M-stars, two late K-stars, one
-early K-star, and one G-star. TIC 272349442 is a candidate member of TW Hydrae ($t_\textrm{age} = 10 \pm 3$\,Myr), TIC 142015852, 270676943, 308186412, 339668420, 350559457, and 452357628 are
-candidate members of Carina ($t_\textrm{age} = 45 \pm 9$\,Myr), TIC 235056185 and  260351540 are candidate members of IC 2602 ($t_\textrm{age} = 52.5 \pm 2.95$\,Myr), and TIC 391745863 and 393490554
+The TESS Extended Missions have provided a five-year baseline that we can use to
+search for evidence of stellar cycles. This is a comparable baseline to \textit{Kepler},
+although with sparser sampling. We search for evidence of stellar cycles  within
+our sample of fast rotators. Our sample contains 108 stars which have been observed
+for $t_\textrm{obs} \geq 200$\,days across five years. We search for evidence of
+changes in the stellar magnetic activity by looking for correlations in (i)
+variations in the total luminosity emitted in flares  (ii) the total flare rate
+per year and (iii) annual changes in the FFD.  We group our observations by the
+year in which the observations were taken, even for the cases where the star was
+not continuously observed throughout that year (e.g. Sectors 1-26 are Year 1,
+Sectors 27-55 are Year 2, and Sectors 56-67 are Year 3.
+
+We searched our 108 candidates by eye for correlations in the aforementioned criteria.
+The correlations are categorized into the following four options: (i) \textbf{Positive}:
+$E_\textrm{f, max}$ and the total number of flares has increased over five years; (ii)
+\textbf{Negative}:  $E_\textrm{f, max}$ and the total number of flares has decreased
+over five years; (iii) \textbf{Trough}: $E_\textrm{f, max}$ and the total number of
+flares was greater in the first and third years observed with a minima in the second
+year; (iv) \textbf{Peak}:  $E_\textrm{f, max}$ and the total number of flares was
+fewer in the first and third years observed with a maxima in the second year.
+
+From these three observables, we identified eleven stars which all display evidence
+of scenario Peak, with the exception of one star displaying evidence of scenario
+Negative, which are presented in Figure~\ref{fig:stellar_cycles}. These stars are TIC
+142015852, 235056185, 260351540, 270676943, 272349442, 308186412, 339668420, 350559457,
+391745863, 393490554, and 452357628.  Our sample includes seven early type M-stars,
+two late K-stars, one early K-star, and one G-star. TIC 272349442 is a candidate member
+of TW Hydrae ($t_\textrm{age} = 10 \pm 3$\,Myr), TIC 142015852, 270676943, 308186412,
+339668420, 350559457, and 452357628 are candidate members of Carina
+($t_\textrm{age} = 45 \pm 9$\,Myr), TIC 235056185 and  260351540 are candidate members
+of IC 2602 ($t_\textrm{age} = 52.5 \pm 2.95$\,Myr), and TIC 391745863 and 393490554
 are candidate members of the AB Doradus Moving Group ($t_\textrm{age} = 133 \pm 12.5$\,Myr).
 
-We report the measured $\xi_\textrm{flare}/t_\textrm{exp}$ and flare rates across all three years in presented in Figure~\ref{fig:stellar_cycles} in Table~\ref{tab:cycles}. Across our sample, we
-find the largest change in flare parameters in TIC 235056185, which has a $\Delta log_{10}(\xi_\textrm{flare} / t_\textrm{exp}) = 1.14$ and $\Delta \mathcal{R} = 0.5$. Additionally, we see some
-targets (e.g. TIC 350559457) become very flare quiet, going from $\mathcal{R} = 0.2$~day$^{-1}$ to $\mathcal{R} = 0.05$~day$^{-1}$, which is obvious when visually inspecting the light curve. For
-stars showing the Peak scenario, we find that the year before and after the peak do not necessarily return to the same value of $\xi_\textrm{flare} / t_\textrm{exp}$ and $\mathcal{R}$, although it
-does for some stars.
+We report the measured $\xi_\textrm{flare}/t_\textrm{exp}$ and flare rates across
+all three years in presented in Figure~\ref{fig:stellar_cycles} in Table~\ref{tab:cycles}.
+Across our sample, we find the largest change in flare parameters in TIC 235056185,
+which has a $\Delta log_{10}(\xi_\textrm{flare} / t_\textrm{exp}) = 1.14$ and
+$\Delta \mathcal{R} = 0.5$. Additionally, we see some targets (e.g. TIC 350559457)
+become very flare quiet, going from $\mathcal{R} = 0.2$~day$^{-1}$ to $\mathcal{R} = 0.05$~day$^{-1}$,
+which is obvious when visually inspecting the light curve. For stars showing the
+Peak scenario, we find that the year before and after the peak do not necessarily
+return to the same value of $\xi_\textrm{flare} / t_\textrm{exp}$ and $\mathcal{R}$,
+although it does for some stars.
 
@@
 
-The majority of stars identified with evidence of stellar cycles exhibit the Peak scenario. To determine if this is astrophysical or driven by some unknown instrumental systematic,
-we perform an injection-recovery test on this sub-sample of stars. Injection-recovery tests are used to address biases in our detection method.  Injection-recovery tests are typically
-not recommended for machine-learning detection techniques \citep{feinstein20}. However, we perform them because these are some of the first results of searching for evidence of stellar
-cycles via flare activity.
-
-We inject a total of 50 flares into each sector of data for our eleven stars. We draw the amplitude of our flares from a Gaussian distribution centered at a 3\% increase in flux, with a
-standard deviation of 1\%. We do not inject flares with amplitudes below 0.5\%. We used the Llamaradas Estelares flare model. We fit a line between flare amplitude and FWHM from our new
-catalog to extract an appropriate FHWM for any given amplitude. We added additional noise to the FHWM, as the relationship between amplitude and FWHM exhibits scatter similar to
-distribution of flare energy and ED shown in Figure~\ref{fig:flare_distribution}. Once the flares were injected, we followed the steps outlined in
-Sections~\ref{subsec2:Flareidentification} - \ref{subsec2:qualitychecks} to identify these injected flares.
-
-We considered a flare recovered if the $t_\textrm{peak}$ is within 15~minutes of the injected $t_\textrm{peak}$. We are able to recover 93\% of flares with $A \geq 3$\% and 80\% of flares
-with $A < 3$\%. This is consistent with previous results using this flare identification method \citep{feinstein20}. We note that there is a steep drop-off in flare recovery rate at
-$T_\textrm{mag} > 13$,  with average recovery rates dropping from  90\% to 70\%.  The variation in recovery rates between years observed by TESS ranges from $1 - 8$\% across all eleven
-targets. There is no correlation between recovery rate,  $\xi_\textrm{flare}/t_\textrm{exp}$ and flare rate, with the exception of TIC 142015852 and 339668420. We find an 8\% increase
-between Years 1 and 2, and a 3\% decrease between Years 2 and 3 in the recovery rate for TIC 142015852. Additionally, we find an 1\% increase between Years 1 and 2, and a 2\% decrease
-between Years 2 and 3 in the recovery rate for TIC 339668420. An 8\% change in the recovered flare rate correlates to $\Delta (\xi_\textrm{flare} / t_\textrm{exp}) = 0.09$, assuming
-ED~$= 1$\,minute, and a $\Delta \mathcal{R} = 0.03$. These estimates are smaller than the annual variations seen in flare statistics for these two stars, leading us to conclude that these
-variations are astrophysical.
+The majority of stars identified with evidence of stellar cycles exhibit the Peak
+scenario. To determine if this is astrophysical or driven by some unknown instrumental
+systematic, we perform an injection-recovery test on this sub-sample of stars.
+Injection-recovery tests are used to address biases in our detection method.
+Injection-recovery tests are typically not recommended for machine-learning
+detection techniques \citep{feinstein20}. However, we perform them because these
+are some of the first results of searching for evidence of stellar cycles via
+flare activity.
+
+We inject a total of 50 flares into each sector of data for our eleven stars.
+We draw the amplitude of our flares from a Gaussian distribution centered at a
+3\% increase in flux, with a standard deviation of 1\%. We do not inject flares
+with amplitudes below 0.5\%. We used the Llamaradas Estelares flare model. We
+fit a line between flare amplitude and FWHM from our new catalog to extract an
+appropriate FHWM for any given amplitude. We added additional noise to the FHWM,
+as the relationship between amplitude and FWHM exhibits scatter similar to
+distribution of flare energy and ED shown in Figure~\ref{fig:flare_distribution}.
+Once the flares were injected, we followed the steps outlined in
+Sections~\ref{subsec2:Flareidentification} - \ref{subsec2:qualitychecks}
+to identify these injected flares.
+
+We considered a flare recovered if the $t_\textrm{peak}$ is within 15~minutes of
+the injected $t_\textrm{peak}$. We are able to recover 93\% of flares with
+$A \geq 3$\% and 80\% of flares with $A < 3$\%. This is consistent with previous
+results using this flare identification method \citep{feinstein20}. We note that
+there is a steep drop-off in flare recovery rate at $T_\textrm{mag} > 13$, with
+average recovery rates dropping from  90\% to 70\%.  The variation in recovery rates
+between years observed by TESS ranges from $1 - 8$\% across all eleven targets.
+There is no correlation between recovery rate,  $\xi_\textrm{flare}/t_\textrm{exp}$
+and flare rate, with the exception of TIC 142015852 and 339668420. We find an 8\%
+increase between Years 1 and 2, and a 3\% decrease between Years 2 and 3 in the
+recovery rate for TIC 142015852. Additionally, we find an 1\% increase between
+Years 1 and 2, and a 2\% decrease between Years 2 and 3 in the recovery rate for
+TIC 339668420. An 8\% change in the recovered flare rate correlates to
+$\Delta (\xi_\textrm{flare} / t_\textrm{exp}) = 0.09$, assuming ED~$= 1$\,minute,
+and a $\Delta \mathcal{R} = 0.03$. These estimates are smaller than the annual
+variations seen in flare statistics for these two stars, leading us to conclude
+that these variations are astrophysical.
 
@@
 
-In the Section~\ref{subsec:inj-rec} we demonstrated that 10 out of 108 stars with $> 200$~days of observations exhibited Peak behavior in their variability patterns and found no bias in flare
-detection as a function of year. This is approximately what we would expect to find for an unbiased sample. Our analysis requires a large number of bright flares to be observable to
-characterize the stellar cycle. Therefore, our sample of objects should be biased towards stars that are undergoing a local maximum, rather than a local miinimum, in their activity cycle.
-
-It is not clear what the length of the activity cycles are for stars other than the Sun. For this order of magnitude estimate we therefore assume that the activity cycles of all stars in our
-sample are similar to that of the Sun. This approximation is valid   if the length of stellar cycles on average is not more than an order of magnitude different than that of the sun. By
-observing $N\sim$108 stars for a $\tau\sim$5 year baseline, assuming that each has a $P\sim10$ year activity cycle, we would expect that during that time period $\tau /P N\sim50$ stars should
-experience a peak in their stellar cycle during the observations. Moreover, our analysis will only be sensitive to activity cycles if there is not only a peak, but also lower activity in the
-year before and after the peak. Therefore, the number of stars that we would expect to identify that have a peak in year 2 should be $\tau /P N /3\sim16$. Therefore we would expect to identify
-$\sim16$ stars exhibiting a peak in their activity cycle during these observations, which is  similar to what we have found. However, it is likely that there is a variety of lengths of stellar
-cycles in our population and the exact correspondence between the number found and the number estimated is simply a manifestation of the crude order of magnitude approximation that we employed
-rather than an exact correspondence. Nevertheless, this represents  tentative detections of peaks in stellar activity cycles and that on average the length of these cycles is not an order of
-magnitude different than that of the Sun.
+In the Section~\ref{subsec:inj-rec} we demonstrated that 10 out of 108 stars with
+$> 200$~days of observations exhibited Peak behavior in their variability patterns
+and found no bias in flare detection as a function of year. This is approximately
+what we would expect to find for an unbiased sample. Our analysis requires a large
+number of bright flares to be observable to characterize the stellar cycle. Therefore,
+our sample of objects should be biased towards stars that are undergoing a local
+maximum, rather than a local miinimum, in their activity cycle.
+
+It is not clear what the length of the activity cycles are for stars other than
+the Sun. For this order of magnitude estimate we therefore assume that the activity
+cycles of all stars in our sample are similar to that of the Sun. This approximation
+is valid   if the length of stellar cycles on average is not more than an order
+of magnitude different than that of the sun. By observing $N\sim$108 stars for a
+$\tau\sim$5 year baseline, assuming that each has a $P\sim10$ year activity cycle,
+we would expect that during that time period $\tau /P N\sim50$ stars should
+experience a peak in their stellar cycle during the observations. Moreover, our
+analysis will only be sensitive to activity cycles if there is not only a peak,
+but also lower activity in the year before and after the peak. Therefore, the
+number of stars that we would expect to identify that have a peak in year 2 should
+be $\tau /P N /3\sim16$. Therefore we would expect to identify $\sim16$ stars
+exhibiting a peak in their activity cycle during these observations, which is
+similar to what we have found.
+
+However, it is likely that there is a variety of lengths of stellar cycles in our
+population and the exact correspondence between the number found and the number
+estimated is simply a manifestation of the crude order of magnitude approximation
+that we employed rather than an exact correspondence. Nevertheless, this represents
+tentative detections of peaks in stellar activity cycles and that on average the
+length of these cycles is not an order of magnitude different than that of the Sun.
+
+\textcolor{red}{The results presented here are consistent with those presented in
+previous studies of magnetic activity cycles in young stars. \cite{olah16} analyzed
+29 stars from the Mount Wilson survey which had $\sim 36$ years of \ion{Ca}{2}
+H \& K monitoring. Roughly 16 stars in this sample have constrained ages of $< 1$~Gyr
+via gyrochronology. This sample of stars have $P_\textrm{rot} = 18.1 \pm 12.2$~days
+and magnetic activity cycles of $P_\textrm{cyc} = 7.6 \pm 4.9$~years. There is
+significantly more dispersion in the young stellar cycle lengths than for the older
+stars. \cite{olah16} concluded that young stars show more complex interannual variations
+in magnetic activity. While stars age, magnetic braking will increase the rotation
+of the star. Once this process has occurred, the magnetic activity cycle becomes more
+well-behaved, as seen on the Sun.}
+
+\textcolor{red}{We apply the relationship between $log(1/P_\textrm{rot})$ and 
+$log(P_\textrm{cyc}/P_\textrm{rot})$ described in \cite{olah16} to estimate the
+activity cycles in our sample. 10 of our 11 candidates have measured
+$P_\textrm{rot} = 0.41 - 5.22$~days. Using the best-fit slope of $0.76 \pm 0.15$,
+we estimate the $P_\textrm{cyc} = 0.81 - 1.49$~years. Strong evidence of shorter
+activity cycles than $\sim 3$~years may be missed by the sparse annual sampling
+from TESS. Redesigning the next TESS extended mission to stare at the northern and
+southern ecliptic poles continuously for two years, instead of alternating poles,
+may help resolve these shorter activity cycles, if present.}
 
@@
 
-We thank David Wilson for thoughtful insights and useful conversations.
-This work made use of the open-source package, \textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes reproducible publications.
-ADF acknowledges funding from NASA through the NASA Hubble Fellowship grant HST-HF2-51530.001-A awarded by STScI.
-DZS is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-2202135.
-This research award is partially funded by a generous gift of Charles Simonyi to the NSF Division of Astronomical Sciences.
-The award is made in recognition of significant contributions to Rubin Observatory’s Legacy Survey of Space and Time.
+We thank David Wilson for thoughtful conversations. \textcolor{red}{We thank the anonymous reviewer for their insightful report,
+which improved the clarity and quality of this manuscript.} This work made use of the open-source package,
+\textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes reproducible publications. ADF acknowledges funding from
+NASA through the NASA Hubble Fellowship grant HST-HF2-51530.001-A awarded by STScI. DZS is supported by an NSF Astronomy and Astrophysics
+Postdoctoral Fellowship under award AST-2202135. This research award is partially funded by a generous gift of Charles Simonyi to the NSF
+Division of Astronomical Sciences. The award is made in recognition of significant contributions to Rubin Observatory’s Legacy Survey of Space and Time.
 

### 2024-04-30 src/scripts/yp_rates.py

@@ -88,7 +88,7 @@ fig, axes = plt.subplots(nrows=2, figsize=(10,6),
                                gridspec_kw={'height_ratios':[1,2]})
 ax1, ax2 = axes.reshape(-1)
 
-fig.set_facecolor('w')
+fig.set_facecolor('k')
 
 # For the color bar only
 sc = ax1.scatter(np.arange(len(yp)), yp, c=teff, cmap=cmap, vmin=2300, vmax=5930, s=0)

### 2024-04-30 src/scripts/yp_rates.py
latest updates

@@ -88,8 +88,6 @@ fig, axes = plt.subplots(nrows=2, figsize=(10,6),
                                gridspec_kw={'height_ratios':[1,2]})
 ax1, ax2 = axes.reshape(-1)
 
-fig.set_facecolor('k')
-
 # For the color bar only
 sc = ax1.scatter(np.arange(len(yp)), yp, c=teff, cmap=cmap, vmin=2300, vmax=5930, s=0)
 

### 2024-05-01 src/tex/ms.tex
latest updates
updated, no tracked edits

@@
 % Define document class
-\documentclass[twocolumn, linenumbers]{aastex631}
+\documentclass[twocolumn]{aastex631}
 \usepackage{showyourwork}
@@
 
-\textcolor{red}{This paper was written using the \textit{showyourwork!} open-source
-software package. The objective of \textit{showyourwork!} is to improve reproducibility
+This paper was written using the \textcolor{red}{\textit{showyourwork!}} open-source
+software package. The objective of \textcolor{red}{\textit{showyourwork!}} is to improve reproducibility
 and transparency of scientific research by compiling the manuscript and figures
 simultaneously. All of the data in this work is hosted on GitHub\footnote{The GitHub is
-hyperlinked in the \textit{showyourwork!} stamp at the top of the first page of this manuscript,
+hyperlinked in the \textcolor{red}{\textit{showyourwork!}} stamp at the top of the first page of this manuscript,
  and can also be found here: \url{https://github.com/afeinstein20/young-stellar-flares}.} and
  Zenodo.\footnote{} At the end of every caption figure in this manuscript, there is a GitHub icon
- (\faGithub), which links to the Python script used to create that figure.}
+ (\faGithub), which links to the Python script used to create that figure.
 
@@
 processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16},
-\textcolor{red}{which can be accessed on MAST under DOI  \href{http://dx.doi.org/10.17909/t9-nmc8-f686}{10.17909/t9-nmc8-f686}.}
+which can be accessed on MAST under DOI  \href{http://dx.doi.org/10.17909/t9-nmc8-f686}{10.17909/t9-nmc8-f686}.
 Our sample has an average of $\sim 3$ light curves per target (although with significant
-spread across targets). \textcolor{red}{We downloaded all light curves using \texttt{lightkurve}\footnote{\url{https://doi.org/10.5281/zenodo.4654522}}.}
+spread across targets). We downloaded all light curves using \texttt{lightkurve}\footnote{\url{https://doi.org/10.5281/zenodo.4654522}}.
 For our analysis, we used the SPOC-processed SAP\_FLUX.
@@
 the convolutional neural network (CNN) \texttt{stella} \citep{feinstein20},
-\textcolor{red}{although other architectures have been explored for flare identification
-\citep[e.g.][]{vida18}.}  The CNN  was trained on a by-eye validated catalogue of flares
+although other architectures have been explored for flare identification
+\citep[e.g.][]{vida18}. The CNN  was trained on a by-eye validated catalogue of flares
 from TESS Sectors 1 and 2 with 2-minute data \citep{guenther19_flares}.
@@
 are typically not identified in traditional sigma-outlier identification
-methods \textcolor{red}{\citep[e.g.][]{chang15, vasilyev22}}. \textcolor{red}{While
+methods \citep[e.g.][]{chang15, vasilyev22}. While
 significant developments have been achieved to better model and detrend stellar
-variability \citep[e.g.][]{bicz22}, these methods can be computationally intensive}
+variability \citep[e.g.][]{bicz22}, these methods can be computationally intensive
 The \texttt{stella} CNN models calculate the probability that a data point in a light
@@
 the CNN ignores 200-minutes before and after any gaps in the data. Therefore, any
-flares which occur during these times are not identified. \textcolor{red}{From by-eye
+flares which occur during these times are not identified. From by-eye
 vetting of $\sim 300$ light curves, we found 2~flares within the first 200~minutes of
-the orbital gaps. Therefore, we estimate $\leq 120$~flares are missed in our catalog.}
+the orbital gaps. Therefore, we estimate $\leq 120$~flares are missed in our catalog.
 
@@
 ($t_\textrm{peak}$), full width at half maximum (FWHM), and the amplitude ($A$)
-of each flare in the sample. \textcolor{red}{We note that there are several other
+of each flare in the sample. We note that there are several other
 physically-motivated flare models which could be used, such as those presented in
 \cite{gryciuk17, pietras22, yang23_lp}; these models include using two profiles to
-fit the impulsive and late phases of the flare.} We combine the model with a
+fit the impulsive and late phases of the flare. We combine the model with a
 second-order polynomial fit to a 1.2-hour baseline before and after the flare
@@
 
-\subsubsection{\textcolor{red}{Comparison of Flare Models}}
-
-\textcolor{red}{\cite{tovar22} demonstrated that the flare model works well for
+\subsubsection{Comparison of Flare Models}
+
+\cite{tovar22} demonstrated that the flare model works well for
 flares with amplitudes $\geq 2$ (i.e. double the baseline flux). However, other
@@
 we refit and calculate the $\chi^2$ for a subset of high amplitude flares ($A \geq 0.4$)
-using Equation 3 in \cite{pietras22}, a double-peak flare model, which is:}
+using Equation 3 in \cite{pietras22}, a double-peak flare model, which is:
 
@@
 
-\textcolor{red}{where $A$ is is related to amplitude of the flare, $B$ relates
+where $A$ is is related to amplitude of the flare, $B$ relates
 to the total energy released during the flare, $C$ relates to the timescale of
@@
 refit 900~high-amplitude flares following Equation~\ref{eqn:flare}. We plot the
-results of this refitting in Figure~\ref{fig:model_fit}.}
+results of this refitting in Figure~\ref{fig:model_fit}.
 
@@
         \caption{
-            \textcolor{red}{Comparison fits between the Llamaradas Estelares
+            Comparison fits between the Llamaradas Estelares
             single-peak model from \cite{tovar22} and the double-peak flare model
@@
             (D, E), and where the models perform equally as well (F, G). We note
-            there is no correlation between flare amplitude and preferred model.}
+            there is no correlation between flare amplitude and preferred model.
         }
@@
 
-\textcolor{red}{Broadly, we find the flare model from \cite{tovar22} and \cite{pietras22}
+Broadly, we find the flare model from \cite{tovar22} and \cite{pietras22}
 to fit the majority of the high-amplitude flares equally as well (Figure~\ref{fig:model_fit}\,A).
@@
 both models tend to have a better fit to the amplitude in the Llamaradas Estelares model, but a
-better fit to the decay timescale in the double-peak flare model.}
+better fit to the decay timescale in the double-peak flare model.
 
@@
 While other stars should also experience activity cycles like the Sun, they are
-more difficult to measure. \textcolor{red}{Constraints on stellar cycles have
+more difficult to measure. Constraints on stellar cycles have
 predominantly relied on long baseline variations in stellar photometry, typically
 observed at cadences which cannot resolve stellar flares \citep[see recent reviews
-by ][]{jeffers23, isik23}}. However,  tracing stellar cycles via stellar flares may
+by ][]{jeffers23, isik23}. However,  tracing stellar cycles via stellar flares may
 be more reliable, as flares are a direct consequence of magnetic activity. \cite{scoggins19}
@@
 catalog.\footnote{\url{https://hesperia.gsfc.nasa.gov/rhessi3/data-access/rhessi-data/flare-list/index.html}}
-\textcolor{red}{The RHESSI mission observes the Sun across a wide range of X-ray energies,
+The RHESSI mission observes the Sun across a wide range of X-ray energies,
 from 3 keV-17 MeV, with high temporal and energy resolutions as well as with high signal
@@
 non-thermal emission observed during flare events. Over 16 years of operations, over
-$100,000$ solar flares have been observed and characterized in RHESSI data.} These
+$100,000$ solar flares have been observed and characterized in RHESSI data. These
 observations covered the second half of solar Cycle 23 and the beginning of Solar
@@
 and temporal correspondence between HXR and white-light flares on the Sun
-\citep{fletcher07, krucker11, kleint16}. \textcolor{red}{In particular, \cite{namekata17}
+\citep{fletcher07, krucker11, kleint16}. In particular, \cite{namekata17}
 demonstrated the difference spatially resolved flares as observed with RHESSI HXR and the
@@
 some examples, the HMI white-light emission is seen to last longer than the HXR,
-indicating the white-light emission is related to non-thermal electrons.}
-
-\textcolor{red}{However, other examples of simultaneous HXR and white-light flare
+indicating the white-light emission is related to non-thermal electrons.
+
+However, other examples of simultaneous HXR and white-light flare
 observations in \citep{namekata17} show similar flare durations. Therefore, we take
 the HXR solar flares with energies between $25 - 50$~keV as likely representative
-of solar white-light flares, and are a comparable sample to our TESS sample.} First,
+of solar white-light flares, and are a comparable sample to our TESS sample. First,
 the total number of flares detected in the $25 - 50$~keV bandpass varied by 650~flares
@@
 \begin{sidewaysfigure*}[ht!]
-    \vspace{-10cm}
+    \vspace{10cm}
     \script{stellar_cycles.py}
@@
 
-\textcolor{red}{The results presented here are consistent with those presented in
+The results presented here are consistent with those presented in
 previous studies of magnetic activity cycles in young stars. \cite{olah16} analyzed
@@
 of the star. Once this process has occurred, the magnetic activity cycle becomes more
-well-behaved, as seen on the Sun.}
-
-\textcolor{red}{We apply the relationship between $log(1/P_\textrm{rot})$ and 
+well-behaved, as seen on the Sun.
+
+We apply the relationship between $log(1/P_\textrm{rot})$ and
 $log(P_\textrm{cyc}/P_\textrm{rot})$ described in \cite{olah16} to estimate the
@@
 southern ecliptic poles continuously for two years, instead of alternating poles,
-may help resolve these shorter activity cycles, if present.}
+may help resolve these shorter activity cycles, if present.
 
@@
         \caption{
-            Comparison of flare rates from young planet host stars with respect to a comparable sample with respect to age [Myr] and $T_\textrm{eff}$ [K].
-Circles represent the flare rate of the host star (name along the x-axis); vertical bars represent the lower 16\textsuperscript{th} and upper 84\textsuperscript{th} percentiles for the comparable sample.
-The majority of young planet host stars have comparable flare rates to the lower end of the comparison sample.
-A handful of hosts have more flares, including HIP 67522, AU Mic, DS Tuc A, and TOI 451.
-We find no correlation with spectral type or age which may indicate why these host stars are relatively flare quiet.
-The measured flare rates are presented in
+            Comparison of flare rates from young planet host stars with respect
+            to a comparable sample with respect to age [Myr] and $T_\textrm{eff}$
+            [K]. Circles represent the flare rate of the host star (name along the x-axis);
+            vertical bars represent the lower 16\textsuperscript{th} and upper
+            84\textsuperscript{th} percentiles for the comparable sample. The
+            majority of young planet host stars have comparable flare rates to
+            the lower end of the comparison sample. A handful of hosts have more
+            flares, including HIP 67522, AU Mic, DS Tuc A, and TOI 451. We find no
+            correlation with spectral type or age which may indicate why these host
+            stars are relatively flare quiet. The measured flare rates are presented in
             Table~\ref{tab:yp_rates}.
@@
 
-We thank David Wilson for thoughtful conversations. \textcolor{red}{We thank the anonymous reviewer for their insightful report,
-which improved the clarity and quality of this manuscript.} This work made use of the open-source package,
+We thank David Wilson for thoughtful conversations. We thank the anonymous reviewer for their insightful report,
+which improved the clarity and quality of this manuscript. This work made use of the open-source package,
 \textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes reproducible publications. ADF acknowledges funding from
